### 2018-11-30 paper/main.tex
Paper empezado

% !TeX spellcheck = en_UK
\documentclass[10pt, a4paper, titlepage]{article}

\input{preambulo.tex}

\setlength{\columnsep}{0.7cm}

\begin{document}
	\fontfamily{lmr}\selectfont

	\begin{multicols}{2}

	\section{Experiments}
	\subsection{Data}
	We make use of two ordinal datasets appropriate for deep neural networks:

	\begin{itemize}
		\item \textit{Diabetic Retinopathy}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}. This is a dataset consisting of extremely high-resolution fundus image data. The training set consists of $17563$ pairs of images (where a  pair  consists of a left and right eye image corresponding to a patient). In this dataset, we try and predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images). The images are taken in variable conditions: by different cameras, illumination conditions and resolutions. These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform. Also, this dataset was used in later works \cite{de2018weighted} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve a better performance. A validation set is set aside, consisting of $10\%$ of the patients in the training set. The images are resized to 256 by 256 pixels. Data augmentation techniques are applied in order to achieve a higher number of samples.

		\item \textit{Adience}\footnote{http://www.openu.ac.il/home/hassner/Adience/data.html}. This dataset consists of $26580$ faces belonging to $2284$ subjects. We use the form of the dataset where faces have been pre-cropped and aligned. The dataset was preprocessed, using the methods described in a previous work \cite{beckham2017unimodal}, so that the images are 256px in width and height and pixels values follow a $(0;1)$ normal distribution. The original dataset is splitted in 5 cross-validation folds. The training set consists of merging the first four folds together which comprises a total of $15554$ images. From this, $10\%$ of the images are held out as part of a validation set. The last fold is used as test set.
	\end{itemize}

	\subsection{The model}
	A convolutional neural network (CNN) has been used for both datasets. The architecture of this CNN is presented in the Table \ref{table:CNNArquitecture}.

	\begin{table}[H]
		\centering
		\begin{tabular}{|l|c|}
			\hline
			Layer & Output shape\\
			\hline
			Conv\_32\_3x3 & 254x254x32\\\hline
			Conv\_32\_3x3 & 252x252x32\\\hline
			MaxPool\_2x2 & 126x126x32\\\hline

			Conv\_64\_3x3 & 124x124x64\\\hline
			Conv\_64\_3x3 & 122x122x64\\\hline
			MaxPool\_2x2 & 61x61x64\\\hline

			Conv\_128\_3x3 & 59x59x128\\\hline
			Conv\_128\_3x3 & 57x57x128\\\hline
			MaxPool\_2x2 & 28x28x128\\\hline

			Conv\_128\_3x3 & 26x26x128\\\hline
			Conv\_128\_3x3 & 24x24x128\\\hline
			MaxPool\_2x2 & 12x12x128\\\hline

			Conv\_128\_4x4 & 9x9x128\\\hline
			Dense\_1\_output & 1\\
			\hline
		\end{tabular}
		\caption{Description of the architecture used in the experiments. For convolutional layers, Conv\_N\_WxH, where N is the number of filters, W the filter width and H the filter height. Stride is 1 for every convolutional layer. For max pool layers, MaxPool\_SxS, where S is the pool size.}
		\label{table:CNNArquitecture}
	\end{table}

	Every convolutional layer is followed by an ELU activation layer \cite{clevert2015fast} and a batch normalization \cite{ioffe2015batch}. At the output, a Proportional Odds Model is used with different link functions (logit, probit, complementary log-log).

	\printbibliography

	\end{multicols}
\end{document}

### 2018-11-30 experiment.py

@@ -312,7 +312,7 @@ class Experiment():
 		)
 
 		# Calculate the number of steps per epoch
-		steps = (len(ds_train.y) * 3) // self.batch_size
+		steps = (len(ds_train.y) * 1) // self.batch_size
 
 		# Get class weights based on frequency
 		class_weight = ds_train.get_class_weights()

### 2018-12-04 experiment.py
Corregido error en test

@@ -7,11 +7,13 @@ import glob
 import time
 import click
 import pickle
+import h5py
 from scipy import io as spio
 from callbacks import MomentumScheduler, ComputeMetricsCallback
 from losses import qwk_loss, make_cost_matrix
-from metrics import np_quadratic_weighted_kappa
+from metrics import np_quadratic_weighted_kappa, quadratic_weighted_kappa_cm
 from dataset import Dataset
+from sklearn.metrics import confusion_matrix
 
 
 class Experiment():
@@ -21,7 +23,7 @@ class Experiment():
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
 				 checkpoint_dir='checkpoint', loss='crossentropy', activation='relu', final_activation='softmax',
 				 prob_layer=None,
-				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0):
+				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, only_eval=False):
 		self._name = name
 		self._db = db
 		self._net_type = net_type
@@ -36,6 +38,7 @@ class Experiment():
 		self._lr = lr
 		self._momentum = momentum
 		self._dropout = dropout
+		self._only_eval = only_eval
 		self._finished = False
 
 		self._best_qwk = -1
@@ -230,6 +233,18 @@ class Experiment():
 		del self._dropout
 
 	@property
+	def only_eval(self):
+		return self._only_eval
+
+	@only_eval.setter
+	def only_eval(self, only_eval):
+		self._only_eval = only_eval
+
+	@only_eval.deleter
+	def only_eval(self):
+		del self._only_eval
+
+	@property
 	def finished(self):
 		return self._finished
 
@@ -344,6 +359,8 @@ class Experiment():
 			model = net_object.vgg19()
 		elif self.net_type == 'conv128':
 			model = net_object.conv128()
+		elif self.net_type == 'testing':
+			model = net_object.testing()
 		else:
 			raise Exception('Invalid net type. You must select one of these: vgg19, conv128')
 
@@ -352,8 +369,8 @@ class Experiment():
 			os.makedirs(self.checkpoint_dir)
 
 		# Model and results file names
-		model_file = 'model.hdf5'
-		best_model_file = 'best_model.hdf5'
+		model_file = 'model.h5'
+		best_model_file = 'best_model.h5'
[…]

### 2018-12-04 experimentset.py

@@ -115,7 +115,7 @@ class ExperimentSet():
 		for experiment in self.experiments:
 				os.environ["CUDA_VISIBLE_DEVICES"] = str(gpu_number)
 				with tf.device('/device:GPU:' + str(gpu_number)):
-					if not experiment.finished:
+					if not experiment.finished and not experiment.only_eval:
 						experiment.run()
 					print(experiment.evaluate())
 					# Clear session

### 2018-12-04 metrics.py

@@ -140,6 +140,7 @@ def np_quadratic_weighted_kappa(rater_a, rater_b, min_rating=None, max_rating=No
 		max_rating = max(max(rater_a), max(rater_b))
 	conf_mat = confusion_matrix(rater_a, rater_b,
 								min_rating, max_rating)
+
 	num_ratings = len(conf_mat)
 	num_scored_items = float(len(rater_a))
 

### 2018-12-04 net_keras.py

@@ -183,6 +183,38 @@ class Net:
 
 		return model
 
+	def testing(self):
+		model = tf.keras.Sequential([
+			tf.keras.layers.Conv2D(32, 3, strides=(1, 1),
+								   kernel_initializer='he_uniform', input_shape=(self.size, self.size, self.num_channels),
+								   data_format='channels_last'),
+			self.__get_activation(),
+			tf.keras.layers.BatchNormalization(),
+			tf.keras.layers.MaxPooling2D(pool_size=8),
+
+			tf.keras.layers.Flatten(),
+		])
+
+		if self.dropout > 0:
+			model.add(tf.keras.layers.Dropout(rate=self.dropout))
+
+		if self.final_activation == 'poml':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'logit'))
+		elif self.final_activation == 'pomp':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'probit'))
+		elif self.final_activation == 'pomclog':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'cloglog'))
+		else:
+			model.add(tf.keras.layers.Dense(self.num_classes))
+			if self.prob_layer == 'geometric':
+				model.add(GeometricLayer())
+			model.add(tf.keras.layers.Activation(self.final_activation))
+
+		return model
+
 	def __get_activation(self):
 		if self.activation == 'relu':
 			return tf.keras.layers.Activation('relu')

### 2018-12-04 experiment.py
Cambiado parámetro only_eval a task

@@ -23,7 +23,7 @@ class Experiment():
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
 				 checkpoint_dir='checkpoint', loss='crossentropy', activation='relu', final_activation='softmax',
 				 prob_layer=None,
-				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, only_eval=False):
+				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both'):
 		self._name = name
 		self._db = db
 		self._net_type = net_type
@@ -38,7 +38,7 @@ class Experiment():
 		self._lr = lr
 		self._momentum = momentum
 		self._dropout = dropout
-		self._only_eval = only_eval
+		self._task = task
 		self._finished = False
 
 		self._best_qwk = -1
@@ -233,16 +233,16 @@ class Experiment():
 		del self._dropout
 
 	@property
-	def only_eval(self):
-		return self._only_eval
+	def task(self):
+		return self._task
 
-	@only_eval.setter
-	def only_eval(self, only_eval):
-		self._only_eval = only_eval
+	@task.setter
+	def task(self, task):
+		self._task = task
 
-	@only_eval.deleter
-	def only_eval(self):
-		del self._only_eval
+	@task.deleter
+	def task(self):
+		del self._task
 
 	@property
 	def finished(self):
@@ -577,7 +577,7 @@ class Experiment():
 			'lr': self.lr,
 			'momentum': self.momentum,
 			'dropout': self.dropout,
-			'only_eval': self.only_eval
+			'task': self.task
 		}
 
 	def set_config(self, config):
@@ -599,7 +599,7 @@ class Experiment():
 		self.lr = 'lr' in config and config['lr'] or 0.1
 		self.momentum = 'momentum' in config and config['momentum'] or 0
 		self.dropout = 'dropout' in config and config['dropout'] or 0
-		self.only_eval = 'only_eval' in config and config['only_eval'] or False
+		self.task = 'task' in config and config['task'] or 'both'
 
 		if 'name' in config:
 			self.name = config['name']

### 2018-12-04 experimentset.py

@@ -115,8 +115,9 @@ class ExperimentSet():
 		for experiment in self.experiments:
 				os.environ["CUDA_VISIBLE_DEVICES"] = str(gpu_number)
 				with tf.device('/device:GPU:' + str(gpu_number)):
-					if not experiment.finished and not experiment.only_eval:
+					if not experiment.finished and experiment.task != 'test': # 'train' or 'both'
 						experiment.run()
-					print(experiment.evaluate())
+					if experiment.task != 'train': # 'test' or 'both'
+						print(experiment.evaluate())
 					# Clear session
 					tf.keras.backend.clear_session()

### 2018-12-05 paper/main.tex
Paper + cambiado predict a predict generator

@@
 
+	\section{Introduction}
+	...
+
+	\section{Related work}
+	\begin{itemize}
+		\item Cyclical learning rates for training neural networks \cite{smith2017cyclical}.
+		\item An empirical study of learning rates in deep neural networks for speech recognition \cite{senior2013empirical}.
+	\end{itemize}
+
 	\section{Experiments}
@@
 	\begin{itemize}
-		\item \textit{Diabetic Retinopathy}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}.
-This is a dataset consisting of extremely high-resolution fundus image data.
+		\item \textit{Diabetic Retinopathy (DR)}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}.
+DR is a dataset consisting of extremely high-resolution fundus image data.
 The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient).
@@
 These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform.
-Also, this dataset was used in later works \cite{de2018weighted} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve a better performance.
+Also, this dataset was used in later works \cite{de2018weighted} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
 The images are resized to 256 by 256 pixels.
-Data augmentation techniques are applied in order to achieve a higher number of samples.
+Data augmentation techniques are applied to achieve a higher number of samples.
 
@@
 We use the form of the dataset where faces have been pre-cropped and aligned.
-The dataset was preprocessed, using the methods described in a previous work \cite{beckham2017unimodal}, so that the images are 256px in width and height and pixels values follow a $(0;1)$ normal distribution.
-The original dataset is splitted in 5 cross-validation folds.
-The training set consists of merging the first four folds together which comprises a total of $15554$ images.
+The dataset was preprocessed, using the methods described in a previous work \cite{beckham2017unimodal}, so that the images are 256px in width and height, and pixels values follow a $(0;1)$ normal distribution.
+The original dataset is split into five cross-validation folds.
+The training set consists of merging the first four folds which comprise a total of $15554$ images.
 From this, $10\%$ of the images are held out as part of a validation set.
@@
 	\subsection{The model}
-	A convolutional neural network (CNN) has been used for both datasets. The architecture of this CNN is presented in the Table \ref{table:CNNArquitecture}.
+	A convolutional neural network (CNN) has been used for both datasets. The architecture of this CNN is presented in the Table \ref{table:CNNArchitecture}.
 
@@
 For max pool layers, MaxPool\_SxS, where S is the pool size.}
-		\label{table:CNNArquitecture}
+		\label{table:CNNArchitecture}
 	\end{table}
@@
 	Every convolutional layer is followed by an ELU activation layer \cite{clevert2015fast} and a batch normalization \cite{ioffe2015batch}.
-At the output, a Proportional Odds Model is used with different link functions (logit, probit, complementary log-log).
+At the output, a Proportional Odds Model (POM) is used with different link functions \cite{agresti2010analysis}.
+The logit link function is commonly used within POM.
+In this paper, we are comparing other link functions like probit or complementary log-log with the logit link.
+These three types of links are explained below.
+
+	\begin{itemize}
+		\item \textit{Logit}.
+Logit link function is the most widely used function for Proportional Odds Models.
+These kind of models are also called Cummulative Logit Models.
+The logit link is shown in Equation \ref{eq:logit}.
+		\begin{equation}
+		\small
+		logit[P(Y_i \le j)] = \alpha_j + \beta'x_i,\quad j = 1, ..., c - 1
+		\label{eq:logit}
+		\end{equation}
+		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in Equation \ref{eq:probit}.	
+		\begin{equation}
+		\small
+		\Phi^-1[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
+		\label{eq:probit}
+		\end{equation}
+		\item \textit{Complementary log-log}.
+Unlike logit and probit, complementary log-log function is not symmetric.
+With a continuous predictor $x$, for example, $P(Y \le j)$ approaches 0 at a different rate than it approaches 1.
+Complementary log-log expression is shown in Equation \ref{eq:cloglog}.
+		\begin{equation}
+		\footnotesize
+		log[-log[1 - P(Y \le j)]] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
+		\label{eq:cloglog}
+		\end{equation}
+	\end{itemize}
+
+	\subsection{Procedure}
+	The model is optimized using a batch based first-order optimization algorithm called Adam \cite{kingma2014adam}.
+We study different initial learning rates in order to find the optimal one for each problem.
+We apply an exponential decay across training epochs to the initial learning rate.
+
+	Quadratic Weighted Kappa Loss, that J. de la Torre described in previous work, is considered as loss function for this optimizer as it gives better performance for ordinal classification problems.
+
+	Both datasets have been artificially equalised using data augmentation techniques \cite{van2001art}\cite{krizhevsky2012imagenet} based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
+In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch.
+For the Adience dataset, epoch size is the number of images in the training set.
+
+	The model is evaluated with Quadratic Weighted Kappa metric \cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
+
+	\subsection{Parameters}
+	Three different parameters have been considered: learning rate, batch size and link function for the final output layer.
+
+	\begin{itemize}
+		\item \textit{Learning rate}.
+Learning rate is one of the most critical hyper-parameters to tune for training deep neural networks.
+Optimal learning rate can vary depending on the dataset and the CNN architecture.
+Within this work, we have considered three different values for this parameter: $10^-2$, $10^-3$ and $10^-4$.
+		\item \textit{Batch size}.
+Batch size is also an important parameter as it controls the number of weight updates that are made on every epoch.
+It can affect the training time and the model performance.
+In this paper, we have tried three separate batch sizes: $5$, $10$ and $15$.
+		\item \textit{Link function}. Different link functions have been used for the POM at the last layer output: logit, probit and complementary log-log.
+	\end{itemize}
+
+	\section{Results}
+	In this section, we present the results of the experiments. For each dataset, we show a table with the detailed experiments done training the model with each combination of parameters.
+
+	\subsection{Diabetic Retinopathy}
+	... \ref{table:DRresults}
+
+	\begin{table}[H]
+		\footnotesize
+		\centering
+		\begin{tabular}{ccc|cc}
+			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
+			$5$ & $10^{-02}$ & poml & $0.44888$ & $0.5009$\\
+			$5$ & $10^{-02}$ & pomp & $0.46724$ & $0.49614$\\
+			$5$ & $10^{-02}$ & cloglog & $0.42854$ & $0.50006$\\
+			$5$ & $10^{-03}$ & poml & $0.56496$ & $0.5198$\\
+			$5$ & $10^{-03}$ & pomp & $0.57084$ & $0.51114$\\
+			$5$ & $10^{-03}$ & cloglog & $0.54796$ & $0.50808$\\
+			$5$ & $10^{-04}$ & poml & $0.52884$ & $0.57954$\\
+			$5$ & $10^{-04}$ & pomp & $0.53802$ & $0.5772$\\
+			$5$ & $10^{-04}$ & cloglog & $0.53824$ & $0.57636$\\
+			$10$ & $10^{-02}$ & poml & $0.5497$ & $0.48474$\\
+			$10$ & $10^{-02}$ & pomp & $0.52124$ & $0.5092$\\
+			$10$ & $10^{-02}$ & cloglog & $0.4276$ & $0.52524$\\
+			$10$ & $10^{-03}$ & poml & $0.58036$ & $0.54692$\\
+			$10$ & $10^{-03}$ & pomp & $0.56536$ & $0.52716$\\
+			$10$ & $10^{-03}$ & cloglog & $0.5883$ & $0.53076$\\
+			$10$ & $10^{-04}$ & poml & $0.53158$ & $0.59238$\\
+			$10$ & $10^{-04}$ & pomp & $0.5456$ & $0.59372$\\
+			$10$ & $10^{-04}$ & cloglog & $0.53928$ & $0.59242$\\
+			$15$ & $10^{-02}$ & poml & $0.55828$ & $0.50664$\\
+			$15$ & $10^{-02}$ & pomp & $0.54112$ & $0.50426$\\
+			$15$ & $10^{-02}$ & cloglog & $0.56676$ & $0.4991$\\
+			$15$ & $10^{-03}$ & poml & $0.55748$ & $0.57388$\\
+			$15$ & $10^{-03}$ & pomp & $0.58182$ & $0.5573$\\
+			$15$ & $10^{-03}$ & cloglog & $0.5634$ & $0.55906$\\
+			$15$ & $10^{-04}$ & poml & $0.54686$ & $0.5994$\\
+			$15$ & $10^{-04}$ & pomp & $0.53258$ & $0.60264$\\
+			$15$ & $10^{-04}$ & cloglog & $0.539$ & $0.6005$
+		\end{tabular}
+		\caption{Diabetic Retinopathy results.}
+		\label{table:DRresults}
+	\end{table}
+
+	\subsection{Adience}
+	...
 

### 2018-12-05 experiment.py

@@ -323,7 +323,8 @@ class Experiment():
 		val_generator = val_datagen.flow(
 			ds_val.x,
 			ds_val.y,
-			batch_size=self.batch_size
+			batch_size=self.batch_size,
+			shuffle=False
 		)
 
 		# Calculate the number of steps per epoch
@@ -469,7 +470,8 @@ class Experiment():
 		test_generator = test_datagen.flow(
 			ds_test.x,
 			ds_test.y,
-			batch_size=self.batch_size
+			batch_size=self.batch_size,
+			shuffle=False
 		)
 
 		# NNet object
@@ -518,11 +520,13 @@ class Experiment():
 		)
 
 		# Get predictions
-		predictions = model.predict(
-			ds_test.x / 255.0
+		# predictions = model.predict(
+		#	ds_test.x / 255.0
+		# )
+		test_generator.reset()
+		predictions = model.predict_generator(
+			test_generator
 		)
-
-
 
 		# conf_mat = confusion_matrix(np.argmax(ds_test.y, axis=1), np.argmax(predictions, axis=1), labels=range(0, num_classes))
 
@@ -536,7 +540,6 @@ class Experiment():
 		# print(qwk)
 
 		# Calculate QWK
-		print(np.bincount(np.argmax(ds_test.y, axis=1)))
 		qwk = np_quadratic_weighted_kappa(np.argmax(ds_test.y, axis=1), np.argmax(predictions, axis=1), 0, num_classes-1)
 
 		with open(os.path.join(self.checkpoint_dir, evaluation_file), 'w') as f:

### 2018-12-10 paper/main.tex
Añadido IRNV2

@@
 	\section{Related work}
-	\begin{itemize}
-		\item Cyclical learning rates for training neural networks \cite{smith2017cyclical}.
-		\item An empirical study of learning rates in deep neural networks for speech recognition \cite{senior2013empirical}.
-	\end{itemize}
+	...
 
@@
 			\hline
-			Layer & Output shape\\
+			\textbf{Layer} & \textbf{Output shape}\\
 			\hline
@@
 These kind of models are also called Cummulative Logit Models.
-The logit link is shown in Equation \ref{eq:logit}.
+The logit link is shown in Eq.
+\ref{eq:logit}.
 		\begin{equation}
@@
 		\end{equation}
-		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in Equation \ref{eq:probit}.	
+		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in Eq. \ref{eq:probit}.	
 		\begin{equation}
@@
 With a continuous predictor $x$, for example, $P(Y \le j)$ approaches 0 at a different rate than it approaches 1.
-Complementary log-log expression is shown in Equation \ref{eq:cloglog}.
+Complementary log-log expression is shown in Eq.
+\ref{eq:cloglog}.
 		\begin{equation}
@@
 
-	The model is evaluated with Quadratic Weighted Kappa metric \cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
+	The model is evaluated with Quadratic Weighted Kappa metric (QWK) \cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
 
@@
 Optimal learning rate can vary depending on the dataset and the CNN architecture.
-Within this work, we have considered three different values for this parameter: $10^-2$, $10^-3$ and $10^-4$.
+Previous works have presented some techniques that adjust this parameter in order to achieve better performance \cite{smith2017cyclical}\cite{senior2013empirical}.
+Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
 		\item \textit{Batch size}.
@@
 	\section{Results}
-	In this section, we present the results of the experiments. For each dataset, we show a table with the detailed experiments done training the model with each combination of parameters.
+	In this section, we present the results of the experiments.
+For each dataset, we show a table with the detailed experiments done training the model with each combination of parameters.
+Every parameter combination has been run five times.
+These tables show the average quadratic weighted kappa across these five executions for validation and test values.
 
 	\subsection{Diabetic Retinopathy}
-	... \ref{table:DRresults}
+	Detailed results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}.
 
@@
 		\begin{tabular}{ccc|cc}
-			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
-			$5$ & $10^{-02}$ & poml & $0.44888$ & $0.5009$\\
-			$5$ & $10^{-02}$ & pomp & $0.46724$ & $0.49614$\\
-			$5$ & $10^{-02}$ & cloglog & $0.42854$ & $0.50006$\\
-			$5$ & $10^{-03}$ & poml & $0.56496$ & $0.5198$\\
-			$5$ & $10^{-03}$ & pomp & $0.57084$ & $0.51114$\\
-			$5$ & $10^{-03}$ & cloglog & $0.54796$ & $0.50808$\\
-			$5$ & $10^{-04}$ & poml & $0.52884$ & $0.57954$\\
-			$5$ & $10^{-04}$ & pomp & $0.53802$ & $0.5772$\\
-			$5$ & $10^{-04}$ & cloglog & $0.53824$ & $0.57636$\\
-			$10$ & $10^{-02}$ & poml & $0.5497$ & $0.48474$\\
-			$10$ & $10^{-02}$ & pomp & $0.52124$ & $0.5092$\\
-			$10$ & $10^{-02}$ & cloglog & $0.4276$ & $0.52524$\\
-			$10$ & $10^{-03}$ & poml & $0.58036$ & $0.54692$\\
-			$10$ & $10^{-03}$ & pomp & $0.56536$ & $0.52716$\\
-			$10$ & $10^{-03}$ & cloglog & $0.5883$ & $0.53076$\\
-			$10$ & $10^{-04}$ & poml & $0.53158$ & $0.59238$\\
-			$10$ & $10^{-04}$ & pomp & $0.5456$ & $0.59372$\\
-			$10$ & $10^{-04}$ & cloglog & $0.53928$ & $0.59242$\\
-			$15$ & $10^{-02}$ & poml & $0.55828$ & $0.50664$\\
-			$15$ & $10^{-02}$ & pomp & $0.54112$ & $0.50426$\\
-			$15$ & $10^{-02}$ & cloglog & $0.56676$ & $0.4991$\\
-			$15$ & $10^{-03}$ & poml & $0.55748$ & $0.57388$\\
-			$15$ & $10^{-03}$ & pomp & $0.58182$ & $0.5573$\\
-			$15$ & $10^{-03}$ & cloglog & $0.5634$ & $0.55906$\\
-			$15$ & $10^{-04}$ & poml & $0.54686$ & $0.5994$\\
-			$15$ & $10^{-04}$ & pomp & $0.53258$ & $0.60264$\\
-			$15$ & $10^{-04}$ & cloglog & $0.539$ & $0.6005$
+			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
+			$5$ & $10^{-2}$ & Logit & $0.44888$ & $0.4163$\\
+			& & Probit & $0.46724$ & $0.45972$\\
+			& & c log-log & $0.42854$ & $0.41448$\\
+			& $10^{-3}$ & Logit & $0.56496$ & $0.55356$\\
+			& & Probit & $0.57084$ & $0.56392$\\
+			& & c log-log & $0.54796$ & $0.53436$\\
+			& $10^{-4}$ & Logit & $0.52884$ & $0.52032$\\
+			& & Probit & $0.53802$ & $0.52302$\\
+			& & c log-log & $0.53824$ & $0.51974$\\
+			$10$ & $10^{-2}$ & Logit & $0.5497$ & $0.53142$\\
+			& & Probit & $0.52124$ & $0.50806$\\
+			& & c log-log & $0.4276$ & $0.4227$\\
+			& $10^{-3}$ & Logit & $0.58036$ & $0.57686$\\
+			& & Probit & $0.56536$ & $0.5581$\\
+			& & c log-log & $\textbf{0.5883}$ & $\textbf{0.5815}$\\
+			& $10^{-4}$ & Logit & $0.53158$ & $0.5385$\\
+			& & Probit & $0.5456$ & $0.54082$\\
+			& & c log-log & $0.53928$ & $0.53742$\\
+			$15$ & $10^{-2}$ & Logit & $0.55828$ & $0.55076$\\
+			& & Probit & $0.54112$ & $0.5343$\\
+			& & c log-log & $0.56676$ & $0.56428$\\
+			& $10^{-3}$ & Logit & $0.55748$ & $0.55106$\\
+			& & Probit & $0.58182$ & $0.57894$\\
+			& & c log-log & $0.5634$ & $0.55938$\\
+			& $10^{-4}$ & Logit & $0.54686$ & $0.54342$\\
+			& & Probit & $0.53258$ & $0.53278$\\
+			& & c log-log & $0.539$ & $0.53828$
 		\end{tabular}
-		\caption{Diabetic Retinopathy results.}
+		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
 		\label{table:DRresults}
@@
 
+	\begin{table}[H]
+		\footnotesize
+		\centering
+		\begin{tabular}{ccc|cc}
+			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
+			$5$ & $10^{-2}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			& $10^{-3}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			& $10^{-4}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			$10$ & $10^{-2}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			& $10^{-3}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			& $10^{-4}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			$15$ & $10^{-2}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			& $10^{-3}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$\\
+			& $10^{-4}$ & Logit & $-$ & $-$\\
+			& & Probit & $-$ & $-$\\
+			& & c log-log & $-$ & $-$
+		\end{tabular}
+		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\label{table:Adienceresults}
+	\end{table}
+
+	\subsection{Statistical analysis}
+	The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each, were obtained using ANalysis Of the VAriance (ANOVA)
+
+	The ANalysis Of the VAriance (ANOVA) \cite{miller1997beyond} is one of the most widely used statistical techniques.
+ANOVA is essentially a method of analysing the variance to which a response is subject into its various components, corresponding to the sources of variation which can be identified.
+
+	ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
+Considered factors are the link function, which can be logit, probit and complementary log-log, the learning rate for the Adam optimisation algorithm ($10^{-2}$, $10^{-3}$ and $10^{-4}$) and the batch size (5, 10 and 15).
+
+	Following the setup of the previous study, we performed an ANOVA III analysis and multiple comparison tests.
+The tests show that there is no batch size whose results are significatively better than the results of all other batch sizes.
+This does not mean that these differences could not exist for specific numbers of samples per batch.
+So, in order to determine for each type of function whether a batch size is better than the others, we have performed an ANOVA I analysis - where the only factor is the batch size - and multiple comparison tests.
+
+	We denote by $W_{i,j,k}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
+We assume that the two factors do not act independently and therefore there exists an interaction between them.
+In this case, the observations fit Eq.
+\ref{eq:anova3}.
+
+	\begin{equation}
+	\begin{aligned}
+	\footnotesize
+	W_{i,j,k} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k}
+	\label{eq:anova3}
+	\end{aligned}
+	\end{equation}
+
+	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (logit, probit, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the parameter factor ($10^{-4}$, $10^{-3}$, $10^{-2}$) and $B_k$ is the effect associated with the \textit{k-th} level of the size batch factor (5, 10, 15).
+The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors.
+The same interaction effect is appreciated on $LB_{i,k}$, $PB_{j,k}$ and $LPB_{i,j,k}$.
+The term $\epsilon_{i,j,k}$ is the influence on the result of everything that could not be assigned or of random factors.
+$W_{i,j,k}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
+
 	\printbibliography

### 2018-12-10 experiment.py

@@ -356,14 +356,7 @@ class Experiment():
 						 self.spp_alpha,
 						 self.dropout)
 
-		if self.net_type == 'vgg19':
-			model = net_object.vgg19()
-		elif self.net_type == 'conv128':
-			model = net_object.conv128()
-		elif self.net_type == 'testing':
-			model = net_object.testing()
-		else:
-			raise Exception('Invalid net type. You must select one of these: vgg19, conv128')
+		model = self.get_model(net_object, self.net_type)
 
 		# Create checkpoint dir if not exists
 		if not os.path.isdir(self.checkpoint_dir):
@@ -479,14 +472,7 @@ class Experiment():
 						 self.spp_alpha,
 						 self.dropout)
 
-		if self.net_type == 'vgg19':
-			model = net_object.vgg19()
-		elif self.net_type == 'conv128':
-			model = net_object.conv128()
-		elif self.net_type == 'testing':
-			model = net_object.testing()
-		else:
-			raise Exception('Invalid net type. You must select one of these: vgg19, conv128')
+		model = self.get_model(net_object, self.net_type)
 
 		best_model_file = 'best_model.h5'
 
@@ -546,6 +532,20 @@ class Experiment():
 			f.write(str(qwk))
 
 		return qwk
+
+	def get_model(self, net_object, name):
+		if name == 'vgg19':
+			model = net_object.vgg19()
+		elif name == 'conv128':
+			model = net_object.conv128()
+		elif name == 'testing':
+			model = net_object.testing()
+		elif name == 'inceptionresnetv2':
+			model = net_object.InceptionResNetV2()
+		else:
+			raise Exception('Invalid net type. You must select one of these: vgg19, conv128')
+
+		return model
 
 	def get_db_path(self, db):
 		"""

### 2018-12-10 net_keras.py

@@ -183,6 +183,33 @@ class Net:
 
 		return model
 
+	def InceptionResNetV2(self):
+		model = tf.keras.Sequential()
+		inception = tf.keras.applications.inception_resnet_v2.InceptionResNetV2(include_top=False, input_shape=(self.size, self.size, self.num_channels), classes=self.num_classes)
+
+		model.add(inception)
+		model.add(tf.keras.layers.Flatten())
+
+		if self.dropout > 0:
+			model.add(tf.keras.layers.Dropout(rate=self.dropout))
+
+		if self.final_activation == 'poml':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'logit'))
+		elif self.final_activation == 'pomp':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'probit'))
+		elif self.final_activation == 'pomclog':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'cloglog'))
+		else:
+			model.add(tf.keras.layers.Dense(self.num_classes))
+			if self.prob_layer == 'geometric':
+				model.add(GeometricLayer())
+			model.add(tf.keras.layers.Activation(self.final_activation))
+
+		return model
+
 	def testing(self):
 		model = tf.keras.Sequential([
 			tf.keras.layers.Conv2D(32, 3, strides=(1, 1),

### 2018-12-11 paper/main.tex
Workers parameter. IRNV2 freeze conv layers

@@
 		\small
-		\Phi^-1[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
+		\Phi^{-1}[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
 		\label{eq:probit}
@@
 			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
-			$5$ & $10^{-2}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			& $10^{-3}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			& $10^{-4}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			$10$ & $10^{-2}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			& $10^{-3}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			& $10^{-4}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			$15$ & $10^{-2}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			& $10^{-3}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$\\
-			& $10^{-4}$ & Logit & $-$ & $-$\\
-			& & Probit & $-$ & $-$\\
-			& & c log-log & $-$ & $-$
+			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
+			& & Probit & $0.77608$ & $0.72574$\\
+			& & c log-log & $0.7543$ & $0.70742$\\
+			& $10^{-3}$ & Logit & $0.7146$ & $0.67868$\\
+			& & Probit & $0.81906$ & $0.77154$\\
+			& & c log-log & $0.57196$ & $0.55608$\\
+			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
+			& & Probit & $0.5436$ & $0.52422$\\
+			& & c log-log & $0.54802$ & $0.52484$\\
+			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
+			& & Probit & $0.79332$ & $0.7475$\\
+			& & c log-log & $0.78004$ & $0.7326$\\
+			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
+			& & Probit & $0.59778$ & $0.58476$\\
+			& & c log-log & $0.52016$ & $0.49968$\\
+			& $10^{-4}$ & Logit & $0.60972$ & $0.56814$\\
+			& & Probit & $0.54638$ & $0.52632$\\
+			& & c log-log & $0.75428$ & $0.52094$\\
+			$15$ & $10^{-2}$ & Logit & $0.79104$ & $0.74388$\\
+			& & Probit & $\textbf{0.84254}$ & $\textbf{0.78666}$\\
+			& & c log-log & $0.78802$ & $0.74624$\\
+			& $10^{-3}$ & Logit & $0.56946$ & $0.52978$\\
+			& & Probit & $0.70262$ & $0.65416$\\
+			& & c log-log & $0.49242$ & $0.4732$\\
+			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
+			& & Probit & $0.54288$ & $0.5174$\\
+			& & c log-log & $0.53826$ & $0.52542$
 		\end{tabular}

### 2018-12-11 experiment.py

@@ -23,7 +23,7 @@ class Experiment():
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
 				 checkpoint_dir='checkpoint', loss='crossentropy', activation='relu', final_activation='softmax',
 				 prob_layer=None,
-				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both'):
+				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both', workers=4):
 		self._name = name
 		self._db = db
 		self._net_type = net_type
@@ -40,6 +40,7 @@ class Experiment():
 		self._dropout = dropout
 		self._task = task
 		self._finished = False
+		self._workers = workers
 
 		self._best_qwk = -1
 
@@ -257,6 +258,18 @@ class Experiment():
 		del self._finished
 
 	@property
+	def workers(self):
+		return self._workers
+
+	@workers.setter
+	def workers(self, workers):
+		self._workers = workers
+
+	@workers.deleter
+	def workers(self):
+		del self._workers
+
+	@property
 	def best_qwk(self):
 		return self._best_qwk
 
@@ -423,9 +436,9 @@ class Experiment():
 																	append=True),
 									   tf.keras.callbacks.TensorBoard(log_dir=self.checkpoint_dir),
 									   ],
-							workers=4,
+							workers=self.workers,
 							use_multiprocessing=True,
-							max_queue_size=self.batch_size * 10,
+							max_queue_size=self.batch_size * 3,
 							class_weight=class_weight
 							)
 
@@ -580,7 +593,8 @@ class Experiment():
 			'lr': self.lr,
 			'momentum': self.momentum,
 			'dropout': self.dropout,
-			'task': self.task
+			'task': self.task,
+			'workers' : self.workers
 		}
 
 	def set_config(self, config):
@@ -603,6 +617,7 @@ class Experiment():
 		self.momentum = 'momentum' in config and config['momentum'] or 0
 		self.dropout = 'dropout' in config and config['dropout'] or 0
 		self.task = 'task' in config and config['task'] or 'both'
+		self.workers = 'workers' in config and config['workers'] or 4
 
 		if 'name' in config:
 			self.name = config['name']

### 2018-12-11 net_keras.py

@@ -1,6 +1,7 @@
 import tensorflow as tf
 from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, NNPOM
 from layers import GeometricLayer
+from resnet import inference
 
 
 class Net:
@@ -186,6 +187,9 @@ class Net:
 	def InceptionResNetV2(self):
 		model = tf.keras.Sequential()
 		inception = tf.keras.applications.inception_resnet_v2.InceptionResNetV2(include_top=False, input_shape=(self.size, self.size, self.num_channels), classes=self.num_classes)
+
+		for layer in inception.layers:
+			layer.trainable = False
 
 		model.add(inception)
 		model.add(tf.keras.layers.Flatten())

### 2018-12-13 paper/main.tex
New POM init

@@
 % !TeX spellcheck = en_UK
-\documentclass[10pt, a4paper, titlepage]{article}
+\documentclass[10pt, a4paper, titlepage, twocolumn]{article}
 
@@
 
-	\begin{multicols}{2}
+	%\begin{multicols}{2}
 
@@
 These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform.
-Also, this dataset was used in later works \cite{de2018weighted} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
+Also, this dataset was used in later works \cite{de2018weighted}\cite{nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
@@
 
-	\begin{table}[H]
+	\begin{table}[htbp]
 		\centering
@@
 
-	\begin{table}[H]
+	\begin{table}[htbp]
 		\footnotesize
@@
 	\subsection{Adience}
-	...
+	Results for the experiments made with the Adience dataset are shown in Table \ref{table:Adienceresults}.
 
-	\begin{table}[H]
+	\begin{table}[htbp]
 		\footnotesize
@@
 
-	We denote by $W_{i,j,k}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
+	We denote by $W_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
 We assume that the two factors do not act independently and therefore there exists an interaction between them.
@@
 	\footnotesize
-	W_{i,j,k} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k}
+	W_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l}
 	\label{eq:anova3}
@@
 The same interaction effect is appreciated on $LB_{i,k}$, $PB_{j,k}$ and $LPB_{i,j,k}$.
-The term $\epsilon_{i,j,k}$ is the influence on the result of everything that could not be assigned or of random factors.
-$W_{i,j,k}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
+The term $\epsilon_{i,j,k,l}$ is the influence on the result of everything that could not be assigned or of random factors.
+$W_{i,j,k,l}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
+
+	We consider some hypotheses testing where the null hypothesis is proposed that each term of the above equation is independent of the levels involved. The hypotheses for the levels the L factor are
+	\[
+		H_0 \equiv L_1 = L_2 = L_3
+	\]
+	\[
+		H_1 \equiv \text{ some } L_i \text{ is different}
+	\]
+
+	The same hypotheses are made for the other factors.
+In this way, we test in the null hypothesis that all of the population means are equal against an alternative hypothesis that there is at least one mean that is not equal to the others.
+
+	The hypothesis associated with the interaction between L and P is
+	\[
+		H_0 \equiv LP_{i,j} = 0 \quad \forall i,j
+	\]
+	\[
+		H_1 \equiv \exists LP_{i,j} \ne 0
+	\]
+
+	Similar hypotheses can be assumed for the interaction between the other factors.
+
+	The analysis of variance table containing the sum of squares, degrees of freedom, mean square, test statistics and significance level represents the initial study in a compact form.
+
+	\begin{table}[htbp]
+		\centering
+		\small
+		\begin{tabular}{l|ccccc}
+			\multicolumn{6}{c}{Response variable WK}\\\hline
+			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
+			Model & $37.860$ & $9$ & $4.207$ & $1562.840$ & $.000$\\
+			$L$ factor & $.057$ & $2$ & $.029$ & $10.646$ & $.000$\\
+			$P$ factor & $.121$ & $2$ & $.060$ & $22.468$ & $.000$\\
+			$LP$ factors & $.057$ & $4$ & $.014$ & $5.261$ & $.001$\\
+			Error & $.339$ & $126$ & $.003$ & & \\
+			Total & $38.199$ & $135$ & & & 
+		\end{tabular}
+		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
+		\label{table:ANOVARetinopathy}
+	\end{table}
+
+	The results of the ANOVA III test for the Diabetic Retinopathy dataset are resumed in Table \ref{table:ANOVARetinopathy}.
+There are significative differences in the means depending on the link function and also depending on the learning rate for $\alpha=0.05$.
+Moreover, an interaction between the link function and the learning rate can be recognised ($\text{p-value} = 0.001$).
+
+	As Table \ref{table:ANOVARetinopathy} showed that there exist significative differences between the means, we are now analysing those differences.
+A post-hoc multiple comparison test has been performed on the average WK obtained.
+An HSD Tukey's test was made under the null hypothesis that the variance of the error of the dependent variable is the same between groups.
+The best link function is the complementary log-log, though it doesn't have significative differences with the probit function ($\alpha=0.05$).
+There are differences between the complementary log-log and the probit function concerning the logit function.
+
+	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
+Significative differences can be observed in the mean values for $\eta = 10^{-3}$ with respect to the other values of the parameter ($\alpha=0.05$).
+Also, there are differences for $\eta = 10^{-4}$ concerning $\eta = 10^{-2}$.
+
+	\begin{table}[htbp]
+		\centering
+		\small
+		\begin{tabular}{l|ccccc}
+			\multicolumn{6}{c}{Response variable WK}\\\hline
+			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
+			Model & $52.328$ & $15$ & $3.489$ & $1426.170$ & $.000$\\
+			$L$ factor & $.027$ & $2$ & $.014$ & $5.582$ & $.005$\\
+			$P$ factor & $1.031$ & $2$ & $.516$ & $210.809$ & $.000$\\
+			$B$ factor & $.089$ & $2$ & $.045$ & $18.253$ & $.000$\\
+			$LP$ factors & $.183$ & $4$ & $.046$ & $18.695$ & $.000$\\
+			$PB$ factors & $.124$ & $4$ & $.031$ & $12.695$ & $.000$\\
+			Error & $.294$ & $120$ & $.002$ & & \\
+			Total & $52.622$ & $135$ & $3.489$ & & 
+		\end{tabular}
+		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
+		\label{table:ANOVAAdience}
+	\end{table}
+
+	The results of the ANOVA III test for the Adience dataset are shown in Table \ref{table:ANOVAAdience}.
+The interactions where there are not significative differences have been omitted.
+First, the factor associated with the link function is analysed.
+The differences between the means are significative ($\text{p-value} = 0.005$).
+Secondly, there are significative differences concerning the learning rate factor too ($\text{p-value} = 0.000$).
+Also, there are differences for the means for the batch size factor.
+Significative interactions exist between two pairs of factors: link function and learning rate, and learning rate and batch size ($\text{p-value = 0.000}$ for both cases).
+
+	A post-hoc multiple comparison test has been performed on the average WK obtained for this dataset too.
+Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been done.
+The results showed that the best link function is the logit one, in this case, with $0.632438$ as mean WK value.
+However, there are not significative differences between this function and the complementary log-log ($\text{p-value}=0.110$).
+It has differences with the probit function though ($\text{p-value} = 0.003$).
+The complementary log-log link reported the best results after the logit function, having a mean WK of $0.611287$.
+The complementary log-log function doesn't show significative differences with the probit function.
+	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
+The test reported significative differences between $\eta=10^{-2}$ (mean value $0.733784$) and the rest of values of this parameter ($\alpha=0.005$), being this one the best value for this factor.
+The best value after $10^{-2}$ is $10^{-3}$, which have a mean WK value of $0.579889$.
+Lastly, the best value for the batch size parameter is $10$ (mean value $0.648700$) as it has significative differences with the rest of values.
+The second best value is $5$ (mean $0.605533$), but it has no significative differences with $15$ ($\text{p-value}= 0.194$).
+
+	\section{Conclusions}
+	In this section, the conclusions obtained from this work are exposed. The first thing that we have noticed is that the optimal values for the different parameters considered are problem-dependant.
+
+	The complementary log-log function has the best average performance across both datasets.
+It offers the best results in Diabetic Retinopathy dataset and the second best result in Adience dataset.
+These results provide an opportunity for exploring new generalised link functions.
+
+	The best value for the learning rate parameter for  Diabetic Retinopathy dataset is $\eta = 10^{-3}$ while this value is the second best option for Adience dataset.
+It can be considered a good value for this parameter when training the model with new datasets.
+
+	Both datasets have obtained the best performance with batch size 10.
+
+	Also, the statistical tests reported that there are interactions between some parameters like the link function and the learning rate, for Diabetic Retinopathy, or those factors in addition to learning rate and batch size, for Adience dataset.
 
@@
 
-	\end{multicols}
+	%\end{multicols}
 \end{document}

### 2018-12-13 activations.py

@@ -1,4 +1,5 @@
 import tensorflow as tf
+import math
 
 
 class SPP(tf.keras.layers.Activation):
@@ -218,15 +219,13 @@ class NNPOM(tf.keras.layers.Layer):
 
 	def build(self, input_shape):
 		self.thresholds_b = self.add_weight('b_b_nnpom', shape=(1,),
-											initializer=tf.random_uniform_initializer(minval=-1, maxval=1))
+											initializer=tf.random_uniform_initializer(minval=0, maxval=0.1))
 		self.thresholds_a = self.add_weight('b_a_nnpom', shape=(self.num_classes - 2,),
-											initializer=tf.random_uniform_initializer(minval=-0.5, maxval=0.5))
-		self.thresholds_t = self.add_weight('t_nnpom', shape=(1,), initializer=tf.constant_initializer(1000.0),
-											dtype=tf.float32)
+											initializer=tf.random_uniform_initializer(minval=math.sqrt((1.0 / (self.num_classes - 2))/2), maxval=math.sqrt(1.0 / (self.num_classes - 2))))
 
 	def call(self, x):
 		thresholds = self._convert_thresholds(self.thresholds_b, self.thresholds_a)
-		return self._nnpom(x / self.thresholds_t, thresholds / self.thresholds_t)
+		return self._nnpom(x, thresholds)
 
 	def compute_output_shape(self, input_shape):
 		print(input_shape)

### 2018-12-13 experiment.py

@@ -348,7 +348,7 @@ class Experiment():
 
 		# Learning rate scheduler callback
 		def learning_rate_scheduler(epoch):
-			return self.lr * np.exp(-0.025 * epoch)
+			return self.lr * np.exp(-0.035 * epoch)
 
 		# Save epoch callback for training process
 		def save_epoch(epoch, logs):

### 2018-12-13 experimentset.py

@@ -113,11 +113,11 @@ class ExperimentSet():
 		:return: None
 		"""
 		for experiment in self.experiments:
-				os.environ["CUDA_VISIBLE_DEVICES"] = str(gpu_number)
-				with tf.device('/device:GPU:' + str(gpu_number)):
-					if not experiment.finished and experiment.task != 'test': # 'train' or 'both'
-						experiment.run()
-					if experiment.task != 'train': # 'test' or 'both'
-						print(experiment.evaluate())
-					# Clear session
-					tf.keras.backend.clear_session()
+			os.environ["CUDA_VISIBLE_DEVICES"] = str(gpu_number)
+			with tf.device('/device:GPU:' + str(gpu_number)):
+				if not experiment.finished and experiment.task != 'test': # 'train' or 'both'
+					experiment.run()
+				if experiment.task != 'train': # 'test' or 'both'
+					print(experiment.evaluate())
+				# Clear session
+				tf.keras.backend.clear_session()

### 2018-12-13 net_keras.py

@@ -169,12 +169,15 @@ class Net:
 
 		if self.final_activation == 'poml':
 			model.add(tf.keras.layers.Dense(1))
+			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'logit'))
 		elif self.final_activation == 'pomp':
 			model.add(tf.keras.layers.Dense(1))
+			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'probit'))
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
+			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'cloglog'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
@@ -188,8 +191,8 @@ class Net:
 		model = tf.keras.Sequential()
 		inception = tf.keras.applications.inception_resnet_v2.InceptionResNetV2(include_top=False, input_shape=(self.size, self.size, self.num_channels), classes=self.num_classes)
 
-		for layer in inception.layers:
-			layer.trainable = False
+		# for layer in inception.layers:
+		# 	layer.trainable = False
 
 		model.add(inception)
 		model.add(tf.keras.layers.Flatten())

### 2018-12-17 paper/main.tex
0.025 decay

@@
 
-	%\begin{multicols}{2}
+	\section{Introduction}
+	\label{sect:introduction}
+	Deep learning \cite{lecun2015deep} combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
+These methods have dramatically improved the state-of-the-art in many domains, such as image classification or speech recognition.
+Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to indicate how a machine should change its internal parameters that are used to compute the representation in each layer from the features in the previous layer.
 
-	\section{Introduction}
-	...
+	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
+The layer's parameters are updated after backpropagating the loss function gradients through the network.
+Deep convolutional nets are suited for images, video, speech and audio processing and they have been used extensively in the last years for automatic classification tasks.
+For the case of images, convolutional layers extract the main features from the pixels of the images and, after that, the fully connected layer classify every sample based on its extracted features.
+At the output of the convolutional net, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks.
+These outputs are compared against the correct values.
+
+	Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics}\cite{mehdiyev2016evaluating}.
+Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories.
+Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables.
+Weighted Kappa loss was described in previous work \cite{de2018weighted} and is a cost function that is based on the WK metric.
+These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk.
+This kind of problems is associated with ordinal data processing.
+Those weights are predefined and depend on the type of the chosen WK.
+In a linear penalisation, the weight is proportional to the distance between the predicted and the real class.
+In the Quadratic Weighted Kappa (QWK) the penalisation is proportional to the square of the distance.
+In this work, we will combine the QWK metric and the QWK loss.
+
+	Softmax function is widely used for the output layer in neural networks for classification tasks.
+It is a simple and efficient function for multi-class problems but not the best when working with ordinal data.
+In this paper, the Proportional Odds Model (POM) will be used instead of the softmax function.
+Different link functions will be explored to compare their performance.
+Also, the influence of other parameters like the learning rate of the optimisation algorithm and the batch size will be studied.
+We will contrast the results obtained with statistical analysis to provide more robust results.
+
+	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy and Adience.
+
+	This paper is organised as follows: in Section \ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section \ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section \ref{sect:results} we present the results obtained and the statistical analysis and finally in Section \ref{sect:conclusions} we expose the conclusions of this study.
 
 	\section{Related work}
-	...
+	\label{sect:relatedwork}
+	J.
+de la Torre et al.
+proposed the use of QWK loss function for the optimisation algorithm.
+They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
+They proved that their function could improve the results as it reduces the overfitting and the required training time.
+Also, they checked the importance of hyper-parameter tuning.
 
 	\section{Experiments}
+	\label{sect:experiments}
 	\subsection{Data}
@@
 
-	\begin{table}[htbp]
+	\begin{table}[ht]
 		\centering
@@
 	Every convolutional layer is followed by an ELU activation layer \cite{clevert2015fast} and a batch normalization \cite{ioffe2015batch}.
-At the output, a Proportional Odds Model (POM) is used with different link functions \cite{agresti2010analysis}.
+At the output, a Proportional Odds Model is used with different link functions \cite{agresti2010analysis}.
 The logit link function is commonly used within POM.
@@
 	\section{Results}
+	\label{sect:results}
 	In this section, we present the results of the experiments.
@@
 
-	\begin{table}[htbp]
+	\begin{table}[ht]
 		\footnotesize
@@
 	Following the setup of the previous study, we performed an ANOVA III analysis and multiple comparison tests.
-The tests show that there is no batch size whose results are significatively better than the results of all other batch sizes.
+We assume that five executions are enough to do the statistical tests because of the computational time limitations.
+The test shows that there is no batch size whose results are significatively better than the results of all other batch sizes.
 This does not mean that these differences could not exist for specific numbers of samples per batch.
@@
 
-	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (logit, probit, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the parameter factor ($10^{-4}$, $10^{-3}$, $10^{-2}$) and $B_k$ is the effect associated with the \textit{k-th} level of the size batch factor (5, 10, 15).
+	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (logit, probit, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the parameter factor ($10^{-4}$, $10^{-3}$, $10^{-2}$) and $B_k$ is the effect associated with the \textit{k-th} level of the batch size factor (5, 10, 15).
 The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors.
@@
 The complementary log-log link reported the best results after the logit function, having a mean WK of $0.611287$.
-The complementary log-log function doesn't show significative differences with the probit function.
+However, it doesn't show significative differences with the probit function.
 	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
@@
 	\section{Conclusions}
+	\label{sect:conclusions}
 	In this section, the conclusions obtained from this work are exposed. The first thing that we have noticed is that the optimal values for the different parameters considered are problem-dependant.
@@
 
-	%\end{multicols}
 \end{document}

### 2018-12-17 activations.py

@@ -228,5 +228,4 @@ class NNPOM(tf.keras.layers.Layer):
 		return self._nnpom(x, thresholds)
 
 	def compute_output_shape(self, input_shape):
-		print(input_shape)
 		return (input_shape[0], 1)

### 2018-12-17 experiment.py

@@ -348,7 +348,7 @@ class Experiment():
 
 		# Learning rate scheduler callback
 		def learning_rate_scheduler(epoch):
-			return self.lr * np.exp(-0.035 * epoch)
+			return self.lr * np.exp(-0.025 * epoch)
 
 		# Save epoch callback for training process
 		def save_epoch(epoch, logs):

### 2018-12-17 callbacks.py
Compute metrics generalization. Cleaning code

@@ -28,11 +28,12 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 	Computed metrics are: accuracy, loss and QWK.
 	"""
 
-	def __init__(self, num_classes, train_generator=None, val_generator=None, train_batches=None, val_batches=None):
+	def __init__(self, num_classes, train_generator=None, val_generator=None, train_batches=None, val_batches=None, metrics=['loss', 'acc']):
 		self.train_generator = train_generator
 		self.val_generator = val_generator
 		self.train_batches = train_batches
 		self.val_batches = val_batches
+		self.metrics = metrics
 		self.classes = []
 		self.num_classes = num_classes
 		self.cost_matrix = make_cost_matrix(self.num_classes)
@@ -69,18 +70,36 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 		mean_loss /= batch_count
 		qwk = sess.run(quadratic_weighted_kappa_cm(conf_mat, self.num_classes, self.cost_matrix))
 
-		return {'acc' : mean_acc, 'qwk' : qwk, 'loss' : mean_loss, 'conf_mat' : conf_mat}
+		metrics = {}
+
+		if 'acc' in self.metrics:
+			metrics['acc'] = mean_acc
+		if 'loss' in self.metrics:
+			metrics['loss'] = mean_loss
+		if 'qwk' in self.metrics:
+			metrics['qwk'] = qwk
+
+		metrics['conf_mat'] = conf_mat
+
+		return metrics
 
 	def on_epoch_end(self, epoch, logs={}):
 		if self.train_generator and self.train_batches:
 			train_metrics = self._compute_metrics(self.train_generator, self.train_batches, self.classes)
 
-			logs['train_acc'] = train_metrics['acc']
-			logs['val_qwk'] = train_metrics['qwk']
-			logs['val_loss'] = train_metrics['loss']
+			s = '\n'
 
-			print('\ntrain_loss: {} - train_acc: {} - train_qwk: {}'.format(train_metrics['loss'], train_metrics['acc'],
-																			train_metrics['qwk']))
+			if 'acc' in self.metrics:
+				logs['train_acc'] = train_metrics['acc']
+				s += 'train_acc: {} '.format(train_metrics['acc'])
+			if 'qwk' in self.metrics:
+				logs['train_qwk'] = train_metrics['qwk']
[…]

### 2018-12-17 experiment.py

@@ -408,9 +408,6 @@ class Experiment():
 		# Only accuracy for training.
 		# Computing QWK for training properly is too expensive
 		metrics = ['accuracy']
-		# If database is retinopathy, add qwk metric
-		# if self.db == 'retinopathy':
-		# 	metrics.append(quadratic_weighted_kappa(num_classes, cost_matrix))
 
 		# Compile the keras model
 		model.compile(
@@ -428,7 +425,8 @@ class Experiment():
 							steps_per_epoch=steps,
 							callbacks=[tf.keras.callbacks.LearningRateScheduler(learning_rate_scheduler),
 									   ComputeMetricsCallback(num_classes, val_generator=val_generator,
-															  val_batches=ds_val.num_batches(self.batch_size)),
+															  val_batches=ds_val.num_batches(self.batch_size),
+															  metrics=['acc', 'loss', 'qwk']),
 									   tf.keras.callbacks.ModelCheckpoint(
 										   os.path.join(self.checkpoint_dir, model_file)),
 									   save_epoch_callback,
@@ -519,24 +517,10 @@ class Experiment():
 		)
 
 		# Get predictions
-		# predictions = model.predict(
-		#	ds_test.x / 255.0
-		# )
 		test_generator.reset()
 		predictions = model.predict_generator(
 			test_generator
 		)
-
-		# conf_mat = confusion_matrix(np.argmax(ds_test.y, axis=1), np.argmax(predictions, axis=1), labels=range(0, num_classes))
-
-		# print(conf_mat)
-		# print(num_classes)
-		# print(cost_matrix)
-
-		# sess = tf.keras.backend.get_session()
-		# qwk = sess.run(quadratic_weighted_kappa_cm(conf_mat, num_classes, cost_matrix))
-
-		# print(qwk)
 
 		# Calculate QWK
 		qwk = np_quadratic_weighted_kappa(np.argmax(ds_test.y, axis=1), np.argmax(predictions, axis=1), 0, num_classes-1)

### 2019-01-08 paper/main.tex
Retoques paper

@@
 Different link functions will be explored to compare their performance.
-Also, the influence of other parameters like the learning rate of the optimisation algorithm and the batch size will be studied.
+Also, the influence of other parameters like the learning rate of the optimization algorithm and the batch size will be studied.
 We will contrast the results obtained with statistical analysis to provide more robust results.
@@
 de la Torre et al.
-proposed the use of QWK loss function for the optimisation algorithm.
+proposed the use of QWK loss function for the optimization algorithm.
 They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
@@
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
-The images are resized to 256 by 256 pixels.
+The images are resized to 128 by 128 pixels.
 Data augmentation techniques are applied to achieve a higher number of samples.
@@
 We use the form of the dataset where faces have been pre-cropped and aligned.
-The dataset was preprocessed, using the methods described in a previous work \cite{beckham2017unimodal}, so that the images are 256px in width and height, and pixels values follow a $(0;1)$ normal distribution.
+The dataset was preprocessed, using the methods described in a previous work \cite{beckham2017unimodal}, so that the images are 256 pixels in width and height, and pixels values follow a $(0;1)$ normal distribution.
 The original dataset is split into five cross-validation folds.
@@
 
-	Quadratic Weighted Kappa Loss, that J. de la Torre described in previous work, is considered as loss function for this optimizer as it gives better performance for ordinal classification problems.
+	Quadratic Weighted Kappa Loss is considered as loss function for this optimizer as it gives better performance for ordinal classification problems.
 
@@
 	The model is evaluated with Quadratic Weighted Kappa metric (QWK) \cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
+
+	 Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of the QWK loss and the Proportional Odds Model.
+The results of these experiments are analysed in Appendix \ref{app:NominalComparison}.
 
@@
 
+	The best mean WK value was obtained with the complementary log-log link function using a batch size of 10 and a learning rate of $10^{-3}$.
+
 	\subsection{Adience}
@@
 
+	The best mean WK value was obtained with the probit link function using a batch size of 15 and a learning rate of $10^{-2}$.
+
 	\subsection{Statistical analysis}
-	The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each, were obtained using ANalysis Of the VAriance (ANOVA)
+	In this subsection, a statistical analysis will be performed in order to obtain robust conclusions from the results presented in this section.
 
-	The ANalysis Of the VAriance (ANOVA) \cite{miller1997beyond} is one of the most widely used statistical techniques.
+	The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each, were obtained using the ANalysis Of the VAriance (ANOVA) test.
+
+	The ANOVA test \cite{miller1997beyond} is one of the most widely used statistical techniques.
 ANOVA is essentially a method of analysing the variance to which a response is subject into its various components, corresponding to the sources of variation which can be identified.
@@
 	ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
-Considered factors are the link function, which can be logit, probit and complementary log-log, the learning rate for the Adam optimisation algorithm ($10^{-2}$, $10^{-3}$ and $10^{-4}$) and the batch size (5, 10 and 15).
+Considered factors are the link function, which can be logit, probit and complementary log-log, the learning rate for the Adam optimization algorithm ($10^{-2}$, $10^{-3}$ and $10^{-4}$) and the batch size (5, 10 and 15).
 
@@
 We assume that five executions are enough to do the statistical tests because of the computational time limitations.
+
 	The test shows that there is no batch size whose results are significatively better than the results of all other batch sizes.
@@
 
-	We consider some hypotheses testing where the null hypothesis is proposed that each term of the above equation is independent of the levels involved. The hypotheses for the levels the L factor are
+	We consider some hypotheses testing where the null hypothesis is proposed that each term of the above equation is independent of the levels involved. The hypotheses for the levels of the L factor are
 	\[
@@
 
+	The proposed POM model has improved the performance of the deep network regarding Weighted Kappa compared to the model that uses the softmax function.
+This enhancement is more notable for the Diabetic Retinopathy dataset.
+Also, it reduces the chance that the model gets stuck when training with some parameter configurations.
+So, the most significant improvements of these link functions are the WK performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
+
 	\printbibliography
 
+	\appendix
+	\section{Statistical comparison between nominal and ordinal methods}
+	\label{app:NominalComparison}
+
+	The same experiments described in section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimiser and the softmax function instead of the Proportional Odds Model for the output of the network.
+	The results for both datasets are shown in Table \ref{table:NominalResults}.
+
+	\begin{table}[ht]
+		\footnotesize
+		\centering
+		\begin{tabular}{lcc|cc}
+			Dataset & BS & LR & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
+			Retinopathy & $5$ & $10^{-2}$ & $0.2210$ & $0.2050$\\
+			Retinopathy & $5$ & $10^{-3}$ & $0.2807$ & $0.2654$\\
+			Retinopathy & $5$ & $10^{-4}$ & $0.4580$ & $0.4449$\\
+
+			Retinopathy & $10$ & $10^{-2}$ & $0.2972$ & $0.2997$\\
+			Retinopathy & $10$ & $10^{-3}$ & $0.3972$ & $0.3989$\\
+			Retinopathy & $10$ & $10^{-4}$ & $\textbf{0.4972}$ & $\textbf{0.4967}$\\
+
+			Retinopathy & $15$ & $10^{-2}$ & $0.3692$ & $0.3676$\\
+			Retinopathy & $15$ & $10^{-3}$ & $0.4107$ & $0.4162$\\
+			Retinopathy & $15$ & $10^{-4}$ & $0.4929$ & $0.4859$\\
+			\hline\addlinespace[0.05cm]
+			Adience & $5$ & $10^{-2}$ & $0.0605$ & $0.0769$\\
+			Adience & $5$ & $10^{-3}$ & $0.7994$ & $0.7313$\\
+			Adience & $5$ & $10^{-4}$ & $0.8009$ & $0.7383$\\
+
+			Adience & $10$ & $10^{-2}$ & $0.0559$ & $0.0576$\\
+			Adience & $10$ & $10^{-3}$ & $0.8239$ & $0.7436$\\
+			Adience & $10$ & $10^{-4}$ & $0.7938$ & $0.7218$\\
+
+			Adience & $15$ & $10^{-2}$ & $0.0593$ & $0.0713$\\
+			Adience & $15$ & $10^{-3}$ & $\textbf{0.8309}$ & $\textbf{0.7575}$\\
+			Adience & $15$ & $10^{-4}$ & $0.7867$ & $0.7129$\\
+		\end{tabular}
+		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\label{table:NominalResults}
+	\end{table}
+
+	As we did in Section X, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the WK metric.
+So, we make an ANOVA II analysis for each dataset.
+
+	In the Diabetic Retinopathy dataset, there are significative differences between the mean values of WK depending on the batch size and the initial value of the learning rate.
+Also, no significative interaction was detected between these factors.
+
+	After that, a post-hoc Tukey's test shows that the best value for the batch size factor is 15 followed by 10.
+However, there are no significative differences between them, but there are differences with size 5.
+Also, the best value for the learning rate is $10^{-4}$ and there are significative differences with the rest of values.
+
+	A similar study was made for the Adience dataset.
+There are not significative differences for the mean value of WK w.r.t.
+the batch size factor.
+Also, there are no interactions between the batch size and the learning rate.
+The best results were obtained with $10^{-3}$ for the learning rate followed by $10^{-4}$, without significative differences between them.
+
+	Finally, the conclusions of this study are exposed below:
+	\begin{itemize}
+		\item There are no interactions between both factors.
+		\item Batch sizes 10 and 15 obtained the best results.
+		\item Learning rate $10^{-4}$ is the best choice for both datasets as it the best for Diabetic Retinopathy, with significative differences, and it is the second for Adience, without significative differences with the best.
+	\end{itemize}
+
 \end{document}

### 2019-01-08 paper/main.tex
Paper related work. Validation metrics customization

@@
 de la Torre et al.
-proposed the use of QWK loss function for the optimization algorithm.
+\cite{de2018weighted} proposed the use of QWK loss function for the optimization algorithm.
 They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
@@
 Also, they checked the importance of hyper-parameter tuning.
+
+	Christopher Beckham and Christopher Pal \cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal via the use of the Poisson and binomial probability distributions.
+They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, and they obtained promising results.
+
+	The Exponential Linear Unit (ELU), used in this paper, was described in previous work from D.-A.
+Clevert et al.
+\cite{clevert2015fast}.
+They proved that ELUs alleviate the vanishing gradient problem via the identity for positive values.
+In their experiments, ELUs lead not only to faster learning but also to significantly better generalization performance than ReLUs and LReLUs on networks with more than five layers.
+
+	Sergey Ioffe and Christian Szegedy \cite{ioffe2015batch} described Batch Normalization and its benefits in previous work.
+It reduces the internal covariate shift by normalizing layer inputs.
+Their method draws its strength from making normalization a part of the model architecture and performing the normalization for each training batch.
+It allows them to use higher learning rates and be less careful about initialization.
+It also eliminates the need for using regularization techniques like Dropout.
 
@@
 
-	The same experiments described in section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimiser and the softmax function instead of the Proportional Odds Model for the output of the network.
+	The same experiments described in section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
 	The results for both datasets are shown in Table \ref{table:NominalResults}.

### 2019-01-08 callbacks.py

@@ -68,7 +68,6 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 
 		mean_acc /= batch_count
 		mean_loss /= batch_count
-		qwk = sess.run(quadratic_weighted_kappa_cm(conf_mat, self.num_classes, self.cost_matrix))
 
 		metrics = {}
 
@@ -77,6 +76,7 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 		if 'loss' in self.metrics:
 			metrics['loss'] = mean_loss
 		if 'qwk' in self.metrics:
+			qwk = sess.run(quadratic_weighted_kappa_cm(conf_mat, self.num_classes, self.cost_matrix))
 			metrics['qwk'] = qwk
 
 		metrics['conf_mat'] = conf_mat

### 2019-01-08 experiment.py

@@ -23,7 +23,7 @@ class Experiment():
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
 				 checkpoint_dir='checkpoint', loss='crossentropy', activation='relu', final_activation='softmax',
 				 prob_layer=None,
-				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both', workers=4):
+				 spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both', workers=4, val_metrics=['loss', 'acc']):
 		self._name = name
 		self._db = db
 		self._net_type = net_type
@@ -41,6 +41,7 @@ class Experiment():
 		self._task = task
 		self._finished = False
 		self._workers = workers
+		self._val_metrics = val_metrics
 
 		self._best_metric = -1
 
@@ -270,6 +271,18 @@ class Experiment():
 		del self._workers
 
 	@property
+	def val_metrics(self):
+		return self._val_metrics
+
+	@val_metrics.setter
+	def val_metrics(self, val_metrics):
+		self._val_metrics = val_metrics
+
+	@val_metrics.deleter
+	def val_metrics(self):
+		del self._val_metrics
+
+	@property
 	def best_metric(self):
 		return self._best_metric
 
@@ -426,7 +439,7 @@ class Experiment():
 							callbacks=[tf.keras.callbacks.LearningRateScheduler(learning_rate_scheduler),
 									   ComputeMetricsCallback(num_classes, val_generator=val_generator,
 															  val_batches=ds_val.num_batches(self.batch_size),
-															  metrics=['acc', 'loss', 'qwk']),
+															  metrics=self.val_metrics),
 									   tf.keras.callbacks.ModelCheckpoint(
 										   os.path.join(self.checkpoint_dir, model_file)),
 									   save_epoch_callback,
@@ -578,7 +591,8 @@ class Experiment():
 			'momentum': self.momentum,
 			'dropout': self.dropout,
 			'task': self.task,
-			'workers' : self.workers
+			'workers' : self.workers,
+			'val_metrics' : self.val_metrics
 		}
 
 	def set_config(self, config):
@@ -602,6 +616,7 @@ class Experiment():
 		self.dropout = 'dropout' in config and config['dropout'] or 0
 		self.task = 'task' in config and config['task'] or 'both'
 		self.workers = 'workers' in config and config['workers'] or 4
[…]

### 2019-01-09 paper/main.tex
Cambios paper

@@
 	\label{sect:introduction}
-	Deep learning \cite{lecun2015deep} combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
+	Deep learning, introduced by Yann Lecun \cite{lecun2015deep}, combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
 These methods have dramatically improved the state-of-the-art in many domains, such as image classification or speech recognition.
@@
 
-	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
-The layer's parameters are updated after backpropagating the loss function gradients through the network.
-Deep convolutional nets are suited for images, video, speech and audio processing and they have been used extensively in the last years for automatic classification tasks.
-For the case of images, convolutional layers extract the main features from the pixels of the images and, after that, the fully connected layer classify every sample based on its extracted features.
+	Convolutional neural networks (ConvNets) are designed to process data that comes in the form of multiple arrays.
+ConvNets are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks \cite{dong2014learning}\cite{sun2013deep}\cite{ronneberger2015u}.
+On image classification tasks, each colour channel is represented by a 2D array.
+In this case, convolutional layers extract the main features from the pixels of the images and, after that, a fully connected layer classify every sample based on its extracted features.
 At the output of the convolutional net, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks.
@@
 
+	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
+It has been used in the last years in many works \cite{leonard1990improvement}\cite{yu1995dynamic}\cite{krizhevsky2012imagenet}\cite{de2018weighted} for training swallow and deep neural networks.
+It updates the layer's parameters after backpropagating the loss function gradients through the network.
+Learning rate hyper-parameter controls the strength of the changes that are applied to those parameters.
+Some works have checked the importance of finding the optimal value for this parameter \cite{senior2013empirical} and have tried different approaches to try to improve the training process \cite{smith2017cyclical}.
+
+	Batch normalization is another technique that is used for this kind of networks.
+It reduces the internal covariate shift by normalizing layer inputs.
+It was presented in 2015 \cite{ioffe2015batch} and gives a critical enhancement to the training phase.
+Batch size is an important hyper-parameter that should be adjusted as it affects the layer's parameters updates and also the normalization \cite{keskar2016large}\cite{radiuk2017impact}.
+
+	Ordinal classification problems are those where labels are ordered.
 Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics}\cite{mehdiyev2016evaluating}.
@@
 Those weights are predefined and depend on the type of the chosen WK.
-In a linear penalisation, the weight is proportional to the distance between the predicted and the real class.
-In the Quadratic Weighted Kappa (QWK) the penalisation is proportional to the square of the distance.
+In a linear penalization, the weight is proportional to the distance between the predicted and the real class.
+In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance.
 In this work, we will combine the QWK metric and the QWK loss.
@@
 It is a simple and efficient function for multi-class problems but not the best when working with ordinal data.
-In this paper, the Proportional Odds Model (POM) will be used instead of the softmax function.
+In this paper, the Proportional Odds Model (POM) \cite{agresti2010analysis} will be used instead of the softmax function.
 Different link functions will be explored to compare their performance.
@@
 We will contrast the results obtained with statistical analysis to provide more robust results.
+An approximated ANOVA III test will be performed because of the limitations of the computational time required to run a higher number of executions.
 
-	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy and Adience.
+	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy, that contains high-resolution fundus images related with diabetes disease, and Adience, that is formed of human faces images that are assigned an age range.
 
@@
 	 Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of the QWK loss and the Proportional Odds Model.
-The results of these experiments are analysed in Appendix \ref{app:NominalComparison}.
+The results of these experiments are analysed in Section \ref{app:NominalComparison}.
 
@@
 	\subsection{Statistical analysis}
+	\label{sect:statisticalanalysis}
 	In this subsection, a statistical analysis will be performed in order to obtain robust conclusions from the results presented in this section.
@@
 
-	\section{Conclusions}
-	\label{sect:conclusions}
-	In this section, the conclusions obtained from this work are exposed. The first thing that we have noticed is that the optimal values for the different parameters considered are problem-dependant.
-
-	The complementary log-log function has the best average performance across both datasets.
-It offers the best results in Diabetic Retinopathy dataset and the second best result in Adience dataset.
-These results provide an opportunity for exploring new generalised link functions.
-
-	The best value for the learning rate parameter for  Diabetic Retinopathy dataset is $\eta = 10^{-3}$ while this value is the second best option for Adience dataset.
-It can be considered a good value for this parameter when training the model with new datasets.
-
-	Both datasets have obtained the best performance with batch size 10.
-
-	Also, the statistical tests reported that there are interactions between some parameters like the link function and the learning rate, for Diabetic Retinopathy, or those factors in addition to learning rate and batch size, for Adience dataset.
-
-	The proposed POM model has improved the performance of the deep network regarding Weighted Kappa compared to the model that uses the softmax function.
-This enhancement is more notable for the Diabetic Retinopathy dataset.
-Also, it reduces the chance that the model gets stuck when training with some parameter configurations.
-So, the most significant improvements of these link functions are the WK performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
-
-	\printbibliography
-
-	\appendix
-	\section{Statistical comparison between nominal and ordinal methods}
+	\subsection{Statistical comparison between nominal and ordinal methods}
 	\label{app:NominalComparison}
 
-	The same experiments described in section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
+	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
 	The results for both datasets are shown in Table \ref{table:NominalResults}.
@@
 		\end{tabular}
-		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
 		\label{table:NominalResults}
@@
 
-	As we did in Section X, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the WK metric.
+	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the WK metric.
 So, we make an ANOVA II analysis for each dataset.
@@
 
+	\section{Conclusions}
+	\label{sect:conclusions}
+	In this section, the conclusions obtained from this work are exposed. The first thing that we have noticed is that the optimal values for the different parameters considered are problem-dependant.
+
+	The complementary log-log function has the best average performance across both datasets.
+It offers the best results in Diabetic Retinopathy dataset and the second best result in Adience dataset.
+These results provide an opportunity for exploring new generalised link functions.
+
+	The best value for the learning rate parameter for  Diabetic Retinopathy dataset is $\eta = 10^{-3}$ while this value is the second best option for Adience dataset.
+It can be considered a good value for this parameter when training the model with new datasets.
+
+	Both datasets have obtained the best performance with batch size 10.
+
+	Also, the statistical tests reported that there are interactions between some parameters like the link function and the learning rate, for Diabetic Retinopathy, or those factors in addition to learning rate and batch size, for Adience dataset.
+
+	The proposed POM model has improved the performance of the deep network regarding Weighted Kappa compared to the model that uses the softmax function.
+This enhancement is more notable for the Diabetic Retinopathy dataset.
+Also, it reduces the chance that the model gets stuck when training with some parameter configurations.
+So, the most significant improvements of these link functions are the WK performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
+
+	\printbibliography
+
 \end{document}

### 2019-01-10 paper/ieee.tex
IEEE format

--- 2019-01-09 paper/main.tex
@@
-% !TeX spellcheck = en_UK
-\documentclass[10pt, a4paper, titlepage, twocolumn]{article}
+%% bare_jrnl.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% see http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
 
-\input{preambulo.tex}
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
 
-\setlength{\columnsep}{0.7cm}
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[journal]{IEEEtran}
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+% \usepackage[pdftex]{graphicx}
+% declare the path(s) where your graphic files are
+% \graphicspath{{../pdf/}{../jpeg/}}
+% and their extensions so you won't have to specify these with
+% every instance of \includegraphics
+% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+% will default to the driver specified in the system graphics.cfg if no
+% driver is specified.
+% \usepackage[dvips]{graphicx}
+% declare the path(s) where your graphic files are
+% \graphicspath{{../eps/}}
+% and their extensions so you won't have to specify these with
+% every instance of \includegraphics
+% \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
+%
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+\usepackage{url}
+\usepackage{hyperref}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+\usepackage[utf8]{inputenc}
+
+\usepackage[backend=bibtex, style=ieee]{biblatex}
+
+\usepackage{lmodern}
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\addbibresource{main.bib}
 
 \begin{document}
-	\fontfamily{lmr}\selectfont
+	%
+	% paper title
+	% Titles are generally capitalized except for words such as a, an, and, as,
+	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+	% not capitalized unless they are the first or last word of the title.
+	% Linebreaks \\ can be used within to get better formatting as desired.
+	% Do not put math or special symbols in the title.
+	\title{Classification of ordinal data in deep learning: an experimental study}
+	%
+	%
+	% author names and IEEE memberships
+	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+	% a structure at a ~ so this keeps an author's name from being broken across
+	% two lines.
+	% use \thanks{} to gain access to the first footnote area
+	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+	% was not built to handle multiple paragraphs
+	%
+
+	\author{Victor-Manuel~Vargas, Pedro-Antonio~Gutiérrez and César~Hervás}
+
+	% note the % following the last \IEEEmembership and also \thanks - 
+	% these prevent an unwanted space from occurring between the last author name
+	% and the end of the author line. i.e., if you had this:
+	% 
+	% \author{....lastname \thanks{...} \thanks{...} }
+	%                     ^------------^------------^----Do not want these spaces!
+	%
+	% a space would be appended to the last name and could cause every name on that
+	% line to be shifted left slightly. This is one of those "LaTeX things". For
+	% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+	% "AB" then you have to do: "\textbf{A}\textbf{B}"
+	% \thanks is no different in this regard, so shield the last } of each \thanks
+	% that ends a line with a % and do not let a space in before the next \thanks.
+	% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+	% you are supposed to have spaces between the names. For what it is worth,
+	% this is a minor point as most people would not even notice if the said evil
+	% space somehow managed to creep in.
+
+	% The paper headers
+	\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+	{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+	% The only time the second header will appear is for the odd numbered pages
+	% after the title page when using the twoside option.
+	% 
+	% *** Note that you probably will NOT want to include the author's ***
+	% *** name in the headers of peer review papers.                   ***
+	% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+	% you desire.
+
+	% If you want to put a publisher's ID mark on the page you can do it like
+	% this:
+	%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+	% Remember, if you use this you must call \IEEEpubidadjcol in the second
+	% column for its text to clear the IEEEpubid mark.
+
+	% use for special paper notices
+	%\IEEEspecialpapernotice{(Invited Paper)}
+
+	% make the title area
+	\maketitle
+
+	% As a general rule, do not put math, special symbols or citations
+	% in the abstract or keywords.
+	\begin{abstract}
+		The abstract goes here.
+	\end{abstract}
+
+	% Note that keywords are not normally used for peerreview papers.
+	\begin{IEEEkeywords}
+		IEEE, IEEEtran, journal, \LaTeX, paper, template.
+	\end{IEEEkeywords}
+
+	% For peer review papers, you can put extra information on the cover
+	% page as needed:
+	% \ifCLASSOPTIONpeerreview
+	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+	% \fi
+	%
+	% For peerreview papers, this IEEEtran command inserts a page break and
+	% creates the second title. It will be ignored for other modes.
+	\IEEEpeerreviewmaketitle
 
@@
 	\label{sect:introduction}
-	Deep learning, introduced by Yann Lecun \cite{lecun2015deep}, combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
-These methods have dramatically improved the state-of-the-art in many domains, such as image classification or speech recognition.
+	% The very first letter is a 2 line initial drop letter followed
+	% by the rest of the first word in caps.
+	% 
+	% form to use if the first word consists of a single letter:
+	% \IEEEPARstart{A}{demo} file is ....
+	% 
+	% form to use if you need the single drop letter followed by
+	% normal text (unknown if ever used by the IEEE):
+	% \IEEEPARstart{A}{}demo file is ....
+	% 
+	% Some journals put the first two words in caps:
+	% \IEEEPARstart{T}{his demo} file is ....
+	% 
+	% Here we have the typical use of a "T" for an initial drop letter
+	% and "HIS" in caps to complete the first word.
+	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
+These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi, he2016deep, krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed, girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
 Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to indicate how a machine should change its internal parameters that are used to compute the representation in each layer from the features in the previous layer.
@@
 	Convolutional neural networks (ConvNets) are designed to process data that comes in the form of multiple arrays.
-ConvNets are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks \cite{dong2014learning}\cite{sun2013deep}\cite{ronneberger2015u}.
+ConvNets are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning, sun2013deep, ronneberger2015u}.
 On image classification tasks, each colour channel is represented by a 2D array.
@@
 	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
-It has been used in the last years in many works \cite{leonard1990improvement}\cite{yu1995dynamic}\cite{krizhevsky2012imagenet}\cite{de2018weighted} for training swallow and deep neural networks.
+It has been used in the last years in many works~\cite{leonard1990improvement, yu1995dynamic, krizhevsky2012imagenet, de2018weighted} for training shallow and deep neural networks.
 It updates the layer's parameters after backpropagating the loss function gradients through the network.
 Learning rate hyper-parameter controls the strength of the changes that are applied to those parameters.
-Some works have checked the importance of finding the optimal value for this parameter \cite{senior2013empirical} and have tried different approaches to try to improve the training process \cite{smith2017cyclical}.
+Some works have checked the importance of finding the optimal value for this parameter~\cite{senior2013empirical} and have tried different approaches to try to improve the training process~\cite{smith2017cyclical}.
 
@@
 It reduces the internal covariate shift by normalizing layer inputs.
-It was presented in 2015 \cite{ioffe2015batch} and gives a critical enhancement to the training phase.
-Batch size is an important hyper-parameter that should be adjusted as it affects the layer's parameters updates and also the normalization \cite{keskar2016large}\cite{radiuk2017impact}.
+It was presented in 2015~\cite{ioffe2015batch} and gives a critical enhancement to the training phase.
+Batch size is an important hyper-parameter that should be adjusted as it affects the layer's parameters updates and also the normalization~\cite{keskar2016large}\cite{radiuk2017impact}.
 
-	Ordinal classification problems are those where labels are ordered.
-Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics}\cite{mehdiyev2016evaluating}.
+	Ordinal classification problems are those where labels are ordered, and there are different inter-classes weights for each pair of classes.
+This kind of problem can be treated as a nominal classification problem, but when you do this, you are the discarding ordinal information.
+A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model.
+One way to use the ordinal information is to evaluate the model using an ordinal metric.
+Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics, mehdiyev2016evaluating}.
 Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories.
 Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables.
-Weighted Kappa loss was described in previous work \cite{de2018weighted} and is a cost function that is based on the WK metric.
+Weighted Kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric.
 These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk.
@@
 It is a simple and efficient function for multi-class problems but not the best when working with ordinal data.
-In this paper, the Proportional Odds Model (POM) \cite{agresti2010analysis} will be used instead of the softmax function.
+In this paper, the Proportional Odds Model (POM)~\cite{agresti2010analysis} will be used instead of the softmax function.
 Different link functions will be explored to compare their performance.
@@
 
-	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy, that contains high-resolution fundus images related with diabetes disease, and Adience, that is formed of human faces images that are assigned an age range.
+	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy~\cite{de2018weighted}, that contains high-resolution fundus images related with diabetes disease, and Adience~\cite{beckham2017unimodal}, that is formed of human faces images that are assigned an age range.
 
-	This paper is organised as follows: in Section \ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section \ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section \ref{sect:results} we present the results obtained and the statistical analysis and finally in Section \ref{sect:conclusions} we expose the conclusions of this study.
+	This paper is organised as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this study.
 
@@
 	\label{sect:relatedwork}
+	There are many works related to the application and development of convolutional neural networks models. Few works treat ordinal classification problems, though.
+
 	J.
-de la Torre et al.
-\cite{de2018weighted} proposed the use of QWK loss function for the optimization algorithm.
+de la Torre et al.~\cite{de2018weighted} proposed the use of QWK loss function for the optimization algorithm.
 They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
@@
 
-	Christopher Beckham and Christopher Pal \cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal via the use of the Poisson and binomial probability distributions.
+	Christopher Beckham and Christopher Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal via the use of the Poisson and binomial probability distributions.
 They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, and they obtained promising results.
 
-	The Exponential Linear Unit (ELU), used in this paper, was described in previous work from D.-A.
-Clevert et al.
-\cite{clevert2015fast}.
+	At present, there is a great discussion in terms of finding the best activation function that offers good performance and mitigates the effects of the gradients vanishing problem \cite{bengio1994learning, pascanu2013difficulty}.
+Rectified Linear Unit (ReLU)~\cite{nair2010rectified} is widely used in most deep learning works, but recently, Clevert et al.
+proposed the Exponential Linear Unit (ELU)~\cite{clevert2015fast}.
 They proved that ELUs alleviate the vanishing gradient problem via the identity for positive values.
 In their experiments, ELUs lead not only to faster learning but also to significantly better generalization performance than ReLUs and LReLUs on networks with more than five layers.
+That's why we decided to use the ELU function for the experiments described in this paper.
 
-	Sergey Ioffe and Christian Szegedy \cite{ioffe2015batch} described Batch Normalization and its benefits in previous work.
+	Sergey Ioffe and Christian Szegedy~\cite{ioffe2015batch} described Batch Normalization and its benefits in previous work.
 It reduces the internal covariate shift by normalizing layer inputs.
@@
 These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform.
-Also, this dataset was used in later works \cite{de2018weighted}\cite{nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
+Also, this dataset was used in later works~\cite{de2018weighted, nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
@@
 We use the form of the dataset where faces have been pre-cropped and aligned.
-The dataset was preprocessed, using the methods described in a previous work \cite{beckham2017unimodal}, so that the images are 256 pixels in width and height, and pixels values follow a $(0;1)$ normal distribution.
+The dataset was preprocessed, using the methods described in a previous work~\cite{beckham2017unimodal}, so that the images are 256 pixels in width and height, and pixels values follow a $(0;1)$ normal distribution.
 The original dataset is split into five cross-validation folds.
@@
 
-	\begin{table}[ht]
+	\begin{table}[!t]
+		\caption{Description of the architecture used in the experiments.
+For convolutional layers, Conv\_N\_WxH, where N is the number of filters, W the filter width and H the filter height.
+Stride is 1 for every convolutional layer.
+For max pool layers, MaxPool\_SxS, where S is the pool size.}
+		\label{table:CNNArchitecture}
 		\centering
@@
 		\end{tabular}	
-		\caption{Description of the architecture used in the experiments.
-For convolutional layers, Conv\_N\_WxH, where N is the number of filters, W the filter width and H the filter height.
-Stride is 1 for every convolutional layer.
-For max pool layers, MaxPool\_SxS, where S is the pool size.}
-		\label{table:CNNArchitecture}
 	\end{table}
 
-	Every convolutional layer is followed by an ELU activation layer \cite{clevert2015fast} and a batch normalization \cite{ioffe2015batch}.
-At the output, a Proportional Odds Model is used with different link functions \cite{agresti2010analysis}.
+	Every convolutional layer is followed by an ELU activation layer~\cite{clevert2015fast} and a batch normalization~\cite{ioffe2015batch}.
+At the output, a Proportional Odds Model is used with different link functions~\cite{agresti2010analysis}.
 The logit link function is commonly used within POM.
@@
 		\begin{equation}
-		\small
 		logit[P(Y_i \le j)] = \alpha_j + \beta'x_i,\quad j = 1, ..., c - 1
@@
 		\begin{equation}
-		\small
 		\Phi^{-1}[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
@@
 		\begin{equation}
-		\footnotesize
+		\small
 		log[-log[1 - P(Y \le j)]] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
@@
 	\subsection{Procedure}
-	The model is optimized using a batch based first-order optimization algorithm called Adam \cite{kingma2014adam}.
+	The model is optimized using a batch based first-order optimization algorithm called Adam~\cite{kingma2014adam}.
 We study different initial learning rates in order to find the optimal one for each problem.
@@
 
-	Both datasets have been artificially equalised using data augmentation techniques \cite{van2001art}\cite{krizhevsky2012imagenet} based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
+	Both datasets have been artificially equalised using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet} based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
 In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch.
@@
 
-	The model is evaluated with Quadratic Weighted Kappa metric (QWK) \cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
+	The model is evaluated with Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
 
@@
 Optimal learning rate can vary depending on the dataset and the CNN architecture.
-Previous works have presented some techniques that adjust this parameter in order to achieve better performance \cite{smith2017cyclical}\cite{senior2013empirical}.
+Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical, senior2013empirical}.
 Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
@@
 
-	\begin{table}[ht]
+	\begin{table}[!t]
+		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\label{table:DRresults}
 		\footnotesize
@@
 		\begin{tabular}{ccc|cc}
-			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
+			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
 			$5$ & $10^{-2}$ & Logit & $0.44888$ & $0.4163$\\
@@
 		\end{tabular}
-		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
-		\label{table:DRresults}
 	\end{table}
@@
 	\begin{table}[ht]
+		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\label{table:Adienceresults}
 		\footnotesize
@@
 		\begin{tabular}{ccc|cc}
-			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
+			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
 			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
@@
 		\end{tabular}
-		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
-		\label{table:Adienceresults}
+
 	\end{table}
@@
 
-	The ANOVA test \cite{miller1997beyond} is one of the most widely used statistical techniques.
+	The ANOVA test~\cite{miller1997beyond} is one of the most widely used statistical techniques.
 ANOVA is essentially a method of analysing the variance to which a response is subject into its various components, corresponding to the sources of variation which can be identified.
@@
 	\begin{table}[ht]
+		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
+		\label{table:ANOVARetinopathy}
 		\centering
@@
 		\end{tabular}
-		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
-		\label{table:ANOVARetinopathy}
 	\end{table}
@@
 	\begin{table}[ht]
+		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
+		\label{table:ANOVAAdience}
 		\centering
@@
 		\end{tabular}
-		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
-		\label{table:ANOVAAdience}
 	\end{table}
@@
 	\begin{table}[ht]
+		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
+		\label{table:NominalResults}
 		\footnotesize
@@
 		\begin{tabular}{lcc|cc}
-			Dataset & BS & LR & $\kappa_{val}$ & $\kappa_{test}$\\\hline\addlinespace[0.05cm]
+			Dataset & BS & LR & $\kappa_{val}$ & $\kappa_{test}$\\\hline
 			Retinopathy & $5$ & $10^{-2}$ & $0.2210$ & $0.2050$\\
@@
 			Retinopathy & $15$ & $10^{-4}$ & $0.4929$ & $0.4859$\\
-			\hline\addlinespace[0.05cm]
+			\hline
 			Adience & $5$ & $10^{-2}$ & $0.0605$ & $0.0769$\\
@@
 		\end{tabular}
-		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
-		\label{table:NominalResults}
 	\end{table}
@@
 
+	% if have a single appendix:
+	%\appendix[Proof of the Zonklar Equations]
+	% or
+	%\appendix  % for no appendix heading
+	% do not use \section anymore after \appendix, only \section*
+	% is possibly needed
+
+	% use appendices with more than one appendix
+	% then use \section to start each appendix
+	% you must declare a \section before using any
+	% \subsection or using \label (\appendices by itself
+	% starts a section numbered zero.)
+	%
+
+	% Can use something like this to put references on a page
+	% by themselves when using endfloat and the captionsoff option.
+	\ifCLASSOPTIONcaptionsoff
+	\newpage
+	\fi
+
+	% trigger a \newpage just before the given reference
+	% number - used to balance the columns on the last page
+	% adjust value as needed - may need to be readjusted if
+	% the document is modified later
+	%\IEEEtriggeratref{8}
+	% The "triggered" command can be changed if desired:
+	%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+	% references section
+
+	% can use a bibliography generated by BibTeX as a .bbl file
+	% BibTeX documentation can be easily obtained at:
+	% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+	% The IEEEtran BibTeX style support page is at:
+	% http://www.michaelshell.org/tex/ieeetran/bibtex/
+	%\bibliographystyle{IEEEtran}
+	% argument is your BibTeX string definitions and bibliography database(s)
+	%\bibliography{IEEEabrv,../bib/paper}
+	%
+	% <OR> manually copy in the resultant .bbl file
+	% set second argument of \begin to the number of references
+	% (used to reserve space for the reference number labels box)
+
 	\printbibliography
 
+	% You can push biographies down or up by placing
+	% a \vfill before or after them. The appropriate
+	% use of \vfill depends on what kind of text is
+	% on the last page and whether or not the columns
+	% are being equalized.
+
+	%\vfill
+
+	% Can be used to pull up biographies so that the bottom of the last one
+	% is flush with the other column.
+	%\enlargethispage{-5in}
+
+	% that's all folks
 \end{document}

### 2019-01-10 dataset.py

@@ -3,6 +3,8 @@ import numpy as np
 import os
 import math
 import h5py
+from sklearn.model_selection import train_test_split
+import tensorflow as tf
 
 class Dataset():
 	"""
@@ -76,7 +78,13 @@ class Dataset():
 		del self._sample_shape
 
 	def load(self, path):
-		if os.path.isdir(path):
+		if path == 'cifar10train':
+			self._load_cifar10('train')
+		elif path == 'cifar10val':
+			self._load_cifar10('val')
+		elif path == 'cifar10test':
+			self._load_cifar10('test')
+		elif os.path.isdir(path):
 			self._load_from_dir(path)
 		else:
 			self._load_from_h5(path)
@@ -111,6 +119,33 @@ class Dataset():
 
 	def _load_from_h5(self, path):
 		pass
+
+	def _load_cifar10(self, split):
+		(x_train, y_train), (x_test, y_test) = tf.keras.datasets.cifar10.load_data()
+
+		self._data = {}
+		self._data['x'] = []
+		self._data['y'] = []
+		self._sample_shape = (32,32,3)
+
+		if split == 'train':
+			self._data['x'] = x_train
+			self._data['y'] = y_train
+		elif split == 'val' or split == 'test':
+			xt, xv, yt, yv = train_test_split(x_test, y_test, test_size=0.2, random_state=1)
+
+			if split == 'val':
+				self._data['x'] = xv
+				self._data['y'] = yv
+			elif split == 'test':
+				self._data['x'] = xt
+				self._data['y'] = yt
+
+		y_onehot = np.zeros((len(self._data['y']), 10))
+		y_onehot[np.arange(len(self._data['y'])), np.array(self._data['y'])] = 1
+		self._data['y'] = list(y_onehot)
+		self.num_classes = 10
+
 
 	def size(self):
 		"""

### 2019-01-10 experiment.py

@@ -292,7 +292,7 @@ class Experiment():
 		:param metric: new metric.
 		:return: True if new metric is better than best metric or False otherwise.
 		"""
-		if metric >= self._best_metric:
+		if metric <= self._best_metric:
 			self._best_metric = metric
 			return True
 		return False
@@ -366,7 +366,7 @@ class Experiment():
 		# Save epoch callback for training process
 		def save_epoch(epoch, logs):
 			# Check whether new metric is better than best metric
-			if (self.new_metric(logs['val_qwk'])):
+			if (self.new_metric(logs['val_loss'])):
 				model.save(os.path.join(self.checkpoint_dir, best_model_file))
 
 			with open(os.path.join(self.checkpoint_dir, model_file_extra), 'w') as f:
@@ -551,7 +551,7 @@ class Experiment():
 		elif name == 'testing':
 			model = net_object.testing()
 		elif name == 'inceptionresnetv2':
-			model = net_object.InceptionResNetV2()
+			model = net_object.inception_resnet_v2_custom()
 		else:
 			raise Exception('Invalid net type. You must select one of these: vgg19, conv128')
 
@@ -567,6 +567,8 @@ class Experiment():
 			return "../retinopathy/128/train", "../retinopathy/128/val", "../retinopathy/128/test"
 		elif db.lower() == 'adience':
 			return "../adience/256/train", "../adience/256/val", "../adience/256/test"
+		elif db.lower() == 'cifar10' or db.lower() == 'cifar100':
+			return db.lower() + 'train', db.lower() + 'val', db.lower() + 'test'
 		else:
 			return "", "", ""
 

### 2019-01-10 inception_resnet_v2.py

@@ -1,0 +1,375 @@
+"""Inception-ResNet V2 model for Keras.
+
+Model naming and structure follows TF-slim implementation
+(which has some additional layers and different number of
+filters from the original arXiv paper):
+https://github.com/tensorflow/models/blob/master/research/slim/nets/inception_resnet_v2.py
+
+Pre-trained ImageNet weights are also converted from TF-slim,
+which can be found in:
+https://github.com/tensorflow/models/tree/master/research/slim#pre-trained-models
+
+# Reference
+- [Inception-v4, Inception-ResNet and the Impact of
+   Residual Connections on Learning](https://arxiv.org/abs/1602.07261)
+
+"""
+from __future__ import absolute_import
+from __future__ import division
+from __future__ import print_function
+
+import os
+
+import imagenet_utils
+from keras_utils import get_submodules_from_kwargs
+from imagenet_utils import decode_predictions
+from imagenet_utils import _obtain_input_shape
+
+
+
+
+BASE_WEIGHT_URL = ('https://github.com/fchollet/deep-learning-models/'
+                   'releases/download/v0.7/')
+
+backend = None
+layers = None
+models = None
+keras_utils = None
+
+
+def preprocess_input(x, **kwargs):
+    """Preprocesses a numpy array encoding a batch of images.
+
+    # Arguments
+        x: a 4D numpy array consists of RGB values within [0, 255].
+
+    # Returns
+        Preprocessed array.
+    """
+    return imagenet_utils.preprocess_input(x, mode='tf', **kwargs)
+
+
+def conv2d_bn(x,
+              filters,
+              kernel_size,
+              strides=1,
+              padding='same',
+              activation='relu',
+              use_bias=False,
+              name=None):
+    """Utility function to apply conv + BN.
+
+    # Arguments
+        x: input tensor.
+        filters: filters in `Conv2D`.
+        kernel_size: kernel size as in `Conv2D`.
+        strides: strides in `Conv2D`.
+        padding: padding mode in `Conv2D`.
+        activation: activation in `Conv2D`.
+        use_bias: whether to use a bias in `Conv2D`.
+        name: name of the ops; will become `name + '_ac'` for the activation
+            and `name + '_bn'` for the batch norm layer.
+
+    # Returns
+        Output tensor after applying `Conv2D` and `BatchNormalization`.
+    """
+    x = layers.Conv2D(filters,
+                      kernel_size,
+                      strides=strides,
+                      padding=padding,
[…]

### 2019-01-10 net_keras.py

@@ -3,6 +3,8 @@ from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, Paired
 from layers import GeometricLayer
 from resnet import inference
 
+from inception_resnet_v2 import InceptionResNetV2 as Irvn2
+
 
 class Net:
 	def __init__(self, size, activation, final_activation, prob_layer=None, num_channels=3, num_classes=5, spp_alpha=0.2, dropout=0):
@@ -187,7 +189,7 @@ class Net:
 
 		return model
 
-	def InceptionResNetV2(self):
+	def inception_resnet_v2(self):
 		model = tf.keras.Sequential()
 		inception = tf.keras.applications.inception_resnet_v2.InceptionResNetV2(include_top=False, input_shape=(self.size, self.size, self.num_channels), classes=self.num_classes)
 
@@ -216,6 +218,38 @@ class Net:
 			model.add(tf.keras.layers.Activation(self.final_activation))
 
 		return model
+
+	def inception_resnet_v2_custom(self):
+		model = tf.keras.Sequential()
+		inception = tf.keras.applications.NASNetLarge(include_top=False, input_shape=(self.size, self.size, self.num_channels),
+						  classes=self.num_classes)
+
+		# for layer in inception.layers:
+		# 	layer.trainable = False
+
+		model.add(inception)
+		model.add(tf.keras.layers.Flatten())
+
+		if self.dropout > 0:
+			model.add(tf.keras.layers.Dropout(rate=self.dropout))
+
+		if self.final_activation == 'poml':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'logit'))
+		elif self.final_activation == 'pomp':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'probit'))
+		elif self.final_activation == 'pomclog':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'cloglog'))
+		else:
+			model.add(tf.keras.layers.Dense(self.num_classes))
+			if self.prob_layer == 'geometric':
+				model.add(GeometricLayer())
+			model.add(tf.keras.layers.Activation(self.final_activation))
+
+		return model
+
 
 	def testing(self):
 		model = tf.keras.Sequential([

### 2019-01-11 paper/ieee.tex
Correcciones paper

@@
 \ifCLASSINFOpdf
-% \usepackage[pdftex]{graphicx}
+\usepackage[pdftex]{graphicx}
 % declare the path(s) where your graphic files are
@@
 
+\usepackage{dsfont}
+\usepackage{amssymb}
+
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 It is a simple and efficient function for multi-class problems but not the best when working with ordinal data.
-In this paper, the Proportional Odds Model (POM)~\cite{agresti2010analysis} will be used instead of the softmax function.
+In this paper, the Proportional Odds Model (POM)~\cite{gutierrez2016ordinal, agresti2010analysis} will be used instead of the softmax function.
 Different link functions will be explored to compare their performance.
@@
 
+	\section{Ordinal problem definition}
+	\label{sect:ordinalproblem}
+	The ordinal problem consists of predicting the label y of an input vector x, where $x \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
+x is in a K-dimensional input space, and $y$ is in a label space of $Q$ different labels.
+The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ points, $D = \{(x_i, y_i), i = 1, ..., N\}$.
+A natural label ordering exists for ordinal problems: $\mathcal{C}_1 \prec \mathcal{C}_2 \prec ...
+\prec \mathcal{C}_Q$.
+The assumption of order between class labels makes that two different elements of $\mathcal{Y}$ can always be compared by using the relation $\prec$, which is not possible under the nominal classification setting.
+In regression (where $y \in \mathds{R}$), real values in $\mathds{R}$ can be ordered by the standard $<$ operator, but labels in ordinal regression ($y \in \mathcal{Y}$) do not carry metric information, so the category serves as a qualitative indication of the pattern rather than a quantitative one.
+
+	\section{Proportional Odds Model}
+	\label{sect:pom}
+	Arising from a statistical background, the Proportional Odds Model (POM) is one of the first models designed explicitly for ordinal regression~\cite{mccullagh1980regression}, dated back to 1980.
+It is a member of a wider family of models recognised as Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
+CLMs predict probabilities of groups of contiguous categories, taking the ordinal scale into account.
+In this way, cumulative probabilities $P(y \prec Cj |x)$ are estimated, which can be directly related to standard probabilities:
+	\[
+		P(y \preceq \mathcal{C}_q | x) = P(y = \mathcal{C}_1 | x) + ... + P(y = \mathcal{C}_q | x),
+	\]
+	\[
+		P(y = \mathcal{C}_q | x) = P(y \preceq \mathcal{C}_q | x) - P(y \preceq \mathcal{C}_{q-1} | x),
+	\]
+	with $q = 2, ..., Q$, and considering that $P(y = \mathcal{C}_1 | x) = P(y \preceq \mathcal{C}_1 | x)$ and $P(y \preceq \mathcal{C}_Q | x) = 1$.
+
+	The model in inspired by the notion of latent variable, considering a linear transformation $f(x) = w^Tx$ of the input variables as the one-dimensional mapping.
+The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
+	\[
+		g^{-1}(P(y \preceq \mathcal{C}_q | x)) = b_q - w^Tx, \quad 1, ..., Q-1,
+	\]
+	where $g^{-1} : [0,1] \rightarrow (-\infty, +\infty)$ is a monotonic function often termed as the inverse link function and $b_q$ is the threshold defined for class $\mathcal{C}_q$.
+Consider the latent variable $y* = f(x)* = w^Tx + \epsilon$, where $\epsilon$ is the random error component.
+The most common choice for the distribution of $\epsilon$ is the logistic function (which is the default function for POM).
+Label $\mathcal{C}_q$ is observed if and only if $f(x) \in [b_{q-1}, b_q]$, where the function $f$ and $b = (b_0, b_1, ..., b_{Q-1}, b_Q)$ are to be determined from the data.
+it is assumed that $b_0 = -\infty$ and $b_Q = +\infty$, so the real line defined by $f(x), x \in \mathcal{X}$, is divided into $Q$ consecutive intervals.
+Each region corresponds to a category.
+The constraints $b_1 \le b_2 \le ...
+\le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | x)$ increases with $q$ \cite{mccullagh1980regression}.
+	In this work, we use this ordinal model with different link functions, including logit, probit and complementary log-log. These functions will be detailed in Section \ref{sect:model}.
 	\section{Experiments}
@@
 In this dataset, we try and predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
-The images are taken in variable conditions: by different cameras, illumination conditions and resolutions.
+The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions.
 These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform.
@@
 	\subsection{The model}
+	\label{sect:model}
 	A convolutional neural network (CNN) has been used for both datasets. The architecture of this CNN is presented in the Table \ref{table:CNNArchitecture}.
@@
 In this paper, we are comparing other link functions like probit or complementary log-log with the logit link.
-These three types of links are explained below.
+These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
 
 	\begin{itemize}
-		\item \textit{Logit}.
-Logit link function is the most widely used function for Proportional Odds Models.
-These kind of models are also called Cummulative Logit Models.
-The logit link is shown in Eq.
-\ref{eq:logit}.
+		\item \textit{Logit}. Logit link function is the most widely used function for Proportional Odds Models. The logit link is shown in \ref{eq:logit}.
 		\begin{equation}
-		logit[P(Y_i \le j)] = \alpha_j + \beta'x_i,\quad j = 1, ..., c - 1
+		logit[P(y \preceq \mathcal{C}_q)] = b_q - w^Tx, \quad 1, ..., Q-1
 		\label{eq:logit}
 		\end{equation}
-		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in Eq. \ref{eq:probit}.	
+		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in \ref{eq:probit}.	
 		\begin{equation}
-		\Phi^{-1}[P(Y \le j)] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
+		\Phi^{-1}[P(y \preceq \mathcal{C}_q)] = b_q - w^Tx, \quad 1, ..., Q-1
 		\label{eq:probit}
@@
 		\item \textit{Complementary log-log}.
-Unlike logit and probit, complementary log-log function is not symmetric.
+Like the logit and the probit transformation, the complementary log-log transformation takes a response that is restricted to the (0,1) interval and converts it into something in $(-\infty, +\infty)$ interval, but unlike the logit and the probit, the complementary log-log function is not symmetric.
 With a continuous predictor $x$, for example, $P(Y \le j)$ approaches 0 at a different rate than it approaches 1.
-Complementary log-log expression is shown in Eq.
-\ref{eq:cloglog}.
+Complementary log-log expression is shown in  \ref{eq:cloglog}.
 		\begin{equation}
 		\small
-		log[-log[1 - P(Y \le j)]] = \alpha_j + \beta'x,\quad j = 1, ..., c - 1
+		log[-log[1 - P(y \preceq \mathcal{C}_q)]] = b_q - w^Tx, \quad 1, ..., Q-1
 		\label{eq:cloglog}
@@
 	\end{itemize}
+
+	\begin{figure}[!t]
+		\centering
+		\includegraphics[width=2.5in]{img/linkfunctions.png}
+		\caption{Representation of link functions.}
+		\label{fig:linkfunctions}
+	\end{figure}
+
+	When the given data is not symmetric in the [0,1] interval and increase slowly at small to moderate value, but increases sharply near 1, the logit and probit models are inappropriate.
+However, in this situation, the complementary log-log model might give satisfying results.
 
@@
 
-	Quadratic Weighted Kappa Loss is considered as loss function for this optimizer as it gives better performance for ordinal classification problems.
-
 	Both datasets have been artificially equalised using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet} based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
@@
 
-	The model is evaluated with Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
+	The model is evaluated with Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}.
+This evaluation measure gives a higher weight to the errors that are further from the correct class.
+Quadratic Weighted Kappa Loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems.
 
@@
 
-	\subsection{Parameters}
-	Three different parameters have been considered: learning rate, batch size and link function for the final output layer.
+	\subsection{Factors}
+	Three different factors have been considered: learning rate, batch size and link function for the final output layer.
 
@@
 			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
-			$5$ & $10^{-2}$ & Logit & $0.44888$ & $0.4163$\\
+			$5$ & $10^{-2}$ & Logit & $0.44888$ & $0.41630$\\
 			& & Probit & $0.46724$ & $0.45972$\\
@@
 			& & c log-log & $0.53824$ & $0.51974$\\
-			$10$ & $10^{-2}$ & Logit & $0.5497$ & $0.53142$\\
+			$10$ & $10^{-2}$ & Logit & $0.54970$ & $0.53142$\\
 			& & Probit & $0.52124$ & $0.50806$\\
-			& & c log-log & $0.4276$ & $0.4227$\\
+			& & c log-log & $0.42760$ & $0.42270$\\
 			& $10^{-3}$ & Logit & $0.58036$ & $0.57686$\\
-			& & Probit & $0.56536$ & $0.5581$\\
-			& & c log-log & $\textbf{0.5883}$ & $\textbf{0.5815}$\\
-			& $10^{-4}$ & Logit & $0.53158$ & $0.5385$\\
-			& & Probit & $0.5456$ & $0.54082$\\
+			& & Probit & $0.56536$ & $0.55810$\\
+			& & c log-log & $\textbf{0.58830}$ & $\textbf{0.58150}$\\
+			& $10^{-4}$ & Logit & $0.53158$ & $0.53850$\\
+			& & Probit & $0.54560$ & $0.54082$\\
 			& & c log-log & $0.53928$ & $0.53742$\\
 			$15$ & $10^{-2}$ & Logit & $0.55828$ & $0.55076$\\
-			& & Probit & $0.54112$ & $0.5343$\\
+			& & Probit & $0.54112$ & $0.53430$\\
 			& & c log-log & $0.56676$ & $0.56428$\\
@@
 			& & Probit & $0.58182$ & $0.57894$\\
-			& & c log-log & $0.5634$ & $0.55938$\\
+			& & c log-log & $0.56340$ & $0.55938$\\
 			& $10^{-4}$ & Logit & $0.54686$ & $0.54342$\\
 			& & Probit & $0.53258$ & $0.53278$\\
-			& & c log-log & $0.539$ & $0.53828$
+			& & c log-log & $0.53900$ & $0.53828$
 		\end{tabular}
@@
 
-	\begin{table}[ht]
+	\begin{table}[!t]
 		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
@@
 			& & Probit & $0.77608$ & $0.72574$\\
-			& & c log-log & $0.7543$ & $0.70742$\\
-			& $10^{-3}$ & Logit & $0.7146$ & $0.67868$\\
+			& & c log-log & $0.75430$ & $0.70742$\\
+			& $10^{-3}$ & Logit & $0.71460$ & $0.67868$\\
 			& & Probit & $0.81906$ & $0.77154$\\
@@
 			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
-			& & Probit & $0.5436$ & $0.52422$\\
+			& & Probit & $0.54360$ & $0.52422$\\
 			& & c log-log & $0.54802$ & $0.52484$\\
 			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
-			& & Probit & $0.79332$ & $0.7475$\\
-			& & c log-log & $0.78004$ & $0.7326$\\
+			& & Probit & $0.79332$ & $0.74750$\\
+			& & c log-log & $0.78004$ & $0.73260$\\
 			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
@@
 			& & Probit & $0.70262$ & $0.65416$\\
-			& & c log-log & $0.49242$ & $0.4732$\\
+			& & c log-log & $0.49242$ & $0.47320$\\
 			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
-			& & Probit & $0.54288$ & $0.5174$\\
+			& & Probit & $0.54288$ & $0.51740$\\
 			& & c log-log & $0.53826$ & $0.52542$
@@
 	\label{sect:statisticalanalysis}
-	In this subsection, a statistical analysis will be performed in order to obtain robust conclusions from the results presented in this section.
+	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the results presented in this section.
 
@@
 
-	We denote by $W_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
+	We denote by $WK_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
 We assume that the two factors do not act independently and therefore there exists an interaction between them.
-In this case, the observations fit Eq.
-\ref{eq:anova3}.
+In this case, the observations fit \ref{eq:anova3}.
 
@@
 	\footnotesize
-	W_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l}
+	WK_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l}
 	\label{eq:anova3}
@@
 
-	\begin{table}[ht]
+	\begin{table}[!t]
 		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
@@
 			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
-			Model & $37.860$ & $9$ & $4.207$ & $1562.840$ & $.000$\\
-			$L$ factor & $.057$ & $2$ & $.029$ & $10.646$ & $.000$\\
-			$P$ factor & $.121$ & $2$ & $.060$ & $22.468$ & $.000$\\
-			$LP$ factors & $.057$ & $4$ & $.014$ & $5.261$ & $.001$\\
-			Error & $.339$ & $126$ & $.003$ & & \\
+			Model & $37.860$ & $9$ & $4.207$ & $1562.840$ & $0.000$\\
+			$L$ factor & $0.057$ & $2$ & $0.029$ & $10.646$ & $0.000$\\
+			$P$ factor & $0.121$ & $2$ & $0.060$ & $22.468$ & $0.000$\\
+			$LP$ factors & $0.057$ & $4$ & $0.014$ & $5.261$ & $0.001$\\
+			Error & $0.339$ & $126$ & $0.003$ & & \\
 			Total & $38.199$ & $135$ & & & 
@@
 
-	\begin{table}[ht]
+	\begin{table}[!t]
 		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
@@
 			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
-			Model & $52.328$ & $15$ & $3.489$ & $1426.170$ & $.000$\\
-			$L$ factor & $.027$ & $2$ & $.014$ & $5.582$ & $.005$\\
-			$P$ factor & $1.031$ & $2$ & $.516$ & $210.809$ & $.000$\\
-			$B$ factor & $.089$ & $2$ & $.045$ & $18.253$ & $.000$\\
-			$LP$ factors & $.183$ & $4$ & $.046$ & $18.695$ & $.000$\\
-			$PB$ factors & $.124$ & $4$ & $.031$ & $12.695$ & $.000$\\
-			Error & $.294$ & $120$ & $.002$ & & \\
+			Model & $52.328$ & $15$ & $3.489$ & $1426.170$ & $0.000$\\
+			$L$ factor & $0.027$ & $2$ & $0.014$ & $5.582$ & $0.005$\\
+			$P$ factor & $1.031$ & $2$ & $0.516$ & $210.809$ & $0.000$\\
+			$B$ factor & $0.089$ & $2$ & $0.045$ & $18.253$ & $0.000$\\
+			$LP$ factors & $0.183$ & $4$ & $0.046$ & $18.695$ & $0.000$\\
+			$PB$ factors & $0.124$ & $4$ & $0.031$ & $12.695$ & $0.000$\\
+			Error & $0.294$ & $120$ & $0.002$ & & \\
 			Total & $52.622$ & $135$ & $3.489$ & & 
@@
 
-	\begin{table}[ht]
+	\begin{table}[!t]
 		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
@@
 			Retinopathy & $5$ & $10^{-2}$ & $0.2210$ & $0.2050$\\
-			Retinopathy & $5$ & $10^{-3}$ & $0.2807$ & $0.2654$\\
-			Retinopathy & $5$ & $10^{-4}$ & $0.4580$ & $0.4449$\\
-
-			Retinopathy & $10$ & $10^{-2}$ & $0.2972$ & $0.2997$\\
-			Retinopathy & $10$ & $10^{-3}$ & $0.3972$ & $0.3989$\\
-			Retinopathy & $10$ & $10^{-4}$ & $\textbf{0.4972}$ & $\textbf{0.4967}$\\
-
-			Retinopathy & $15$ & $10^{-2}$ & $0.3692$ & $0.3676$\\
-			Retinopathy & $15$ & $10^{-3}$ & $0.4107$ & $0.4162$\\
-			Retinopathy & $15$ & $10^{-4}$ & $0.4929$ & $0.4859$\\
+			 & & $10^{-3}$ & $0.2807$ & $0.2654$\\
+			 & & $10^{-4}$ & $0.4580$ & $0.4449$\\
+
+			 & $10$ & $10^{-2}$ & $0.2972$ & $0.2997$\\
+			 &  & $10^{-3}$ & $0.3972$ & $0.3989$\\
+			 &  & $10^{-4}$ & $\textbf{0.4972}$ & $\textbf{0.4967}$\\
+
+			 & $15$ & $10^{-2}$ & $0.3692$ & $0.3676$\\
+			 & & $10^{-3}$ & $0.4107$ & $0.4162$\\
+			 & & $10^{-4}$ & $0.4929$ & $0.4859$\\
 			\hline
 			Adience & $5$ & $10^{-2}$ & $0.0605$ & $0.0769$\\
-			Adience & $5$ & $10^{-3}$ & $0.7994$ & $0.7313$\\
-			Adience & $5$ & $10^{-4}$ & $0.8009$ & $0.7383$\\
-
-			Adience & $10$ & $10^{-2}$ & $0.0559$ & $0.0576$\\
-			Adience & $10$ & $10^{-3}$ & $0.8239$ & $0.7436$\\
-			Adience & $10$ & $10^{-4}$ & $0.7938$ & $0.7218$\\
-
-			Adience & $15$ & $10^{-2}$ & $0.0593$ & $0.0713$\\
-			Adience & $15$ & $10^{-3}$ & $\textbf{0.8309}$ & $\textbf{0.7575}$\\
-			Adience & $15$ & $10^{-4}$ & $0.7867$ & $0.7129$\\
+			 & & $10^{-3}$ & $0.7994$ & $0.7313$\\
+			 & & $10^{-4}$ & $0.8009$ & $0.7383$\\
+
+			 & $10$ & $10^{-2}$ & $0.0559$ & $0.0576$\\
+			 & & $10^{-3}$ & $0.8239$ & $0.7436$\\
+			 & & $10^{-4}$ & $0.7938$ & $0.7218$\\
+
+			 & $15$ & $10^{-2}$ & $0.0593$ & $0.0713$\\
+			 & & $10^{-3}$ & $\textbf{0.8309}$ & $\textbf{0.7575}$\\
+			 & & $10^{-4}$ & $0.7867$ & $0.7129$\\
 		\end{tabular}

### 2019-01-14 paper/ieee.tex
Paper

@@
 
+\renewcommand{\bibfont}{\footnotesize}
+
 \begin{document}
@@
 Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables.
-Weighted Kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric.
+weighted kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric.
 These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk.
@@
 
-	This paper is organised as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this study.
+	This paper is organised as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this work.
 
@@
 		\centering
-		\includegraphics[width=2.5in]{img/linkfunctions.png}
+		\includegraphics[width=3in]{img/linkfunctions.png}
 		\caption{Representation of link functions.}
@@
 This evaluation measure gives a higher weight to the errors that are further from the correct class.
-Quadratic Weighted Kappa Loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems.
+Quadratic weighted kappa loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems.
 
@@
 	\subsection{Diabetic Retinopathy}
+	\label{sect:dr}
 	Detailed results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}.
@@
 
-	The best mean WK value was obtained with the complementary log-log link function using a batch size of 10 and a learning rate of $10^{-3}$.
+	The best mean QWK value was obtained with the complementary log-log link function using a batch size of 10 and a learning rate of $10^{-3}$.
 
 	\subsection{Adience}
+	\label{sect:adience}
 	Results for the experiments made with the Adience dataset are shown in Table \ref{table:Adienceresults}.
@@
 
-	The best mean WK value was obtained with the probit link function using a batch size of 15 and a learning rate of $10^{-2}$.
+	The best mean QWK value was obtained with the probit link function using a batch size of 15 and a learning rate of $10^{-2}$.
 
@@
 
-	We denote by $WK_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
-We assume that the two factors do not act independently and therefore there exists an interaction between them.
+	We denote by $QWK_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
+We assume that the three factors do not act independently and therefore there exists an interaction between each pair of them and between the three factors.
 In this case, the observations fit \ref{eq:anova3}.
@@
 	\footnotesize
-	WK_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l}
+	QWK_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l}
 	\label{eq:anova3}
@@
 
-	The analysis of variance table containing the sum of squares, degrees of freedom, mean square, test statistics and significance level represents the initial study in a compact form.
+	The analysis of variance table containing the sum of squares, degrees of freedom, mean square, test statistics and significance level represent the initial study in a compact form, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
+These factors and interactions take part of the error component now.
 
@@
 		\begin{tabular}{l|ccccc}
-			\multicolumn{6}{c}{Response variable WK}\\\hline
+			\multicolumn{6}{c}{Response variable QWK}\\\hline
 			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
@@
 	The results of the ANOVA III test for the Diabetic Retinopathy dataset are resumed in Table \ref{table:ANOVARetinopathy}.
-There are significative differences in the means depending on the link function and also depending on the learning rate for $\alpha=0.05$.
+There are significative differences in the means of QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$.
 Moreover, an interaction between the link function and the learning rate can be recognised ($\text{p-value} = 0.001$).
@@
 	As Table \ref{table:ANOVARetinopathy} showed that there exist significative differences between the means, we are now analysing those differences.
-A post-hoc multiple comparison test has been performed on the average WK obtained.
+A post-hoc multiple comparison test has been performed on the mean QWK obtained.
 An HSD Tukey's test was made under the null hypothesis that the variance of the error of the dependent variable is the same between groups.
@@
 	The results of the ANOVA III test for the Adience dataset are shown in Table \ref{table:ANOVAAdience}.
-The interactions where there are not significative differences have been omitted.
+The interactions where there are not significative differences in QWK means have been omitted.
 First, the factor associated with the link function is analysed.
@@
 Secondly, there are significative differences concerning the learning rate factor too ($\text{p-value} = 0.000$).
-Also, there are differences for the means for the batch size factor.
+Also, there are differences for the means of QWK for the batch size factor.
 Significative interactions exist between two pairs of factors: link function and learning rate, and learning rate and batch size ($\text{p-value = 0.000}$ for both cases).
 
-	A post-hoc multiple comparison test has been performed on the average WK obtained for this dataset too.
+	A post-hoc multiple comparison test has been performed on the average QWK obtained for this dataset too.
 Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been done.
-The results showed that the best link function is the logit one, in this case, with $0.632438$ as mean WK value.
+The results showed that the best link function is the logit one, in this case, with $0.60553$ as mean QWK value.
 However, there are not significative differences between this function and the complementary log-log ($\text{p-value}=0.110$).
 It has differences with the probit function though ($\text{p-value} = 0.003$).
-The complementary log-log link reported the best results after the logit function, having a mean WK of $0.611287$.
+The complementary log-log link reported the best results after the logit function, having a mean QWK of $0.58738$.
 However, it doesn't show significative differences with the probit function.
 	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
-The test reported significative differences between $\eta=10^{-2}$ (mean value $0.733784$) and the rest of values of this parameter ($\alpha=0.005$), being this one the best value for this factor.
-The best value after $10^{-2}$ is $10^{-3}$, which have a mean WK value of $0.579889$.
-Lastly, the best value for the batch size parameter is $10$ (mean value $0.648700$) as it has significative differences with the rest of values.
-The second best value is $5$ (mean $0.605533$), but it has no significative differences with $15$ ($\text{p-value}= 0.194$).
+The test reported significative differences between $\eta=10^{-2}$ (mean value $0.73378$) and the rest of values of this parameter ($\alpha=0.005$), being this one the best value for this factor.
+The best value after $10^{-2}$ is $10^{-3}$, which have a mean QWK value of $0.57989$.
+Lastly, the best value for the batch size parameter is $5$ (mean value $0.63243$) as it has significative differences with the rest of values.
+The second best value is $15$ (mean $0.61129$), but it has no significative differences with $10$ ($\text{p-value}= 0.194$).
+
+	To sum up, the results showed that the best parameter configuration depends on the problem that is being solved.
+None of the optimal parameters is the same for Retinopathy and Adience datasets.
+These results highlight the importance of adjusting the hyper-parameters for each problem that is treated instead of trying to find an optimal configuration for all the datasets.
 
@@
 	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
+The evaluation metric remains the same in order to be able to compare.
 The results for both datasets are shown in Table \ref{table:NominalResults}.
+There are some parameter configurations where the training process gets stagnated and a very low QWK is obtained.
+As we saw in Sections \ref{sect:dr} and \ref{sect:adience}, this problem is not present when using the ordinal method.
 
@@
 
-	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the WK metric.
+	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the QWK metric.
 So, we make an ANOVA II analysis for each dataset.
 
-	In the Diabetic Retinopathy dataset, there are significative differences between the mean values of WK depending on the batch size and the initial value of the learning rate.
+	In the Diabetic Retinopathy dataset, there are significative differences between the mean values of QWK depending on the batch size and the initial value of the learning rate.
 Also, no significative interaction was detected between these factors.
@@
 	A similar study was made for the Adience dataset.
-There are not significative differences for the mean value of WK w.r.t.
+There are not significative differences for the mean value of QWK w.r.t.
 the batch size factor.
@@
 
-	Finally, the conclusions of this study are exposed below:
+	The conclusions obtained from the results are exposed below:
 	\begin{itemize}
@@
 
+	Finally, a comparison of the best QWK for each dataset for ordinal and nominal cases is shown in Table \ref{table:ComparisonNomOrd}.
+Also, it is compared with previous works.
+The proposed ordinal model outperforms all the other alternatives.
+The performance increase of POM over softmax reaches $17.07\%$ for Diabetic Retinopathy and $3.85\%$ for Adience dataset.
+The enhancement of the ordinal method for Retinopathy dataset is more notable than the rise for Adience dataset.
+It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
+
+	\begin{table}[!t]
+		\caption{Comparison between the best QWK results of nominal, ordinal and previous works.}
+		\label{table:ComparisonNomOrd}
+		\footnotesize
+		\centering
+		\begin{tabular}{lccc|cc}
+			\multicolumn{6}{c}{Diabetic Retinopathy}\\
+			\hline
+			Method & BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
+			Ord. proposed & 10 & $10^{-3}$ & c log-log & $0.58830$ & $0.58150$\\
+			Nom. proposed & 10 & $10^{-4}$ & softmax & $0.49720$ & $0.49670$\\
+			Best from \cite{de2018weighted} & 20 & $10^{-4}$ & softmax & $0.53700$ & -\\
+			Best from \cite{nebot2016diabetic} & - & - & softmax & - & $0.55500$\\
+			\hline\hline
+			\multicolumn{6}{c}{Adience}\\
+			\hline
+			Ord. proposed & 15 & $10^{-2}$ & probit & $0.84254$ & $0.78666$\\
+			Nom. proposed & 15 & $10^{-3}$ & softmax & $0.83090$ & $0.75750$\\
+		\end{tabular}
+	\end{table}
+
 	\section{Conclusions}
@@
 
-	The proposed POM model has improved the performance of the deep network regarding Weighted Kappa compared to the model that uses the softmax function.
+	The proposed POM has improved the performance of the deep network regarding quadratic weighted kappa compared to the model that uses the softmax function.
 This enhancement is more notable for the Diabetic Retinopathy dataset.
 Also, it reduces the chance that the model gets stuck when training with some parameter configurations.
-So, the most significant improvements of these link functions are the WK performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
+So, the most significant improvements of these link functions are the QWK performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
 

### 2019-01-15 experiment.py
Beckham resnet. Split data script

@@ -552,6 +552,8 @@ class Experiment():
 			model = net_object.testing()
 		elif name == 'inceptionresnetv2':
 			model = net_object.inception_resnet_v2_custom()
+		elif name == 'beckhamresnet':
+			model = net_object.beckham_resnet()
 		else:
 			raise Exception('Invalid net type. You must select one of these: vgg19, conv128')
 
@@ -565,6 +567,8 @@ class Experiment():
 		"""
 		if db.lower() == 'retinopathy':
 			return "../retinopathy/128/train", "../retinopathy/128/val", "../retinopathy/128/test"
+		elif db.lower() == 'retinopathy256':
+			return "../retinopathy/256/train", "../retinopathy/256/val", "../retinopathy/256/test"
 		elif db.lower() == 'adience':
 			return "../adience/256/train", "../adience/256/val", "../adience/256/test"
 		elif db.lower() == 'cifar10' or db.lower() == 'cifar100':

### 2019-01-15 inception_resnet_v2.py

@@ -175,6 +175,8 @@ def inception_resnet_block(x, scale, block_type, block_idx, activation='relu'):
         x = layers.Activation(activation, name=block_name + '_ac')(x)
     return x
 
+from tensorflow.keras import utils as keras_utils
+from tensorflow.keras import backend, layers, models
 
 def InceptionResNetV2(include_top=True,
                       weights='imagenet',
@@ -226,8 +228,8 @@ def InceptionResNetV2(include_top=True,
         ValueError: in case of invalid argument for `weights`,
             or invalid input shape.
     """
-    global backend, layers, models, keras_utils
-    backend, layers, models, keras_utils = get_submodules_from_kwargs(kwargs)
+    # global backend, layers, models, keras_utils
+    # backend, layers, models, keras_utils = get_submodules_from_kwargs(kwargs)
 
     if not (weights in {'imagenet', None} or os.path.exists(weights)):
         raise ValueError('The `weights` argument should be either '

### 2019-01-15 main_experiment.py

@@ -25,7 +25,7 @@ def cli():
 @click.option('--rep', '-r', default=1, help=u'Repetitions for this execution.')
 @click.option('--dropout', '-o', default=0.0, help=u'Drop rate.')
 def train(db, net_type, batch_size, epochs, checkpoint_dir, loss, activation, final_activation, prob_layer, spp_alpha, lr, momentum, rep, dropout):
-	config = tf.ConfigProto()
+	config = tf.ConfigProto(allow_soft_placement=False)
 	config.gpu_options.allow_growth = True
 	tf.keras.backend.set_session(tf.Session(config=config))
 	for execution in range(1, rep + 1):

### 2019-01-15 net_keras.py

@@ -1,7 +1,7 @@
 import tensorflow as tf
 from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, NNPOM
 from layers import GeometricLayer
-from resnet import inference
+from resnet import Resnet_2x4
 
 from inception_resnet_v2 import InceptionResNetV2 as Irvn2
 
@@ -221,14 +221,38 @@ class Net:
 
 	def inception_resnet_v2_custom(self):
 		model = tf.keras.Sequential()
-		inception = tf.keras.applications.NASNetLarge(include_top=False, input_shape=(self.size, self.size, self.num_channels),
-						  classes=self.num_classes)
+		inception = Irvn2(include_top=False, input_shape=(self.size, self.size, self.num_channels),
+						  classes=self.num_classes, activation=self.activation)
 
 		# for layer in inception.layers:
 		# 	layer.trainable = False
 
 		model.add(inception)
 		model.add(tf.keras.layers.Flatten())
+
+		if self.dropout > 0:
+			model.add(tf.keras.layers.Dropout(rate=self.dropout))
+
+		if self.final_activation == 'poml':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'logit'))
+		elif self.final_activation == 'pomp':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'probit'))
+		elif self.final_activation == 'pomclog':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'cloglog'))
+		else:
+			model.add(tf.keras.layers.Dense(self.num_classes))
+			if self.prob_layer == 'geometric':
+				model.add(GeometricLayer())
+			model.add(tf.keras.layers.Activation(self.final_activation))
+
+		return model
+
+	def beckham_resnet(self):
+		resnet = Resnet_2x4((self.size, self.size, self.num_channels))
+		model = resnet.get_net()
 
 		if self.dropout > 0:
 			model.add(tf.keras.layers.Dropout(rate=self.dropout))

### 2019-01-15 resnet.py

@@ -1,217 +1,122 @@
-# Coder: Wenxin Xu
-# Github: https://github.com/wenxinxu/resnet_in_tensorflow
-# ==============================================================================
-'''
-This is the resnet structure
-'''
-import numpy as np
-import tensorflow as tf
+# -*- coding: utf-8 -*-
+
+from tensorflow.keras.regularizers import l2
+
+from tensorflow.keras.models import Model, Sequential
+from tensorflow.keras.initializers import Constant, he_normal
+from tensorflow.keras.layers import Input, Conv2D, MaxPooling2D, AveragePooling2D, \
+	Dense, Flatten, Activation, ZeroPadding2D, \
+	Add, Activation, BatchNormalization, GlobalAveragePooling2D
 
 
-BN_EPSILON = 0.001
+def _residual_block(layer, n_out_channels, stride=1, nonlinearity='relu'):
+	"""Crea un bloque residual de la red.
 
-def activation_summary(x):
-    '''
-    :param x: A Tensor
-    :return: Add histogram summary and scalar summary of the sparsity of the tensor
-    '''
-    tensor_name = x.op.name
-    tf.summary.histogram(tensor_name + '/activations', x)
-    tf.summary.scalar(tensor_name + '/sparsity', tf.nn.zero_fraction(x))
-
-
-def create_variables(name, shape, initializer=tf.contrib.layers.xavier_initializer(), is_fc_layer=False):
-    '''
-    :param name: A string. The name of the new variable
-    :param shape: A list of dimensions
-    :param initializer: User Xavier as default.
-    :param is_fc_layer: Want to create fc layer variable? May use different weight_decay for fc
-    layers.
-    :return: The created variable
-    '''
-    
-    ## TODO: to allow different weight decay to fully connected layer and conv layer
-    regularizer = tf.contrib.layers.l2_regularizer(scale=0.0002)
-
-    new_variables = tf.get_variable(name, shape=shape, initializer=initializer,
-                                    regularizer=regularizer)
-    return new_variables
-
-
-def output_layer(input_layer, num_labels):
-    '''
-    :param input_layer: 2D tensor
-    :param num_labels: int. How many output labels in total? (10 for cifar10 and 100 for cifar100)
-    :return: output layer Y = WX + B
-    '''
-    input_dim = input_layer.get_shape().as_list()[-1]
[…]

### 2019-01-15 split_data.py

@@ -1,0 +1,85 @@
+import os
+import pandas as pd
+import numpy as np
+from shutil import copyfile
+from sklearn.model_selection import StratifiedShuffleSplit
+
+train_path = '../retinopathy/train_small_bmp'
+train_labels = '../retinopathy/trainLabels.csv'
+train_ext = '.bmp'
+test_path = '../retinopathy/test_small_bmp'
+test_labels = '../retinopathy/testLabels.csv'
+test_ext = '.bmp'
+
+train_dest = '../retinopathy/256/train'
+val_dest = '../retinopathy/256/val'
+test_dest = '../retinopathy/256/test'
+
+try:
+	os.makedirs(train_dest)
+except OSError as exc:
+	pass
+
+try:
+	os.makedirs(val_dest)
+except OSError as exc:
+	pass
+
+try:
+	os.makedirs(test_dest)
+except OSError as exc:
+	pass
+
+# TRAIN
+
+df = pd.read_csv(train_labels)
+data = np.array(df)
+
+sss = StratifiedShuffleSplit(n_splits=1, test_size=0.1, random_state=1)
+splits = sss.split(data[:,0], data[:,1])
+for train_indices, val_indices in splits:
+	for train_index in train_indices:
+		img, label = data[train_index]
+		try:
+			os.makedirs(os.path.join(train_dest, str(label)))
+		except OSError as exc:
+			pass
+
+		src = os.path.join(train_path, "{}{}".format(img, train_ext))
+		dst = os.path.join(train_dest, str(label), "{}{}".format(img, train_ext))
+
+		if os.path.isfile(src) and not os.path.isfile(dst):
+			copyfile(src, dst)
+			print("Copied {} to {}".format(src, dst))
+
+	for val_index in val_indices:
+		img, label = data[val_index]
+		try:
+			os.makedirs(os.path.join(val_dest, str(label)))
+		except OSError as exc:
+			pass
+
+		src = os.path.join(train_path, "{}{}".format(img, train_ext))
+		dst = os.path.join(val_dest, str(label), "{}{}".format(img, train_ext))
+
+		if os.path.isfile(src) and not os.path.isfile(dst):
+			copyfile(src, dst)
+			print("Copied {} to {}".format(src, dst))
+
+# TEST
+
+df = pd.read_csv(test_labels)
+data = np.array(df)
+
+for img, label, _ in data:
+	try:
+		os.makedirs(os.path.join(test_dest, str(label)))
[…]

### 2019-01-28 paper/ieee.tex
Correcciones paper. H5 r

@@
 They proved that ELUs alleviate the vanishing gradient problem via the identity for positive values.
-In their experiments, ELUs lead not only to faster learning but also to significantly better generalization performance than ReLUs and LReLUs on networks with more than five layers.
+In their experiments, ELUs lead not only to faster learning but also to significantly better generalization performance than ReLUs and Leaky ReLU functions (LReLU) on networks with more than five layers.
 That's why we decided to use the ELU function for the experiments described in this paper.
@@
 	\label{sect:ordinalproblem}
-	The ordinal problem consists of predicting the label y of an input vector x, where $x \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
-x is in a K-dimensional input space, and $y$ is in a label space of $Q$ different labels.
+	The ordinal problem consists of predicting the label y of an input vector $\mathbf{x}$, where $\mathbf{x} \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
+$\mathbf{x}$ is in a K-dimensional input space, and $y$ is in a label space of $Q$ different labels.
 The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ points, $D = \{(x_i, y_i), i = 1, ..., N\}$.
@@
 CLMs predict probabilities of groups of contiguous categories, taking the ordinal scale into account.
-In this way, cumulative probabilities $P(y \prec Cj |x)$ are estimated, which can be directly related to standard probabilities:
-	\[
-		P(y \preceq \mathcal{C}_q | x) = P(y = \mathcal{C}_1 | x) + ... + P(y = \mathcal{C}_q | x),
-	\]
-	\[
-		P(y = \mathcal{C}_q | x) = P(y \preceq \mathcal{C}_q | x) - P(y \preceq \mathcal{C}_{q-1} | x),
-	\]
-	with $q = 2, ..., Q$, and considering that $P(y = \mathcal{C}_1 | x) = P(y \preceq \mathcal{C}_1 | x)$ and $P(y \preceq \mathcal{C}_Q | x) = 1$.
-
-	The model in inspired by the notion of latent variable, considering a linear transformation $f(x) = w^Tx$ of the input variables as the one-dimensional mapping.
+In this way, cumulative probabilities $P(y \prec Cj |\mathbf{x})$ are estimated, which can be directly related to standard probabilities:
+	\begin{equation}
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = P(y = \mathcal{C}_1 | \mathbf{x}) + ... + P(y = \mathcal{C}_q | \mathbf{x}),
+	\end{equation}
+	\begin{equation}
+		P(y = \mathcal{C}_q | \mathbf{x}) = P(y \preceq \mathcal{C}_q | \mathbf{x}) - P(y \preceq \mathcal{C}_{q-1} | \mathbf{x}),
+	\end{equation}
+	with $q = 2, ..., Q-1$, and considering that $P(y = \mathcal{C}_1 | \mathbf{x}) = P(y \preceq \mathcal{C}_1 | \mathbf{x})$ and $P(y \preceq \mathcal{C}_Q | \mathbf{x}) = 1$.
+
+	The model in inspired by the notion of latent variable, considering a linear transformation $f(x) = \mathbf{w^Tx}$ of the input variables as the one-dimensional mapping.
 The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
-	\[
-		g^{-1}(P(y \preceq \mathcal{C}_q | x)) = b_q - w^Tx, \quad 1, ..., Q-1,
-	\]
+	\begin{equation}
+		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - \mathbf{w^Tx}, \quad 1, ..., Q-1,
+	\end{equation}
 	where $g^{-1} : [0,1] \rightarrow (-\infty, +\infty)$ is a monotonic function often termed as the inverse link function and $b_q$ is the threshold defined for class $\mathcal{C}_q$.
-Consider the latent variable $y* = f(x)* = w^Tx + \epsilon$, where $\epsilon$ is the random error component.
-The most common choice for the distribution of $\epsilon$ is the logistic function (which is the default function for POM).
-Label $\mathcal{C}_q$ is observed if and only if $f(x) \in [b_{q-1}, b_q]$, where the function $f$ and $b = (b_0, b_1, ..., b_{Q-1}, b_Q)$ are to be determined from the data.
+Consider the latent variable $y^* = f(x)^* = \mathbf{w^Tx} + \epsilon$, where $\epsilon$ is the random variable of the error.
+The most common choice for the probability distribution of $\epsilon$ is the logistic function (which is the default function for POM).
+Label $\mathcal{C}_q$ is proposed if and only if $f(x) \in [b_{q-1}, b_q]$, where the function $f$ and $\mathbf{b} = (b_0, b_1, ..., b_{Q-1}, b_Q)$ are to be determined from the data.
 it is assumed that $b_0 = -\infty$ and $b_Q = +\infty$, so the real line defined by $f(x), x \in \mathcal{X}$, is divided into $Q$ consecutive intervals.
-Each region corresponds to a category.
+Each interval corresponds to a category.
 The constraints $b_1 \le b_2 \le ...
-\le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | x)$ increases with $q$ \cite{mccullagh1980regression}.
-	In this work, we use this ordinal model with different link functions, including logit, probit and complementary log-log. These functions will be detailed in Section \ref{sect:model}.
+\le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | \mathbf{x})$ increases with $q$ \cite{mccullagh1980regression}.
+	In this work, we use this ordinal model with different link functions for the probability distribution of $\epsilon$, including logit, probit and complementary log-log.
+These functions will be detailed in Section \ref{sect:model}.
 	\section{Experiments}
@@
 	\label{sect:model}
-	A convolutional neural network (CNN) has been used for both datasets. The architecture of this CNN is presented in the Table \ref{table:CNNArchitecture}.
+	Convolutional Neural Networks (CNN) has been used for both datasets.
+The different architectures of CNN used in these experiments are presented in tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
+The architecture for DR is the same that was used in \cite{de2018weighted} and the network for adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
+For convolutional layers, ConvWxH@FsS = F filters of size WxH and stride S.
+For pooling layers, PoolWxHsS = pool size of WxH and stride S.
 
 	\begin{table}[!t]
-		\caption{Description of the architecture used in the experiments.
-For convolutional layers, Conv\_N\_WxH, where N is the number of filters, W the filter width and H the filter height.
-Stride is 1 for every convolutional layer.
-For max pool layers, MaxPool\_SxS, where S is the pool size.}
+		\caption{Description of the architecture used in the DR experiments.}
 		\label{table:CNNArchitecture}
@@
 			\hline
-			Conv\_32\_3x3 & 254x254x32\\\hline
-			Conv\_32\_3x3 & 252x252x32\\\hline
-			MaxPool\_2x2 & 126x126x32\\\hline
-
-			Conv\_64\_3x3 & 124x124x64\\\hline
-			Conv\_64\_3x3 & 122x122x64\\\hline
-			MaxPool\_2x2 & 61x61x64\\\hline
-
-			Conv\_128\_3x3 & 59x59x128\\\hline
-			Conv\_128\_3x3 & 57x57x128\\\hline
-			MaxPool\_2x2 & 28x28x128\\\hline
-
-			Conv\_128\_3x3 & 26x26x128\\\hline
-			Conv\_128\_3x3 & 24x24x128\\\hline
-			MaxPool\_2x2 & 12x12x128\\\hline
-
-			Conv\_128\_4x4 & 9x9x128\\\hline
-			Dense\_1\_output & 1\\
+			Conv3x3@32s1 & 254x254x32\\\hline
+			Conv3x3@32s1 & 252x252x32\\\hline
+			MaxPool2x2s2 & 126x126x32\\\hline
+
+			Conv3x3@64s1 & 124x124x64\\\hline
+			Conv3x3@64s1 & 122x122x64\\\hline
+			MaxPool2x2s2 & 61x61x64\\\hline
+
+			Conv3x3@128s1 & 59x59x128\\\hline
+			Conv3x3@128s1 & 57x57x128\\\hline
+			MaxPool2x2s2 & 28x28x128\\\hline
+
+			Conv3x3@128s1 & 26x26x128\\\hline
+			Conv3x3@128s1 & 24x24x128\\\hline
+			MaxPool2x2s2 & 12x12x128\\\hline
+
+			Conv4x4@128s1 & 9x9x128\\
 			\hline
@@
 
-	Every convolutional layer is followed by an ELU activation layer~\cite{clevert2015fast} and a batch normalization~\cite{ioffe2015batch}.
-At the output, a Proportional Odds Model is used with different link functions~\cite{agresti2010analysis}.
-The logit link function is commonly used within POM.
-In this paper, we are comparing other link functions like probit or complementary log-log with the logit link.
-These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
-
-	\begin{itemize}
-		\item \textit{Logit}. Logit link function is the most widely used function for Proportional Odds Models. The logit link is shown in \ref{eq:logit}.
-		\begin{equation}
-		logit[P(y \preceq \mathcal{C}_q)] = b_q - w^Tx, \quad 1, ..., Q-1
-		\label{eq:logit}
-		\end{equation}
-		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf). Its expression is shown in \ref{eq:probit}.	
-		\begin{equation}
-		\Phi^{-1}[P(y \preceq \mathcal{C}_q)] = b_q - w^Tx, \quad 1, ..., Q-1
-		\label{eq:probit}
-		\end{equation}
-		\item \textit{Complementary log-log}.
-Like the logit and the probit transformation, the complementary log-log transformation takes a response that is restricted to the (0,1) interval and converts it into something in $(-\infty, +\infty)$ interval, but unlike the logit and the probit, the complementary log-log function is not symmetric.
-With a continuous predictor $x$, for example, $P(Y \le j)$ approaches 0 at a different rate than it approaches 1.
-Complementary log-log expression is shown in  \ref{eq:cloglog}.
-		\begin{equation}
-		\small
-		log[-log[1 - P(y \preceq \mathcal{C}_q)]] = b_q - w^Tx, \quad 1, ..., Q-1
-		\label{eq:cloglog}
-		\end{equation}
-	\end{itemize}
+	\begin{table}[!t]
+		\caption{Description of the architecture used in the Adience experiments.}
+		\label{table:ResNetArchitecture}
+		\centering
+		\begin{tabular}{|l|c|}
+			\hline
+			\textbf{Layer} & \textbf{Output shape}\\
+			\hline
+			Conv7x7@32s2 & 112x112x32\\\hline
+			MaxPool3x3s2 & 55x55x32\\\hline
+			2 x ResBlock3x3@64s1 & 55x55x32\\\hline
+			1 x ResBlock3x3@128s2 & 28x28x64\\\hline
+			2 x ResBlock3x3@128s1 & 28x28x64\\\hline
+			1 x ResBlock3x3@256s2 & 14x14x128\\\hline
+			2 x ResBlock3x3@256s1 & 14x14x128\\\hline
+			1 x ResBlock3x3@512s2 & 7x7x256\\\hline
+			2 x ResBlock3x3@512s1 & 7x7x256\\\hline
+			AveragePool7x7s2 & 1x1x256\\
+			\hline
+		\end{tabular}	
+	\end{table}
 
@@
 
-	When the given data is not symmetric in the [0,1] interval and increase slowly at small to moderate value, but increases sharply near 1, the logit and probit models are inappropriate.
-However, in this situation, the complementary log-log model might give satisfying results.
+	Every convolutional layer is followed by an ELU activation layer~\cite{clevert2015fast} and a batch normalization~\cite{ioffe2015batch}.
+At the output, a Proportional Odds Model is used with different link functions~\cite{agresti2010analysis}.
+The logit link function is commonly used within POM.
+In this paper, we are comparing other link functions like probit or complementary log-log with the logit link.
+These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
+They all follow the same form $P(y \prec \mathcal{C}_q) = \Phi(b_q-\mathbf{w^Tx})$ for a continuous cdf~$\Phi$.
+
+	\begin{itemize}
+		\item \textit{Logit}. Logit link function is the most widely used function for Proportional Odds Models. The logit link is shown in \ref{eq:logit} and \ref{eq:logit2}.
+		\begin{equation}
+		\begin{aligned}
+		logit[P(y \preceq \mathcal{C}_q)] = log\frac{P(y \preceq \mathcal{C}_q)}{1 - P(y \preceq \mathcal{C}_q)}=& \\ = b_q - \mathbf{w^Tx}, \quad q = 1, ..., Q-1
+		\end{aligned}
+		\label{eq:logit}
+		\end{equation}
+
+		or the equivalent expression
+
+		\begin{equation}
+		P(y \preceq \mathcal{C}_q) = \frac{1}{1 + e^{-(b-\mathbf{w^Tx})}}
+		\label{eq:logit2}
+		\end{equation}
+		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf) $\Phi$. Its expression is shown in \ref{eq:probit} and \ref{eq:probit2}.	
+		\begin{equation}
+		\begin{aligned}
+		&\Phi^{-1}[P(y \preceq \mathcal{C}_q)] = b_q - \mathbf{w^Tx}, &q = 1, ..., Q-1\\
+		&P(y \preceq \mathcal{C}_q) = \Phi(b_q - \mathbf{w^Tx}), &q = 1, ..., Q-1		
+		\end{aligned}
+		\label{eq:probit}
+		\end{equation}
+
+		or
+
+		\begin{equation}
+		P(y \preceq \mathcal{C}_q) = \int_{-\infty}^{b_q - \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
+		\label{eq:probit2}
+		\end{equation}
+
+		\item \textit{Complementary log-log}.
+Like the logit and the probit transformation, the complementary log-log transformation takes a response that is restricted to the (0,1) interval and converts it into something in $(-\infty, +\infty)$ interval.
+Complementary log-log expression is shown in \ref{eq:cloglog} and \ref{eq:cloglog2}.
+		\begin{equation}
+		\begin{aligned}
+		log[-log[1 - P(y \preceq \mathcal{C}_q)]] =&\\
+		= b_q - \mathbf{w^Tx}, \quad q = 1, ..., Q-1&
+		\end{aligned}
+		\label{eq:cloglog}
+		\end{equation}
+
+		or
+
+		\begin{equation}
+		P(y \preceq \mathcal{C}_q) = 1 - e^{-e^{b_q - \mathbf{w^Tx}}}, \quad q = 1, ..., Q-1
+		\label{eq:cloglog2}
+		\end{equation}
+	\end{itemize}
+
+	Logit and probit links are symmetric, that is
+
+	\begin{equation}
+	link[P(y \preceq \mathcal{C}_q)] = -link[1 - P(y \preceq \mathcal{C}_q)]
+	\end{equation}
+
+	This means that the response curve for $P(y \preceq \mathcal{C}_q)$ has a symmetric appearance about the point $P(y \preceq \mathcal{C}_q) = 0.5$, and so $P(y \preceq \mathcal{C}_q)$ has the same rate for approaching 0 than for approaching 1.
+This symmetric property can be demonstrated as follows:
+
+	\begin{enumerate}
+		\item If we define $P(y \preceq \mathcal{C}_q) \equiv p$, we have
+			\begin{equation}
+			\begin{aligned}
+			link(p) = logit(p) &= log\left(\frac{p}{1-p}\right) =\\
+			&= log(p) - log(1-p)
+			\end{aligned}
+			\end{equation}
+
+			while
+
+			\begin{equation}
+			\begin{aligned}
+			-link(1 - p) &= -logit(1 - p) =\\
+			=- log\left(\frac{1- p}{p}\right) &= - log(1 - p) + log(p)
+			\end{aligned}
+			\end{equation}
+
+			The symmetry has been proven for logit link.
+
+		\item If we define
+
+		\begin{equation}
+		\begin{aligned}
+		p \equiv P(y \preceq \mathcal{C}_q) &= \Phi(b_q - \mathbf{w^Tx}) =\\
+		&= \int_{-\infty}^{b_q - \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
+		\end{aligned}
+		\end{equation}
+
+		then
+
+		\begin{equation}
+		probit(p) = \Phi^{-1}(p) = b_q - \mathbf{w^Tx}
+		\end{equation}
+
+		and
+
+		\begin{equation}
+		-probit(1-p) = \Phi^{-1}(1-p) = -b_q + \mathbf{w^Tx}
+		\end{equation}
+
+		where
+
+		\begin{equation}
+		1 - p = \int_{-\infty}^{-b_q + \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
+		\end{equation}
+
+		and
+
+		\begin{equation}
+		p = 1 - \int_{-\infty}^{-b_q + \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
+		\end{equation}
+
+		the symmetric property for the probit function has been proven.
+	\end{enumerate}
+
+	Unlike logit and probit, the complementary log-log model is asymmetrical.
+It is frequently used when the probability of an event is very small or very large.
+When the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the logit and probit models are inappropriate.
+However, in this situation, the complementary log-log model might give a satisfying answer.
 

### 2019-01-28 dataset.py

@@ -120,7 +120,7 @@ class Dataset():
 		assert(len(self._data['x']) == len(self._data['y']))
 
 	def _load_from_h5(self, path):
-		with h5py.File(path, 'r+') as f:
+		with h5py.File(path, 'r') as f:
 			keys = list(f.keys())
 
 			if 'x' in keys and 'y' in keys:

### 2019-01-28 results.py

@@ -6,7 +6,7 @@ import pickle
 import os
 import prettytable
 
-results_path = '../results_adience'
+results_path = '../results_adience_h5'
 evaluation_file = 'evaluation.pickle'
 
 
@@ -78,6 +78,89 @@ def show_confusion_matrices():
 	print(t)
 
 
+def show_latex_table():
+	header, train, val, test = '', '', '', ''
+	for item in sorted(os.listdir(results_path)):
+		if os.path.isdir(os.path.join(results_path, item)):
+			metrics = {'Train' : {}, 'Validation' : {}, 'Test' : {}}
+			count = len(os.listdir(os.path.join(results_path, item)))
+			for item2 in sorted(os.listdir(os.path.join(results_path, item))):
+				if os.path.isdir(os.path.join(results_path, item, item2)) and os.path.isfile(
+						os.path.join(results_path, item, item2, evaluation_file)):
+					with open(os.path.join(results_path, item, item2, evaluation_file), 'rb') as f:
+						p = pickle.load(f)
+
+						for metric, value in p['metrics']['Train'].items():
+							if metric != 'Confusion matrix':
+								if metric in metrics['Train']:
+									metrics['Train'][metric] += value / count
+								else:
+									metrics['Train'][metric] = value / count
+
+						for metric, value in p['metrics']['Validation'].items():
+							if metric != 'Confusion matrix':
+								if metric in metrics['Validation']:
+									metrics['Validation'][metric] += value / count
+								else:
+									metrics['Validation'][metric] = value / count
+
+						for metric, value in p['metrics']['Test'].items():
+							if metric != 'Confusion matrix':
+								if metric in metrics['Test']:
+									metrics['Test'][metric] += value / count
+								else:
+									metrics['Test'][metric] = value / count
+			
+			if header == '':
+				header = 'Dataset & BS & LR & LF'
+
+				for metric, value in metrics['Train'].items():
+					if metric != 'Confusion matrix':
+						header += ' & {}'.format(metric)
+
+				header += '\\\\\\hline'
+
+			t = '{} & {} & {} & {}'.format(
+				p['config']['db'],
+				p['config']['batch_size'],
+				p['config']['lr'],
+				p['config']['final_activation'])
+
+			train += t
+			val += t
+			test += t
+
+			for metric, value in metrics['Train'].items():
+				if metric != 'Confusion matrix':
[…]

### 2019-02-05 tools.py
tools improvement

@@ -88,7 +88,9 @@ def show_latex_table(results_path, show_std=False):
 				if os.path.isdir(os.path.join(results_path, item, item2)) and os.path.isfile(
 						os.path.join(results_path, item, item2, evaluation_file)):
 					with open(os.path.join(results_path, item, item2, evaluation_file), 'rb') as f:
-						p = pickle.load(f)
+						p_aux = pickle.load(f)
+						if p_aux is not None:
+							p = p_aux
 
 						for metric, value in p['metrics']['Train'].items():
 							if metric != 'Confusion matrix':
@@ -110,21 +112,28 @@ def show_latex_table(results_path, show_std=False):
 									metrics['Test'][metric].append(value)
 								else:
 									metrics['Test'][metric] = [value]
-			
+
+			if not 'p' in locals():
+				continue
+
 			if header == '':
-				header = 'Dataset & BS & LR & LF'
+				header = 'Dataset & BS & LF & LR'
 
 				for metric, value in metrics['Train'].items():
 					if metric != 'Confusion matrix':
-						header += ' & {}'.format(metric)
+						header += ' & $\overline{{\\text{{{}}}}}{}$'.format(metric, '_{{(SD)}}' if show_std else '')
 
 				header += '\\\\\\hline'
 
 			t = '{} & {} & {} & {}'.format(
 				p['config']['db'],
 				p['config']['batch_size'],
-				p['config']['lr'],
-				p['config']['final_activation'])
+				p['config']['final_activation'].replace('poml', 'logit')
+												 .replace('pomp', 'probit')
+												 .replace('pomclog', 'c log-log'),
+			'${:.0E}}}$'.format(p['config']['lr']).replace('E-0', '0^{-')
+				.replace('E+0', '0^{+')
+			)
 
 			train += t
 			val += t
@@ -132,27 +141,27 @@ def show_latex_table(results_path, show_std=False):
 
 			for metric, values in metrics['Train'].items():
 				if metric != 'Confusion matrix':
-					train += ' & ${:.5f}'.format(round(np.mean(values), 5))
+					train += ' & ${:.3f}'.format(round(np.mean(values), 3))
 					if show_std:
-						train += ' \pm {:.2f}'.format(round(np.std(values), 2))
+						train += '_{{({:.3f})}}'.format(round(np.std(values), 3))
 					train += '$'
 
 			train += '\\\\\n'
 
[…]

### 2019-02-06 paper/ieee.tex
Paper update

@@
 Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables.
-weighted kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric.
+Weighted kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric.
 These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk.
@@
 
-	This paper is organised as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper, in Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this work.
+	This paper is organized as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper.
+Sections~\ref{sect:ordinalproblem} and \ref{sect:pom} present a formal description of an ordinal problem and the Proportional Odds Model.
+In Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this work.
 
@@
 They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, and they obtained promising results.
+
+	Adience dataset has been used in other works for human age estimation.
+E.
+Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks.
+J.-C.
+Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep convolutional networks.
+G.
+Levi \cite{levi2015age} presented another convolutional network model for age estimation.
 
@@
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
-The images are resized to 128 by 128 pixels.
+The images are resized to 128 by 128 pixels and rescaled to $[0,1]$ range.
 Data augmentation techniques are applied to achieve a higher number of samples.
@@
 
-	Both datasets have been artificially equalised using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet} based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
-In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch.
-For the Adience dataset, epoch size is the number of images in the training set.
+	Both datasets have been artificially equalized using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet}.
+However, different transformations were applied to each one.
+Diabetic Retinopathy dataset augmentation was based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
+Horizontal flipping was the only transformation applied to Adience dataset.
+
+	In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch. For the Adience dataset, epoch size is the number of images in the training set.
 
@@
 Quadratic weighted kappa loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems.
+
+	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS), Mean Absolute Error (MAE), Mean Squared Error (MSE), Correct Classification Rate (CCR), Top-2 CCR, Top-3 CCR and 1-off accuracy.
 
@@
 It can affect the training time and the model performance.
-In this paper, we have tried three separate batch sizes: $5$, $10$ and $15$.
+In this paper, we have tried three separate batch sizes for each dataset.
+For DR dataset, we have used $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ was used.
+We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expanded the range on both sides.
 		\item \textit{Link function}. Different link functions have been used for the POM at the last layer output: logit, probit and complementary log-log.
@@
 Every parameter combination has been run five times.
-These tables show the average quadratic weighted kappa across these five executions for validation and test values.
+These tables show the mean value and the standard deviation of each metric across these five executions for the test set.
+These values are exposed using the format $\text{MEAN}_{(SD)}$.
 
@@
 
-	\begin{table}[!t]
-		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+	\begin{table*}[!t]
+		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LF for link function and LR for Learning Rate.}
 		\label{table:DRresults}
@@
 		\centering
-		\begin{tabular}{ccc|cc}
-			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
-			$5$ & $10^{-2}$ & Logit & $0.44888$ & $0.41630$\\
-			& & Probit & $0.46724$ & $0.45972$\\
-			& & c log-log & $0.42854$ & $0.41448$\\
-			& $10^{-3}$ & Logit & $0.56496$ & $0.55356$\\
-			& & Probit & $0.57084$ & $0.56392$\\
-			& & c log-log & $0.54796$ & $0.53436$\\
-			& $10^{-4}$ & Logit & $0.52884$ & $0.52032$\\
-			& & Probit & $0.53802$ & $0.52302$\\
-			& & c log-log & $0.53824$ & $0.51974$\\
-			$10$ & $10^{-2}$ & Logit & $0.54970$ & $0.53142$\\
-			& & Probit & $0.52124$ & $0.50806$\\
-			& & c log-log & $0.42760$ & $0.42270$\\
-			& $10^{-3}$ & Logit & $0.58036$ & $0.57686$\\
-			& & Probit & $0.56536$ & $0.55810$\\
-			& & c log-log & $\textbf{0.58830}$ & $\textbf{0.58150}$\\
-			& $10^{-4}$ & Logit & $0.53158$ & $0.53850$\\
-			& & Probit & $0.54560$ & $0.54082$\\
-			& & c log-log & $0.53928$ & $0.53742$\\
-			$15$ & $10^{-2}$ & Logit & $0.55828$ & $0.55076$\\
-			& & Probit & $0.54112$ & $0.53430$\\
-			& & c log-log & $0.56676$ & $0.56428$\\
-			& $10^{-3}$ & Logit & $0.55748$ & $0.55106$\\
-			& & Probit & $0.58182$ & $0.57894$\\
-			& & c log-log & $0.56340$ & $0.55938$\\
-			& $10^{-4}$ & Logit & $0.54686$ & $0.54342$\\
-			& & Probit & $0.53258$ & $0.53278$\\
-			& & c log-log & $0.53900$ & $0.53828$
+		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c|c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
+			5 & c log-log & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.165_{(0.020)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
+			5 & c log-log & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.123_{(0.004)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
+			5 & c log-log & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.104_{(0.001)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
+			5 & logit & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.162_{(0.018)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
+			5 & logit & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.123_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
+			5 & logit & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.102_{(0.001)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
+			5 & probit & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.182_{(0.053)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
+			5 & probit & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.132_{(0.014)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
+			5 & probit & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.105_{(0.001)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
+			10 & c log-log & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.120_{(0.014)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
+			10 & c log-log & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.115_{(0.002)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
+			10 & c log-log & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.096_{(0.001)}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
+			10 & logit & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.140_{(0.008)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
+			10 & logit & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.113_{(0.004)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
+			10 & logit & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.095_{(0.002)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
+			10 & probit & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.137_{(0.014)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
+			10 & probit & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.120_{(0.002)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
+			10 & probit & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.098_{(0.001)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
+			15 & c log-log & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.134_{(0.005)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
+			15 & c log-log & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
+			15 & c log-log & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $\mathit{0.093_{(0.001)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
+			15 & logit & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.129_{(0.009)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
+			15 & logit & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.114_{(0.005)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
+			15 & logit & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.090_{(0.001)}}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
+			15 & probit & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.138_{(0.014)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
+			15 & probit & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.116_{(0.005)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
+			15 & probit & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $0.094_{(0.001)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$
 		\end{tabular}
-	\end{table}
+	\end{table*}
 
@@
 	\label{sect:adience}
-	Results for the experiments made with the Adience dataset are shown in Table \ref{table:Adienceresults}.
-
-	\begin{table}[!t]
-		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
-		\label{table:Adienceresults}
+	Results for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}.
+
+	\begin{table*}[!t]
+		\caption{Adience test results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\label{table:AdienceTest}
 		\footnotesize
 		\centering
-		\begin{tabular}{ccc|cc}
-			BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
-			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
-			& & Probit & $0.77608$ & $0.72574$\\
-			& & c log-log & $0.75430$ & $0.70742$\\
-			& $10^{-3}$ & Logit & $0.71460$ & $0.67868$\\
-			& & Probit & $0.81906$ & $0.77154$\\
-			& & c log-log & $0.57196$ & $0.55608$\\
-			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
-			& & Probit & $0.54360$ & $0.52422$\\
-			& & c log-log & $0.54802$ & $0.52484$\\
-			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
-			& & Probit & $0.79332$ & $0.74750$\\
-			& & c log-log & $0.78004$ & $0.73260$\\
-			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
-			& & Probit & $0.59778$ & $0.58476$\\
-			& & c log-log & $0.52016$ & $0.49968$\\
-			& $10^{-4}$ & Logit & $0.60972$ & $0.56814$\\
-			& & Probit & $0.54638$ & $0.52632$\\
-			& & c log-log & $0.75428$ & $0.52094$\\
-			$15$ & $10^{-2}$ & Logit & $0.79104$ & $0.74388$\\
-			& & Probit & $\textbf{0.84254}$ & $\textbf{0.78666}$\\
-			& & c log-log & $0.78802$ & $0.74624$\\
-			& $10^{-3}$ & Logit & $0.56946$ & $0.52978$\\
-			& & Probit & $0.70262$ & $0.65416$\\
-			& & c log-log & $0.49242$ & $0.47320$\\
-			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
-			& & Probit & $0.54288$ & $0.51740$\\
-			& & c log-log & $0.53826$ & $0.52542$
+		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c|c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
+			64 & c log-log & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.129_{(0.007)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
+			64 & c log-log & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $0.101_{(0.003)}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
+			64 & c log-log & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.100_{(0.002)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
+			64 & logit & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.137_{(0.007)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
+			64 & logit & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $0.098_{(0.003)}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
+			64 & logit & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.108_{(0.004)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
+			64 & probit & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.121_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
+			64 & probit & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.105_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
+			64 & probit & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.100_{(0.002)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
+			128 & c log-log & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.117_{(0.002)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
+			128 & c log-log & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.100_{(0.001)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
+			128 & c log-log & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.125_{(0.004)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
+			128 & logit & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.125_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
+			128 & logit & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.099_{(0.003)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
+			128 & logit & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.151_{(0.005)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
+			128 & probit & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.115_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
+			128 & probit & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.100_{(0.003)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
+			128 & probit & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.110_{(0.002)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
+			256 & c log-log & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.110_{(0.001)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
+			256 & c log-log & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.097_{(0.004)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
+			256 & c log-log & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.165_{(0.004)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
+			256 & logit & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.125_{(0.015)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
+			256 & logit & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $\mathbf{0.094_{(0.002)}}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
+			256 & logit & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.191_{(0.002)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
+			256 & probit & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.112_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
+			256 & probit & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $\mathit{0.095_{(0.001)}}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
+			256 & probit & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.150_{(0.005)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$
 		\end{tabular}
-
-	\end{table}
+	\end{table*}
+
+%	\begin{table}[!t]
+%		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+%		\label{table:Adienceresults}
+%		\footnotesize
+%		\centering
+%		\begin{tabular}{ccc|cc}
+%			BS & LR & LF & $QWK_{val}$ & $QWK_{test}$\\\hline
+%			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
+%			& & Probit & $0.77608$ & $0.72574$\\
+%			& & c log-log & $0.75430$ & $0.70742$\\
+%			& $10^{-3}$ & Logit & $0.71460$ & $0.67868$\\
+%			& & Probit & $0.81906$ & $0.77154$\\
+%			& & c log-log & $0.57196$ & $0.55608$\\
+%			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
+%			& & Probit & $0.54360$ & $0.52422$\\
+%			& & c log-log & $0.54802$ & $0.52484$\\
+%			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
+%			& & Probit & $0.79332$ & $0.74750$\\
+%			& & c log-log & $0.78004$ & $0.73260$\\
+%			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
+%			& & Probit & $0.59778$ & $0.58476$\\
+%			& & c log-log & $0.52016$ & $0.49968$\\
+%			& $10^{-4}$ & Logit & $0.60972$ & $0.56814$\\
+%			& & Probit & $0.54638$ & $0.52632$\\
+%			& & c log-log & $0.75428$ & $0.52094$\\
+%			$15$ & $10^{-2}$ & Logit & $0.79104$ & $0.74388$\\
+%			& & Probit & $\textbf{0.84254}$ & $\textbf{0.78666}$\\
+%			& & c log-log & $0.78802$ & $0.74624$\\
+%			& $10^{-3}$ & Logit & $0.56946$ & $0.52978$\\
+%			& & Probit & $0.70262$ & $0.65416$\\
+%			& & c log-log & $0.49242$ & $0.47320$\\
+%			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
+%			& & Probit & $0.54288$ & $0.51740$\\
+%			& & c log-log & $0.53826$ & $0.52542$
+%		\end{tabular}
+%		
+%	\end{table}
 
@@
 	ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
-Considered factors are the link function, which can be logit, probit and complementary log-log, the learning rate for the Adam optimization algorithm ($10^{-2}$, $10^{-3}$ and $10^{-4}$) and the batch size (5, 10 and 15).
+Considered factors are the link function, which can be logit, probit and complementary log-log, the learning rate for the Adam optimization algorithm ($10^{-2}$, $10^{-3}$ and $10^{-4}$) and the batch size (5, 10 and 15 for DR and 64, 128 and 256 for Adience).
 
@@
 
-	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (logit, probit, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the parameter factor ($10^{-4}$, $10^{-3}$, $10^{-2}$) and $B_k$ is the effect associated with the \textit{k-th} level of the batch size factor (5, 10, 15).
+	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (logit, probit, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the parameter factor and $B_k$ is the effect associated with the \textit{k-th} level of the batch size factor.
 The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors.
@@
 		\begin{tabular}{l|ccccc}
-			\multicolumn{6}{c}{Response variable QWK}\\\hline
-			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
-			Model & $37.860$ & $9$ & $4.207$ & $1562.840$ & $0.000$\\
-			$L$ factor & $0.057$ & $2$ & $0.029$ & $10.646$ & $0.000$\\
-			$P$ factor & $0.121$ & $2$ & $0.060$ & $22.468$ & $0.000$\\
-			$LP$ factors & $0.057$ & $4$ & $0.014$ & $5.261$ & $0.001$\\
-			Error & $0.339$ & $126$ & $0.003$ & & \\
+			           \multicolumn{6}{c}{Response variable QWK}             \\ \hline
+			Source       &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
+			Model        & $37.860$ &  $9$  & $4.207$ & $1562.840$ & $0.000$ \\
+			$L$ factor   & $0.057$  &  $2$  & $0.029$ &  $10.646$  & $0.000$ \\
+			$P$ factor   & $0.121$  &  $2$  & $0.060$ &  $22.468$  & $0.000$ \\
+			$LP$ factors & $0.057$  &  $4$  & $0.014$ &  $5.261$   & $0.001$ \\
+			Error        & $0.339$  & $126$ & $0.003$ &            &  \\ \hline
 			Total        & $38.199$ & $135$ &         &            &
@@
 		\begin{tabular}{l|ccccc}
-			\multicolumn{6}{c}{Response variable QWK}\\\hline
-			Source & S.S. & D.F. & M.S. & F-ratio & Sig.\\\hline
-			Model & $52.328$ & $15$ & $3.489$ & $1426.170$ & $0.000$\\
-			$L$ factor & $0.027$ & $2$ & $0.014$ & $5.582$ & $0.005$\\
-			$P$ factor & $1.031$ & $2$ & $0.516$ & $210.809$ & $0.000$\\
-			$B$ factor & $0.089$ & $2$ & $0.045$ & $18.253$ & $0.000$\\
-			$LP$ factors & $0.183$ & $4$ & $0.046$ & $18.695$ & $0.000$\\
-			$PB$ factors & $0.124$ & $4$ & $0.031$ & $12.695$ & $0.000$\\
-			Error & $0.294$ & $120$ & $0.002$ & & \\
-			Total & $52.622$ & $135$ & $3.489$ & & 
+			            \multicolumn{6}{c}{Response variable QWK}              \\ \hline
+			Source         &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
+			Model          & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
+			$L$ factor     & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
+			$P$ factor     & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
+			$B$ factor     & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
+			$LP$ factors   & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
+			% $LB$ factors & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
+			$PB$ factors   & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
+			$LPB$ factors  & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
+			Error          & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
+			Total          & $84.449$ & $135$ &         &            &
 		\end{tabular}
@@
 The interactions where there are not significative differences in QWK means have been omitted.
-First, the factor associated with the link function is analysed.
-The differences between the means are significative ($\text{p-value} = 0.005$).
-Secondly, there are significative differences concerning the learning rate factor too ($\text{p-value} = 0.000$).
-Also, there are differences for the means of QWK for the batch size factor.
-Significative interactions exist between two pairs of factors: link function and learning rate, and learning rate and batch size ($\text{p-value = 0.000}$ for both cases).
-
-	A post-hoc multiple comparison test has been performed on the average QWK obtained for this dataset too.
+First, we observe that there exist significative differences in the mean QWK concerning the three factors (p-values $0.000$).
+Secondly, we found interactions between the following pairs of factors: the link function and the learning rate, the link function and the batch size and, the batch size and the learning rate.
+Also, there are interactions between all the factors together.
+
+	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for this dataset too.
 Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been done.
-The results showed that the best link function is the logit one, in this case, with $0.60553$ as mean QWK value.
-However, there are not significative differences between this function and the complementary log-log ($\text{p-value}=0.110$).
-It has differences with the probit function though ($\text{p-value} = 0.003$).
-The complementary log-log link reported the best results after the logit function, having a mean QWK of $0.58738$.
-However, it doesn't show significative differences with the probit function.
-	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
-The test reported significative differences between $\eta=10^{-2}$ (mean value $0.73378$) and the rest of values of this parameter ($\alpha=0.005$), being this one the best value for this factor.
-The best value after $10^{-2}$ is $10^{-3}$, which have a mean QWK value of $0.57989$.
-Lastly, the best value for the batch size parameter is $5$ (mean value $0.63243$) as it has significative differences with the rest of values.
-The second best value is $15$ (mean $0.61129$), but it has no significative differences with $10$ ($\text{p-value}= 0.194$).
+The results showed that the best link function is the logit one, in this case, with $0.8265$ as mean QWK value.
+Also, there are significative differences between this function and the probit link (p-value $0.000$), that has a mean QWK value of $0.7810$.
+Both links functions present significative differences concerning the complementary log-log function, that has a mean value of $0.7434$.
+
+	The same methodology was followed for the learning rate and the batch size factors.
+The test reported significative differences between $\eta=10^{-3}$ (mean value $0.8636$) and the rest of values of this parameter, being this one the best value for this factor.
+The best value after $10^{-3}$ is $10^{-2}$, which have a mean QWK value of $0.8177$.
+Both values present significative differences with $\eta=10^{-4}$, that has a mean QWK value of $0.6697$.
+
+	Lastly, the best value for the batch size parameter is $128$ (mean value $0.8024$) as it has significative differences with the rest of values.
+The second best value is $256$ (mean $0.7877$), and it has significative differences with $64$, that has a mean value of $0.7609$.
+
+	However, the interactions between these factors made the configuration that uses a logit link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
+It obtained a mean QWK value of $0.9396$ for validation and $0.8808$ for test.
+The same parameters, but using the probit link, achieves the second best results.
 
 	To sum up, the results showed that the best parameter configuration depends on the problem that is being solved.
-None of the optimal parameters is the same for Retinopathy and Adience datasets.
+The optimal value for the batch size and the optimal link function are not the same for Retinopathy and Adience datasets.
 These results highlight the importance of adjusting the hyper-parameters for each problem that is treated instead of trying to find an optimal configuration for all the datasets.
+However, the best learning rate for both datasets were $10^{-3}$.
+It is recommended to use this value for future datasets.
+	The best batch size for DR was 10 while the best value for Adience was 128. Both values are the median value that we have tried.
+	Finally, there are more interactions between the three factors for the Adience dataset than for the Diabetic Retinopathy one.
+This highlights the importance of making experimental designs associated with each dataset to determine the best value for each factor.
 
@@
 The evaluation metric remains the same in order to be able to compare.
-The results for both datasets are shown in Table \ref{table:NominalResults}.
 There are some parameter configurations where the training process gets stagnated and a very low QWK is obtained.
@@
 
-	\begin{table}[!t]
-		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
-		\label{table:NominalResults}
-		\footnotesize
-		\centering
-		\begin{tabular}{lcc|cc}
-			Dataset & BS & LR & $\kappa_{val}$ & $\kappa_{test}$\\\hline
-			Retinopathy & $5$ & $10^{-2}$ & $0.2210$ & $0.2050$\\
-			 & & $10^{-3}$ & $0.2807$ & $0.2654$\\
-			 & & $10^{-4}$ & $0.4580$ & $0.4449$\\
-
-			 & $10$ & $10^{-2}$ & $0.2972$ & $0.2997$\\
-			 &  & $10^{-3}$ & $0.3972$ & $0.3989$\\
-			 &  & $10^{-4}$ & $\textbf{0.4972}$ & $\textbf{0.4967}$\\
-
-			 & $15$ & $10^{-2}$ & $0.3692$ & $0.3676$\\
-			 & & $10^{-3}$ & $0.4107$ & $0.4162$\\
-			 & & $10^{-4}$ & $0.4929$ & $0.4859$\\
-			\hline
-			Adience & $5$ & $10^{-2}$ & $0.0605$ & $0.0769$\\
-			 & & $10^{-3}$ & $0.7994$ & $0.7313$\\
-			 & & $10^{-4}$ & $0.8009$ & $0.7383$\\
-
-			 & $10$ & $10^{-2}$ & $0.0559$ & $0.0576$\\
-			 & & $10^{-3}$ & $0.8239$ & $0.7436$\\
-			 & & $10^{-4}$ & $0.7938$ & $0.7218$\\
-
-			 & $15$ & $10^{-2}$ & $0.0593$ & $0.0713$\\
-			 & & $10^{-3}$ & $\textbf{0.8309}$ & $\textbf{0.7575}$\\
-			 & & $10^{-4}$ & $0.7867$ & $0.7129$\\
-		\end{tabular}
-	\end{table}
-
-	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the QWK metric.
+%	\begin{table*}[!t]
+%		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
+%		\label{table:NominalResults}
+%		\scriptsize
+%		\centering
+%		\begin{tabular}{ccc|cccccccc}
+%			 Dataset & BS & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
+%			 DR & 5 & $10^{-2}$ & $0.205_{(0.060)}$ & $0.032_{(0.035)}$ & $0.269_{(0.009)}$ & $0.138_{(0.011)}$ & $0.527_{(0.035)}$ & $0.827_{(0.028)}$ & $0.952_{(0.006)}$ & $0.673_{(0.064)}$\\
+%			 DR & 5 & $10^{-3}$ & $0.265_{(0.118)}$ & $0.096_{(0.078)}$ & $0.265_{(0.014)}$ & $0.128_{(0.007)}$ & $0.525_{(0.044)}$ & $0.816_{(0.012)}$ & $0.957_{(0.004)}$ & $0.699_{(0.103)}$\\
+%			 DR & 5 & $10^{-4}$ & $0.445_{(0.027)}$ & $0.147_{(0.032)}$ & $0.229_{(0.009)}$ & $0.109_{(0.005)}$ & $0.660_{(0.038)}$ & $0.856_{(0.008)}$ & $0.969_{(0.003)}$ & $0.836_{(0.008)}$\\
+%			 DR & 10 & $10^{-2}$ & $0.300_{(0.050)}$ & $0.093_{(0.056)}$ & $0.260_{(0.007)}$ & $0.125_{(0.004)}$ & $0.569_{(0.027)}$ & $0.819_{(0.017)}$ & $0.949_{(0.007)}$ & $0.717_{(0.054)}$\\
+%			 DR & 10 & $10^{-3}$ & $0.399_{(0.010)}$ & $0.215_{(0.029)}$ & $0.247_{(0.003)}$ & $0.118_{(0.002)}$ & $0.578_{(0.026)}$ & $0.826_{(0.006)}$ & $0.963_{(0.001)}$ & $0.798_{(0.007)}$\\
+%			 DR & 10 & $10^{-4}$ & $0.497_{(0.011)}$ & $0.157_{(0.040)}$ & $0.209_{(0.002)}$ & $0.098_{(0.002)}$ & $0.692_{(0.012)}$ & $0.865_{(0.002)}$ & $0.972_{(0.001)}$ & $0.854_{(0.006)}$\\
+%			 DR & 15 & $10^{-2}$ & $0.368_{(0.062)}$ & $0.133_{(0.048)}$ & $0.244_{(0.011)}$ & $0.116_{(0.005)}$ & $0.616_{(0.032)}$ & $0.836_{(0.022)}$ & $0.958_{(0.010)}$ & $0.775_{(0.044)}$\\
+%			 DR & 15 & $10^{-3}$ & $0.416_{(0.029)}$ & $0.186_{(0.028)}$ & $0.241_{(0.006)}$ & $0.115_{(0.003)}$ & $0.600_{(0.017)}$ & $0.839_{(0.011)}$ & $0.963_{(0.004)}$ & $0.800_{(0.025)}$\\
+%			 DR & 15 & $10^{-4}$ & $0.486_{(0.007)}$ & $0.185_{(0.051)}$ & $0.210_{(0.007)}$ & $0.099_{(0.004)}$ & $0.671_{(0.022)}$ & $0.861_{(0.007)}$ & $0.971_{(0.002)}$ & $0.854_{(0.006)}$\\
+%			 \hline
+%			 Adience & 64 & $10^{-2}$ & $0.779_{(0.013)}$ & $0.100_{(0.072)}$ & $0.152_{(0.007)}$ & $0.089_{(0.003)}$ & $0.447_{(0.021)}$ & $0.712_{(0.014)}$ & $0.838_{(0.013)}$ & $0.795_{(0.019)}$\\
+%			 Adience & 64 & $10^{-3}$ & $0.787_{(0.004)}$ & $0.115_{(0.026)}$ & $0.139_{(0.002)}$ & $0.110_{(0.001)}$ & $0.458_{(0.008)}$ & $0.685_{(0.007)}$ & $0.802_{(0.003)}$ & $0.800_{(0.007)}$\\
+%			 Adience & 64 & $10^{-4}$ & $0.627_{(0.023)}$ & $0.024_{(0.025)}$ & $0.165_{(0.009)}$ & $0.119_{(0.014)}$ & $0.365_{(0.032)}$ & $0.581_{(0.028)}$ & $0.712_{(0.017)}$ & $0.701_{(0.009)}$\\
+%			 Adience & 128 & $10^{-2}$ & $0.762_{(0.013)}$ & $0.124_{(0.033)}$ & $0.141_{(0.002)}$ & $0.116_{(0.001)}$ & $0.443_{(0.007)}$ & $0.685_{(0.009)}$ & $0.812_{(0.007)}$ & $0.790_{(0.009)}$\\
+%			 Adience & 128 & $10^{-3}$ & $0.768_{(0.007)}$ & $0.100_{(0.025)}$ & $0.140_{(0.002)}$ & $0.112_{(0.003)}$ & $0.454_{(0.009)}$ & $0.667_{(0.008)}$ & $0.783_{(0.004)}$ & $0.791_{(0.004)}$\\
+%			 Adience & 128 & $10^{-4}$ & $0.586_{(0.033)}$ & $0.016_{(0.022)}$ & $0.175_{(0.009)}$ & $0.116_{(0.010)}$ & $0.321_{(0.050)}$ & $0.565_{(0.023)}$ & $0.711_{(0.014)}$ & $0.665_{(0.013)}$\\
+%			 Adience & 256 & $10^{-2}$ & $0.759_{(0.007)}$ & $0.113_{(0.036)}$ & $0.141_{(0.001)}$ & $0.113_{(0.002)}$ & $0.447_{(0.006)}$ & $0.691_{(0.009)}$ & $0.815_{(0.006)}$ & $0.793_{(0.004)}$\\
+%			 Adience & 256 & $10^{-3}$ & $0.752_{(0.004)}$ & $0.071_{(0.018)}$ & $0.146_{(0.002)}$ & $0.117_{(0.001)}$ & $0.429_{(0.009)}$ & $0.658_{(0.007)}$ & $0.782_{(0.010)}$ & $0.781_{(0.005)}$\\
+%			 Adience & 256 & $10^{-4}$ & $0.480_{(0.094)}$ & $0.022_{(0.041)}$ & $0.180_{(0.007)}$ & $0.111_{(0.008)}$ & $0.326_{(0.024)}$ & $0.539_{(0.028)}$ & $0.682_{(0.028)}$ & $0.616_{(0.041)}$
+%		\end{tabular}
+%	\end{table*}
+
+	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15 for DR and, 64, 128 and 256 for Adience) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the QWK metric.
 So, we make an ANOVA II analysis for each dataset.
@@
 
-	Finally, a comparison of the best QWK for each dataset for ordinal and nominal cases is shown in Table \ref{table:ComparisonNomOrd}.
+	Finally, a comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
 Also, it is compared with previous works.
 The proposed ordinal model outperforms all the other alternatives.
-The performance increase of POM over softmax reaches $17.07\%$ for Diabetic Retinopathy and $3.85\%$ for Adience dataset.
+The performance increase of POM over softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.
 The enhancement of the ordinal method for Retinopathy dataset is more notable than the rise for Adience dataset.
@@
 	\begin{table}[!t]
-		\caption{Comparison between the best QWK results of nominal, ordinal and previous works.}
-		\label{table:ComparisonNomOrd}
-		\footnotesize
+		\caption{Comparison between the best results of nominal, ordinal and previous works for the Diabetic Retinopathy dataset.}
+		\label{table:ComparisonDR}
+		\scriptsize
 		\centering
-		\begin{tabular}{lccc|cc}
-			\multicolumn{6}{c}{Diabetic Retinopathy}\\
-			\hline
-			Method & BS & LR & LF & $\kappa_{val}$ & $\kappa_{test}$\\\hline
-			Ord. proposed & 10 & $10^{-3}$ & c log-log & $0.58830$ & $0.58150$\\
-			Nom. proposed & 10 & $10^{-4}$ & softmax & $0.49720$ & $0.49670$\\
-			Best from \cite{de2018weighted} & 20 & $10^{-4}$ & softmax & $0.53700$ & -\\
-			Best from \cite{nebot2016diabetic} & - & - & softmax & - & $0.55500$\\
-			\hline\hline
-			\multicolumn{6}{c}{Adience}\\
-			\hline
-			Ord. proposed & 15 & $10^{-2}$ & probit & $0.84254$ & $0.78666$\\
-			Nom. proposed & 15 & $10^{-3}$ & softmax & $0.83090$ & $0.75750$\\
+		\def\arraystretch{1.3}
+		\begin{tabular}{l|ccc}
+			Method                                   & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
+			Ordinal proposed                         &    $0.582_{(0.016)}$    &    $0.681_{(0.067)}$    &        $0.748_{(0.071)}$         \\
+			Nominal proposed                         &    $0.498_{(0.011)}$    &    $0.692_{(0.012)}$    &        $0.854_{(0.006)}$         \\ \hline
+			J. Torre et al. \cite{de2018weighted}    &      $0.537_{(\text{-})}$      &            -            &                -                 \\
+			À. Nebot et al. \cite{nebot2016diabetic} &      $0.555_{(\text{-})}$      &            -            &                -
+		\end{tabular}
+	\end{table}
+
+	\begin{table}[!t]
+		\caption{Comparison between the best results of nominal, ordinal and previous works for the Adience dataset.}
+		\label{table:ComparisonAdience}
+		\scriptsize
+		\centering
+		\def\arraystretch{1.3}
+		\begin{tabular}{l|ccc}
+			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
+			Ordinal proposed                          &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
+			Nominal proposed                          &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\ \hline
+			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
+			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
+			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$
 		\end{tabular}

### 2019-02-06 experiment.py

@@ -671,8 +671,8 @@ class Experiment():
 		:return: train path, validation path, test path.
 		"""
 		if db.lower() == 'retinopathy':
-			# return "../retinopathy/128/train", "../retinopathy/128/val", "../retinopathy/128/test"
-			return "../retinopathy/retinopathy_128_train.h5", "../retinopathy/retinopathy_128_val.h5", "../retinopathy/retinopathy_128_test.h5"
+			return "../retinopathy/128/train", "../retinopathy/128/val", "../retinopathy/128/test"
+			# return "../retinopathy/retinopathy_128_train.h5", "../retinopathy/retinopathy_128_val.h5", "../retinopathy/retinopathy_128_test.h5"
 		elif db.lower() == 'retinopathy256':
 			return "../retinopathy/256/train", "../retinopathy/256/val", "../retinopathy/256/test"
 		elif db.lower() == 'adience':

### 2019-02-06 paper/ieee.tex
Paper

@@
 	\begin{table*}[!t]
-		\caption{Adience test results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
+		\caption{Adience test results. BS stands for Batch Size, LF for link function and LR for Learning Rate.}
 		\label{table:AdienceTest}
@@
 
-	\subsection{Statistical comparison between nominal and ordinal methods}
+	\subsection{Comparison with nominal method and previous works}
 	\label{app:NominalComparison}
@@
 
-%	\begin{table*}[!t]
-%		\caption{Nominal method results. BS stands for Batch Size and LR for Learning Rate.}
-%		\label{table:NominalResults}
-%		\scriptsize
-%		\centering
-%		\begin{tabular}{ccc|cccccccc}
-%			 Dataset & BS & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-%			 DR & 5 & $10^{-2}$ & $0.205_{(0.060)}$ & $0.032_{(0.035)}$ & $0.269_{(0.009)}$ & $0.138_{(0.011)}$ & $0.527_{(0.035)}$ & $0.827_{(0.028)}$ & $0.952_{(0.006)}$ & $0.673_{(0.064)}$\\
-%			 DR & 5 & $10^{-3}$ & $0.265_{(0.118)}$ & $0.096_{(0.078)}$ & $0.265_{(0.014)}$ & $0.128_{(0.007)}$ & $0.525_{(0.044)}$ & $0.816_{(0.012)}$ & $0.957_{(0.004)}$ & $0.699_{(0.103)}$\\
-%			 DR & 5 & $10^{-4}$ & $0.445_{(0.027)}$ & $0.147_{(0.032)}$ & $0.229_{(0.009)}$ & $0.109_{(0.005)}$ & $0.660_{(0.038)}$ & $0.856_{(0.008)}$ & $0.969_{(0.003)}$ & $0.836_{(0.008)}$\\
-%			 DR & 10 & $10^{-2}$ & $0.300_{(0.050)}$ & $0.093_{(0.056)}$ & $0.260_{(0.007)}$ & $0.125_{(0.004)}$ & $0.569_{(0.027)}$ & $0.819_{(0.017)}$ & $0.949_{(0.007)}$ & $0.717_{(0.054)}$\\
-%			 DR & 10 & $10^{-3}$ & $0.399_{(0.010)}$ & $0.215_{(0.029)}$ & $0.247_{(0.003)}$ & $0.118_{(0.002)}$ & $0.578_{(0.026)}$ & $0.826_{(0.006)}$ & $0.963_{(0.001)}$ & $0.798_{(0.007)}$\\
-%			 DR & 10 & $10^{-4}$ & $0.497_{(0.011)}$ & $0.157_{(0.040)}$ & $0.209_{(0.002)}$ & $0.098_{(0.002)}$ & $0.692_{(0.012)}$ & $0.865_{(0.002)}$ & $0.972_{(0.001)}$ & $0.854_{(0.006)}$\\
-%			 DR & 15 & $10^{-2}$ & $0.368_{(0.062)}$ & $0.133_{(0.048)}$ & $0.244_{(0.011)}$ & $0.116_{(0.005)}$ & $0.616_{(0.032)}$ & $0.836_{(0.022)}$ & $0.958_{(0.010)}$ & $0.775_{(0.044)}$\\
-%			 DR & 15 & $10^{-3}$ & $0.416_{(0.029)}$ & $0.186_{(0.028)}$ & $0.241_{(0.006)}$ & $0.115_{(0.003)}$ & $0.600_{(0.017)}$ & $0.839_{(0.011)}$ & $0.963_{(0.004)}$ & $0.800_{(0.025)}$\\
-%			 DR & 15 & $10^{-4}$ & $0.486_{(0.007)}$ & $0.185_{(0.051)}$ & $0.210_{(0.007)}$ & $0.099_{(0.004)}$ & $0.671_{(0.022)}$ & $0.861_{(0.007)}$ & $0.971_{(0.002)}$ & $0.854_{(0.006)}$\\
-%			 \hline
-%			 Adience & 64 & $10^{-2}$ & $0.779_{(0.013)}$ & $0.100_{(0.072)}$ & $0.152_{(0.007)}$ & $0.089_{(0.003)}$ & $0.447_{(0.021)}$ & $0.712_{(0.014)}$ & $0.838_{(0.013)}$ & $0.795_{(0.019)}$\\
-%			 Adience & 64 & $10^{-3}$ & $0.787_{(0.004)}$ & $0.115_{(0.026)}$ & $0.139_{(0.002)}$ & $0.110_{(0.001)}$ & $0.458_{(0.008)}$ & $0.685_{(0.007)}$ & $0.802_{(0.003)}$ & $0.800_{(0.007)}$\\
-%			 Adience & 64 & $10^{-4}$ & $0.627_{(0.023)}$ & $0.024_{(0.025)}$ & $0.165_{(0.009)}$ & $0.119_{(0.014)}$ & $0.365_{(0.032)}$ & $0.581_{(0.028)}$ & $0.712_{(0.017)}$ & $0.701_{(0.009)}$\\
-%			 Adience & 128 & $10^{-2}$ & $0.762_{(0.013)}$ & $0.124_{(0.033)}$ & $0.141_{(0.002)}$ & $0.116_{(0.001)}$ & $0.443_{(0.007)}$ & $0.685_{(0.009)}$ & $0.812_{(0.007)}$ & $0.790_{(0.009)}$\\
-%			 Adience & 128 & $10^{-3}$ & $0.768_{(0.007)}$ & $0.100_{(0.025)}$ & $0.140_{(0.002)}$ & $0.112_{(0.003)}$ & $0.454_{(0.009)}$ & $0.667_{(0.008)}$ & $0.783_{(0.004)}$ & $0.791_{(0.004)}$\\
-%			 Adience & 128 & $10^{-4}$ & $0.586_{(0.033)}$ & $0.016_{(0.022)}$ & $0.175_{(0.009)}$ & $0.116_{(0.010)}$ & $0.321_{(0.050)}$ & $0.565_{(0.023)}$ & $0.711_{(0.014)}$ & $0.665_{(0.013)}$\\
-%			 Adience & 256 & $10^{-2}$ & $0.759_{(0.007)}$ & $0.113_{(0.036)}$ & $0.141_{(0.001)}$ & $0.113_{(0.002)}$ & $0.447_{(0.006)}$ & $0.691_{(0.009)}$ & $0.815_{(0.006)}$ & $0.793_{(0.004)}$\\
-%			 Adience & 256 & $10^{-3}$ & $0.752_{(0.004)}$ & $0.071_{(0.018)}$ & $0.146_{(0.002)}$ & $0.117_{(0.001)}$ & $0.429_{(0.009)}$ & $0.658_{(0.007)}$ & $0.782_{(0.010)}$ & $0.781_{(0.005)}$\\
-%			 Adience & 256 & $10^{-4}$ & $0.480_{(0.094)}$ & $0.022_{(0.041)}$ & $0.180_{(0.007)}$ & $0.111_{(0.008)}$ & $0.326_{(0.024)}$ & $0.539_{(0.028)}$ & $0.682_{(0.028)}$ & $0.616_{(0.041)}$
-%		\end{tabular}
-%	\end{table*}
-
-	As we did in Section \ref{sect:statisticalanalysis}, we must analyse the effect of the batch size (with values 5, 10 and 15 for DR and, 64, 128 and 256 for Adience) and the learning rate ($10^{-2}$, $10^{-3}$ and $10^{-4}$) factors have over the QWK metric.
-So, we make an ANOVA II analysis for each dataset.
-
-	In the Diabetic Retinopathy dataset, there are significative differences between the mean values of QWK depending on the batch size and the initial value of the learning rate.
-Also, no significative interaction was detected between these factors.
-
-	After that, a post-hoc Tukey's test shows that the best value for the batch size factor is 15 followed by 10.
-However, there are no significative differences between them, but there are differences with size 5.
-Also, the best value for the learning rate is $10^{-4}$ and there are significative differences with the rest of values.
-
-	A similar study was made for the Adience dataset.
-There are not significative differences for the mean value of QWK w.r.t.
-the batch size factor.
-Also, there are no interactions between the batch size and the learning rate.
-The best results were obtained with $10^{-3}$ for the learning rate followed by $10^{-4}$, without significative differences between them.
-
-	The conclusions obtained from the results are exposed below:
-	\begin{itemize}
-		\item There are no interactions between both factors.
-		\item Batch sizes 10 and 15 obtained the best results.
-		\item Learning rate $10^{-4}$ is the best choice for both datasets as it the best for Diabetic Retinopathy, with significative differences, and it is the second for Adience, without significative differences with the best.
-	\end{itemize}
+	For the Diabetic Retinopathy dataset, the best mean value of QWK was $0.497$ and was obtained when using a batch size of 10 and a learning rate of $10^{-4}$.
+
+	In the case of Adience dataset, the highest QWK was $0.787$ and was achieved with a batch size of 64 and a learning rate of $10^{-3}$.
 
@@
 Also, it is compared with previous works.
-The proposed ordinal model outperforms all the other alternatives.
+The proposed ordinal model outperforms all the other alternatives in terms of QWK.
 The performance increase of POM over softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.
@@
 It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
+
+	In the case of DR, the nominal method obtained a higher CCR and 1-off accuracy value because of the important dataset unbalance.
+It is possible to achieve a high accuracy classifying all the examples in the majority class.
+However, as we are working with an ordinal problem, it is preferable to achieve a good QWK value rather than a high accuracy.
+This effect is not seen in the Adience dataset as it less unbalanced.
 
@@
 
-	The complementary log-log function has the best average performance across both datasets.
-It offers the best results in Diabetic Retinopathy dataset and the second best result in Adience dataset.
-These results provide an opportunity for exploring new generalised link functions.
-
-	The best value for the learning rate parameter for Diabetic Retinopathy dataset is $\eta = 10^{-3}$ while this value is the second best option for Adience dataset.
-It can be considered a good value for this parameter when training the model with new datasets.
-
-	Both datasets have obtained the best performance with batch size 10.
-
-	Also, the statistical tests reported that there are interactions between some parameters like the link function and the learning rate, for Diabetic Retinopathy, or those factors in addition to learning rate and batch size, for Adience dataset.
-
-	The proposed POM has improved the performance of the deep network regarding quadratic weighted kappa compared to the model that uses the softmax function.
-This enhancement is more notable for the Diabetic Retinopathy dataset.
+	The complementary log-log function offers the best results in Diabetic Retinopathy dataset while the logit link is the best result for the Adience dataset.
+These results provide an opportunity for exploring new generalised link functions that can suit any problem.
+
+	The best value for the learning rate parameter for both datasets is $\eta = 10^{-3}$. It can be considered a good value for this parameter when training the model with new datasets.
+
+	Both datasets have obtained the best performance with the intermedium batch size: 10 for Diabetic Retinopathy and 128 for Adience.
+
+	Also, the statistical tests reported that there are relevant interactions between the three factors that we have take into account.
+The results highlight the importance of making an experimental design were all of these parameters are adjusted for each problem.
+
+	The proposed POM has improved the performance of the deep network compared to the model that uses the softmax function and the models proposed in previous works.
 Also, it reduces the chance that the model gets stuck when training with some parameter configurations.
-So, the most significant improvements of these link functions are the QWK performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
+So, the most significant improvements of these link functions are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
 

### 2019-02-06 experiment.py

@@ -24,7 +24,7 @@ class Experiment():
 	Class that represents a single experiment that can be run and evaluated.
 	"""
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
-				 checkpoint_dir='checkpoint', loss='crossentropy', activation='relu', final_activation='softmax',
+				 checkpoint_dir='checkpoint', loss='categorical_crossentropy', activation='relu', final_activation='softmax',
 				 prob_layer=None, spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both', workers=4,
 				 queue_size=1024, val_metrics=['loss', 'acc'], rescale_factor=0, augmentation={}):
 		self._name = name

### 2019-02-11 paper/ieee.tex
Paper corrections

@@
 In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance.
-In this work, we will combine the QWK metric and the QWK loss.
+In this work, we will use the QWK metric and the QWK loss.
 
@@
 We will contrast the results obtained with statistical analysis to provide more robust results.
-An approximated ANOVA III test will be performed because of the limitations of the computational time required to run a higher number of executions.
+An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.
 
@@
 CLMs predict probabilities of groups of contiguous categories, taking the ordinal scale into account.
-In this way, cumulative probabilities $P(y \prec Cj |\mathbf{x})$ are estimated, which can be directly related to standard probabilities:
+In this way, cumulative probabilities $P(y \prec C_q |\mathbf{x})$ are estimated, which can be directly related to standard probabilities:
 	\begin{equation}
@@
 
-	The model in inspired by the notion of latent variable, considering a linear transformation $f(x) = \mathbf{w^Tx}$ of the input variables as the one-dimensional mapping.
+	The model is inspired by the notion of latent variable, considering a linear transformation $f(x) = \mathbf{w^Tx}$ of the input variables as the one-dimensional mapping.
 The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
 	\begin{equation}
-		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - \mathbf{w^Tx}, \quad 1, ..., Q-1,
+		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - \mathbf{w^Tx}, \quad q = 1, ..., Q-1,
 	\end{equation}
@@
 The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient).
-In this dataset, we try and predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
+In this dataset, we try to predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
 The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions.
@@
 The images are resized to 128 by 128 pixels and rescaled to $[0,1]$ range.
-Data augmentation techniques are applied to achieve a higher number of samples.
+Data augmentation techniques, described in Section \ref{sect:procedure}, are applied to achieve a higher number of samples.
 
@@
 The different architectures of CNN used in these experiments are presented in tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
-The architecture for DR is the same that was used in \cite{de2018weighted} and the network for adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
+The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
 For convolutional layers, ConvWxH@FsS = F filters of size WxH and stride S.
@@
 			\hline
-			Conv3x3@32s1 & 254x254x32\\\hline
-			Conv3x3@32s1 & 252x252x32\\\hline
+			%Conv3x3@32s1 & 254x254x32\\\hline
+			2 x Conv3x3@32s1 & 252x252x32\\\hline
 			MaxPool2x2s2 & 126x126x32\\\hline
 
-			Conv3x3@64s1 & 124x124x64\\\hline
-			Conv3x3@64s1 & 122x122x64\\\hline
+			%Conv3x3@64s1 & 124x124x64\\\hline
+			2 x Conv3x3@64s1 & 122x122x64\\\hline
 			MaxPool2x2s2 & 61x61x64\\\hline
 
-			Conv3x3@128s1 & 59x59x128\\\hline
-			Conv3x3@128s1 & 57x57x128\\\hline
+			%Conv3x3@128s1 & 59x59x128\\\hline
+			2 x Conv3x3@128s1 & 57x57x128\\\hline
 			MaxPool2x2s2 & 28x28x128\\\hline
 
-			Conv3x3@128s1 & 26x26x128\\\hline
-			Conv3x3@128s1 & 24x24x128\\\hline
+			%Conv3x3@128s1 & 26x26x128\\\hline
+			2 x Conv3x3@128s1 & 24x24x128\\\hline
 			MaxPool2x2s2 & 12x12x128\\\hline
@@
 	\subsection{Procedure}
+	\label{sect:procedure}
 	The model is optimized using a batch based first-order optimization algorithm called Adam~\cite{kingma2014adam}.
@@
 This evaluation measure gives a higher weight to the errors that are further from the correct class.
-Quadratic weighted kappa loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems.
-
-	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS), Mean Absolute Error (MAE), Mean Squared Error (MSE), Correct Classification Rate (CCR), Top-2 CCR, Top-3 CCR and 1-off accuracy.
+Quadratic weighted kappa loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems \cite{de2018weighted}.
+
+	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS) \cite{cruz2014metrics}, Mean Absolute Error (MAE) \cite{cruz2014metrics}, Mean Squared Error (MSE) \cite{wang2009mean}, Correct Classification Rate (CCR), Top-2 CCR \cite{beckham2017unimodal}, Top-3 CCR \cite{beckham2017unimodal} and 1-off accuracy \cite{chen2016cascaded, levi2015age, eidinger2014age}.
 
@@
 Every parameter combination has been run five times.
-These tables show the mean value and the standard deviation of each metric across these five executions for the test set.
+These tables show the mean value and the standard deviation (SD) of each metric across these five executions for the test set.
 These values are exposed using the format $\text{MEAN}_{(SD)}$.
@@
 	\label{sect:dr}
-	Detailed results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}.
+	Detailed results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}. The best result for each metric is marked in bold and the second best is in italic font.
 
@@
 	The best mean QWK value was obtained with the complementary log-log link function using a batch size of 10 and a learning rate of $10^{-3}$.
+However, the best CCR value was obtained with a batch size of 15, the logit link and a learning rate of $10^{-4}$.
+The optimal configuration depends on the metric we are analysing.
+In this case, as we are working with an ordinal problem, the most reliable metric is the QWK.
 
@@
 	\label{sect:adience}
-	Results for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}.
+	Results for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}. The best result for each metric is marked in bold and the second best is in italic font.
 
@@
 
-%	\begin{table}[!t]
-%		\caption{Adience results. BS stands for Batch Size, LR for Learning Rate and LF for link function.}
-%		\label{table:Adienceresults}
-%		\footnotesize
-%		\centering
-%		\begin{tabular}{ccc|cc}
-%			BS & LR & LF & $QWK_{val}$ & $QWK_{test}$\\\hline
-%			$5$ & $10^{-2}$ & Logit & $0.72072$ & $0.68408$\\
-%			& & Probit & $0.77608$ & $0.72574$\\
-%			& & c log-log & $0.75430$ & $0.70742$\\
-%			& $10^{-3}$ & Logit & $0.71460$ & $0.67868$\\
-%			& & Probit & $0.81906$ & $0.77154$\\
-%			& & c log-log & $0.57196$ & $0.55608$\\
-%			& $10^{-4}$ & Logit & $0.54432$ & $0.51934$\\
-%			& & Probit & $0.54360$ & $0.52422$\\
-%			& & c log-log & $0.54802$ & $0.52484$\\
-%			$10$ & $10^{-2}$ & Logit & $0.78872$ & $0.72994$\\
-%			& & Probit & $0.79332$ & $0.74750$\\
-%			& & c log-log & $0.78004$ & $0.73260$\\
-%			& $10^{-3}$ & Logit & $0.49686$ & $0.47112$\\
-%			& & Probit & $0.59778$ & $0.58476$\\
-%			& & c log-log & $0.52016$ & $0.49968$\\
-%			& $10^{-4}$ & Logit & $0.60972$ & $0.56814$\\
-%			& & Probit & $0.54638$ & $0.52632$\\
-%			& & c log-log & $0.75428$ & $0.52094$\\
-%			$15$ & $10^{-2}$ & Logit & $0.79104$ & $0.74388$\\
-%			& & Probit & $\textbf{0.84254}$ & $\textbf{0.78666}$\\
-%			& & c log-log & $0.78802$ & $0.74624$\\
-%			& $10^{-3}$ & Logit & $0.56946$ & $0.52978$\\
-%			& & Probit & $0.70262$ & $0.65416$\\
-%			& & c log-log & $0.49242$ & $0.47320$\\
-%			& $10^{-4}$ & Logit & $0.55202$ & $0.52484$\\
-%			& & Probit & $0.54288$ & $0.51740$\\
-%			& & c log-log & $0.53826$ & $0.52542$
-%		\end{tabular}
-%		
-%	\end{table}
-
-	The best mean QWK value was obtained with the probit link function using a batch size of 15 and a learning rate of $10^{-2}$.
+	The best mean QWK value was obtained with the logit link function using a batch size of 64 and a learning rate of $10^{-4}$.
+Also, this configuration obtained the best score for Top-2, Top-3 and 1-off accuracy, and the second best for MS, MAE and CCR.
+In this case, this configuration can be selected as the optimal for this problem.
 
@@
 
-	The test shows that there is no batch size whose results are significatively better than the results of all other batch sizes.
+	%The test shows that there is no batch size whose results are significatively better than the results of all other batch sizes.
 This does not mean that these differences could not exist for specific numbers of samples per batch.
@@
 The term $\epsilon_{i,j,k,l}$ is the influence on the result of everything that could not be assigned or of random factors.
-$W_{i,j,k,l}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
+$QWK_{i,j,k,l}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
 
@@
 	The results of the ANOVA III test for the Diabetic Retinopathy dataset are resumed in Table \ref{table:ANOVARetinopathy}.
-There are significative differences in the means of QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$.
+There are significative differences in the means of QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$ ($\text{p-value} = 0.000$).
 Moreover, an interaction between the link function and the learning rate can be recognised ($\text{p-value} = 0.001$).
+It means that the learning rate and the link functions have a significative impact on the optimization algorithm results.
 
@@
 A post-hoc multiple comparison test has been performed on the mean QWK obtained.
-An HSD Tukey's test was made under the null hypothesis that the variance of the error of the dependent variable is the same between groups.
-The best link function is the complementary log-log, though it doesn't have significative differences with the probit function ($\alpha=0.05$).
-There are differences between the complementary log-log and the probit function concerning the logit function.
+An HSD Tukey's test \cite{tukey1949comparing} was made under the null hypothesis that the variance of the error of the dependent variable is the same between groups.
+The results over the test set show that the best link function is the complementary log-log, though it doesn't have significative differences with the probit function ($\text{p-value} = 0.248$).
+There are differences between the complementary log-log and the probit function concerning the logit function (p-values $0.000$ and $0.011$).
 
 	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
-Significative differences can be observed in the mean values for $\eta = 10^{-3}$ with respect to the other values of the parameter ($\alpha=0.05$).
-Also, there are differences for $\eta = 10^{-4}$ concerning $\eta = 10^{-2}$.
+Significative differences can be observed in the mean values for $\eta = 10^{-3}$ with respect to the other values of the parameter (p-values $0.023$ for $10^{-4}$ and $0.000$ for $10^{-2}$).
+Also, there are differences for $\eta = 10^{-4}$ concerning $\eta = 10^{-2}$ ($\text{p-value} = 0.000$).
 
@@
 			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
-			% $LB$ factors & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
+			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
 			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
@@
 	The results of the ANOVA III test for the Adience dataset are shown in Table \ref{table:ANOVAAdience}.
-The interactions where there are not significative differences in QWK means have been omitted.
-First, we observe that there exist significative differences in the mean QWK concerning the three factors (p-values $0.000$).
-Secondly, we found interactions between the following pairs of factors: the link function and the learning rate, the link function and the batch size and, the batch size and the learning rate.
-Also, there are interactions between all the factors together.
-
-	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for this dataset too.
+First, we observe that there exist significative differences in the mean QWK concerning the three factors ($\text{p-value} = 0.000$).
+Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$).
+It means that the joint action of two or three factors significatively affects the results obtained by the algorithm.
+
+	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for Adience.
 Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been done.
-The results showed that the best link function is the logit one, in this case, with $0.8265$ as mean QWK value.
-Also, there are significative differences between this function and the probit link (p-value $0.000$), that has a mean QWK value of $0.7810$.
-Both links functions present significative differences concerning the complementary log-log function, that has a mean value of $0.7434$.
+The results showed that the best link function is the logit one, in this case, with $0.827$ as mean QWK value.
+Also, there are significative differences between this function and the probit link ($\text{p-value} = 0.000$), that has a mean QWK value of $0.781$.
+Both links functions present significative differences concerning the complementary log-log function, that has a mean value of $0.743$.
 
 	The same methodology was followed for the learning rate and the batch size factors.
-The test reported significative differences between $\eta=10^{-3}$ (mean value $0.8636$) and the rest of values of this parameter, being this one the best value for this factor.
-The best value after $10^{-3}$ is $10^{-2}$, which have a mean QWK value of $0.8177$.
-Both values present significative differences with $\eta=10^{-4}$, that has a mean QWK value of $0.6697$.
-
-	Lastly, the best value for the batch size parameter is $128$ (mean value $0.8024$) as it has significative differences with the rest of values.
-The second best value is $256$ (mean $0.7877$), and it has significative differences with $64$, that has a mean value of $0.7609$.
+The test reported significative differences between $\eta=10^{-3}$ (mean value $0.864$) and the rest of values of this parameter ($\text{p-value} = 0.000$ for both values), being this one the best value for this factor.
+The best value after $10^{-3}$ is $10^{-2}$, which have a mean QWK value of $0.818$.
+Both values present significative differences with $\eta=10^{-4}$, that has a mean QWK value of $0.670$ ($\text{p-value = 0.000}$).
+
+	Lastly, the best value for the batch size parameter is $128$ (mean value $0.802$) as it has significative differences with the rest of values (p-values $0.026$ and $0.000$).
+The second best value is $256$ (mean $0.788$), and it has significative differences with $64$ ($\text{p-value} = 0.000$), that has a mean value of $0.761$.
 
 	However, the interactions between these factors made the configuration that uses a logit link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
-It obtained a mean QWK value of $0.9396$ for validation and $0.8808$ for test.
-The same parameters, but using the probit link, achieves the second best results.
+It obtained a mean QWK value of $0.940$ for validation and $0.881$ for test.
+The same parameters, but using the probit link, achieves the second best result ($0.874$).
+The standard deviation is very low for both cases.
 
@@
 It is recommended to use this value for future datasets.
-	The best batch size for DR was 10 while the best value for Adience was 128. Both values are the median value that we have tried.
+	The best batch size for DR was 10 while the best value for Adience was 128. Both values are the intermediate value that we have tried.
 	Finally, there are more interactions between the three factors for the Adience dataset than for the Diabetic Retinopathy one.
@@
 The enhancement of the ordinal method for Retinopathy dataset is more notable than the rise for Adience dataset.
-It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
+It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases: it is harder to detect the diabetes disease from a retina image than predicting the age range of a person.
 
@@
 However, as we are working with an ordinal problem, it is preferable to achieve a good QWK value rather than a high accuracy.
-This effect is not seen in the Adience dataset as it less unbalanced.
+This effect is not seen in the Adience dataset as it is less unbalanced.
 

### 2019-02-11 experiment.py

@@ -11,7 +11,7 @@ import h5py
 from scipy import io as spio
 from callbacks import ComputeMetricsCallback
 from losses import qwk_loss, make_cost_matrix
-from metrics import np_quadratic_weighted_kappa, quadratic_weighted_kappa_cm, top_2_accuracy, top_3_accuracy,\
+from metrics import np_quadratic_weighted_kappa, quadratic_weighted_kappa_cm, top_2_accuracy, top_3_accuracy, \
 	minimum_sensitivity, accuracy_off1
 from dataset import Dataset
 from sklearn.metrics import confusion_matrix
@@ -23,8 +23,10 @@ class Experiment():
 	"""
 	Class that represents a single experiment that can be run and evaluated.
 	"""
+
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
-				 checkpoint_dir='checkpoint', loss='categorical_crossentropy', activation='relu', final_activation='softmax',
+				 checkpoint_dir='checkpoint', loss='categorical_crossentropy', activation='relu',
+				 final_activation='softmax',
 				 prob_layer=None, spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both', workers=4,
 				 queue_size=1024, val_metrics=['loss', 'acc'], rescale_factor=0, augmentation={}):
 		self._name = name
@@ -342,7 +344,8 @@ class Experiment():
 		:param maximize: maximize metric instead of minimizing.
 		:return: True if new metric is better than best metric or False otherwise.
 		"""
-		if self._best_metric is None or (maximize and metric > self._best_metric or not maximize and metric <= self._best_metric):
+		if self._best_metric is None or (
+				maximize and metric > self._best_metric or not maximize and metric <= self._best_metric):
 			self._best_metric = metric
 			return True
 		return False
@@ -373,7 +376,6 @@ class Experiment():
 		if start_epoch >= self.epochs:
 			print("Training already finished. Skipping...")
 			return
-
 
 		# Train data generator
 		train_datagen = tf.keras.preprocessing.image.ImageDataGenerator(
@@ -407,6 +409,10 @@ class Experiment():
 		num_classes = ds_train.num_classes
 		num_channels = ds_train.num_channels
[…]

### 2019-02-18 paper/ieee.tex
Paper y congreso

@@
 
-\usepackage[backend=bibtex, style=ieee]{biblatex}
+%\usepackage[backend=bibtex, style=ieee]{biblatex}
 
@@
 
-\addbibresource{main.bib}
-
-\renewcommand{\bibfont}{\footnotesize}
+%\addbibresource{main.bib}
+
+%\renewcommand{\bibfont}{\footnotesize}
 
@@
 	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
-These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi, he2016deep, krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed, girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
+These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
 Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to indicate how a machine should change its internal parameters that are used to compute the representation in each layer from the features in the previous layer.
 
-	Convolutional neural networks (ConvNets) are designed to process data that comes in the form of multiple arrays.
-ConvNets are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning, sun2013deep, ronneberger2015u}.
+	Convolutional Neural Networks (CNN) are designed to process data that comes in the form of multiple arrays.
+CNNs are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
 On image classification tasks, each colour channel is represented by a 2D array.
@@
 	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
-It has been used in the last years in many works~\cite{leonard1990improvement, yu1995dynamic, krizhevsky2012imagenet, de2018weighted} for training shallow and deep neural networks.
+It has been used in the last years in many works~\cite{leonard1990improvement,yu1995dynamic,krizhevsky2012imagenet,de2018weighted} for training shallow and deep neural networks.
 It updates the layer's parameters after backpropagating the loss function gradients through the network.
@@
 	Ordinal classification problems are those where labels are ordered, and there are different inter-classes weights for each pair of classes.
-This kind of problem can be treated as a nominal classification problem, but when you do this, you are the discarding ordinal information.
+This kind of problem can be treated as a nominal classification problem, but when you do this, you are discarding ordinal information.
 A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model.
 One way to use the ordinal information is to evaluate the model using an ordinal metric.
-Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics, mehdiyev2016evaluating}.
+Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics,mehdiyev2016evaluating}.
 Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories.
@@
 It is a simple and efficient function for multi-class problems but not the best when working with ordinal data.
-In this paper, the Proportional Odds Model (POM)~\cite{gutierrez2016ordinal, agresti2010analysis} will be used instead of the softmax function.
+In this paper, the Proportional Odds Model (POM)~\cite{gutierrez2016ordinal,agresti2010analysis} will be used instead of the softmax function.
 Different link functions will be explored to compare their performance.
@@
 
-	At present, there is a great discussion in terms of finding the best activation function that offers good performance and mitigates the effects of the gradients vanishing problem \cite{bengio1994learning, pascanu2013difficulty}.
+	At present, there is a great discussion in terms of finding the best activation function that offers good performance and mitigates the effects of the gradients vanishing problem \cite{bengio1994learning,pascanu2013difficulty}.
 Rectified Linear Unit (ReLU)~\cite{nair2010rectified} is widely used in most deep learning works, but recently, Clevert et al.
@@
 These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform.
-Also, this dataset was used in later works~\cite{de2018weighted, nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
+Also, this dataset was used in later works~\cite{de2018weighted,nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
@@
 
-	Both datasets have been artificially equalized using data augmentation techniques~\cite{van2001art, krizhevsky2012imagenet}.
+	Both datasets have been artificially equalized using data augmentation techniques~\cite{van2001art,krizhevsky2012imagenet}.
 However, different transformations were applied to each one.
@@
 
-	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS) \cite{cruz2014metrics}, Mean Absolute Error (MAE) \cite{cruz2014metrics}, Mean Squared Error (MSE) \cite{wang2009mean}, Correct Classification Rate (CCR), Top-2 CCR \cite{beckham2017unimodal}, Top-3 CCR \cite{beckham2017unimodal} and 1-off accuracy \cite{chen2016cascaded, levi2015age, eidinger2014age}.
+	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS) \cite{cruz2014metrics}, Mean Absolute Error (MAE) \cite{cruz2014metrics}, Mean Squared Error (MSE) \cite{wang2009mean}, Correct Classification Rate (CCR), Top-2 CCR \cite{beckham2017unimodal}, Top-3 CCR \cite{beckham2017unimodal} and 1-off accuracy \cite{chen2016cascaded,levi2015age,eidinger2014age}.
 
@@
 Optimal learning rate can vary depending on the dataset and the CNN architecture.
-Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical, senior2013empirical}.
+Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical,senior2013empirical}.
 Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
@@
 	% http://www.michaelshell.org/tex/ieeetran/bibtex/
-	%\bibliographystyle{IEEEtran}
+	\bibliographystyle{IEEEtran}
 	% argument is your BibTeX string definitions and bibliography database(s)
-	%\bibliography{IEEEabrv,../bib/paper}
+	\bibliography{main.bib}
 	%
@@
 
-	\printbibliography
+	%\printbibliography
 

### 2019-02-18 dataset.py

@@ -149,7 +149,7 @@ class Dataset():
 		self._data = {}
 		self._data['x'] = []
 		self._data['y'] = []
-		self._sample_shape = (75,75,3)
+		self._sample_shape = (32,32,3)
 
 		if split == 'train':
 			self._data['x'] = x_train
@@ -172,7 +172,7 @@ class Dataset():
 		self.num_classes = 10
 
 		# Upscale
-		self._resize_data(75, 75)
+		self._resize_data(32, 32)
 
 
 	def _resize_data(self, width, height):

### 2019-02-18 experiment.py

@@ -345,7 +345,7 @@ class Experiment():
 		:return: True if new metric is better than best metric or False otherwise.
 		"""
 		if self._best_metric is None or (
-				maximize and metric > self._best_metric or not maximize and metric <= self._best_metric):
+						maximize and metric > self._best_metric or not maximize and metric <= self._best_metric):
 			self._best_metric = metric
 			return True
 		return False
@@ -383,6 +383,10 @@ class Experiment():
 			**self.augmentation
 		)
 
+		# Augmentation for validation / test
+		eval_augmentation = {k: v for k, v in self.augmentation.items() if
+							 k == 'featurewise_center' or k == 'featurewise_std_normalization'}
+
 		# shear_range=0.2,
 		# zoom_range=0.2,
 		# horizontal_flip=True,
@@ -392,7 +396,7 @@ class Experiment():
 		# fill_mode='nearest',
 
 		# Validation data generator
-		val_datagen = tf.keras.preprocessing.image.ImageDataGenerator(rescale=self.rescale_factor)
+		val_datagen = tf.keras.preprocessing.image.ImageDataGenerator(rescale=self.rescale_factor, **eval_augmentation)
 
 		# Get database paths
 		train_path, val_path, _ = self.get_db_path(self.db)
@@ -413,6 +417,8 @@ class Experiment():
 		# Fit for zca_whitening, featurewise_center, featurewise_std_normalization
 		if 'zca_whitening' in self.augmentation or 'featurewise_center' in self.augmentation or 'featurewise_std_normalization' in self.augmentation:
 			train_datagen.fit(ds_train.x)
+			val_datagen.mean = train_datagen.mean
+			val_datagen.std = train_datagen.std
 
 		# Train data generator used for training
 		train_generator = train_datagen.flow(
@@ -556,8 +562,16 @@ class Experiment():
 
 		all_metrics = {}
 
+		# Augmentation for validation / test
+		eval_augmentation = {k: v for k, v in self.augmentation.items() if
+							 k == 'featurewise_center' or k == 'featurewise_std_normalization'}
+
+		mean = 0
+		std = 0
+
 		for path, set in zip(paths, ['Train', 'Validation', 'Test']):
 			print('\n=== {} dataset ===\n'.format(set))
+
 			# Load test dataset
 			ds_test = Dataset(path)
 
@@ -567,7 +581,19 @@ class Experiment():
 			img_size = ds_test.img_size
 
 			# Validation data generator
[…]

### 2019-02-27 paper/ieee.tex
paper

@@
+% !TeX spellcheck = en_GB
+
 %% bare_jrnl.tex
@@
 \usepackage{url}
-\usepackage{hyperref}
 % url.sty was written by Donald Arseneau. It provides better support for
@@
 
+\usepackage{color}
+
+\usepackage{ulem}
+
+\usepackage{array,booktabs}
+
+\usepackage{hyperref}
+
 % *** Do not adjust lengths that control margins, column widths, etc. ***
@@
 % correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+\hyphenation{op-tical net-works semi-conduc-tor mi-ni-mi-zes des-cri-bed di-ffe-rent sig-ni-fi-can-ce}
 
@@
 
-	\author{Victor-Manuel~Vargas, Pedro-Antonio~Gutiérrez and César~Hervás}
+	\author{Víctor-Manuel~Vargas, Pedro-Antonio~Gutiérrez and César~Hervás}
 
@@
 	% and "HIS" in caps to complete the first word.
-	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple Machine Learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
+	\textcolor{red}{Habría que restructurar la introducción: 1) deep learning y CNN, pero corto 2) clasificación ordinal, modelos de umbral, POM y funciones de enlace (más bien breve) 3) clasificación ordinal profunda 4) objetivo del paper (un estudio experimental sobre funciones de enlace y otros parámetros en deep learning ordinal).
+learning rate y batch normalization, si se mete, debería ser más breve}
+
+	1) \IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
 These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
-Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to indicate how a machine should change its internal parameters that are used to compute the representation in each layer from the features in the previous layer.
-
-	Convolutional Neural Networks (CNN) are designed to process data that comes in the form of multiple arrays.
-CNNs are suited for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
+\textcolor{blue}{\sout{Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to change the internal parameters of the model and compute better representations in each layer from the features in the previous layer.} Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that comes in the form of multiple arrays.} CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
 On image classification tasks, each colour channel is represented by a 2D array.
 In this case, convolutional layers extract the main features from the pixels of the images and, after that, a fully connected layer classify every sample based on its extracted features.
-At the output of the convolutional net, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks.
+At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks.
 These outputs are compared against the correct values.
 
-	The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
-It has been used in the last years in many works~\cite{leonard1990improvement,yu1995dynamic,krizhevsky2012imagenet,de2018weighted} for training shallow and deep neural networks.
-It updates the layer's parameters after backpropagating the loss function gradients through the network.
-Learning rate hyper-parameter controls the strength of the changes that are applied to those parameters.
-Some works have checked the importance of finding the optimal value for this parameter~\cite{senior2013empirical} and have tried different approaches to try to improve the training process~\cite{smith2017cyclical}.
-
-	Batch normalization is another technique that is used for this kind of networks.
-It reduces the internal covariate shift by normalizing layer inputs.
-It was presented in 2015~\cite{ioffe2015batch} and gives a critical enhancement to the training phase.
-Batch size is an important hyper-parameter that should be adjusted as it affects the layer's parameters updates and also the normalization~\cite{keskar2016large}\cite{radiuk2017impact}.
-
-	Ordinal classification problems are those where labels are ordered, and there are different inter-classes weights for each pair of classes.
-This kind of problem can be treated as a nominal classification problem, but when you do this, you are discarding ordinal information.
+	2) Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of classes.
+This kind of problem can be treated as a nominal classification problem, but this discards ordinal information.
 A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model.
-One way to use the ordinal information is to evaluate the model using an ordinal metric.
+\textcolor{blue}{\sout{One way to use the ordinal information is to evaluate the model using an ordinal metric.
 Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics,mehdiyev2016evaluating}.
@@
 Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables.
-Weighted kappa loss was described in previous work~\cite{de2018weighted} and is a cost function that is based on the WK metric.
-These functions are indicated for problems where different inter-classes weights are assigned, and that work proved that using these functions improves the model performance and reduce the overfitting risk.
-This kind of problems is associated with ordinal data processing.
-Those weights are predefined and depend on the type of the chosen WK.
-In a linear penalization, the weight is proportional to the distance between the predicted and the real class.
+An ordinal weighted kappa loss was described in a previous work~\cite{de2018weighted}, which is a differentiable cost function based on the WK metric.
+This previous work proved that using these functions improves the model performance and reduce the overfitting risk.
+Different weights can be assigned in an ordinal classification problem.
+In a linear penalization, the weight is proportional to the distance between the predicted and the real class (in number of categories).
 In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance.
-In this work, we will use the QWK metric and the QWK loss.
-
-	Softmax function is widely used for the output layer in neural networks for classification tasks.
-It is a simple and efficient function for multi-class problems but not the best when working with ordinal data.
-In this paper, the Proportional Odds Model (POM)~\cite{gutierrez2016ordinal,agresti2010analysis} will be used instead of the softmax function.
+In this work, we will use the QWK metric and the QWK loss.} The Proportional Odds Model (POM)~\cite{agresti2010analysis} is an ordinal alternative to the softmax function that was designed for ordinal regression.
+It belongs to a wider family of models called Cumulative Link Models (CLM).
+It is inspired in the concept of a latent variable that is projected in an n-dimensional space and a set of thresholds that divides this space into the different ordinal levels.
+This kind of models uses a link function which can be of different types.
+The most common link function is the \texttt{logit} one, that is used in POM.
+However, there are other functions that can be explored.
+This model will be described in depth in Section \ref{sect:ordinalproblem}.}
+
+	\textcolor{blue}{3) Ordinal models can also be applied to deep learning models.
+In the case of convolutional networks, the model projection used by the threshold model will be obtained from the last layer of the network.
+When working with a 1-dimensional space, the last layer will have only one neuron, and its value will be used to classify every sample in the corresponding class according to the thresholds.
+Some previous works have used the POM in traditional neural networks~\cite{gutierrez2016ordinal}, but it has not been applied to convolutional networks yet.
+Also, there are some link functions that has not been explored.}
+
+	\textcolor{blue}{4) In this paper, an experimental study regarding link functions for Cumulative Link Models will be made.
+Also, other parameters that can affect the training process and the model performance, like the learning rate of the optimization algorithm and the batch size, and its interaction will be studied.
+The nominal version of this model will be used as a baseline for comparison.
+We will contrast the results obtained with statistical analysis to provide more robust conclusions.
+An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.}
+
+	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy~\cite{de2018weighted}, which contains high-resolution fundus images related with diabetes disease, and Adience~\cite{beckham2017unimodal}, which includes human faces images associated with an age range.
+
+	This paper is organized as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper.
+Section~\ref{sect:ordinalproblem} present a formal description of an ordinal problem and the Cumulative Link Models.
+In Section~\ref{sect:experiments}, we describe the model, the experiments and the datasets used, while, in Section~\ref{sect:results}, we present the results obtained and the statistical analysis.
+Finally, Section~\ref{sect:conclusions} exposes the conclusions of this work.
+
+%	\textcolor{red}{The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
+It has been used in the last years in many works~\cite{leonard1990improvement,yu1995dynamic,krizhevsky2012imagenet,de2018weighted} for training shallow and deep neural networks.
+It updates the weights of each layer after backpropagating the loss function gradients through the network.
+The learning rate hyper-parameter controls the strength of the changes that are applied to the weights.
+Some works have checked the importance of finding the optimal value for this parameter~\cite{senior2013empirical} and have tried different approaches to improve the training process~\cite{smith2017cyclical}.}
+%	
+%	\textcolor{red}{Batch normalization is another technique used for this kind of networks.
+It reduces the internal covariate shift by normalizing layer inputs.
+It was presented in 2015~\cite{ioffe2015batch} and gives a critical enhancement during the training phase.
+Batch size is another important hyper-parameter that should be adjusted as it affects the weight updates and also the normalization~\cite{keskar2016large}\cite{radiuk2017impact}.}
+%	
+%	The softmax function is widely used for the output layer in neural networks for classification tasks.
+It is a simple and efficient function for multi-class problems, but it is not the best when working with ordinal data.
+In this paper, the Cumulative Link Model (CLM)~\cite{gutierrez2016ordinal,agresti2010analysis} will be used instead of the softmax function.
 Different link functions will be explored to compare their performance.
 Also, the influence of other parameters like the learning rate of the optimization algorithm and the batch size will be studied.
-We will contrast the results obtained with statistical analysis to provide more robust results.
+We will contrast the results obtained with statistical analysis to provide more robust conclusions.
 An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.
 
-	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy~\cite{de2018weighted}, that contains high-resolution fundus images related with diabetes disease, and Adience~\cite{beckham2017unimodal}, that is formed of human faces images that are assigned an age range.
-
-	This paper is organized as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper.
-Sections~\ref{sect:ordinalproblem} and \ref{sect:pom} present a formal description of an ordinal problem and the Proportional Odds Model.
-In Section~\ref{sect:experiments} we describe the model, the experiments and the datasets used, in Section~\ref{sect:results} we present the results obtained and the statistical analysis and finally in Section~\ref{sect:conclusions} we expose the conclusions of this work.
-
-	\section{Related work}
+	\section{Related works}
 	\label{sect:relatedwork}
-	There are many works related to the application and development of convolutional neural networks models. Few works treat ordinal classification problems, though.
+	There are many works related to the application and development of CNN models. However, few works are focused on ordinal classification problems.
 
 	J.
-de la Torre et al.~\cite{de2018weighted} proposed the use of QWK loss function for the optimization algorithm.
+de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the QWK loss function for the optimization algorithm.
 They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
-They proved that their function could improve the results as it reduces the overfitting and the required training time.
+They proved that their function could improve the results as it reduces overfitting and training time.
 Also, they checked the importance of hyper-parameter tuning.
-
-	Christopher Beckham and Christopher Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal via the use of the Poisson and binomial probability distributions.
-They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, and they obtained promising results.
+First, they defined QWK metric as follows:
+	\begin{equation}
+	\textcolor{blue}{\text{QWK} = 1 - \frac{\sum_{i,j} \omega_{i,j} O_{i,j}}{\sum_{i,j} \omega_{i,j} E_{i,j}},}
+	\end{equation}
+	\textcolor{blue}{where $\omega$ is the penalization matrix, $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.}
+
+	\textcolor{blue}{Then, they provided the QWK loss ($\text{QWK}_l$) definition below:}
+	\begin{equation}
+	\textcolor{blue}{\text{QWK}_l = 1 - \frac{\sum_{k=1}^N \sum_{c=1}^C \omega_{t_k, c} P_c(X_k)}{\sum_{i=1}^C \frac{N_i}{N} \sum_{j=1}^C ( \omega_{i,j} \sum_{k=1}^N P_j(X_k) ) },}
+	\end{equation}
+	\textcolor{blue}{where $X_k$ is the input data of the $k$th sample, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class and $P_c(X_k)$ is the conditional probability that the $k$th sample belongs to class $c$ given that the true class is $t_k$.}
+
+	\textcolor{blue}{Z.
+Niu et al.
+\cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using convolutional neural networks.
+They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively resolve these classification sub-problems, taking into account the correlation between them.}
+
+	Christopher Beckham and Christopher Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
+They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.	\textcolor{blue}{Also, they proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.}
 
@@
 Levi \cite{levi2015age} presented another convolutional network model for age estimation.
-
-	At present, there is a great discussion in terms of finding the best activation function that offers good performance and mitigates the effects of the gradients vanishing problem \cite{bengio1994learning,pascanu2013difficulty}.
+\textcolor{red}{Estos son ordinales?} \textcolor{blue}{No son ordinales pero los cito aqui porque luego los uso para comparar con ellos ya que son los que he encontrado que utilicen las base de datos Adience para predecir edad.}
+
+	\textcolor{blue}{H. Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease.}
+
+	\textcolor{blue}{Y.
+Liu et al.
+\cite{liu2017deep} proposed a new approach of which transforms the ordinal regression problem to binary classification problems and use triplets with instances from different categories to train deep neural networks.
+In this way, high-level features describing the ordinal relationship are extracted automatically.}
+
+	\textcolor{blue}{A.
+Rios et al.
+\cite{rios2017ordinal} presented a CNN model designed to handle ordinal regression tasks on psychiatric notes.
+They combined an ordinal loss function, a CNN model and conventional feature engineering.
+Also, they applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.}
+
+	\textcolor{blue}{S.
+Chen et al.
+\cite{chen2017using} proposed a deep method termed Ranking-CNN.
+This method combines multiple binary CNNs that are trained with ordinal age labels.
+The binary outputs are aggregated for the final age prediction and they achieved a tighter error bound for ranking-based age estimation.}
+
+	\textcolor{blue}{H.
+Fu et al.
+\cite{fu2018deep} applied deep learning techniques to Monocular Depth Estimation.
+They introduced a spacing-increasing discretization strategy to treat the problem as an ordinal regression problem.
+They improved the performance when training the network with an ordinary regression loss.
+Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.}
+
+	\textcolor{blue}{Y.
+Liu et al.
+\cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes de negative loglikelihood for multiple categories constrained by the order relationship between instances.}
+
+	\textcolor{blue}{A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.}
+
+	\textcolor{blue}{M.
+ALALI et al.
+\cite{alali2018multi} proposed a complex CNN architecture for solving Twitter Sentiment Classification as an ordinal problem.
+They checked that using average pooling preserves significant features that provide more expresiveness to ordinal scale.}
+
+	\textcolor{blue}{\sout{Currently, there is a great discussion in terms of finding the best activation function, offering good performance and mitigating the effects of the gradient vanishing problem \cite{bengio1994learning,pascanu2013difficulty}.
 Rectified Linear Unit (ReLU)~\cite{nair2010rectified} is widely used in most deep learning works, but recently, Clevert et al.
@@
 In their experiments, ELUs lead not only to faster learning but also to significantly better generalization performance than ReLUs and Leaky ReLU functions (LReLU) on networks with more than five layers.
-That's why we decided to use the ELU function for the experiments described in this paper.
-
-	Sergey Ioffe and Christian Szegedy~\cite{ioffe2015batch} described Batch Normalization and its benefits in previous work.
+In this way, this paper considers the ELU function for the different experiments.}}
+
+	\textcolor{blue}{\sout{Sergey Ioffe and Christian Szegedy~\cite{ioffe2015batch} described Batch Normalization and its benefits.
 It reduces the internal covariate shift by normalizing layer inputs.
@@
 It allows them to use higher learning rates and be less careful about initialization.
-It also eliminates the need for using regularization techniques like Dropout.
-
-	\section{Ordinal problem definition}
+It also eliminates the need for using regularization techniques like Dropout.}}
+
+	\section{Cumulative Link Models (CLM)}
 	\label{sect:ordinalproblem}
-	The ordinal problem consists of predicting the label y of an input vector $\mathbf{x}$, where $\mathbf{x} \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
+	An ordinal classification problem consists of predicting the label $y$ of an input vector $\mathbf{x}$, where $\mathbf{x} \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
 $\mathbf{x}$ is in a K-dimensional input space, and $y$ is in a label space of $Q$ different labels.
-The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ points, $D = \{(x_i, y_i), i = 1, ..., N\}$.
-A natural label ordering exists for ordinal problems: $\mathcal{C}_1 \prec \mathcal{C}_2 \prec ...
+The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ points, $D = \{(\mathbf{x}_i, y_i), i = 1, ..., N\}$.
+Labels have a natural ordering in ordinal problems: $\mathcal{C}_1 \prec \mathcal{C}_2 \prec ...
 \prec \mathcal{C}_Q$.
-The assumption of order between class labels makes that two different elements of $\mathcal{Y}$ can always be compared by using the relation $\prec$, which is not possible under the nominal classification setting.
+The order between labels makes it possible to compare two different elements of $\mathcal{Y}$ by using the relation $\prec$.
+This is not possible under the nominal classification setting.
 In regression (where $y \in \mathds{R}$), real values in $\mathds{R}$ can be ordered by the standard $<$ operator, but labels in ordinal regression ($y \in \mathcal{Y}$) do not carry metric information, so the category serves as a qualitative indication of the pattern rather than a quantitative one.
 
-	\section{Proportional Odds Model}
-	\label{sect:pom}
-	Arising from a statistical background, the Proportional Odds Model (POM) is one of the first models designed explicitly for ordinal regression~\cite{mccullagh1980regression}, dated back to 1980.
-It is a member of a wider family of models recognised as Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
+	The Proportional Odds Model (POM) arises from a statistical background and is one of the first models designed explicitly for ordinal regression~\cite{mccullagh1980regression}.
+It dated back to 1980 and is a member of a wider family of models recognised as Cumulative Link Models (CLM)~\cite{agresti2010analysis}.
 CLMs predict probabilities of groups of contiguous categories, taking the ordinal scale into account.
@@
 
-	The model is inspired by the notion of latent variable, considering a linear transformation $f(x) = \mathbf{w^Tx}$ of the input variables as the one-dimensional mapping.
-The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
-	\begin{equation}
-		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - \mathbf{w^Tx}, \quad q = 1, ..., Q-1,
-	\end{equation}
-	where $g^{-1} : [0,1] \rightarrow (-\infty, +\infty)$ is a monotonic function often termed as the inverse link function and $b_q$ is the threshold defined for class $\mathcal{C}_q$.
-Consider the latent variable $y^* = f(x)^* = \mathbf{w^Tx} + \epsilon$, where $\epsilon$ is the random variable of the error.
+	\textcolor{blue}{The model is inspired by the notion of a latent variable, where $f(x)$ represents a one-dimensional mapping obtained from the output of the last layer, which has only one neuron.} The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
+	\begin{equation}
+		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,
+	\end{equation}
+	where $g^{-1} : [0,1] \rightarrow (-\infty, +\infty)$ is a monotonic function often termed as the inverse link function, and $b_q$ is the threshold defined for class $\mathcal{C}_q$.
+Consider the latent variable $y^* = f(\mathbf{x})^* = \textcolor{blue}{f(\mathbf{x})} + \epsilon$, where $\epsilon$ is the random variable of the error.
 The most common choice for the probability distribution of $\epsilon$ is the logistic function (which is the default function for POM).
-Label $\mathcal{C}_q$ is proposed if and only if $f(x) \in [b_{q-1}, b_q]$, where the function $f$ and $\mathbf{b} = (b_0, b_1, ..., b_{Q-1}, b_Q)$ are to be determined from the data.
-it is assumed that $b_0 = -\infty$ and $b_Q = +\infty$, so the real line defined by $f(x), x \in \mathcal{X}$, is divided into $Q$ consecutive intervals.
+Label $\mathcal{C}_q$ is predicted if and only if $f(\mathbf{x}) \in [b_{q-1}, b_q]$, where the function $f$ and $\mathbf{b} = (b_0, b_1, ..., b_{Q-1}, b_Q)$ are to be determined from the data.
+It is assumed that $b_0 = -\infty$ and $b_Q = +\infty$, so the real line defined by $f(x), x \in \mathcal{X}$, is divided into $Q$ consecutive intervals.
 Each interval corresponds to a category.
@@
 \le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | \mathbf{x})$ increases with $q$ \cite{mccullagh1980regression}.
-	In this work, we use this ordinal model with different link functions for the probability distribution of $\epsilon$, including logit, probit and complementary log-log.
-These functions will be detailed in Section \ref{sect:model}.
-	\section{Experiments}
-	\label{sect:experiments}
-	\subsection{Data}
-	We make use of two ordinal datasets appropriate for deep neural networks:
-
-	\begin{itemize}
-		\item \textit{Diabetic Retinopathy (DR)}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}.
-DR is a dataset consisting of extremely high-resolution fundus image data.
-The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient).
-In this dataset, we try to predict from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
-The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions.
-These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition that was hosted on the Kaggle platform.
-Also, this dataset was used in later works~\cite{de2018weighted,nebot2016diabetic} and ordinal techniques (such as an ordinal cost function) were applied in order to achieve better performance.
-A validation set is set aside, consisting of $10\%$ of the patients in the training set.
-The images are resized to 128 by 128 pixels and rescaled to $[0,1]$ range.
-Data augmentation techniques, described in Section \ref{sect:procedure}, are applied to achieve a higher number of samples.
-
-		\item \textit{Adience}\footnote{http://www.openu.ac.il/home/hassner/Adience/data.html}.
-This dataset consists of $26580$ faces belonging to $2284$ subjects.
-We use the form of the dataset where faces have been pre-cropped and aligned.
-The dataset was preprocessed, using the methods described in a previous work~\cite{beckham2017unimodal}, so that the images are 256 pixels in width and height, and pixels values follow a $(0;1)$ normal distribution.
-The original dataset is split into five cross-validation folds.
-The training set consists of merging the first four folds which comprise a total of $15554$ images.
-From this, $10\%$ of the images are held out as part of a validation set.
-The last fold is used as test set.
-	\end{itemize}
-
-	\subsection{The model}
-	\label{sect:model}
-	Convolutional Neural Networks (CNN) has been used for both datasets.
-The different architectures of CNN used in these experiments are presented in tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
-The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
-For convolutional layers, ConvWxH@FsS = F filters of size WxH and stride S.
-For pooling layers, PoolWxHsS = pool size of WxH and stride S.
-
-	\begin{table}[!t]
-		\caption{Description of the architecture used in the DR experiments.}
-		\label{table:CNNArchitecture}
-		\centering
-		\begin{tabular}{|l|c|}
-			\hline
-			\textbf{Layer} & \textbf{Output shape}\\
-			\hline
-			%Conv3x3@32s1 & 254x254x32\\\hline
-			2 x Conv3x3@32s1 & 252x252x32\\\hline
-			MaxPool2x2s2 & 126x126x32\\\hline
-
-			%Conv3x3@64s1 & 124x124x64\\\hline
-			2 x Conv3x3@64s1 & 122x122x64\\\hline
-			MaxPool2x2s2 & 61x61x64\\\hline
-
-			%Conv3x3@128s1 & 59x59x128\\\hline
-			2 x Conv3x3@128s1 & 57x57x128\\\hline
-			MaxPool2x2s2 & 28x28x128\\\hline
-
-			%Conv3x3@128s1 & 26x26x128\\\hline
-			2 x Conv3x3@128s1 & 24x24x128\\\hline
-			MaxPool2x2s2 & 12x12x128\\\hline
-
-			Conv4x4@128s1 & 9x9x128\\
-			\hline
-		\end{tabular}	
-	\end{table}
-
-	\begin{table}[!t]
-		\caption{Description of the architecture used in the Adience experiments.}
-		\label{table:ResNetArchitecture}
-		\centering
-		\begin{tabular}{|l|c|}
-			\hline
-			\textbf{Layer} & \textbf{Output shape}\\
-			\hline
-			Conv7x7@32s2 & 112x112x32\\\hline
-			MaxPool3x3s2 & 55x55x32\\\hline
-			2 x ResBlock3x3@64s1 & 55x55x32\\\hline
-			1 x ResBlock3x3@128s2 & 28x28x64\\\hline
-			2 x ResBlock3x3@128s1 & 28x28x64\\\hline
-			1 x ResBlock3x3@256s2 & 14x14x128\\\hline
-			2 x ResBlock3x3@256s1 & 14x14x128\\\hline
-			1 x ResBlock3x3@512s2 & 7x7x256\\\hline
-			2 x ResBlock3x3@512s1 & 7x7x256\\\hline
-			AveragePool7x7s2 & 1x1x256\\
-			\hline
-		\end{tabular}	
-	\end{table}
+	\textcolor{blue}{This order is achieved by defining the first threshold and calculating the rest of thresholds from the first in the following form:}
+
+	\begin{equation}
+	\textcolor{blue}{b_n = b_1 + \sum_{i=1}^{n-1} \alpha_i^2, \quad n = 2, ..., N},
+	\end{equation}
+	\textcolor{blue}{where $b_1$ and $\alpha_i$ are learnable parameters, and $N$ is the number of classes.}
+
+	In this work, we use this ordinal model with different link functions for the probability distribution of $\epsilon$, including \texttt{logit}, \texttt{probit} and complementary log-log (\texttt{clog-log}).
+
+	These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
+They all follow the same form $P(y \prec \mathcal{C}_q) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})})$ for a continuous cdf~$\Phi$.
 
@@
 
-	Every convolutional layer is followed by an ELU activation layer~\cite{clevert2015fast} and a batch normalization~\cite{ioffe2015batch}.
-At the output, a Proportional Odds Model is used with different link functions~\cite{agresti2010analysis}.
-The logit link function is commonly used within POM.
-In this paper, we are comparing other link functions like probit or complementary log-log with the logit link.
-These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
-They all follow the same form $P(y \prec \mathcal{C}_q) = \Phi(b_q-\mathbf{w^Tx})$ for a continuous cdf~$\Phi$.
-
 	\begin{itemize}
-		\item \textit{Logit}. Logit link function is the most widely used function for Proportional Odds Models. The logit link is shown in \ref{eq:logit} and \ref{eq:logit2}.
+		\item \texttt{Logit}. \texttt{logit} link function is the function used for the Proportional Odds Model. The \texttt{logit} link is:
 		\begin{equation}
 		\begin{aligned}
-		logit[P(y \preceq \mathcal{C}_q)] = log\frac{P(y \preceq \mathcal{C}_q)}{1 - P(y \preceq \mathcal{C}_q)}=& \\ = b_q - \mathbf{w^Tx}, \quad q = 1, ..., Q-1
+		\text{logit}[P(y \preceq \mathcal{C}_q)] = \log\frac{P(y \preceq \mathcal{C}_q)}{1 - P(y \preceq \mathcal{C}_q)}=& \\ = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,
 		\end{aligned}
@@
 		\end{equation}		
-
-		or the equivalent expression
-
-		\begin{equation}
-		P(y \preceq \mathcal{C}_q) = \frac{1}{1 + e^{-(b-\mathbf{w^Tx})}}
+		or the equivalent expression:		
+		\begin{equation}
+		P(y \preceq \mathcal{C}_q) = \frac{1}{1 + e^{-(b - \textcolor{blue}{f(\mathbf{x})})}}.
 		\label{eq:logit2}
 		\end{equation}
-		\item \textit{Probit}. Probit link function is the inverse of the standard normal cummulative distribution function (cdf) $\Phi$. Its expression is shown in \ref{eq:probit} and \ref{eq:probit2}.	
+
+		\item \texttt{Probit}. \texttt{probit} link function is the inverse of the standard normal cumulative distribution function (cdf) $\Phi$. Its expression is:
 		\begin{equation}
 		\begin{aligned}
-		&\Phi^{-1}[P(y \preceq \mathcal{C}_q)] = b_q - \mathbf{w^Tx}, &q = 1, ..., Q-1\\
-		&P(y \preceq \mathcal{C}_q) = \Phi(b_q - \mathbf{w^Tx}), &q = 1, ..., Q-1		
+		&\Phi^{-1}[P(y \preceq \mathcal{C}_q)] = b_q - \textcolor{blue}{f(\mathbf{x})}, &q = 1, ..., Q-1\\
+		&P(y \preceq \mathcal{C}_q) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}), &q = 1, ..., Q-1,
 		\end{aligned}
@@
 		\end{equation}		
-
-		or
-
-		\begin{equation}
-		P(y \preceq \mathcal{C}_q) = \int_{-\infty}^{b_q - \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
+		which can also be expressed as:
+		\begin{equation}
+		P(y \preceq \mathcal{C}_q) = \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
 		\label{eq:probit2}
@@
 		\item \textit{Complementary log-log}.
-Like the logit and the probit transformation, the complementary log-log transformation takes a response that is restricted to the (0,1) interval and converts it into something in $(-\infty, +\infty)$ interval.
-Complementary log-log expression is shown in \ref{eq:cloglog} and \ref{eq:cloglog2}.
+Like the \texttt{logit} and the \texttt{probit} transformation, the complementary log-log transformation takes a response that is restricted to the $(0,1)$ interval and converts it into something in the $(-\infty, +\infty)$ interval.
+Complementary log-log expression is:
 		\begin{equation}
 		\begin{aligned}
-		log[-log[1 - P(y \preceq \mathcal{C}_q)]] =&\\
-		= b_q - \mathbf{w^Tx}, \quad q = 1, ..., Q-1&
+		\log[-\log[1 - P(y \preceq \mathcal{C}_q)]] =&\\
+		= b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,&
 		\end{aligned}
@@
 		\end{equation}
-
-		or
-
-		\begin{equation}
-		P(y \preceq \mathcal{C}_q) = 1 - e^{-e^{b_q - \mathbf{w^Tx}}}, \quad q = 1, ..., Q-1
+		that is:
+		\begin{equation}
+		P(y \preceq \mathcal{C}_q) = 1 - e^{-e^{b_q - \textcolor{blue}{f(\mathbf{x})}}}, \quad q = 1, ..., Q-1.
 		\label{eq:cloglog2}
@@
 
-	Logit and probit links are symmetric, that is
-
-	\begin{equation}
-	link[P(y \preceq \mathcal{C}_q)] = -link[1 - P(y \preceq \mathcal{C}_q)]
-	\end{equation}
-
-	This means that the response curve for $P(y \preceq \mathcal{C}_q)$ has a symmetric appearance about the point $P(y \preceq \mathcal{C}_q) = 0.5$, and so $P(y \preceq \mathcal{C}_q)$ has the same rate for approaching 0 than for approaching 1.
+	\texttt{Logit} and \texttt{probit} links are symmetric:	
+	\begin{equation}
+	\text{link}[P(y \preceq \mathcal{C}_q)] = -\text{link}[1 - P(y \preceq \mathcal{C}_q)],
+	\end{equation}
+	which means that the response curve for $P(y \preceq \mathcal{C}_q)$ is symmetric around the point $P(y \preceq \mathcal{C}_q) = 0.5$, i.e.
+$P(y \preceq \mathcal{C}_q)$ has the same rate when approaching 0 than when approaching 1.
 This symmetric property can be demonstrated as follows:
-
 	\begin{enumerate}
-		\item If we define $P(y \preceq \mathcal{C}_q) \equiv p$, we have
+		\item Let $P(y \preceq \mathcal{C}_q) \equiv p$. For the \texttt{logit} function, we have:
 		\begin{equation}
 		\begin{aligned}
-			link(p) = logit(p) &= log\left(\frac{p}{1-p}\right) =\\
-			&= log(p) - log(1-p)
+		\text{link}(p) = \text{logit}(p) &= \log\left(\frac{p}{1-p}\right) =\\
+		&= \log(p) - \log(1-p),
 		\end{aligned}
 		\end{equation}			
-
-			while
-
+		while:			
 		\begin{equation}
 		\begin{aligned}
-			-link(1 - p) &= -logit(1 - p) =\\
-			=- log\left(\frac{1- p}{p}\right) &= - log(1 - p) + log(p)
+		-\text{link}(1 - p) &= -\text{logit}(1 - p) =\\
+		=- \log\left(\frac{1- p}{p}\right) &= - \log(1 - p) + \log(p).
 		\end{aligned}
@@
 
-			The symmetry has been proven for logit link.
-
-		\item If we define
-
+		\item For the \texttt{probit}:		
 		\begin{equation}
 		\begin{aligned}
-		p \equiv P(y \preceq \mathcal{C}_q) &= \Phi(b_q - \mathbf{w^Tx}) =\\
-		&= \int_{-\infty}^{b_q - \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
+		p \equiv P(y \preceq \mathcal{C}_q) &= \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}) =\\
+		&= \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
 		\end{aligned}
 		\end{equation}
-
-		then
-
-		\begin{equation}
-		probit(p) = \Phi^{-1}(p) = b_q - \mathbf{w^Tx}
-		\end{equation}
-
-		and
-
-		\begin{equation}
-		-probit(1-p) = \Phi^{-1}(1-p) = -b_q + \mathbf{w^Tx}
-		\end{equation}
-
-		where
-
-		\begin{equation}
-		1 - p = \int_{-\infty}^{-b_q + \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
-		\end{equation}
-
-		and
-
-		\begin{equation}
-		p = 1 - \int_{-\infty}^{-b_q + \mathbf{w^Tx}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} dx
-		\end{equation}
-
-		the symmetric property for the probit function has been proven.
+		which leads to:
+		\begin{align}
+		\text{probit}(p) & = \Phi^{-1}(p) = b_q - \textcolor{blue}{f(\mathbf{x})},\\
+		-\text{probit}(1-p) &= \Phi^{-1}(1-p) = -b_q + \textcolor{blue}{f(\mathbf{x})},
+		\end{align}
+		where:		
+		\begin{equation}
+		1 - p = \int_{-\infty}^{-b_q + \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
+		\end{equation}
+		\begin{equation}
+		p = 1 - \int_{-\infty}^{-b_q + \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
+		\end{equation}
 	\end{enumerate}
 
-	Unlike logit and probit, the complementary log-log model is asymmetrical.
+	Unlike \texttt{logit} and \texttt{probit}, the complementary log-log model is asymmetrical.
 It is frequently used when the probability of an event is very small or very large.
-When the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the logit and probit models are inappropriate.
+When the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate.
 However, in this situation, the complementary log-log model might give a satisfying answer.
 
-	\subsection{Procedure}
-	\label{sect:procedure}
+	\section{Experiments}
+	\label{sect:experiments}
+	\subsection{Data}
+	In order to evaluate the different models, we make use of two ordinal datasets:
+
+	\begin{itemize}
+		\item \textit{Diabetic Retinopathy (DR)}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}.
+DR is a dataset consisting of extremely high-resolution fundus image data.
+The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient).
+In this dataset, we try to predict the correct category from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
+The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions.
+These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition hosted on the Kaggle platform.
+Also, this dataset was used in later works~\cite{de2018weighted,nebot2016diabetic}, applying an ordinal QWK cost function in \cite{de2018weighted} to achieve better performance.
+A validation set is set aside, consisting of $10\%$ of the patients in the training set.
+The images are resized to 128 by 128 pixels and rescaled to $[0,1]$ range.
+Data augmentation techniques, described in Section \ref{sect:settings}, are applied to achieve a higher number of samples.
+A few images of this dataset are shown in Figure \ref{fig:DRexamples}.
+
+		\begin{figure}[!t]
+			\centering
+			\begin{tabular}{cccc}
+			\includegraphics[width=1.6cm]{img/retinopathy/1.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/2.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/3.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/4.jpg}\\
+			\includegraphics[width=1.6cm]{img/retinopathy/5.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/6.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/7.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/8.jpg}
+			\end{tabular}						
+			\caption{Examples of the Diabetic Retinopathy test set.}
+			\label{fig:DRexamples}
+		\end{figure}
+
+		\item \textit{Adience}\footnote{http://www.openu.ac.il/home/hassner/Adience/data.html}.
+This dataset consists of $26580$ faces belonging to $2284$ subjects.
+We use the form of the dataset where faces have been pre-cropped and aligned.
+The dataset was preprocessed, using the methods described in a previous work~\cite{beckham2017unimodal}, so that the images are 256 pixels in width and height, and pixels values follow a $(0;1)$ normal distribution.
+The original dataset was split into five cross-validation folds.
+The training set consists of merging the first four folds which comprise a total of $15554$ images.
+From this, $10\%$ of the images are held out as part of a validation set.
+The last fold is used as test set.
+Some images of this dataset are shown in Figure \ref{fig:AdienceExamples}.
+
+		\begin{figure}[!t]
+			\centering
+			\begin{tabular}{cccc}
+				\includegraphics[width=1.6cm]{img/adience/1.jpg} & \includegraphics[width=1.6cm]{img/adience/2.jpg} & \includegraphics[width=1.6cm]{img/adience/3.jpg} & \includegraphics[width=1.6cm]{img/adience/4.jpg}\\
+				\includegraphics[width=1.6cm]{img/adience/5.jpg} & \includegraphics[width=1.6cm]{img/adience/6.jpg} & \includegraphics[width=1.6cm]{img/adience/7.jpg} & \includegraphics[width=1.6cm]{img/adience/8.jpg}
+			\end{tabular}						
+			\caption{Examples of the Diabetic Retinopathy test set.}
+			\label{fig:AdienceExamples}
+		\end{figure}
+	\end{itemize}
+
+	\subsection{Model}
+	\label{sect:model}
+	CNNs have been used for both datasets.
+The different architectures of CNN used in these experiments are presented in tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
+The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
+\textcolor{blue}{The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved for obtaining the next pixel.
+Pooling layers have got similar parameters: the pool size is the number of pixels that will be involved in the pooling operation, and the stride represents the same concept that in convolutional layers.} For convolutional layers, ConvWxH@FsS~=~F filters of size WxH and stride S.
+For pooling layers, PoolWxHsS~=~pool size of WxH and stride S.
+
+	\textcolor{blue}{The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used for activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradients problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
+Also, ELUs lead to faster training and better generalization performance than ReLU and Leaky ReLU (LReLU)~\cite{maas2013rectifier} functions on networks with more than five layers.}
+
+	\textcolor{blue}{After every ELU activation function of the convolutional layers, Batch Normalization~\cite{ioffe2015batch} is applied.
+This method reduces the internal covariate shift by normalizing layer outputs.
+It allows us to use higher learning rates and be less careful about weights initialization.
+It also eliminates the need for using regularization techniques like Dropout.}
+
+	\textcolor{blue}{At the output of the network, the CLM is used.
+Also, a learnable parameter has been used to rescale the projections used by the Cumulative Link Model to make it more stable and guarantee the convergence in most cases.}
+
+	\begin{table}[!t]
+		\caption{Description of the architecture used in the DR experiments.}
+		\label{table:CNNArchitecture}
+		\centering
+		\begin{tabular}{lc}
+			\hline
+			\hline
+			\textbf{Layer} & \textbf{Output shape}\\
+			\hline
+			%Conv3x3@32s1 & 254x254x32\\\hline
+			2 x Conv3x3@32s1 & 252x252x32\\
+			MaxPool2x2s2 & 126x126x32\\
+
+			%Conv3x3@64s1 & 124x124x64\\\hline
+			2 x Conv3x3@64s1 & 122x122x64\\
+			MaxPool2x2s2 & 61x61x64\\
+
+			%Conv3x3@128s1 & 59x59x128\\\hline
+			2 x Conv3x3@128s1 & 57x57x128\\
+			MaxPool2x2s2 & 28x28x128\\
+
+			%Conv3x3@128s1 & 26x26x128\\\hline
+			2 x Conv3x3@128s1 & 24x24x128\\
+			MaxPool2x2s2 & 12x12x128\\
+
+			Conv4x4@128s1 & 9x9x128\\
+			\hline
+			\hline
+		\end{tabular}	
+	\end{table}
+
+	\begin{table}[!t]
+		\caption{Description of the architecture used in the Adience experiments.}
+		\label{table:ResNetArchitecture}
+		\centering
+		\begin{tabular}{lc}
+			\hline
+			\hline
+			\textbf{Layer} & \textbf{Output shape}\\
+			\hline
+			Conv7x7@32s2 & 112x112x32\\
+			MaxPool3x3s2 & 55x55x32\\
+			2 x ResBlock3x3@64s1 & 55x55x32\\
+			1 x ResBlock3x3@128s2 & 28x28x64\\
+			2 x ResBlock3x3@128s1 & 28x28x64\\
+			1 x ResBlock3x3@256s2 & 14x14x128\\
+			2 x ResBlock3x3@256s1 & 14x14x128\\
+			1 x ResBlock3x3@512s2 & 7x7x256\\
+			2 x ResBlock3x3@512s1 & 7x7x256\\
+			AveragePool7x7s2 & 1x1x256\\
+			\hline
+			\hline
+		\end{tabular}	
+	\end{table}
+
+	\subsection{Experimental design}
+	\label{sect:settings}
 	The model is optimized using a batch based first-order optimization algorithm called Adam~\cite{kingma2014adam}.
@@
 However, different transformations were applied to each one.
-Diabetic Retinopathy dataset augmentation was based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
+DR dataset augmentation was based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
 Horizontal flipping was the only transformation applied to Adience dataset.
 
-	In the case of Diabetic Retinopathy Detection, the epoch size has been fixed to $100000$ images per epoch. For the Adience dataset, epoch size is the number of images in the training set.
-
-	The model is evaluated with Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}.
-This evaluation measure gives a higher weight to the errors that are further from the correct class.
+	In the case of DR dataset, the epoch size has been fixed to $100000$ images per epoch. For the Adience dataset, epoch size is the number of images in the training set.
+
+	The model is evaluated using the Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
 	Quadratic weighted kappa loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems \cite{de2018weighted}.
@@
 
-	Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of the QWK loss and the Proportional Odds Model.
-The results of these experiments are analysed in Section \ref{app:NominalComparison}.
+	Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the Cumulative Link Model).
+The results of these experiments are analysed in Section \ref{sect:NominalComparison}.
 
@@
 	\begin{itemize}
-		\item \textit{Learning rate}.
+		\item \textit{Learning rate} (LR, $\eta$).
 Learning rate is one of the most critical hyper-parameters to tune for training deep neural networks.
@@
 Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
-		\item \textit{Batch size}.
+		\item \textit{Batch size} (BS).
 Batch size is also an important parameter as it controls the number of weight updates that are made on every epoch.
@@
 In this paper, we have tried three separate batch sizes for each dataset.
-For DR dataset, we have used $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ was used.
+For DR dataset, we have used $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ images were used.
 We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expanded the range on both sides.
-		\item \textit{Link function}. Different link functions have been used for the POM at the last layer output: logit, probit and complementary log-log.
+		\item \textit{Link function} (LF). Different link functions have been used for the CLM at the last layer output: \texttt{logit}, \texttt{probit} and complementary log-log.
 	\end{itemize}
@@
 	In this section, we present the results of the experiments.
-For each dataset, we show a table with the detailed experiments done training the model with each combination of parameters.
+For each dataset, we show a table with the detailed experiments performed for training the model with each combination of parameters.
 Every parameter combination has been run five times.
 These tables show the mean value and the standard deviation (SD) of each metric across these five executions for the test set.
-These values are exposed using the format $\text{MEAN}_{(SD)}$.
 
@@
 	\label{sect:dr}
-	Detailed results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}. The best result for each metric is marked in bold and the second best is in italic font.
+	Detailed \textcolor{blue}{test results} for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}.
+The best result for each metric is marked in bold and the second best is in italic font.
 
 	\begin{table*}[!t]
-		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LF for link function and LR for Learning Rate.}
+		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LF for link function and LR for Learning Rate. Mean and standard deviation $\text{Mean}_\text{SD}$.}
 		\label{table:DRresults}
@@
 		\centering
-		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c|c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+			\hline
+			\hline
 			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-			5 & c log-log & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.165_{(0.020)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
-			5 & c log-log & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.123_{(0.004)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
-			5 & c log-log & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.104_{(0.001)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
-			5 & logit & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.162_{(0.018)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
-			5 & logit & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.123_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
-			5 & logit & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.102_{(0.001)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
-			5 & probit & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.182_{(0.053)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
-			5 & probit & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.132_{(0.014)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
-			5 & probit & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.105_{(0.001)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
-			10 & c log-log & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.120_{(0.014)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
-			10 & c log-log & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.115_{(0.002)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
-			10 & c log-log & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.096_{(0.001)}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
-			10 & logit & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.140_{(0.008)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
-			10 & logit & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.113_{(0.004)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
-			10 & logit & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.095_{(0.002)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
-			10 & probit & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.137_{(0.014)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
-			10 & probit & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.120_{(0.002)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
-			10 & probit & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.098_{(0.001)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
-			15 & c log-log & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.134_{(0.005)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
-			15 & c log-log & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
-			15 & c log-log & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $\mathit{0.093_{(0.001)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
-			15 & logit & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.129_{(0.009)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
-			15 & logit & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.114_{(0.005)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
-			15 & logit & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.090_{(0.001)}}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
-			15 & probit & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.138_{(0.014)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
-			15 & probit & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.116_{(0.005)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
-			15 & probit & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $0.094_{(0.001)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$
+			5 & \texttt{clog-log} & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.165_{(0.020)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
+			5 & \texttt{clog-log} & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.123_{(0.004)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
+			5 & \texttt{clog-log} & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.104_{(0.001)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
+			5 & \texttt{logit} & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.162_{(0.018)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
+			5 & \texttt{logit} & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.123_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
+			5 & \texttt{logit} & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.102_{(0.001)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
+			5 & \texttt{probit} & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.182_{(0.053)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
+			5 & \texttt{probit} & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.132_{(0.014)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
+			5 & \texttt{probit} & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.105_{(0.001)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
+			10 & \texttt{clog-log} & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.120_{(0.014)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
+			10 & \texttt{clog-log} & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.115_{(0.002)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
+			10 & \texttt{clog-log} & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.096_{(0.001)}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
+			10 & \texttt{logit} & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.140_{(0.008)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
+			10 & \texttt{logit} & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.113_{(0.004)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
+			10 & \texttt{logit} & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.095_{(0.002)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
+			10 & \texttt{probit} & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.137_{(0.014)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
+			10 & \texttt{probit} & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.120_{(0.002)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
+			10 & \texttt{probit} & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.098_{(0.001)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
+			15 & \texttt{clog-log} & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.134_{(0.005)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
+			15 & \texttt{clog-log}g & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
+			15 & \texttt{clog-log} & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $\mathit{0.093_{(0.001)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
+			15 & \texttt{logit} & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.129_{(0.009)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
+			15 & \texttt{logit} & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.114_{(0.005)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
+			15 & \texttt{logit} & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.090_{(0.001)}}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
+			15 & \texttt{probit} & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.138_{(0.014)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
+			15 & \texttt{probit} & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.116_{(0.005)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
+			15 & \texttt{probit} & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $0.094_{(0.001)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$\\
+			\hline
+			\hline
 		\end{tabular}
@@
 	The best mean QWK value was obtained with the complementary log-log link function using a batch size of 10 and a learning rate of $10^{-3}$.
-However, the best CCR value was obtained with a batch size of 15, the logit link and a learning rate of $10^{-4}$.
+However, the best CCR value was obtained with a batch size of 15, the \texttt{logit} link and a learning rate of $10^{-4}$.
 The optimal configuration depends on the metric we are analysing.
 In this case, as we are working with an ordinal problem, the most reliable metric is the QWK.
+\textcolor{red}{No se entonces si tiene sentido poner el resto de métricas???} \textcolor{blue}{Están puestas para comparar con artículos que no dan el QWK.}
 
@@
 	\label{sect:adience}
-	Results for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}. The best result for each metric is marked in bold and the second best is in italic font.
+	\textcolor{blue}{Test results} for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}.
+The best result for each metric is marked in bold and the second best is in italic font.
 
 	\begin{table*}[!t]
-		\caption{Adience test results. BS stands for Batch Size, LF for link function and LR for Learning Rate.}
+		\caption{Adience test results. BS stands for Batch Size, LF for link function and LR for Learning Rate. Mean and standard deviation $\text{Mean}_\text{SD}$.}
 		\label{table:AdienceTest}
@@
 		\centering
-		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c|c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+			\hline
+			\hline
 			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-			64 & c log-log & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.129_{(0.007)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
-			64 & c log-log & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $0.101_{(0.003)}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
-			64 & c log-log & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.100_{(0.002)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
-			64 & logit & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.137_{(0.007)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
-			64 & logit & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $0.098_{(0.003)}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
-			64 & logit & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.108_{(0.004)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
-			64 & probit & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.121_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
-			64 & probit & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.105_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
-			64 & probit & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.100_{(0.002)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
-			128 & c log-log & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.117_{(0.002)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
-			128 & c log-log & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.100_{(0.001)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
-			128 & c log-log & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.125_{(0.004)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
-			128 & logit & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.125_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
-			128 & logit & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.099_{(0.003)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
-			128 & logit & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.151_{(0.005)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
-			128 & probit & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.115_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
-			128 & probit & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.100_{(0.003)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
-			128 & probit & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.110_{(0.002)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
-			256 & c log-log & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.110_{(0.001)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
-			256 & c log-log & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.097_{(0.004)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
-			256 & c log-log & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.165_{(0.004)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
-			256 & logit & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.125_{(0.015)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
-			256 & logit & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $\mathbf{0.094_{(0.002)}}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
-			256 & logit & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.191_{(0.002)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
-			256 & probit & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.112_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
-			256 & probit & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $\mathit{0.095_{(0.001)}}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
-			256 & probit & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.150_{(0.005)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$
+			64 & \texttt{clog-log} & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.129_{(0.007)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
+			64 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $0.101_{(0.003)}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
+			64 & \texttt{clog-log} & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.100_{(0.002)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
+			64 & \texttt{logit} & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.137_{(0.007)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
+			64 & \texttt{logit} & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $0.098_{(0.003)}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
+			64 & \texttt{logit} & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.108_{(0.004)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
+			64 & \texttt{probit} & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.121_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
+			64 & \texttt{probit} & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.105_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
+			64 & \texttt{probit} & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.100_{(0.002)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
+			128 & \texttt{clog-log} & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.117_{(0.002)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
+			128 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.100_{(0.001)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
+			128 & \texttt{clog-log} & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.125_{(0.004)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
+			128 & \texttt{logit} & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.125_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
+			128 & \texttt{logit} & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.099_{(0.003)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
+			128 & \texttt{logit} & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.151_{(0.005)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
+			128 & \texttt{probit} & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.115_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
+			128 & \texttt{probit} & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.100_{(0.003)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
+			128 & \texttt{probit} & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.110_{(0.002)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
+			256 & \texttt{clog-log} & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.110_{(0.001)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
+			256 & \texttt{clog-log} & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.097_{(0.004)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
+			256 & \texttt{clog-log} & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.165_{(0.004)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
+			256 & \texttt{logit} & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.125_{(0.015)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
+			256 & \texttt{logit} & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $\mathbf{0.094_{(0.002)}}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
+			256 & \texttt{logit} & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.191_{(0.002)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
+			256 & \texttt{probit} & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.112_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
+			256 & \texttt{probit} & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $\mathit{0.095_{(0.001)}}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
+			256 & \texttt{probit} & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.150_{(0.005)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$\\
+			\hline
+			\hline
 		\end{tabular}
@@
 
-	The best mean QWK value was obtained with the logit link function using a batch size of 64 and a learning rate of $10^{-4}$.
+	The best mean QWK value was obtained with the \texttt{logit} link function using a batch size of 64 and a learning rate of $10^{-4}$.
 Also, this configuration obtained the best score for Top-2, Top-3 and 1-off accuracy, and the second best for MS, MAE and CCR.
@@
 	\label{sect:statisticalanalysis}
-	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the results presented in this section.
-
-	The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each, were obtained using the ANalysis Of the VAriance (ANOVA) test.
+	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the result,
+
+	The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each of them, were obtained using an ANalysis Of the VAriance (ANOVA).
 
@@
 	ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
-Considered factors are the link function, which can be logit, probit and complementary log-log, the learning rate for the Adam optimization algorithm ($10^{-2}$, $10^{-3}$ and $10^{-4}$) and the batch size (5, 10 and 15 for DR and 64, 128 and 256 for Adience).
+Considered factors are the link function\textcolor{blue}{\sout{, which can be \texttt{logit}, \texttt{probit} and complementary log-log,}} the learning rate for the Adam optimization algorithm \textcolor{blue}{\sout{($10^{-2}$, $10^{-3}$ and $10^{-4}$)}}, and the batch size \textcolor{blue}{\sout{(5, 10 and 15 for DR and 64, 128 and 256 for Adience)}}.
+\textcolor{red}{Esto está repitiendo mucho}
 
@@
 
-	We denote by $QWK_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the i-th level, the second at the j-th level and the third at k-th level.
+	We denote by $QWK_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level.
 We assume that the three factors do not act independently and therefore there exists an interaction between each pair of them and between the three factors.
-In this case, the observations fit \ref{eq:anova3}.
-
+In this case, the observations fit:
 	\begin{equation}
@@
 	\footnotesize
-	QWK_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l}
+	QWK_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
 	\label{eq:anova3}
@@
 	\end{equation}
-
-	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (logit, probit, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the parameter factor and $B_k$ is the effect associated with the \textit{k-th} level of the batch size factor.
+	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (\texttt{logit}, \texttt{probit}, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the learning rate factor and $B_k$ is the effect associated with the \textit{k-th} level of the batch size factor.
 The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors.
@@
 
-	We consider some hypotheses testing where the null hypothesis is proposed that each term of the above equation is independent of the levels involved. The hypotheses for the levels of the L factor are
-	\[
-	H_0 \equiv L_1 = L_2 = L_3
-	\]
-	\[
-	H_1 \equiv \text{ some } L_i \text{ is different}
-	\]
+	We consider some hypotheses testing where the null hypothesis is proposed that each term of the above equation is independent of the levels involved.
+The hypotheses for the levels of the L factor are $H_0 \equiv L_1 = L_2 = L_3,$ and $H_1 \equiv \text{ some } L_i \text{ is different}$.
 
@@
 
-	The hypothesis associated with the interaction between L and P is
-	\[
-	H_0 \equiv LP_{i,j} = 0 \quad \forall i,j
-	\]
-	\[
-	H_1 \equiv \exists LP_{i,j} \ne 0
-	\]
-
+	The hypothesis associated with the interaction between $L$ and $P$ is $H_0 \equiv LP_{i,j} = 0, \forall i,j$, and $H_1 \equiv \exists LP_{i,j} \ne 0$.
 Similar hypotheses can be assumed for the interaction between the other factors.
 
-	The analysis of variance table containing the sum of squares, degrees of freedom, mean square, test statistics and significance level represent the initial study in a compact form, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
+	The analysis of variance table represents the initial study in a compact form, containing the sum of squares, degrees of freedom, mean square, test statistics and significance level, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
 These factors and interactions take part of the error component now.
+In this way, the results of the ANOVA III test for the Diabetic Retinopathy dataset are summarised in Table  \ref{table:ANOVARetinopathy}.
+There are significant differences in average QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$ ($\text{p-value} = 0.000$).
+Moreover, an interaction between the link function and the learning rate can be recognised ($\text{p-value} = 0.001$).
+It means that the learning rate and the link functions have a significant impact on the optimization algorithm results.
 
@@
 		\small
-		\begin{tabular}{l|ccccc}
+		\begin{tabular}{lccccc}
+			\hline
+			\hline
 			           \multicolumn{6}{c}{Response variable QWK}             \\ \hline
@@
 			Error        & $0.339$  & $126$ & $0.003$ &            &  \\ \hline
-			Total        & $38.199$ & $135$ &         &            &
+			Total        & $38.199$ & $135$ &         &            & \\
+			\hline
+			\hline
 		\end{tabular}
@@
 
-	The results of the ANOVA III test for the Diabetic Retinopathy dataset are resumed in Table \ref{table:ANOVARetinopathy}.
-There are significative differences in the means of QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$ ($\text{p-value} = 0.000$).
-Moreover, an interaction between the link function and the learning rate can be recognised ($\text{p-value} = 0.001$).
-It means that the learning rate and the link functions have a significative impact on the optimization algorithm results.
-
-	As Table \ref{table:ANOVARetinopathy} showed that there exist significative differences between the means, we are now analysing those differences.
+	Given that there exist significant differences between the means, we analyse now those differences.
 A post-hoc multiple comparison test has been performed on the mean QWK obtained.
-An HSD Tukey's test \cite{tukey1949comparing} was made under the null hypothesis that the variance of the error of the dependent variable is the same between groups.
-The results over the test set show that the best link function is the complementary log-log, though it doesn't have significative differences with the probit function ($\text{p-value} = 0.248$).
-There are differences between the complementary log-log and the probit function concerning the logit function (p-values $0.000$ and $0.011$).
-
-	The results have been obtained following a similar methodology with the different values of the learning parameter including the HSD Tukey's test and the learning parameter ranking.
-Significative differences can be observed in the mean values for $\eta = 10^{-3}$ with respect to the other values of the parameter (p-values $0.023$ for $10^{-4}$ and $0.000$ for $10^{-2}$).
+An HSD Tukey's test \cite{tukey1949comparing} was made under the null hypothesis that the variance of the error of the dependent variable is the same between the groups.
+\textcolor{blue}{The results of this test over the test set are shown in Table \ref{table:TukeyDR}.
+They show that the best link function is the complementary log-log but the \texttt{probit} link performance is close to it.
+Also, the best value for the learning rate parameter is $10^{-3}$.
+The batch size is not relevant for this dataset with the values considered.}
+
+%	The results over the test set show that the best link function is the complementary log-log, though it does not present significant differences with respect to the probit function ($\text{p-value} = 0.248$).
+There are differences between the complementary log-log and the probit function with respect to the logit function (p-values $0.000$ and $0.011$, respectively).
+A similar methodology has been applied to the different values of the learning rate.
+Significant differences can be observed in the mean values for $\eta = 10^{-3}$ with respect to the other values of the parameter (p-values $0.023$ for $10^{-4}$ and $0.000$ for $10^{-2}$).
 Also, there are differences for $\eta = 10^{-4}$ concerning $\eta = 10^{-2}$ ($\text{p-value} = 0.000$).
+
+	\begin{table}[!t]
+		\caption{Tukey's test results for the Diabetic Retinopathy dataset.}
+		\label{table:TukeyDR}
+		\centering
+		\begin{tabular}{cccc}
+			\hline\hline
+			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
+			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
+			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
+			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
+			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
+			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
+			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
+			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
+			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
+			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
+			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
+			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
+			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
+			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
+		\end{tabular}
+	\end{table}
 
@@
 		\small
-		\begin{tabular}{l|ccccc}
+		\begin{tabular}{lccccc}
+			\hline\hline
 			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
@@
 			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
-			Total         & $84.449$ & $135$ &         &            &
+			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
 		\end{tabular}
@@
 	The results of the ANOVA III test for the Adience dataset are shown in Table \ref{table:ANOVAAdience}.
-First, we observe that there exist significative differences in the mean QWK concerning the three factors ($\text{p-value} = 0.000$).
+First, we observe that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$).
 Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$).
-It means that the joint action of two or three factors significatively affects the results obtained by the algorithm.
+It means that the joint action of two or three factors significantly affects the results obtained by the algorithm.
 
 	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for Adience.
-Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been done.
-The results showed that the best link function is the logit one, in this case, with $0.827$ as mean QWK value.
-Also, there are significative differences between this function and the probit link ($\text{p-value} = 0.000$), that has a mean QWK value of $0.781$.
-Both links functions present significative differences concerning the complementary log-log function, that has a mean value of $0.743$.
-
-	The same methodology was followed for the learning rate and the batch size factors.
-The test reported significative differences between $\eta=10^{-3}$ (mean value $0.864$) and the rest of values of this parameter ($\text{p-value} = 0.000$ for both values), being this one the best value for this factor.
-The best value after $10^{-3}$ is $10^{-2}$, which have a mean QWK value of $0.818$.
-Both values present significative differences with $\eta=10^{-4}$, that has a mean QWK value of $0.670$ ($\text{p-value = 0.000}$).
-
-	Lastly, the best value for the batch size parameter is $128$ (mean value $0.802$) as it has significative differences with the rest of values (p-values $0.026$ and $0.000$).
-The second best value is $256$ (mean $0.788$), and it has significative differences with $64$ ($\text{p-value} = 0.000$), that has a mean value of $0.761$.
-
-	However, the interactions between these factors made the configuration that uses a logit link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
+Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been applied.
+\textcolor{blue}{The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.}
+
+%	The results showed that the best link function is the logit one, in this case, with $0.827$ as mean QWK value.
+Also, there are significant differences between this function and the probit link ($\text{p-value} = 0.000$), that has a mean QWK value of $0.781$.
+Both links functions present significant differences concerning the complementary log-log function, which has a mean value of $0.743$.
+
+	\begin{table}[!t]
+		\caption{Tukey's test results for the Adience dataset.}
+		\label{table:TukeyAdience}
+		\centering
+%		\begin{tabular}{cccc}
+%			\hline\hline
+%			       LF         & \texttt{logit} & \texttt{probit}  & \texttt{clog-log} \\ \hline
+%			 \texttt{logit}   &    $0.827$     & $\mathbf{0.000}$ & $\mathbf{0.000}$  \\
+%			 \texttt{probit}  &       -        &     $0.781$      & $\mathbf{0.000}$  \\
+%			\texttt{clog-log} &       -        &        -         &      $0.743$      \\ \hline\hline
+%			       LR         &   $10^{-2}$    &    $10^{-3}$     &     $10^{-4}$     \\ \hline
+%			    $10^{-2}$     &    $0.818$     & $\mathbf{0.000}$ & $\mathbf{0.000}$  \\
+%			    $10^{-3}$     &       -        &     $0.864$      & $\mathbf{0.000}$  \\
+%			    $10^{-4}$     &       -        &        -         &      $0.670$      \\ \hline\hline
+%			       BS         &       64       &       128        &        256        \\ \hline
+%			       64         &    $0.761$     & $\mathbf{0.026}$ & $\mathbf{0.000}$  \\
+%			       128        &       -        &     $0.802$      & $\mathbf{0.000}$  \\
+%			       256        &       -        &        -         &      $0.788$      \\ \hline\hline
+%		\end{tabular}
+		\begin{tabular}{cccc}
+			\hline\hline
+			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
+			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
+			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
+			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
+			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
+			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
+			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
+			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
+			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
+			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
+			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
+			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
+			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
+			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
+			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
+			       64         &        128        &  $-0.041$  & $0.026$ \\
+			                  &        256        &  $-0.027$  & $0.000$ \\
+			       128        &        64         &  $0.041$   & $0.026$ \\
+			                  &        256        &  $0.014$   & $0.000$ \\
+			       256        &        64         &  $0.027$   & $0.000$ \\
+			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
+		\end{tabular}
+	\end{table}
+
+%	The same methodology was followed for the learning rate and the batch size factors.
+The test reported significant differences between $\eta=10^{-3}$ (mean value $0.864$) and the rest of values of this parameter ($\text{p-value} = 0.000$ for both values), being this one the best value for this factor.
+The second best value is $10^{-2}$, which has a mean QWK value of $0.818$.
+Both values present significant differences with $\eta=10^{-4}$, which has a mean QWK value of $0.670$ ($\text{p-value = 0.000}$).
+%	
+%	Finally, the best value for the batch size parameter is $128$ (mean value $0.802$) as it shows differences with the rest of values (p-values $0.026$ and $0.000$).
+The second best value is $256$ (mean value of $0.788$), and it has significant differences with respect to $64$ ($\text{p-value} = 0.000$), with a mean value of $0.761$.
+
+	\textcolor{blue}{The results over the test set show that the best link function is the \texttt{logit} one, the best learning rate is $10^{-3}$ and the best batch size is 128.} However, the interactions between these factors made the configuration that uses a \texttt{logit} link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
 It obtained a mean QWK value of $0.940$ for validation and $0.881$ for test.
-The same parameters, but using the probit link, achieves the second best result ($0.874$).
+The same parameters, but using the \texttt{probit} link, achieves the second best result ($0.874$).
 The standard deviation is very low for both cases.
@@
 The optimal value for the batch size and the optimal link function are not the same for Retinopathy and Adience datasets.
-These results highlight the importance of adjusting the hyper-parameters for each problem that is treated instead of trying to find an optimal configuration for all the datasets.
+These results highlight the importance of adjusting the hyper-parameters for each problem instead of trying to find an optimal configuration for all the datasets.
 However, the best learning rate for both datasets were $10^{-3}$.
 It is recommended to use this value for future datasets.
-	The best batch size for DR was 10 while the best value for Adience was 128. Both values are the intermediate value that we have tried.
+	The best batch size for DR was 10 while the best value for Adience was 128 (intermediate values considered).
 	Finally, there are more interactions between the three factors for the Adience dataset than for the Diabetic Retinopathy one.
@@
 	\subsection{Comparison with nominal method and previous works}
-	\label{app:NominalComparison}
-
-	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Proportional Odds Model for the output of the network.
+	\label{sect:NominalComparison}
+
+	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Cumulative Link Model for the output of the network.
 The evaluation metric remains the same in order to be able to compare.
 There are some parameter configurations where the training process gets stagnated and a very low QWK is obtained.
-As we saw in Sections \ref{sect:dr} and \ref{sect:adience}, this problem is not present when using the ordinal method.
+As we saw in Sections \ref{sect:dr} and \ref{sect:adience}, this problem is not found when using the ordinal method.
 
@@
 
-	Finally, a comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
-Also, it is compared with previous works.
+	Finally, a comparison of the best \textcolor{blue}{test results} for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
 The proposed ordinal model outperforms all the other alternatives in terms of QWK.
-The performance increase of POM over softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.
-The enhancement of the ordinal method for Retinopathy dataset is more notable than the rise for Adience dataset.
-It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases: it is harder to detect the diabetes disease from a retina image than predicting the age range of a person.
-
-	In the case of DR, the nominal method obtained a higher CCR and 1-off accuracy value because of the important dataset unbalance.
+The performance gain of CLM over the softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.
+The improvement of the ordinal method for Retinopathy dataset is higher than for Adience dataset.
+It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
+
+%	In the case of DR, the nominal method obtained a higher CCR and 1-off accuracy value because of the important dataset unbalance.
 It is possible to achieve a high accuracy classifying all the examples in the majority class.
@@
 		\def\arraystretch{1.3}
-		\begin{tabular}{l|ccc}
+		\begin{tabular}{lccc}
+			\hline
+			\hline
 			Method                                   & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-			Ordinal proposed                         &    $0.582_{(0.016)}$    &    $0.681_{(0.067)}$    &        $0.748_{(0.071)}$         \\
-			Nominal proposed                         &    $0.498_{(0.011)}$    &    $0.692_{(0.012)}$    &        $0.854_{(0.006)}$         \\ \hline
+			Ordinal network                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
+			Nominal network                          &    $0.498_{(0.011)}$    &    $0.692_{(0.012)}$    &        $0.854_{(0.006)}$         \\
 			J. Torre et al. \cite{de2018weighted}    &  $0.537_{(\text{-})}$   &            -            &                -                 \\
-			À. Nebot et al. \cite{nebot2016diabetic} &      $0.555_{(\text{-})}$      &            -            &                -
+			À. Nebot et al. \cite{nebot2016diabetic} &  $0.555_{(\text{-})}$   &            -            &                -					\\
+			\hline
+			\hline
 		\end{tabular}
@@
 		\def\arraystretch{1.3}
-		\begin{tabular}{l|ccc}
+		\begin{tabular}{lccc}
+			\hline
+			\hline
 			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-			Ordinal proposed                          &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
-			Nominal proposed                          &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\ \hline
+			Ordinal network                           &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
+			Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
 			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
 			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
-			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$
+			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$		 \\
+			\hline
+			\hline
 		\end{tabular}
@@
 	\label{sect:conclusions}
-	In this section, the conclusions obtained from this work are exposed. The first thing that we have noticed is that the optimal values for the different parameters considered are problem-dependant.
-
-	The complementary log-log function offers the best results in Diabetic Retinopathy dataset while the logit link is the best result for the Adience dataset.
-These results provide an opportunity for exploring new generalised link functions that can suit any problem.
+	The first conclusion obtained from our results is that the optimal values for the different parameters considered are problem-dependant.
+
+	The complementary log-log function offers the best results in Diabetic Retinopathy dataset while the \texttt{logit} link is the best option for the Adience dataset.
+These results provide an opportunity for exploring new generalised link functions that could be dynamically adapted to any problem.
 
@@
 
-	Both datasets have obtained the best performance with the intermedium batch size: 10 for Diabetic Retinopathy and 128 for Adience.
+	Both datasets have obtained the best performance with an intermediate batch size: 10 for Diabetic Retinopathy and 128 for Adience.
 
 	Also, the statistical tests reported that there are relevant interactions between the three factors that we have take into account.
-The results highlight the importance of making an experimental design were all of these parameters are adjusted for each problem.
-
-	The proposed POM has improved the performance of the deep network compared to the model that uses the softmax function and the models proposed in previous works.
+The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
+
+	The proposed CLM has improved the performance of the deep network compared to the model that uses the softmax function and the models proposed in previous works.
 Also, it reduces the chance that the model gets stuck when training with some parameter configurations.

### 2019-02-27 losses.py

@@ -30,6 +30,12 @@ def qwk_loss(cost_matrix):
 		targets = tf.argmax(true_prob, axis=1)
 		costs = tf.gather(cost_matrix, targets)
 
+		# costs = tf.Print(costs, data=[costs], summarize=100, message='costs')
+
+#		pred_cls = tf.argmax(pred_prob, axis=1)
+
+# 		conf_mat = tf.confusion_matrix(targets, pred_cls)
+
 		numerator = costs * pred_prob
 		numerator = tf.reduce_sum(numerator)
 
@@ -44,6 +50,6 @@ def qwk_loss(cost_matrix):
 		denominator = a * b
 		denominator = tf.reduce_sum(denominator) + epsilon
 
-		return numerator / denominator
+		return numerator / denominator # + tf.cast(tf.reduce_sum(conf_mat) * 0, dtype=tf.float32)
 
 	return _qwk_loss

### 2019-03-07 paper/ieee.tex
varios

@@
 	\begin{equation}
-	\textcolor{blue}{\text{QWK} = 1 - \frac{\sum_{i,j} \omega_{i,j} O_{i,j}}{\sum_{i,j} \omega_{i,j} E_{i,j}},}
-	\end{equation}
-	\textcolor{blue}{where $\omega$ is the penalization matrix, $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.}
+	\textcolor{blue}{\text{QWK} = 1 - \frac{\sum\limits_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits_{i,j} \omega_{i,j} E_{i,j}},}
+	\end{equation}
+	\textcolor{blue}{where $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.}
 
@@
 	\begin{equation}
-	\textcolor{blue}{\text{QWK}_l = 1 - \frac{\sum_{k=1}^N \sum_{c=1}^C \omega_{t_k, c} P_c(X_k)}{\sum_{i=1}^C \frac{N_i}{N} \sum_{j=1}^C ( \omega_{i,j} \sum_{k=1}^N P_j(X_k) ) },}
-	\end{equation}
-	\textcolor{blue}{where $X_k$ is the input data of the $k$th sample, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class and $P_c(X_k)$ is the conditional probability that the $k$th sample belongs to class $c$ given that the true class is $t_k$.}
+	\textcolor{blue}{\text{QWK}_l = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},}
+	\end{equation}
+	\textcolor{blue}{where $\text{QWK}_l \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
+Generally, $\omega_{i,j} = \frac{|i-j|^n}{(C-1)^n}$, where $\omega_{i,j} \in [0,1]$.
+In this case, the $\text{QWK}_l$ is a function to be minimized while the QWK metric must be maximized.}
 
@@
 In this way, cumulative probabilities $P(y \prec C_q |\mathbf{x})$ are estimated, which can be directly related to standard probabilities:
-	\begin{equation}
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) = P(y = \mathcal{C}_1 | \mathbf{x}) + ... + P(y = \mathcal{C}_q | \mathbf{x}),
-	\end{equation}
-	\begin{equation}
-		P(y = \mathcal{C}_q | \mathbf{x}) = P(y \preceq \mathcal{C}_q | \mathbf{x}) - P(y \preceq \mathcal{C}_{q-1} | \mathbf{x}),
-	\end{equation}
+	\begin{align}
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) &= P(y = \mathcal{C}_1 | \mathbf{x}) + ... + P(y = \mathcal{C}_q | \mathbf{x}),\\
+		P(y = \mathcal{C}_q | \mathbf{x}) &= P(y \preceq \mathcal{C}_q | \mathbf{x}) - P(y \preceq \mathcal{C}_{q-1} | \mathbf{x}),
+	\end{align}
 	with $q = 2, ..., Q-1$, and considering that $P(y = \mathcal{C}_1 | \mathbf{x}) = P(y \preceq \mathcal{C}_1 | \mathbf{x})$ and $P(y \preceq \mathcal{C}_Q | \mathbf{x}) = 1$.
 
-	\textcolor{blue}{The model is inspired by the notion of a latent variable, where $f(x)$ represents a one-dimensional mapping obtained from the output of the last layer, which has only one neuron.} The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
+	\textcolor{blue}{The model is inspired by the notion of a latent variable, where $f(\textbf{x})$ represents a one-dimensional mapping obtained from the output of the last layer, which has only one neuron.} The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
 	\begin{equation}
@@
 Label $\mathcal{C}_q$ is predicted if and only if $f(\mathbf{x}) \in [b_{q-1}, b_q]$, where the function $f$ and $\mathbf{b} = (b_0, b_1, ..., b_{Q-1}, b_Q)$ are to be determined from the data.
-It is assumed that $b_0 = -\infty$ and $b_Q = +\infty$, so the real line defined by $f(x), x \in \mathcal{X}$, is divided into $Q$ consecutive intervals.
+It is assumed that $b_0 = -\infty$ and $b_Q = +\infty$, so the real line defined by $f(\textbf{x}), \textbf{x} \in \mathcal{X}$, is divided into $Q$ consecutive intervals.
 Each interval corresponds to a category.
@@
 	These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
-They all follow the same form $P(y \prec \mathcal{C}_q) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})})$ for a continuous cdf~$\Phi$.
+They all follow the same form $P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})})$ for a continuous cdf~$\Phi$.
 
@@
 		\begin{aligned}
-		\text{logit}[P(y \preceq \mathcal{C}_q)] = \log\frac{P(y \preceq \mathcal{C}_q)}{1 - P(y \preceq \mathcal{C}_q)}=& \\ = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,
+		\text{logit}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = \log\frac{P(y \preceq \mathcal{C}_q | \mathbf{x})}{1 - P(y \preceq \mathcal{C}_q | \mathbf{x})}=& \\ = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,
 		\end{aligned}
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q) = \frac{1}{1 + e^{-(b - \textcolor{blue}{f(\mathbf{x})})}}.
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \frac{1}{1 + e^{-(b - \textcolor{blue}{f(\mathbf{x})})}}.
 		\label{eq:logit2}
@@
 		\begin{aligned}
-		&\Phi^{-1}[P(y \preceq \mathcal{C}_q)] = b_q - \textcolor{blue}{f(\mathbf{x})}, &q = 1, ..., Q-1\\
-		&P(y \preceq \mathcal{C}_q) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}), &q = 1, ..., Q-1,
+		\Phi^{-1}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad &q = 1, ..., Q-1,\\
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}), \quad &q = 1, ..., Q-1,
 		\end{aligned}
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q) = \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
 		\label{eq:probit2}
@@
 		\begin{aligned}
-		\log[-\log[1 - P(y \preceq \mathcal{C}_q)]] =&\\
+		\log[-\log[1 - P(y \preceq \mathcal{C}_q | \mathbf{x})]] =&\\
 		= b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,&
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q) = 1 - e^{-e^{b_q - \textcolor{blue}{f(\mathbf{x})}}}, \quad q = 1, ..., Q-1.
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = 1 - e^{-e^{b_q - \textcolor{blue}{f(\mathbf{x})}}}, \quad q = 1, ..., Q-1.
 		\label{eq:cloglog2}
@@
 	\begin{equation}
-	\text{link}[P(y \preceq \mathcal{C}_q)] = -\text{link}[1 - P(y \preceq \mathcal{C}_q)],
-	\end{equation}
-	which means that the response curve for $P(y \preceq \mathcal{C}_q)$ is symmetric around the point $P(y \preceq \mathcal{C}_q) = 0.5$, i.e.
-$P(y \preceq \mathcal{C}_q)$ has the same rate when approaching 0 than when approaching 1.
+	\text{link}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = -\text{link}[1 - P(y \preceq \mathcal{C}_q | \mathbf{x})],
+	\end{equation}
+	which means that the response curve for $P(y \preceq \mathcal{C}_q | \mathbf{x})$ is symmetric around the point $P(y \preceq \mathcal{C}_q | \mathbf{x}) = 0.5$, i.e.
+$P(y \preceq \mathcal{C}_q | \mathbf{x})$ has the same rate when approaching 0 than when approaching 1.
 This symmetric property can be demonstrated as follows:
 	\begin{enumerate}
-		\item Let $P(y \preceq \mathcal{C}_q) \equiv p$. For the \texttt{logit} function, we have:
+		\item Let $P(y \preceq \mathcal{C}_q | \mathbf{x}) \equiv p$. For the \texttt{logit} function, we have:
 		\begin{equation}
@@
 		\begin{aligned}
-		p \equiv P(y \preceq \mathcal{C}_q) &= \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}) =\\
+		p \equiv P(y \preceq \mathcal{C}_q | \mathbf{x}) &= \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}) =\\
 		&= \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
@@
 In this dataset, we try to predict the correct category from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
-The images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions.
+The test set contains $26788$ pairs of images.
+These images are taken in variable conditions: by different cameras,  varying conditions of illumination and different resolutions.
 These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition hosted on the Kaggle platform.
@@
 The optimal configuration depends on the metric we are analysing.
-In this case, as we are working with an ordinal problem, the most reliable metric is the QWK.
-\textcolor{red}{No se entonces si tiene sentido poner el resto de métricas???} \textcolor{blue}{Están puestas para comparar con artículos que no dan el QWK.}
+\textcolor{blue}{In this case, as we are working with an ordinal problem, the most reliable metric is the QWK.
+However, the rest of the metrics are also included to allow further comparisons with future works.}
 
@@
 	\label{sect:statisticalanalysis}
-	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the result,
+	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the result.
 
@@
 
-	We denote by $QWK_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level.
+	We denote by $\text{QWK}_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level.
 We assume that the three factors do not act independently and therefore there exists an interaction between each pair of them and between the three factors.
@@
 	\footnotesize
-	QWK_{i,j,k,l} = & \mu + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
+	\text{QWK}_{i,j,k,l} = \mu & + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
 	\label{eq:anova3}
@@
 
-	Finally, a comparison of the best \textcolor{blue}{test results} for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
-The proposed ordinal model outperforms all the other alternatives in terms of QWK.
+	Finally, a comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
+\textcolor{blue}{All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).} The proposed ordinal model outperforms all the other alternatives in terms of QWK.
 The performance gain of CLM over the softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.

### 2019-03-07 activations.py

@@ -183,10 +183,10 @@ class NNPOM(tf.keras.layers.Layer):
 	"""
 	Proportional Odds Model activation layer.
 	"""
-	def __init__(self, num_classes, transfer_function, **kwargs):
+	def __init__(self, num_classes, link_function, **kwargs):
 		self.num_classes = num_classes
 		self.dist = tf.distributions.Normal(loc=0., scale=1.)
-		self.transfer_function = transfer_function
+		self.link_function = link_function
 		super(NNPOM, self).__init__(**kwargs)
 
 	def _convert_thresholds(self, b, a):
@@ -205,10 +205,15 @@ class NNPOM(tf.keras.layers.Layer):
 		b = tf.transpose(tf.reshape(tf.tile(projected, [self.num_classes - 1]), shape=[-1, m]))
 		z3 = a - b
 
-		if self.transfer_function == 'probit':
+		if self.link_function == 'probit':
 			a3T = self.dist.cdf(z3)
-		elif self.transfer_function == 'cloglog':
+		elif self.link_function == 'cloglog':
 			a3T = 1 - tf.exp(-tf.exp(z3))
+		elif self.link_function == 'ghf':
+			if self.lmbd == 0:
+				a3T = 1 - tf.exp(-tf.exp(z3))
+			else:
+				a3T = 1 - tf.exp(- tf.pow((self.lmbd * z3 - 1), 1 / self.lmbd) )
 		else:
 			a3T = 1.0 / (1.0 + tf.exp(-z3))
 
@@ -225,6 +230,9 @@ class NNPOM(tf.keras.layers.Layer):
 
 		self.tau = self.add_weight('tau_nnpom', shape=(1,),
 								   initializer=tf.random_uniform_initializer(minval=1, maxval=10))
+
+		if self.link_function == 'ghf':
+			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=-1, maxval=1))
 
 	def call(self, x):
 		thresholds = self._convert_thresholds(self.thresholds_b, self.thresholds_a)

### 2019-03-07 net_keras.py

@@ -104,6 +104,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
+		elif self.final_activation == 'pomghf':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'ghf'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			model.add(tf.keras.layers.Activation(self.final_activation))
@@ -181,6 +184,9 @@ class Net:
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'cloglog'))
+		elif self.final_activation == 'pomghf':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'ghf'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			if self.prob_layer == 'geometric':
@@ -211,6 +217,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
+		elif self.final_activation == 'pomghf':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'ghf'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			if self.prob_layer == 'geometric':
@@ -243,6 +252,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
+		elif self.final_activation == 'pomghf':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(NNPOM(self.num_classes, 'ghf'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			if self.prob_layer == 'geometric':
@@ -269,6 +281,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
+		elif self.final_activation == 'pomghf':
[…]

### 2019-03-12 paper/ieee.tex
Mejoras ieee. Glogit

@@
 \usepackage{amsmath}
+\usepackage{mathrsfs}
 % A popular package from the American Mathematical Society that provides
@@
 
-\usepackage{ulem}
+%\usepackage{ulem}
 
@@
 	\begin{abstract}
-		The abstract goes here.
+		This paper proposes a deep convolutional neural network model for ordinal regression based on the use of a family of probabilistic ordinal link functions in the output layer called Cumulative Link Models.
+This kind of models projects each pattern into a 1-dimensional space.
+In this case, the projections are estimated by a non-linear deep neural network.
+A set of ordered thresholds splits this space into the different classes of the problem.
+Different link functions will be studied in this experimental study, and the results will be contrasted with statistical analysis.
+To further improve the results, we combine these ordinal models with a loss function that takes into account the distance between the categories, based on the weighted Kappa index.
+The experiments run over two different ordinal classification problems, and the statistical tests confirm that these models improve the results of a nominal model and outperform the proposals considered in the literature.
 	\end{abstract}
@@
 	\begin{IEEEkeywords}
-		IEEE, IEEEtran, journal, \LaTeX, paper, template.
+		Deep learning, Ordinal Regression, Link models.
 	\end{IEEEkeywords}
@@
 	% and "HIS" in caps to complete the first word.
-	\textcolor{red}{Habría que restructurar la introducción: 1) deep learning y CNN, pero corto 2) clasificación ordinal, modelos de umbral, POM y funciones de enlace (más bien breve) 3) clasificación ordinal profunda 4) objetivo del paper (un estudio experimental sobre funciones de enlace y otros parámetros en deep learning ordinal).
-learning rate y batch normalization, si se mete, debería ser más breve}
-
-	1) \IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
+	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
 These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
-\textcolor{blue}{\sout{Deep learning discovers complex structures in large datasets by using the backpropagation algorithm to change the internal parameters of the model and compute better representations in each layer from the features in the previous layer.} Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that comes in the form of multiple arrays.} CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
+Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that comes in the form of multiple arrays.
+CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
 On image classification tasks, each colour channel is represented by a 2D array.
@@
 
-	2) Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of classes.
+	Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of classes.
 This kind of problem can be treated as a nominal classification problem, but this discards ordinal information.
 A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model.
-\textcolor{blue}{\sout{One way to use the ordinal information is to evaluate the model using an ordinal metric.
-Multiple metrics exist in the literature of machine learning and statistics \cite{cruz2014metrics,mehdiyev2016evaluating}.
-Kappa index is a well-known statistic coefficient defined by Cohen \cite{cohen1960coefficient} to measure inter-rater agreement on classifying elements into a set of categories.
-Later, Weighted Kappa (WK) is a modified version of the Kappa statistic calculated to allow assigning different weights to different levels of aggregation between two variables.
-An ordinal weighted kappa loss was described in a previous work~\cite{de2018weighted}, which is a differentiable cost function based on the WK metric.
-This previous work proved that using these functions improves the model performance and reduce the overfitting risk.
-Different weights can be assigned in an ordinal classification problem.
-In a linear penalization, the weight is proportional to the distance between the predicted and the real class (in number of categories).
-In the Quadratic Weighted Kappa (QWK) the penalization is proportional to the square of the distance.
-In this work, we will use the QWK metric and the QWK loss.} The Proportional Odds Model (POM)~\cite{agresti2010analysis} is an ordinal alternative to the softmax function that was designed for ordinal regression.
+The Proportional Odds Model (POM)~\cite{agresti2010analysis} is an ordinal alternative to the softmax function that was designed for ordinal regression.
 It belongs to a wider family of models called Cumulative Link Models (CLM).
@@
 However, there are other functions that can be explored.
-This model will be described in depth in Section \ref{sect:ordinalproblem}.}
-
-	\textcolor{blue}{3) Ordinal models can also be applied to deep learning models.
+This model will be described in depth in Section \ref{sect:ordinalproblem}.
+
+	Ordinal models can also be applied to deep learning models.
 In the case of convolutional networks, the model projection used by the threshold model will be obtained from the last layer of the network.
@@
 Some previous works have used the POM in traditional neural networks~\cite{gutierrez2016ordinal}, but it has not been applied to convolutional networks yet.
-Also, there are some link functions that has not been explored.}
-
-	\textcolor{blue}{4) In this paper, an experimental study regarding link functions for Cumulative Link Models will be made.
+Also, there are some link functions that has not been explored.
+
+	In this paper, an experimental study regarding link functions for Cumulative Link Models will be made.
 Also, other parameters that can affect the training process and the model performance, like the learning rate of the optimization algorithm and the batch size, and its interaction will be studied.
@@
 We will contrast the results obtained with statistical analysis to provide more robust conclusions.
-An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.}
+An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.
 
@@
 Finally, Section~\ref{sect:conclusions} exposes the conclusions of this work.
-
-%	\textcolor{red}{The backpropagation algorithm is a stochastic gradient descent algorithm that minimises a predefined loss function.
-It has been used in the last years in many works~\cite{leonard1990improvement,yu1995dynamic,krizhevsky2012imagenet,de2018weighted} for training shallow and deep neural networks.
-It updates the weights of each layer after backpropagating the loss function gradients through the network.
-The learning rate hyper-parameter controls the strength of the changes that are applied to the weights.
-Some works have checked the importance of finding the optimal value for this parameter~\cite{senior2013empirical} and have tried different approaches to improve the training process~\cite{smith2017cyclical}.}
-%	
-%	\textcolor{red}{Batch normalization is another technique used for this kind of networks.
-It reduces the internal covariate shift by normalizing layer inputs.
-It was presented in 2015~\cite{ioffe2015batch} and gives a critical enhancement during the training phase.
-Batch size is another important hyper-parameter that should be adjusted as it affects the weight updates and also the normalization~\cite{keskar2016large}\cite{radiuk2017impact}.}
-%	
-%	The softmax function is widely used for the output layer in neural networks for classification tasks.
-It is a simple and efficient function for multi-class problems, but it is not the best when working with ordinal data.
-In this paper, the Cumulative Link Model (CLM)~\cite{gutierrez2016ordinal,agresti2010analysis} will be used instead of the softmax function.
-Different link functions will be explored to compare their performance.
-Also, the influence of other parameters like the learning rate of the optimization algorithm and the batch size will be studied.
-We will contrast the results obtained with statistical analysis to provide more robust conclusions.
-An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.
 
@@
 	\begin{equation}
-	\textcolor{blue}{\text{QWK} = 1 - \frac{\sum\limits_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits_{i,j} \omega_{i,j} E_{i,j}},}
-	\end{equation}
-	\textcolor{blue}{where $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.}
-
-	\textcolor{blue}{Then, they provided the QWK loss ($\text{QWK}_l$) definition below:}
-	\begin{equation}
-	\textcolor{blue}{\text{QWK}_l = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},}
-	\end{equation}
-	\textcolor{blue}{where $\text{QWK}_l \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
+	\text{QWK} = 1 - \frac{\sum\limits_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits_{i,j} \omega_{i,j} E_{i,j}},
+	\end{equation}
+	where $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.
+
+	Then, they provided a continuous version of the QWK metric ($\text{QWK}_c$) based on the probabilities of the predictions:
+	\begin{equation}
+	\text{QWK}_c = 1 - \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
+	\end{equation}
+	where $\text{QWK}_c \in [-1,1]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
 Generally, $\omega_{i,j} = \frac{|i-j|^n}{(C-1)^n}$, where $\omega_{i,j} \in [0,1]$.
-In this case, the $\text{QWK}_l$ is a function to be minimized while the QWK metric must be maximized.}
-
-	\textcolor{blue}{Z.
+
+	Then, they defined the loss function based on the QWK as follows:
+	\begin{equation}
+	\mathscr{L} = \log(1 - \text{QWK}_c),
+	\end{equation}
+	where $\mathscr{L} \in [-\infty, \log 2]$. This loss is a function to be minimized while the QWK metric must be maximized.
+
+	Z.
 Niu et al.
 \cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using convolutional neural networks.
-They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively resolve these classification sub-problems, taking into account the correlation between them.}
-
-	Christopher Beckham and Christopher Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
-They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.	\textcolor{blue}{Also, they proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.}
+They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively resolve these classification sub-problems, taking into account the correlation between them.
+
+	C.
+Beckham and C.
+Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
+They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.	Also, they proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
 
@@
 
-	\textcolor{blue}{H. Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease.}
-
-	\textcolor{blue}{Y.
+	H. Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease.
+
+	Y.
 Liu et al.
 \cite{liu2017deep} proposed a new approach of which transforms the ordinal regression problem to binary classification problems and use triplets with instances from different categories to train deep neural networks.
-In this way, high-level features describing the ordinal relationship are extracted automatically.}
-
-	\textcolor{blue}{A.
+In this way, high-level features describing the ordinal relationship are extracted automatically.
+
+	A.
 Rios et al.
@@
 They combined an ordinal loss function, a CNN model and conventional feature engineering.
-Also, they applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.}
-
-	\textcolor{blue}{S.
+Also, they applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.
+
+	S.
 Chen et al.
@@
 This method combines multiple binary CNNs that are trained with ordinal age labels.
-The binary outputs are aggregated for the final age prediction and they achieved a tighter error bound for ranking-based age estimation.}
-
-	\textcolor{blue}{H.
+The binary outputs are aggregated for the final age prediction and they achieved a tighter error bound for ranking-based age estimation.
+
+	H.
 Fu et al.
@@
 They improved the performance when training the network with an ordinary regression loss.
-Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.}
-
-	\textcolor{blue}{Y.
+Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.
+
+	Y.
 Liu et al.
-\cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes de negative loglikelihood for multiple categories constrained by the order relationship between instances.}
-
-	\textcolor{blue}{A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.}
-
-	\textcolor{blue}{M.
+\cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes the negative loglikelihood for multiple categories constrained by the order relationship between instances.
+
+	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.
+
+	M.
 ALALI et al.
 \cite{alali2018multi} proposed a complex CNN architecture for solving Twitter Sentiment Classification as an ordinal problem.
-They checked that using average pooling preserves significant features that provide more expresiveness to ordinal scale.}
-
-	\textcolor{blue}{\sout{Currently, there is a great discussion in terms of finding the best activation function, offering good performance and mitigating the effects of the gradient vanishing problem \cite{bengio1994learning,pascanu2013difficulty}.
-Rectified Linear Unit (ReLU)~\cite{nair2010rectified} is widely used in most deep learning works, but recently, Clevert et al.
-proposed the Exponential Linear Unit (ELU)~\cite{clevert2015fast}.
-They proved that ELUs alleviate the vanishing gradient problem via the identity for positive values.
-In their experiments, ELUs lead not only to faster learning but also to significantly better generalization performance than ReLUs and Leaky ReLU functions (LReLU) on networks with more than five layers.
-In this way, this paper considers the ELU function for the different experiments.}}
-
-	\textcolor{blue}{\sout{Sergey Ioffe and Christian Szegedy~\cite{ioffe2015batch} described Batch Normalization and its benefits.
-It reduces the internal covariate shift by normalizing layer inputs.
-Their method draws its strength from making normalization a part of the model architecture and performing the normalization for each training batch.
-It allows them to use higher learning rates and be less careful about initialization.
-It also eliminates the need for using regularization techniques like Dropout.}}
+They checked that using average pooling preserves significant features that provide more expresiveness to ordinal scale.
 
@@
 
-	\textcolor{blue}{The model is inspired by the notion of a latent variable, where $f(\textbf{x})$ represents a one-dimensional mapping obtained from the output of the last layer, which has only one neuron.} The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
-	\begin{equation}
-		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,
+	The model is inspired by the notion of a latent variable, where $f(\textbf{x})$ represents a one-dimensional mapping obtained from the output of the last layer, which has only one neuron.
+The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
+	\begin{equation}
+		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - f(\mathbf{x}), \quad q = 1, ..., Q-1,
 	\end{equation}
 	where $g^{-1} : [0,1] \rightarrow (-\infty, +\infty)$ is a monotonic function often termed as the inverse link function, and $b_q$ is the threshold defined for class $\mathcal{C}_q$.
-Consider the latent variable $y^* = f(\mathbf{x})^* = \textcolor{blue}{f(\mathbf{x})} + \epsilon$, where $\epsilon$ is the random variable of the error.
+Consider the latent variable $y^* = f(\mathbf{x})^* = f(\mathbf{x}) + \epsilon$, where $\epsilon$ is the random variable of the error.
 The most common choice for the probability distribution of $\epsilon$ is the logistic function (which is the default function for POM).
@@
 \le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | \mathbf{x})$ increases with $q$ \cite{mccullagh1980regression}.
-	\textcolor{blue}{This order is achieved by defining the first threshold and calculating the rest of thresholds from the first in the following form:}
-
-	\begin{equation}
-	\textcolor{blue}{b_n = b_1 + \sum_{i=1}^{n-1} \alpha_i^2, \quad n = 2, ..., N},
-	\end{equation}
-	\textcolor{blue}{where $b_1$ and $\alpha_i$ are learnable parameters, and $N$ is the number of classes.}
+	This order is achieved by defining the first threshold and calculating the rest of thresholds from the first in the following form:
+
+	\begin{equation}
+	b_n = b_1 + \sum_{i=1}^{n-1} \alpha_i^2, \quad n = 2, ..., N,
+	\end{equation}
+	where $b_1$ and $\alpha_i$ are learnable parameters, and $N$ is the number of classes.
 
@@
 	These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
-They all follow the same form $P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})})$ for a continuous cdf~$\Phi$.
+They all follow the same form $P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - f(\mathbf{x}))$ for a continuous cdf~$\Phi$.
 
@@
 		\centering
-		\includegraphics[width=3in]{img/linkfunctions.png}
+		\includegraphics[width=3in]{img/linkfunctions.pdf}
 		\caption{Representation of link functions.}
@@
 		\begin{aligned}
-		\text{logit}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = \log\frac{P(y \preceq \mathcal{C}_q | \mathbf{x})}{1 - P(y \preceq \mathcal{C}_q | \mathbf{x})}=& \\ = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,
+		\text{logit}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = \log\frac{P(y \preceq \mathcal{C}_q | \mathbf{x})}{1 - P(y \preceq \mathcal{C}_q | \mathbf{x})}=& \\ = b_q - f(\mathbf{x}), \quad q = 1, ..., Q-1,
 		\end{aligned}
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \frac{1}{1 + e^{-(b - \textcolor{blue}{f(\mathbf{x})})}}.
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \frac{1}{1 + e^{-(b - f(\mathbf{x}))}}.
 		\label{eq:logit2}
@@
 		\begin{aligned}
-		\Phi^{-1}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = b_q - \textcolor{blue}{f(\mathbf{x})}, \quad &q = 1, ..., Q-1,\\
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}), \quad &q = 1, ..., Q-1,
+		\Phi^{-1}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = b_q - f(\mathbf{x}), \quad &q = 1, ..., Q-1,\\
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - f(\mathbf{x})), \quad &q = 1, ..., Q-1,
 		\end{aligned}
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \int_{-\infty}^{b_q - f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
 		\label{eq:probit2}
@@
 		\log[-\log[1 - P(y \preceq \mathcal{C}_q | \mathbf{x})]] =&\\
-		= b_q - \textcolor{blue}{f(\mathbf{x})}, \quad q = 1, ..., Q-1,&
+		= b_q - f(\mathbf{x}), \quad q = 1, ..., Q-1,&
 		\end{aligned}
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) = 1 - e^{-e^{b_q - \textcolor{blue}{f(\mathbf{x})}}}, \quad q = 1, ..., Q-1.
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = 1 - e^{-e^{b_q - f(\mathbf{x})}}, \quad q = 1, ..., Q-1.
 		\label{eq:cloglog2}
@@
 		\begin{aligned}
-		p \equiv P(y \preceq \mathcal{C}_q | \mathbf{x}) &= \Phi(b_q - \textcolor{blue}{f(\mathbf{x})}) =\\
-		&= \int_{-\infty}^{b_q - \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
+		p \equiv P(y \preceq \mathcal{C}_q | \mathbf{x}) &= \Phi(b_q - f(\mathbf{x})) =\\
+		&= \int_{-\infty}^{b_q - f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
 		\end{aligned}
@@
 		\begin{align}
-		\text{probit}(p) & = \Phi^{-1}(p) = b_q - \textcolor{blue}{f(\mathbf{x})},\\
-		-\text{probit}(1-p) &= \Phi^{-1}(1-p) = -b_q + \textcolor{blue}{f(\mathbf{x})},
+		\text{probit}(p) & = \Phi^{-1}(p) = b_q - f(\mathbf{x}),\\
+		-\text{probit}(1-p) &= \Phi^{-1}(1-p) = -b_q + f(\mathbf{x}),
 		\end{align}
@@
 		\begin{equation}
-		1 - p = \int_{-\infty}^{-b_q + \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
-		\end{equation}
-		\begin{equation}
-		p = 1 - \int_{-\infty}^{-b_q + \textcolor{blue}{f(\mathbf{x})}} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
+		1 - p = \int_{-\infty}^{-b_q + f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
+		\end{equation}
+		\begin{equation}
+		p = 1 - \int_{-\infty}^{-b_q + f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
 		\end{equation}
@@
 The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
-\textcolor{blue}{The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved for obtaining the next pixel.
-Pooling layers have got similar parameters: the pool size is the number of pixels that will be involved in the pooling operation, and the stride represents the same concept that in convolutional layers.} For convolutional layers, ConvWxH@FsS~=~F filters of size WxH and stride S.
+The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved for obtaining the next pixel.
+Pooling layers have got similar parameters: the pool size is the number of pixels that will be involved in the pooling operation, and the stride represents the same concept that in convolutional layers.
+For convolutional layers, ConvWxH@FsS~=~F filters of size WxH and stride S.
 For pooling layers, PoolWxHsS~=~pool size of WxH and stride S.
 
-	\textcolor{blue}{The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used for activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradients problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
-Also, ELUs lead to faster training and better generalization performance than ReLU and Leaky ReLU (LReLU)~\cite{maas2013rectifier} functions on networks with more than five layers.}
-
-	\textcolor{blue}{After every ELU activation function of the convolutional layers, Batch Normalization~\cite{ioffe2015batch} is applied.
+	The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used for activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradients problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
+Also, ELUs lead to faster training and better generalization performance than ReLU and Leaky ReLU (LReLU)~\cite{maas2013rectifier} functions on networks with more than five layers.
+
+	After every ELU activation function of the convolutional layers, Batch Normalization~\cite{ioffe2015batch} is applied.
 This method reduces the internal covariate shift by normalizing layer outputs.
 It allows us to use higher learning rates and be less careful about weights initialization.
-It also eliminates the need for using regularization techniques like Dropout.}
-
-	\textcolor{blue}{At the output of the network, the CLM is used.
-Also, a learnable parameter has been used to rescale the projections used by the Cumulative Link Model to make it more stable and guarantee the convergence in most cases.}
+It also eliminates the need for using regularization techniques like Dropout.
+
+	At the output of the network, the CLM is used.
+Also, a learnable parameter has been used to rescale the projections used by the Cumulative Link Model to make it more stable and guarantee the convergence in most cases.
 
@@
 	The model is optimized using a batch based first-order optimization algorithm called Adam~\cite{kingma2014adam}.
-We study different initial learning rates in order to find the optimal one for each problem.
-We apply an exponential decay across training epochs to the initial learning rate.
-
-	Both datasets have been artificially equalized using data augmentation techniques~\cite{van2001art,krizhevsky2012imagenet}.
-However, different transformations were applied to each one.
-DR dataset augmentation was based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
-Horizontal flipping was the only transformation applied to Adience dataset.
-
-	In the case of DR dataset, the epoch size has been fixed to $100000$ images per epoch. For the Adience dataset, epoch size is the number of images in the training set.
-
-	The model is evaluated using the Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}. This evaluation measure gives a higher weight to the errors that are further from the correct class.
-	Quadratic weighted kappa loss is considered as loss function for the optimizer as it gives better performance for ordinal classification problems \cite{de2018weighted}.
-
-	Also, other evaluation metrics have been used to ease the comparison with other works: Minimum Sensitivity (MS) \cite{cruz2014metrics}, Mean Absolute Error (MAE) \cite{cruz2014metrics}, Mean Squared Error (MSE) \cite{wang2009mean}, Correct Classification Rate (CCR), Top-2 CCR \cite{beckham2017unimodal}, Top-3 CCR \cite{beckham2017unimodal} and 1-off accuracy \cite{chen2016cascaded,levi2015age,eidinger2014age}.
-
-	Experiments were run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the Cumulative Link Model).
+We study different initial learning rates ($\eta$) in order to find the optimal one for each problem.
+We apply an exponential decay across training epochs to the initial learning rate ($\eta_0$) following the expression below:
+	\begin{equation}
+		\eta = \eta_0 \cdot e^{-0.025 \cdot \text{epoch}}.
+	\end{equation}
+
+	Fig. \ref{fig:lrdecay} represents the learning rate decay for the different initial values considered in this work.
+	\begin{figure}[!t]
+		\centering
+		\includegraphics[width=3in]{img/lr.pdf}
+		\caption{Representation of the learning rate decay.}
+		\label{fig:lrdecay}
+	\end{figure}
+
+	Both datasets are artificially equalized using data augmentation techniques~\cite{van2001art}.
+However, different transformations are applied to each one.
+DR dataset augmentation is based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
+Horizontal flipping is the only transformation applied to Adience dataset.
+These transformations are applied every time a new batch is loaded, and the parameters of each one are randomly chosen from a defined range, providing a new set of transformed images for each batch.
+This technique reduces the overfitting risk and provides an important performance boost as we always work with different but similar images \cite{krizhevsky2012imagenet}.
+
+	The epoch size is equal to the number of images in the training set.
+It could be a higher number as we are using data augmentation, but instead of increasing the epoch size, we rather run the training for more epochs.
+In this case, we set the maximum number of epochs to $100$.
+However, we always save the best model, that is evaluated when the training finishes.
+
+	The model is evaluated using the Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}.
+This evaluation measure gives a higher weight to the errors that are further from the correct class.
+A similar approach to the one described in \cite{de2018weighted} is used as the loss function as it gives better performance for ordinal classification problems.
+In this case, we define the QWK loss function ($\text{QWK}_l$) as follows:
+	\begin{equation}
+	\text{QWK}_l = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
+	\end{equation}
+	where $\text{QWK}_l \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
+In this case, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, where $\omega_{i,j} \in [0,1]$.
+
+	Also, other evaluation metrics are used to ease the comparison with other works: Minimum Sensitivity (MS) \cite{cruz2014metrics}, Mean Absolute Error (MAE) \cite{cruz2014metrics}, Mean Squared Error (MSE) \cite{wang2009mean}, Correct Classification Rate (CCR), Top-2 CCR \cite{beckham2017unimodal}, Top-3 CCR \cite{beckham2017unimodal} and 1-off accuracy \cite{chen2016cascaded,levi2015age,eidinger2014age}.
+
+	Experiments are run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the Cumulative Link Model).
 The results of these experiments are analysed in Section \ref{sect:NominalComparison}.
@@
 	\subsection{Factors}
-	Three different factors have been considered: learning rate, batch size and link function for the final output layer.
+	Three different factors are considered: learning rate, batch size and link function for the final output layer.
 
@@
 Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical,senior2013empirical}.
-Within this work, we have considered three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
+Within this work, we consider three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
 		\item \textit{Batch size} (BS).
@@
 It can affect the training time and the model performance.
-In this paper, we have tried three separate batch sizes for each dataset.
-For DR dataset, we have used $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ images were used.
+In this paper, we try three separate batch sizes for each dataset.
+For DR dataset, we use $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ images are used.
 We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expanded the range on both sides.
-		\item \textit{Link function} (LF). Different link functions have been used for the CLM at the last layer output: \texttt{logit}, \texttt{probit} and complementary log-log.
+		\item \textit{Link function} (LF). Different link functions are used for the CLM at the last layer output: \texttt{logit}, \texttt{probit} and complementary log-log.
 	\end{itemize}
@@
 	In this section, we present the results of the experiments.
-For each dataset, we show a table with the detailed experiments performed for training the model with each combination of parameters.
-Every parameter combination has been run five times.
+For each dataset, we show a table with the detailed results of the experiments performed for training the model with each combination of parameters.
+Every parameter combination was run five times.
 These tables show the mean value and the standard deviation (SD) of each metric across these five executions for the test set.
@@
 	\label{sect:dr}
-	Detailed \textcolor{blue}{test results} for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}.
-The best result for each metric is marked in bold and the second best is in italic font.
+	Detailed test results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}. The best result for each metric is marked in bold and the second best is in italic font.
 
@@
 The optimal configuration depends on the metric we are analysing.
-\textcolor{blue}{In this case, as we are working with an ordinal problem, the most reliable metric is the QWK.
-However, the rest of the metrics are also included to allow further comparisons with future works.}
+In this case, as we are working with an ordinal problem, the most reliable metric is the QWK.
+However, the rest of the metrics are also included to allow further comparisons with future works.
 
@@
 	\label{sect:adience}
-	\textcolor{blue}{Test results} for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}.
-The best result for each metric is marked in bold and the second best is in italic font.
+	Test results for the experiments made with the Adience dataset are shown in Table \ref{table:AdienceTest}. The best result for each metric is marked in bold and the second best is in italic font.
 
@@
 	ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
-Considered factors are the link function\textcolor{blue}{\sout{, which can be \texttt{logit}, \texttt{probit} and complementary log-log,}} the learning rate for the Adam optimization algorithm \textcolor{blue}{\sout{($10^{-2}$, $10^{-3}$ and $10^{-4}$)}}, and the batch size \textcolor{blue}{\sout{(5, 10 and 15 for DR and 64, 128 and 256 for Adience)}}.
-\textcolor{red}{Esto está repitiendo mucho}
+Considered factors are the link function, the learning rate for the Adam optimization algorithm, and the batch size.
 
@@
 We assume that five executions are enough to do the statistical tests because of the computational time limitations.
-
-	%The test shows that there is no batch size whose results are significatively better than the results of all other batch sizes.
-This does not mean that these differences could not exist for specific numbers of samples per batch.
-So, in order to determine for each type of function whether a batch size is better than the others, we have performed an ANOVA I analysis - where the only factor is the batch size - and multiple comparison tests.
 
@@
 An HSD Tukey's test \cite{tukey1949comparing} was made under the null hypothesis that the variance of the error of the dependent variable is the same between the groups.
-\textcolor{blue}{The results of this test over the test set are shown in Table \ref{table:TukeyDR}.
+The results of this test over the test set are shown in Table \ref{table:TukeyDR}.
 They show that the best link function is the complementary log-log but the \texttt{probit} link performance is close to it.
 Also, the best value for the learning rate parameter is $10^{-3}$.
-The batch size is not relevant for this dataset with the values considered.}
-
-%	The results over the test set show that the best link function is the complementary log-log, though it does not present significant differences with respect to the probit function ($\text{p-value} = 0.248$).
-There are differences between the complementary log-log and the probit function with respect to the logit function (p-values $0.000$ and $0.011$, respectively).
-A similar methodology has been applied to the different values of the learning rate.
-Significant differences can be observed in the mean values for $\eta = 10^{-3}$ with respect to the other values of the parameter (p-values $0.023$ for $10^{-4}$ and $0.000$ for $10^{-2}$).
-Also, there are differences for $\eta = 10^{-4}$ concerning $\eta = 10^{-2}$ ($\text{p-value} = 0.000$).
+The batch size is not relevant for this dataset with the values considered.
 
@@
 Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been applied.
-\textcolor{blue}{The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.}
-
-%	The results showed that the best link function is the logit one, in this case, with $0.827$ as mean QWK value.
-Also, there are significant differences between this function and the probit link ($\text{p-value} = 0.000$), that has a mean QWK value of $0.781$.
-Both links functions present significant differences concerning the complementary log-log function, which has a mean value of $0.743$.
+The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.
 
@@
 		\centering
-%		\begin{tabular}{cccc}
-%			\hline\hline
-%			       LF         & \texttt{logit} & \texttt{probit}  & \texttt{clog-log} \\ \hline
-%			 \texttt{logit}   &    $0.827$     & $\mathbf{0.000}$ & $\mathbf{0.000}$  \\
-%			 \texttt{probit}  &       -        &     $0.781$      & $\mathbf{0.000}$  \\
-%			\texttt{clog-log} &       -        &        -         &      $0.743$      \\ \hline\hline
-%			       LR         &   $10^{-2}$    &    $10^{-3}$     &     $10^{-4}$     \\ \hline
-%			    $10^{-2}$     &    $0.818$     & $\mathbf{0.000}$ & $\mathbf{0.000}$  \\
-%			    $10^{-3}$     &       -        &     $0.864$      & $\mathbf{0.000}$  \\
-%			    $10^{-4}$     &       -        &        -         &      $0.670$      \\ \hline\hline
-%			       BS         &       64       &       128        &        256        \\ \hline
-%			       64         &    $0.761$     & $\mathbf{0.026}$ & $\mathbf{0.000}$  \\
-%			       128        &       -        &     $0.802$      & $\mathbf{0.000}$  \\
-%			       256        &       -        &        -         &      $0.788$      \\ \hline\hline
-%		\end{tabular}
 		\begin{tabular}{cccc}
@@
 
-%	The same methodology was followed for the learning rate and the batch size factors.
-The test reported significant differences between $\eta=10^{-3}$ (mean value $0.864$) and the rest of values of this parameter ($\text{p-value} = 0.000$ for both values), being this one the best value for this factor.
-The second best value is $10^{-2}$, which has a mean QWK value of $0.818$.
-Both values present significant differences with $\eta=10^{-4}$, which has a mean QWK value of $0.670$ ($\text{p-value = 0.000}$).
-%	
-%	Finally, the best value for the batch size parameter is $128$ (mean value $0.802$) as it shows differences with the rest of values (p-values $0.026$ and $0.000$).
-The second best value is $256$ (mean value of $0.788$), and it has significant differences with respect to $64$ ($\text{p-value} = 0.000$), with a mean value of $0.761$.
-
-	\textcolor{blue}{The results over the test set show that the best link function is the \texttt{logit} one, the best learning rate is $10^{-3}$ and the best batch size is 128.} However, the interactions between these factors made the configuration that uses a \texttt{logit} link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
+	The results over the test set show that the best link function is the \texttt{logit} one, the best learning rate is $10^{-3}$ and the best batch size is 128.
+However, the interactions between these factors made the configuration that uses a \texttt{logit} link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
 It obtained a mean QWK value of $0.940$ for validation and $0.881$ for test.
@@
 	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Cumulative Link Model for the output of the network.
-The evaluation metric remains the same in order to be able to compare.
+The evaluation metrics remains the same in order to be able to compare.
 There are some parameter configurations where the training process gets stagnated and a very low QWK is obtained.
@@
 	Finally, a comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
-\textcolor{blue}{All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).} The proposed ordinal model outperforms all the other alternatives in terms of QWK.
+All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).
+The proposed ordinal model outperforms all the other alternatives in terms of QWK.
 The performance gain of CLM over the softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.
@@
 It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
-
-%	In the case of DR, the nominal method obtained a higher CCR and 1-off accuracy value because of the important dataset unbalance.
-It is possible to achieve a high accuracy classifying all the examples in the majority class.
-However, as we are working with an ordinal problem, it is preferable to achieve a good QWK value rather than a high accuracy.
-This effect is not seen in the Adience dataset as it is less unbalanced.
 
@@
 	\label{sect:conclusions}
-	The first conclusion obtained from our results is that the optimal values for the different parameters considered are problem-dependant.
+	The first conclusion obtained from the results of our experiments is that the optimal values for the different parameters considered are problem-dependant.
 

### 2019-03-12 activations.py

@@ -209,11 +209,8 @@ class NNPOM(tf.keras.layers.Layer):
 			a3T = self.dist.cdf(z3)
 		elif self.link_function == 'cloglog':
 			a3T = 1 - tf.exp(-tf.exp(z3))
-		elif self.link_function == 'ghf':
-			if self.lmbd == 0:
-				a3T = 1 - tf.exp(-tf.exp(z3))
-			else:
-				a3T = 1 - tf.exp(- tf.pow((self.lmbd * z3 - 1), 1 / self.lmbd) )
+		elif self.link_function == 'glogit':
+			a3T = 1.0 / tf.pow(1.0 + tf.exp(-self.lmbd * (z3 - self.mu) ), self.alpha)
 		else:
 			a3T = 1.0 / (1.0 + tf.exp(-z3))
 
@@ -231,8 +228,10 @@ class NNPOM(tf.keras.layers.Layer):
 		self.tau = self.add_weight('tau_nnpom', shape=(1,),
 								   initializer=tf.random_uniform_initializer(minval=1, maxval=10))
 
-		if self.link_function == 'ghf':
-			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=-1, maxval=1))
+		if self.link_function == 'glogit':
+			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=3))
+			self.alpha = self.add_weight('alpha_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=3))
+			self.mu = self.add_weight('mu_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=3))
 
 	def call(self, x):
 		thresholds = self._convert_thresholds(self.thresholds_b, self.thresholds_a)

### 2019-03-12 net_keras.py

@@ -104,9 +104,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
-		elif self.final_activation == 'pomghf':
+		elif self.final_activation == 'pomglogit':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'ghf'))
+			model.add(NNPOM(self.num_classes, 'glogit'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			model.add(tf.keras.layers.Activation(self.final_activation))
@@ -184,9 +184,9 @@ class Net:
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'cloglog'))
-		elif self.final_activation == 'pomghf':
+		elif self.final_activation == 'pomglogit':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'ghf'))
+			model.add(NNPOM(self.num_classes, 'glogit'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			if self.prob_layer == 'geometric':
@@ -217,9 +217,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
-		elif self.final_activation == 'pomghf':
+		elif self.final_activation == 'pomglogit':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'ghf'))
+			model.add(NNPOM(self.num_classes, 'glogit'))
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			if self.prob_layer == 'geometric':
@@ -252,9 +252,9 @@ class Net:
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(NNPOM(self.num_classes, 'cloglog'))
-		elif self.final_activation == 'pomghf':
+		elif self.final_activation == 'pomglogit':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'ghf'))
[…]

### 2019-03-15 paper/ieee.tex
Correcciones paper y nuevas funciones generalizadas

@@
 	Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of classes.
-This kind of problem can be treated as a nominal classification problem, but this discards ordinal information.
+This kind of problem can be treated as a nominal classification problem, but doing this discards the ordinal information.
 A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model.
@@
 It belongs to a wider family of models called Cumulative Link Models (CLM).
-It is inspired in the concept of a latent variable that is projected in an n-dimensional space and a set of thresholds that divides this space into the different ordinal levels.
+It is inspired in the concept of a latent variable that is projected in an n-dimensional space and a set of thresholds that divides that space into the different ordinal levels.
 This kind of models uses a link function which can be of different types.
@@
 
-	In this paper, an experimental study regarding link functions for Cumulative Link Models will be made.
-Also, other parameters that can affect the training process and the model performance, like the learning rate of the optimization algorithm and the batch size, and its interaction will be studied.
+	In this paper, an experimental study regarding link functions for Cumulative Link Models in deep learning will be made.
+Also, other parameters that can affect the training process and the model performance, like the learning rate of the optimization algorithm, the batch size, and its interaction will be studied.
 The nominal version of this model will be used as a baseline for comparison.
@@
 	J.
-de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the QWK loss function for the optimization algorithm.
+de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the QWK metric as loss function for the optimization algorithm.
 They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
@@
 Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
-They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.	Also, they proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
+They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.
+Also, they proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
 
@@
 			\end{tabular}						
-			\caption{Examples of the Diabetic Retinopathy test set.}
+			\caption{Examples of the Adience test set.}
 			\label{fig:AdienceExamples}
@@
 
-	Fig. \ref{fig:lrdecay} represents the learning rate decay for the different initial values considered in this work.
+	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
 	\begin{figure}[!t]

### 2019-03-15 activations.py

@@ -211,6 +211,9 @@ class NNPOM(tf.keras.layers.Layer):
 			a3T = 1 - tf.exp(-tf.exp(z3))
 		elif self.link_function == 'glogit':
 			a3T = 1.0 / tf.pow(1.0 + tf.exp(-self.lmbd * (z3 - self.mu) ), self.alpha)
+		elif self.link_function == 'lgamma':
+			a3T = tf.cond(self.q < 0, lambda: tf.igammac(tf.pow(self.q, -2), tf.pow(self.q, -2) * tf.exp(self.q * z3)),
+						  lambda: tf.cond(self.q > 0, lambda: tf.igamma(tf.pow(self.q, -2), tf.pow(self.q, -2) * tf.exp(self.q * z3)), lambda: self.dist.cdf(z3)))
 		else:
 			a3T = 1.0 / (1.0 + tf.exp(-z3))
 
@@ -229,9 +232,11 @@ class NNPOM(tf.keras.layers.Layer):
 								   initializer=tf.random_uniform_initializer(minval=1, maxval=10))
 
 		if self.link_function == 'glogit':
-			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=3))
-			self.alpha = self.add_weight('alpha_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=3))
-			self.mu = self.add_weight('mu_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=3))
+			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=1, maxval=1))
+			self.alpha = self.add_weight('alpha_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=1, maxval=1))
+			self.mu = self.add_weight('mu_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=0, maxval=0))
+		elif self.link_function == 'lgamma':
+			self.q = self.add_weight('q_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=-1, maxval=1))
 
 	def call(self, x):
 		thresholds = self._convert_thresholds(self.thresholds_b, self.thresholds_a)

### 2019-03-15 callbacks.py

@@ -108,3 +108,12 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 
 			print('VALIDATION CONF MATRIX')
 			print(val_metrics['conf_mat'])
+
+
+
+class PrintWeightsCallback(tf.keras.callbacks.Callback):
+	def __init__(self):
+		pass
+
+	def on_epoch_end(self, epoch, logs={}):
+		print(self.model.layers[-1].get_weights())

### 2019-03-15 experiment.py

@@ -9,7 +9,7 @@ import click
 import pickle
 import h5py
 from scipy import io as spio
-from callbacks import ComputeMetricsCallback
+from callbacks import ComputeMetricsCallback, PrintWeightsCallback
 from losses import qwk_loss, make_cost_matrix
 from metrics import np_quadratic_weighted_kappa, quadratic_weighted_kappa_cm, top_2_accuracy, top_3_accuracy, \
 	minimum_sensitivity, accuracy_off1
@@ -461,6 +461,7 @@ class Experiment():
 				f.write(str(epoch + 1))
 				f.write('\n' + str(self.best_metric))
 
+
 		save_epoch_callback = tf.keras.callbacks.LambdaCallback(
 			on_epoch_end=save_epoch
 		)
@@ -518,6 +519,7 @@ class Experiment():
 																	append=True),
 									   tf.keras.callbacks.TensorBoard(log_dir=self.checkpoint_dir),
 									   # tf.keras.callbacks.TerminateOnNaN(),
+									   PrintWeightsCallback()
 									   ],
 							workers=self.workers,
 							use_multiprocessing=True,

### 2019-03-15 net_keras.py

@@ -95,21 +95,7 @@ class Net:
 			self.__get_activation(),
 		])
 
-		if self.final_activation == 'poml':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'logit'))
-		elif self.final_activation == 'pomp':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'probit'))
-		elif self.final_activation == 'pomclog':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'cloglog'))
-		elif self.final_activation == 'pomglogit':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'glogit'))
-		else:
-			model.add(tf.keras.layers.Dense(self.num_classes))
-			model.add(tf.keras.layers.Activation(self.final_activation))
+		model = self.__add_activation(model)
 
 		return model
 
@@ -172,26 +158,7 @@ class Net:
 		if self.dropout > 0:
 			model.add(tf.keras.layers.Dropout(rate=self.dropout))
 
-		if self.final_activation == 'poml':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(tf.keras.layers.BatchNormalization())
-			model.add(NNPOM(self.num_classes, 'logit'))
-		elif self.final_activation == 'pomp':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(tf.keras.layers.BatchNormalization())
-			model.add(NNPOM(self.num_classes, 'probit'))
-		elif self.final_activation == 'pomclog':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(tf.keras.layers.BatchNormalization())
-			model.add(NNPOM(self.num_classes, 'cloglog'))
-		elif self.final_activation == 'pomglogit':
-			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'glogit'))
-		else:
-			model.add(tf.keras.layers.Dense(self.num_classes))
-			if self.prob_layer == 'geometric':
-				model.add(GeometricLayer())
-			model.add(tf.keras.layers.Activation(self.final_activation))
+		model = self.__add_activation(model)
 
 		return model
 
@@ -208,23 +175,7 @@ class Net:
 		if self.dropout > 0:
 			model.add(tf.keras.layers.Dropout(rate=self.dropout))
[…]

### 2019-03-26 activations.py
New gauss version

@@ -205,7 +205,7 @@ class NNPOM(tf.keras.layers.Layer):
 		b = tf.transpose(tf.reshape(tf.tile(projected, [self.num_classes - 1]), shape=[-1, m]))
 		z3 = a - b
 
-		# z3 = tf.Print(z3, data=[tf.reduce_min(z3), tf.reduce_max(z3)], message='z3 min max', summarize=100)
+		# z3 = tf.cond(tf.reduce_min(tf.abs(z3)) < 0.01, lambda: tf.Print(z3, data=[tf.reduce_min(tf.abs(z3))], message='z3 abs min', summarize=100), lambda: z3)
 
 		if self.link_function == 'probit':
 			a3T = self.dist.cdf(z3)
@@ -217,7 +217,8 @@ class NNPOM(tf.keras.layers.Layer):
 			a3T = tf.cond(self.q < 0, lambda: tf.igammac(tf.pow(self.q, -2), tf.pow(self.q, -2) * tf.exp(self.q * z3)),
 						  lambda: tf.cond(self.q > 0, lambda: tf.igamma(tf.pow(self.q, -2), tf.pow(self.q, -2) * tf.exp(self.q * z3)), lambda: self.dist.cdf(z3)))
 		elif self.link_function == 'gauss':
-			a3T = 1.0 / 2.0 + tf.sign(z3) * tf.igamma(1.0 / self.alpha, tf.pow(tf.abs(z3) / self.r, self.alpha)) / (2 * tf.exp(tf.lgamma(1.0 / self.alpha)))
+			# a3T = 1.0 / 2.0 + tf.sign(z3) * tf.igamma(1.0 / self.alpha, tf.pow(tf.abs(z3) / self.r, self.alpha)) / (2 * tf.exp(tf.lgamma(1.0 / self.alpha)))
+			a3T = 1.0 / 2.0 + (2 * tf.sigmoid(- 10 * z3) - 1) * tf.igamma(1.0 / self.alpha, tf.pow(tf.pow(z3, 2) / self.r, self.alpha)) / (2 * tf.exp(tf.lgamma(1.0 / self.alpha)))
 		else:
 			a3T = 1.0 / (1.0 + tf.exp(-z3))
 
@@ -243,9 +244,9 @@ class NNPOM(tf.keras.layers.Layer):
 			self.q = self.add_weight('q_nnpom', shape=(1,), initializer=tf.random_uniform_initializer(minval=-1, maxval=1))
 		elif self.link_function == 'gauss':
[…]

### 2019-03-26 experiment.py

@@ -520,8 +520,8 @@ class Experiment:
 																	append=True),
 									   tf.keras.callbacks.TensorBoard(log_dir=self.checkpoint_dir),
 									   tf.keras.callbacks.TerminateOnNaN(),
-									   tf.keras.callbacks.EarlyStopping(min_delta=0.001, patience=15, verbose=1),
-									   # PrintWeightsCallback()
+									   tf.keras.callbacks.EarlyStopping(min_delta=0.0005, patience=30, verbose=1),
+									   PrintWeightsCallback()
 									   ],
 							workers=self.workers,
 							use_multiprocessing=True,

### 2019-03-27 activations.py
New activations

@@ -6,6 +6,7 @@ class SPP(tf.keras.layers.Activation):
 	"""
 	Parametric softplus activation layer.
 	"""
+
 	def __init__(self, activation, **kwargs):
 		super(SPP, self).__init__(activation, **kwargs)
 		self.__name__ = 'SPP'
@@ -17,6 +18,7 @@ def parametric_softplus(spp_alpha):
 	:param spp_alpha: alpha parameter for softplus function.
 	:return: parametric softplus activation value.
 	"""
+
 	def spp(x):
 		return tf.log(1 + tf.exp(x)) - spp_alpha
 
@@ -174,15 +176,99 @@ class SQRTActivation(tf.keras.layers.Layer):
 
 	def call(self, inputs):
 		pos = tf.sqrt(tf.nn.relu(inputs))
-		neg = - tf.sqrt(tf.nn.relu(-inputs))
+		neg = - tf.sqrt(-tf.nn.relu(-inputs))
 
 		return pos + neg
 
+
+class RReLu(tf.keras.layers.Layer):
+	def __init__(self, **kwargs):
+		super(RReLu, self).__init__(**kwargs)
+
+	def build(self, input_shape):
+		self.alpha = self.add_weight(name='alpha', shape=input_shape, dtype=tf.float32,
+									 initializer=tf.keras.initializers.RandomNormal(stddev=1))
+
+		super(RReLu, self).build(input_shape)
+
+	def call(self, inputs):
+		pos = tf.nn.relu(inputs)
+		neg = self.alpha * tf.nn.relu(-inputs)
+
+		return pos + neg
+
+
+class PELU(tf.keras.layers.Layer):
+	def __init__(self, **kwargs):
+		super(PELU, self).__init__(**kwargs)
+
+	def build(self, input_shape):
+		self.alpha = self.add_weight(name='alpha', shape=(1,), dtype=tf.float32,
+									 initializer=tf.random_uniform_initializer(minval=0.01,
+																			   maxval=1,
+																			   dtype=tf.float32))
+		self.alpha = tf.clip_by_value(self.alpha, 0.0001, 10)
+
+		self.beta = self.add_weight(name='beta', shape=(1,), dtype=tf.float32,
+									 initializer=tf.random_uniform_initializer(minval=0.01,
+																			   maxval=1,
+																			   dtype=tf.float32))
[…]

### 2019-03-27 net_keras.py

@@ -1,5 +1,5 @@
 import tensorflow as tf
-from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, NNPOM
+from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, NNPOM, RReLu, PELU, SlopedReLU, PTELU
 from layers import GeometricLayer
 from resnet import Resnet_2x4
 
@@ -258,6 +258,14 @@ class Net:
 			return EPReLU()
 		elif self.activation == 'sqrt':
 			return SQRTActivation()
+		elif self.activation == 'RReLU':
+			return RReLu()
+		elif self.activation == 'PELU':
+			return PELU()
+		elif self.activation == 'SlopedReLU':
+			return SlopedReLU()
+		elif self.activation == 'PTELU':
+			return PTELU()
 		else:
 			return tf.keras.layers.Activation('relu')
 

### 2019-03-27 activations.py
Tau parameter on/off

@@ -269,10 +269,11 @@ class NNPOM(tf.keras.layers.Layer):
 	Proportional Odds Model activation layer.
 	"""
 
-	def __init__(self, num_classes, link_function, **kwargs):
+	def __init__(self, num_classes, link_function, use_tau, **kwargs):
 		self.num_classes = num_classes
 		self.dist = tf.distributions.Normal(loc=0., scale=1.)
 		self.link_function = link_function
+		self.use_tau = use_tau
 		super(NNPOM, self).__init__(**kwargs)
 
 	def _convert_thresholds(self, b, a):
@@ -285,7 +286,11 @@ class NNPOM(tf.keras.layers.Layer):
 		return th
 
 	def _nnpom(self, projected, thresholds):
-		projected = tf.reshape(projected, shape=[-1]) / self.tau
+		if self.use_tau == 1:
+			projected = tf.reshape(projected, shape=[-1]) / self.tau
+		else:
+			projected = tf.reshape(projected, shape=[-1])
+
 		m = tf.shape(projected)[0]
 		a = tf.reshape(tf.tile(thresholds, [m]), shape=[m, -1])
 		b = tf.transpose(tf.reshape(tf.tile(projected, [self.num_classes - 1]), shape=[-1, m]))
@@ -326,8 +331,10 @@ class NNPOM(tf.keras.layers.Layer):
 												minval=math.sqrt((1.0 / (self.num_classes - 2)) / 2),
 												maxval=math.sqrt(1.0 / (self.num_classes - 2))))
 
-		self.tau = self.add_weight('tau_nnpom', shape=(1,),
-								   initializer=tf.random_uniform_initializer(minval=1, maxval=10))
+		if self.use_tau == 1:
+			print('Using tau')
+			self.tau = self.add_weight('tau_nnpom', shape=(1,),
+									   initializer=tf.random_uniform_initializer(minval=1, maxval=10))
 
 		if self.link_function == 'glogit':
 			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,),

### 2019-03-27 experiment.py

@@ -26,7 +26,7 @@ class Experiment:
 
 	def __init__(self, name='unnamed', db='100', net_type='vgg19', batch_size=128, epochs=100,
 				 checkpoint_dir='checkpoint', loss='categorical_crossentropy', activation='relu',
-				 final_activation='softmax',
+				 final_activation='softmax', use_tau=True,
 				 prob_layer=None, spp_alpha=1.0, lr=0.1, momentum=0.9, dropout=0, task='both', workers=4,
 				 queue_size=1024, val_metrics=['loss', 'acc'], rescale_factor=0, augmentation={}):
 		self._name = name
@@ -37,6 +37,7 @@ class Experiment:
 		self._checkpoint_dir = checkpoint_dir
 		self._loss = loss
 		self._activation = activation
+		self._use_tau = use_tau
 		self._final_activation = final_activation
 		self._prob_layer = prob_layer
 		self._spp_alpha = spp_alpha
@@ -188,6 +189,18 @@ class Experiment:
 	@final_activation.deleter
 	def final_activation(self):
 		del self._final_activation
+
+	@property
+	def use_tau(self):
+		return self._use_tau
+
+	@use_tau.setter
+	def use_tau(self, use_tau):
+		self._use_tau = use_tau
+
+	@use_tau.deleter
+	def use_tau(self):
+		del self._use_tau
 
 	@property
 	def prob_layer(self):
@@ -468,7 +481,7 @@ class Experiment:
 		)
 
 		# NNet object
-		net_object = Net(img_size, self.activation, self.final_activation, self.prob_layer, num_channels, num_classes,
+		net_object = Net(img_size, self.activation, self.final_activation, self.use_tau, self.prob_layer, num_channels, num_classes,
 						 self.spp_alpha,
 						 self.dropout)
 
@@ -735,6 +748,7 @@ class Experiment:
 			'prob_layer': self.prob_layer,
 			'loss': self.loss,
 			'activation': self.activation,
+			'use_tau' : self.use_tau,
 			'final_activation': self.final_activation,
 			'spp_alpha': self.spp_alpha,
 			'lr': self.lr,
@@ -762,6 +776,7 @@ class Experiment:
 		self.loss = 'loss' in config and config['loss'] or 'crossentropy'
 		self.activation = 'activation' in config and config['activation'] or 'relu'
 		self.final_activation = 'final_activation' in config and config['final_activation'] or 'softmax'
[…]

### 2019-03-27 net_keras.py

@@ -7,10 +7,11 @@ from inception_resnet_v2 import InceptionResNetV2 as Irnv2
 
 
 class Net:
-	def __init__(self, size, activation, final_activation, prob_layer=None, num_channels=3, num_classes=5, spp_alpha=0.2, dropout=0):
+	def __init__(self, size, activation, final_activation, use_tau=True, prob_layer=None, num_channels=3, num_classes=5, spp_alpha=0.2, dropout=0):
 		self.size = size
 		self.activation = activation
 		self.final_activation = final_activation
+		self.use_tau = use_tau
 		self.prob_layer = prob_layer
 		self.num_channels = num_channels
 		self.num_classes = num_classes
@@ -273,24 +274,24 @@ class Net:
 		if self.final_activation == 'poml':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
-			model.add(NNPOM(self.num_classes, 'logit'))
+			model.add(NNPOM(self.num_classes, 'logit', use_tau=self.use_tau))
 		elif self.final_activation == 'pomp':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
-			model.add(NNPOM(self.num_classes, 'probit'))
+			model.add(NNPOM(self.num_classes, 'probit', use_tau=self.use_tau))
 		elif self.final_activation == 'pomclog':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
-			model.add(NNPOM(self.num_classes, 'cloglog'))
+			model.add(NNPOM(self.num_classes, 'cloglog', use_tau=self.use_tau))
 		elif self.final_activation == 'pomglogit':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'glogit'))
+			model.add(NNPOM(self.num_classes, 'glogit', use_tau=self.use_tau))
 		elif self.final_activation == 'clmgamma':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'lgamma'))
+			model.add(NNPOM(self.num_classes, 'lgamma', use_tau=self.use_tau))
 		elif self.final_activation == 'clmgauss':
 			model.add(tf.keras.layers.Dense(1))
-			model.add(NNPOM(self.num_classes, 'gauss'))
[…]

### 2019-03-27 experiment.py
Taup fix

@@ -627,7 +627,7 @@ class Experiment:
 			)
 
 			# NNet object
-			net_object = Net(img_size, self.activation, self.final_activation, self.prob_layer, num_channels,
+			net_object = Net(img_size, self.activation, self.final_activation, self.use_tau, self.prob_layer, num_channels,
 							 num_classes,
 							 self.spp_alpha,
 							 self.dropout)

### 2019-03-27 net_keras.py
Activation function name no caps

@@ -259,13 +259,13 @@ class Net:
 			return EPReLU()
 		elif self.activation == 'sqrt':
 			return SQRTActivation()
-		elif self.activation == 'RReLU':
+		elif self.activation == 'prelu':
 			return RReLu()
-		elif self.activation == 'PELU':
+		elif self.activation == 'pelu':
 			return PELU()
-		elif self.activation == 'SlopedReLU':
+		elif self.activation == 'slopedrelu':
 			return SlopedReLU()
-		elif self.activation == 'PTELU':
+		elif self.activation == 'ptelu':
 			return PTELU()
 		else:
 			return tf.keras.layers.Activation('relu')

### 2019-03-27 net_keras.py
rrelu name fix

@@ -259,7 +259,7 @@ class Net:
 			return EPReLU()
 		elif self.activation == 'sqrt':
 			return SQRTActivation()
-		elif self.activation == 'prelu':
+		elif self.activation == 'rrelu':
 			return RReLu()
 		elif self.activation == 'pelu':
 			return PELU()

### 2019-04-04 activations.py
Plot gauss, clmgauss parameters adjustments, clm cauchit added

@@ -309,6 +309,8 @@ class NNPOM(tf.keras.layers.Layer):
 			a3T = 1 - tf.exp(-tf.exp(z3))
 		elif self.link_function == 'glogit':
 			a3T = 1.0 / tf.pow(1.0 + tf.exp(-self.lmbd * (z3 - self.mu)), self.alpha)
+		elif self.link_function == 'cauchit':
+			a3T = tf.atan(z3 / math.pi) + 0.5
 		elif self.link_function == 'lgamma':
 			a3T = tf.cond(self.q < 0, lambda: tf.igammac(tf.pow(self.q, -2), tf.pow(self.q, -2) * tf.exp(self.q * z3)),
 						  lambda: tf.cond(self.q > 0, lambda: tf.igamma(tf.pow(self.q, -2),
@@ -316,8 +318,9 @@ class NNPOM(tf.keras.layers.Layer):
 										  lambda: self.dist.cdf(z3)))
 		elif self.link_function == 'gauss':
 			# a3T = 1.0 / 2.0 + tf.sign(z3) * tf.igamma(1.0 / self.alpha, tf.pow(tf.abs(z3) / self.r, self.alpha)) / (2 * tf.exp(tf.lgamma(1.0 / self.alpha)))
-			a3T = 1.0 / 2.0 + (2 * tf.sigmoid(-z3) - 1) * tf.igamma(1.0 / self.alpha,
-																	tf.pow(tf.pow(z3 / self.r, 2),
+			# z3 = tf.Print(z3, data=[tf.reduce_max(tf.abs(z3))], message='z3 abs max')
+			a3T = 1.0 / 2.0 + (2 * tf.sigmoid(z3 - self.mu) - 1) * tf.igamma(1.0 / self.alpha,
+																	tf.pow(tf.pow((z3 - self.mu) / self.r, 2),
 																		   self.alpha)) / (
 								  2 * tf.exp(tf.lgamma(1.0 / self.alpha)))
 		elif self.link_function == 'expgauss':
@@ -359,10 +362,11 @@ class NNPOM(tf.keras.layers.Layer):
 			self.q = self.add_weight('q_nnpom', shape=(1,),
 									 initializer=tf.random_uniform_initializer(minval=-1, maxval=1))
 		elif self.link_function == 'gauss':
-			self.alpha = self.add_weight('alpha_nnpom', shape=(1,), initializer=tf.constant_initializer(2.0))
-			self.alpha = tf.clip_by_value(self.alpha, 1, 3)
[…]

### 2019-04-04 net_keras.py

@@ -287,6 +287,10 @@ class Net:
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'glogit', use_tau=self.use_tau))
+		elif self.final_activation == 'clmcauchit':
+			model.add(tf.keras.layers.Dense(1))
+			model.add(tf.keras.layers.BatchNormalization())
+			model.add(NNPOM(self.num_classes, 'cauchit', use_tau=self.use_tau))
 		elif self.final_activation == 'clmgamma':
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())

### 2019-04-04 plot_gauss.py

@@ -1,0 +1,43 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import random
+from scipy.special import gamma, gammainc
+
+
+def numerador(x, a, r, mu):
+	return gammainc( 1/a, ((((x - mu) / r) ** 2) ** a)  )
+
+def denominador(a):
+	return 2 * gamma(1/a)
+
+def logfunc(x, a, r, mu):
+	return np.log(np.exp(x) - 1) + np.log(np.exp(x) + 1) + np.log(numerador(x, a, r, mu)) - np.log(2) - np.log(gamma(1.0/a))
+ 
+plots = [
+	{'alphas': np.round(np.arange(0.5,1.5,0.2), 2), 'rs':[1.0], 'mus':[0.0]},
+	{'alphas': [1.0], 'rs': np.round(np.arange(0.2,1.7,0.2), 2), 'mus':[0.0]},
+]
+
+
+for plot in plots:
+	alphas = plot['alphas']
+	rs = plot['rs']
+	mus = plot['mus']
+
+	colors = ['r','g','b','y','k','b','c','m']
+	for i in range(len(colors), len(alphas) * len(rs) * len(mus)):
+		colors.append((random.random(), random.random(), random.random()))
+
+	cid = 0
+	for a in sorted(alphas):
+		for r in rs:
+			for mu in mus:
+				x = np.arange(-5, 5, 0.001)
+				num = numerador(x, a, r, mu)
+				total = 0.5 + (2 * (1/(1+np.exp(-(x-mu)))) - 1) * num / denominador(a)
+				plt.plot(x,num, linestyle='--', c=colors[cid])
+				plt.plot(x,total, label='a={},r={},mu={}'.format(a, r, mu), c=colors[cid])
+				# plt.plot(x,logfunc(x, a, r, mu), label='a={},r={},mu={}'.format(a, r, mu), c = colors[cid])
+				cid += 1
+	plt.legend()
+	plt.show()

### 2019-05-21 paper/ieee.tex
New gauss version
Plot gauss, clmgauss parameters adjustments, clm cauchit added
Correciones paper v2

@@
 % *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+% *** trigger bugs that do not appear when using other class files.       ***
+% The testflow support page is at:                                        ***
+% http://www.michaelshell.org/tex/testflow/                               ***
 
@@
 	% Do not put math or special symbols in the title.
-	\title{Classification of ordinal data in deep learning: an experimental study}
+	\title{Deep ordinal classification based on cumulative link models}
 	%
@@
 	\begin{abstract}
-		This paper proposes a deep convolutional neural network model for ordinal regression based on the use of a family of probabilistic ordinal link functions in the output layer called Cumulative Link Models.
-This kind of models projects each pattern into a 1-dimensional space.
-In this case, the projections are estimated by a non-linear deep neural network.
+		This paper proposes a deep convolutional neural network model for ordinal regression by considering a family of probabilistic ordinal link functions in the output layer.
+The link functions are those used for cumulative link models, which are traditional statistical linear models based on projecting each pattern into a 1-dimensional space.
 A set of ordered thresholds splits this space into the different classes of the problem.
-Different link functions will be studied in this experimental study, and the results will be contrasted with statistical analysis.
+In our case, the projections are estimated by a non-linear deep neural network.
 To further improve the results, we combine these ordinal models with a loss function that takes into account the distance between the categories, based on the weighted Kappa index.
-The experiments run over two different ordinal classification problems, and the statistical tests confirm that these models improve the results of a nominal model and outperform the proposals considered in the literature.
+Three different link functions are studied in the experimental study, and the results are contrasted with statistical analysis.
+The experiments run over two different ordinal classification problems and the statistical tests confirm that these models improve the results of a nominal model and outperform other proposals considered in the literature.
 	\end{abstract}
@@
 	\begin{IEEEkeywords}
-		Deep learning, Ordinal Regression, Link models.
+		Deep learning, ordinal regression, cumulative link models.
 	\end{IEEEkeywords}
@@
 	Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of classes.
-This kind of problem can be treated as a nominal classification problem, but doing this discards the ordinal information.
-A better approach is to use specific methods that take into account this kind of information to improve the performance of the classification model.
-The Proportional Odds Model (POM)~\cite{agresti2010analysis} is an ordinal alternative to the softmax function that was designed for ordinal regression.
-It belongs to a wider family of models called Cumulative Link Models (CLM).
-It is inspired in the concept of a latent variable that is projected in an n-dimensional space and a set of thresholds that divides that space into the different ordinal levels.
-This kind of models uses a link function which can be of different types.
-The most common link function is the \texttt{logit} one, that is used in POM.
-However, there are other functions that can be explored.
-This model will be described in depth in Section \ref{sect:ordinalproblem}.
+This kind of problem can be treated as a nominal classification problem, but this discards the ordinal information.
+A better approach is to use specific methods that take the ordinality into account to improve the performance of the classification model.
+The Proportional Odds Model (POM)~\cite{mccullagh1980regression} is an ordinal alternative to the binary logistic regression.
+It belongs to a wider family of models called Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
+CLMs are inspired in the concept of a latent variable that is projected in a 1-dimensional space and a set of thresholds that divides that space into the different ordinal levels.
+This kind of models uses a link function which can be of different types, although the most common link function is the \texttt{logit}, which is used in POM.
+We explore different alternatives, as explained in depth in Section \ref{sect:ordinalproblem}.
 
 	Ordinal models can also be applied to deep learning models.
-In the case of convolutional networks, the model projection used by the threshold model will be obtained from the last layer of the network.
-When working with a 1-dimensional space, the last layer will have only one neuron, and its value will be used to classify every sample in the corresponding class according to the thresholds.
-Some previous works have used the POM in traditional neural networks~\cite{gutierrez2016ordinal}, but it has not been applied to convolutional networks yet.
-Also, there are some link functions that has not been explored.
-
-	In this paper, an experimental study regarding link functions for Cumulative Link Models in deep learning will be made.
-Also, other parameters that can affect the training process and the model performance, like the learning rate of the optimization algorithm, the batch size, and its interaction will be studied.
-The nominal version of this model will be used as a baseline for comparison.
-We will contrast the results obtained with statistical analysis to provide more robust conclusions.
-An approximated ANOVA III \cite{miller1997beyond} test followed by a posthoc Tukey's test \cite{tukey1949comparing} will be performed because of the limitations of the computational time required to run a higher number of executions.
-
-	The experiments will be run using two different ordinal datasets: Diabetic Retinopathy~\cite{de2018weighted}, which contains high-resolution fundus images related with diabetes disease, and Adience~\cite{beckham2017unimodal}, which includes human faces images associated with an age range.
+In the case of CNNs, the model projection used by the threshold model can be obtained from the last layer of the network.
+Given that we work with a 1-dimensional space, the last layer has only one neuron (projection of the pattern), and its value is used to classify the sample into the corresponding class according to the thresholds.
+Some previous works have used the \texttt{logit} in shallow neural networks~\cite{gutierrez2016ordinal}, but this strategy has not been considered for deep learning, and alternative link functions have not been evaluated.
+To further improve the results, we train these models by minimising an ordinal loss function based on the Weighted Kappa index \cite{de2018weighted}, instead of using the standard cross-entropy.
+
+	In this paper, we propose the use of CLMs for deriving deep learning ordinal classifiers.
+An experimental study evaluating the three most common link functions is performed.
+Also, other parameters that can affect the training process and the model performance are studied, such as the learning rate of the optimization algorithm, the batch size, and their interaction.
+The nominal version of this model is used as a baseline for comparison.
+We contrast the results obtained with a statistical analysis to provide more robust conclusions.
+An ANOVA III test \cite{miller1997beyond} followed by a posthoc Tukey's test \cite{tukey1949comparing} is performed over $5$ runs of the experiments, because of the demands of computational time required to run a higher number of executions.
+The experiments are run using two different ordinal datasets: Diabetic Retinopathy~\cite{de2018weighted}, which contains high-resolution fundus images related with diabetes disease, and Adience~\cite{beckham2017unimodal}, which includes human faces images associated with an age range.
 
 	This paper is organized as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper.
-Section~\ref{sect:ordinalproblem} present a formal description of an ordinal problem and the Cumulative Link Models.
+Section~\ref{sect:ordinalproblem} present a formal description of an ordinal problem and CLMs.
 In Section~\ref{sect:experiments}, we describe the model, the experiments and the datasets used, while, in Section~\ref{sect:results}, we present the results obtained and the statistical analysis.
@@
 	\label{sect:relatedwork}
-	There are many works related to the application and development of CNN models. However, few works are focused on ordinal classification problems.
-
+	There are many works related to the application and development of CNN models \cite{liu2017deep}, but few works focus on ordinal classification problems.
+The approaches proposed on those works are mainly related to
+	solving the ordinal problem as multiple binary sub-problems, using an ordinal loss function, solving the problem as a multi-class problem with constraints or simply using an ordinal evaluation metric.
+These works are described below:
+
+	\vspace{0.2cm}
+	$\bullet$ \textit{Solving the ordinal problem as multiple binary sub-problems.}
+
+%		\textbf{(Binarización. Resolución de varios subproblemas.)}
+	Z.
+Niu et al.
+\cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using convolutional neural networks.
+They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively solve these classification sub-problems, taking into account the correlation between them.
+
+%		\textbf{(Binarización. Resolución de varios subproblemas.)}
+	H.
+Li et al.
+\cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease as multiple binary sub-problems.
+
+%		\textbf{(Binarización. Resolución de varios subproblemas.)}
+	Y.
+Liu et al.
+\cite{liu2017deep} proposed a new approach which transforms the ordinal regression problem to binary classification sub-problems and use triplets with instances from different categories to train deep neural networks.
+In this way, high-level features describing the ordinal relationship are extracted automatically.
+Given that triplets must be generated, this approach is only recommended for small datasets.
+
+%		\textbf{(Binarización. Resolución de varios subproblemas.)}
+	S.
+Chen et al.
+\cite{chen2017using} proposed a deep learning method termed Ranking-CNN.
+This method combines multiple binary CNNs that are trained with ordinal age labels.
+The binary outputs are aggregated for the final age prediction.
+They achieved a tighter error bound for ranking-based age estimation.
+
+	\vspace{0.2cm}
+	$\bullet$ \textit{Using an ordinal loss function.}
+
+%		\textbf{(Función de coste ordinal)}
 	J.
@@
 Also, they checked the importance of hyper-parameter tuning.
-First, they defined QWK metric as follows:
-	\begin{equation}
-	\text{QWK} = 1 - \frac{\sum\limits_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits_{i,j} \omega_{i,j} E_{i,j}},
-	\end{equation}
-	where $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.
-
-	Then, they provided a continuous version of the QWK metric ($\text{QWK}_c$) based on the probabilities of the predictions:
-	\begin{equation}
-	\text{QWK}_c = 1 - \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
-	\end{equation}
-	where $\text{QWK}_c \in [-1,1]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
-Generally, $\omega_{i,j} = \frac{|i-j|^n}{(C-1)^n}$, where $\omega_{i,j} \in [0,1]$.
-
-	Then, they defined the loss function based on the QWK as follows:
-	\begin{equation}
-	\mathscr{L} = \log(1 - \text{QWK}_c),
-	\end{equation}
-	where $\mathscr{L} \in [-\infty, \log 2]$. This loss is a function to be minimized while the QWK metric must be maximized.
-
-	Z.
-Niu et al.
-\cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using convolutional neural networks.
-They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively resolve these classification sub-problems, taking into account the correlation between them.
-
+
+%		\textbf{(Función de coste ordinal y distribución unimodal.)}
 	C.
@@
 Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
-They evaluated this approach in the context of deep learning on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.
-Also, they proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
-
-	Adience dataset has been used in other works for human age estimation.
-E.
-Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks.
-J.-C.
-Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep convolutional networks.
-G.
-Levi \cite{levi2015age} presented another convolutional network model for age estimation.
-\textcolor{red}{Estos son ordinales?} \textcolor{blue}{No son ordinales pero los cito aqui porque luego los uso para comparar con ellos ya que son los que he encontrado que utilicen las base de datos Adience para predecir edad.}
-
-	H. Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease.
-
-	Y.
-Liu et al.
-\cite{liu2017deep} proposed a new approach of which transforms the ordinal regression problem to binary classification problems and use triplets with instances from different categories to train deep neural networks.
-In this way, high-level features describing the ordinal relationship are extracted automatically.
-
+The parameters of these distributions were learnt by using a deep neural network.
+They evaluated this approach on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.
+They also proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
+
+%		\textbf{(Funcion de coste ordinal)}
 	A.
@@
 
-	S.
-Chen et al.
-\cite{chen2017using} proposed a deep method termed Ranking-CNN.
-This method combines multiple binary CNNs that are trained with ordinal age labels.
-The binary outputs are aggregated for the final age prediction and they achieved a tighter error bound for ranking-based age estimation.
-
+%		\textbf{(Funcion de coste ordinal)}
 	H.
@@
 They introduced a spacing-increasing discretization strategy to treat the problem as an ordinal regression problem.
-They improved the performance when training the network with an ordinary regression loss.
+They improved the performance when training the network with an ordinal regression loss.
 Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.
-
+%	\textcolor{red}{La parte ordinal no queda muy clara}
+
+%		\textbf{(Funcion de coste ordinal)}
+	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.
+
+	\vspace{0.2cm}
+	$\bullet$ \textit{Solving the problem as a multi-class problem with constraints.}
+
+%		\textbf{(Multi-clase con restricciones)}
 	Y.
 Liu et al.
-\cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes the negative loglikelihood for multiple categories constrained by the order relationship between instances.
-
-	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.
-
+\cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes the negative loglikelihood for a multi-class problem constrained by the order relationship between instances.
+
+	\vspace{0.2cm}
+	$\bullet$ \textit{Simply using an ordinal evaluation metric.}
+
+%		\textbf{(Métrica ordinal (MAE))}
 	M.
@@
 \cite{alali2018multi} proposed a complex CNN architecture for solving Twitter Sentiment Classification as an ordinal problem.
-They checked that using average pooling preserves significant features that provide more expresiveness to ordinal scale.
+They checked that using average pooling preserves significant features that provide more expressiveness to ordinal scale.
+They didn't propose any method to include the ordinal information into the classifier but they tried to find the best CNN model architecture based on an ordinal metric.
+
+	Adience dataset has been used in other works for human age estimation but most of them solved the problem as a multi-class problem instead of using the ordinal relation between classes.
+E.
+Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks.
+J.-C.
+Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep CNNs, while G.
+Levi \cite{levi2015age} presented another convolutional network model for age estimation.
+
+	However, none of the works mentioned have combined a CNN model with an unimodal probability distribution, without dividing the problem in multiple binary sub-problems and using a continuous loss function based on one of the most common metrics for ordinal classification (Weighted Kappa).
+This is the approach that will be proposed in this work for solving two separate ordinal problems.
+
+%	The QWK metric is defined as follows:
+%	\begin{equation}
+%	\nonumber
+%	\text{QWK} = 1 - \frac{\sum\limits^N_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits^N_{i,j} \omega_{i,j} E_{i,j}},
+%	\end{equation}
+%	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i\bullet} O_{\bullet j}}{N}$, $O_{i\bullet}$ is the sum of the $i\text{-th}$ row and $O_{\bullet j}$ is the sum of the $j\text{-th}$ column.
+%	
+%	Then, they provided a continuous version of the QWK metric ($\text{QWK}_c$) based on the probabilities of the predictions:
+%	\begin{equation}
+%	\nonumber
+%	\text{QWK}_c = 1 - \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q \left( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k)\right)},
+%	\end{equation}
+%	where $\text{QWK}_c \in [-1,1]$, $\mathbf{x}_k$ and $t_k$ are the input vector and the real class of the $k$-th sample, respectively, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
+Generally, $\omega_{i,j} = \frac{|i-j|^n}{(C-1)^n}$, where $\omega_{i,j} \in [0,1]$.
+%	
+%	Then, they defined the loss function based on the QWK as follows:
+%	\begin{equation}
+%	\nonumber
+%	\mathscr{L} = \log(1 - \text{QWK}_c),
+%	\end{equation}
+%	where $\mathscr{L} \in [-\infty, \log 2]$. $\mathscr{L}$ should be minimized, while the $\text{QWK}_c$ metric should be maximized.
+
+%	\textcolor{red}{Yo intentaría organizar un poco el análisis que has hecho.
+Por ejemplo, podrías distinguir entre trabajos que modifican la función de error o los que modifican el modelo (ya sea aplicando binarización o utilizando distribuciones unimodales).
+o los que hacen las dos cosas.
+También habría que ir poniendo posibles pegas a cada artículo y destacar las ventajas de lo que proponemos (se impone una distribución unimodal, sin aplicar binarización, junco con una versión continua de una de las funciones d eerror más usadas)}
 
@@
 	\label{sect:ordinalproblem}
-	An ordinal classification problem consists of predicting the label $y$ of an input vector $\mathbf{x}$, where $\mathbf{x} \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
+	An ordinal classification problem consists in predicting the label $y$ of an input vector $\mathbf{x}$, where $\mathbf{x} \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
 $\mathbf{x}$ is in a K-dimensional input space, and $y$ is in a label space of $Q$ different labels.
-The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ points, $D = \{(\mathbf{x}_i, y_i), i = 1, ..., N\}$.
+The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ samples, $D = \{(\mathbf{x}_i, y_i), i = 1, ..., N\}$.
 Labels have a natural ordering in ordinal problems: $\mathcal{C}_1 \prec \mathcal{C}_2 \prec ...
 \prec \mathcal{C}_Q$.
-The order between labels makes it possible to compare two different elements of $\mathcal{Y}$ by using the relation $\prec$.
+The order between labels gives us the possibility to compare two different elements of $\mathcal{Y}$ by using the relation $\prec$.
 This is not possible under the nominal classification setting.
-In regression (where $y \in \mathds{R}$), real values in $\mathds{R}$ can be ordered by the standard $<$ operator, but labels in ordinal regression ($y \in \mathcal{Y}$) do not carry metric information, so the category serves as a qualitative indication of the pattern rather than a quantitative one.
+In regression (where $y \in \mathds{R}$), real values in $\mathds{R}$ can be ordered by the standard $<$ operator, but labels in ordinal regression ($y \in \mathcal{Y}$) do not carry metric information, i.e.
+the category serves as a qualitative indication of the pattern rather than a quantitative one.
 
 	The Proportional Odds Model (POM) arises from a statistical background and is one of the first models designed explicitly for ordinal regression~\cite{mccullagh1980regression}.
-It dated back to 1980 and is a member of a wider family of models recognised as Cumulative Link Models (CLM)~\cite{agresti2010analysis}.
+It dated back to 1980 and is a member of a wider family of models recognised as Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
 CLMs predict probabilities of groups of contiguous categories, taking the ordinal scale into account.
@@
 	\begin{align}
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) &= P(y = \mathcal{C}_1 | \mathbf{x}) + ... + P(y = \mathcal{C}_q | \mathbf{x}),\\
-		P(y = \mathcal{C}_q | \mathbf{x}) &= P(y \preceq \mathcal{C}_q | \mathbf{x}) - P(y \preceq \mathcal{C}_{q-1} | \mathbf{x}),
+		\nonumber P(y \preceq \mathcal{C}_q | \mathbf{x}) &= P(y = \mathcal{C}_1 | \mathbf{x}) + ... + P(y = \mathcal{C}_q | \mathbf{x}),\\
+		\nonumber P(y = \mathcal{C}_q | \mathbf{x}) &= P(y \preceq \mathcal{C}_q | \mathbf{x}) - P(y \preceq \mathcal{C}_{q-1} | \mathbf{x}),
 	\end{align}
@@
 
-	The model is inspired by the notion of a latent variable, where $f(\textbf{x})$ represents a one-dimensional mapping obtained from the output of the last layer, which has only one neuron.
+	The model is inspired by the notion of a latent variable, where $f(\textbf{x})$ represents a one-dimensional mapping.
 The decision rule $r: \mathcal{X} \rightarrow \mathcal{Y}$ is not fitted directly, but stochastic ordering of space $\mathcal{X}$ is satisfied by the following general model form \cite{herbrich2000large}:
 	\begin{equation}
+		\nonumber
 		g^{-1}(P(y \preceq \mathcal{C}_q | \mathbf{x})) = b_q - f(\mathbf{x}), \quad q = 1, ..., Q-1,
@@
 	where $g^{-1} : [0,1] \rightarrow (-\infty, +\infty)$ is a monotonic function often termed as the inverse link function, and $b_q$ is the threshold defined for class $\mathcal{C}_q$.
-Consider the latent variable $y^* = f(\mathbf{x})^* = f(\mathbf{x}) + \epsilon$, where $\epsilon$ is the random variable of the error.
+Consider the latent variable $y^* = f(\mathbf{x})^* = f(\mathbf{x}) + \epsilon$, where $\epsilon$ is the random component of the error.
 The most common choice for the probability distribution of $\epsilon$ is the logistic function (which is the default function for POM).
@@
 \le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | \mathbf{x})$ increases with $q$ \cite{mccullagh1980regression}.
-	This order is achieved by defining the first threshold and calculating the rest of thresholds from the first in the following form:
-
-	\begin{equation}
-	b_n = b_1 + \sum_{i=1}^{n-1} \alpha_i^2, \quad n = 2, ..., N,
-	\end{equation}
-	where $b_1$ and $\alpha_i$ are learnable parameters, and $N$ is the number of classes.
-
-	In this work, we use this ordinal model with different link functions for the probability distribution of $\epsilon$, including \texttt{logit}, \texttt{probit} and complementary log-log (\texttt{clog-log}).
-
+
+	In this work, we consider different link functions previously proposed in CLMs for the probability distribution of $\epsilon$, including \texttt{logit}, \texttt{probit} and complementary log-log (\texttt{clog-log}).
 These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
-They all follow the same form $P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - f(\mathbf{x}))$ for a continuous cdf~$\Phi$.
+They all follow the same form $\text{link}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = b_q - f(\mathbf{x})$.
 
@@
 		\includegraphics[width=3in]{img/linkfunctions.pdf}
-		\caption{Representation of link functions.}
+		\caption{Different link functions commonly used for CLMs.}
 		\label{fig:linkfunctions}
@@
 	\begin{itemize}
-		\item \texttt{Logit}. \texttt{logit} link function is the function used for the Proportional Odds Model. The \texttt{logit} link is:
-		\begin{equation}
+		\item The \texttt{logit} link function is the function used for the POM and is defined as:
+		\begin{equation}
+		\nonumber
 		\begin{aligned}
@@
 		\begin{equation}
-		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \frac{1}{1 + e^{-(b - f(\mathbf{x}))}}.
+		\nonumber
+		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \frac{1}{1 + e^{-(b_q - f(\mathbf{x}))}}.
 		\label{eq:logit2}
@@
 
-		\item \texttt{Probit}. \texttt{probit} link function is the inverse of the standard normal cumulative distribution function (cdf) $\Phi$. Its expression is:
-		\begin{equation}
+		\item The \texttt{probit} link function is the inverse of the standard normal cumulative distribution function (cdf) $\Phi$. Its expression is:
+		\begin{equation}
+		\nonumber
 		\begin{aligned}
@@
 		\begin{equation}
+		\nonumber
 		P(y \preceq \mathcal{C}_q | \mathbf{x}) = \int_{-\infty}^{b_q - f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
@@
 
-		\item \textit{Complementary log-log}.
-Like the \texttt{logit} and the \texttt{probit} transformation, the complementary log-log transformation takes a response that is restricted to the $(0,1)$ interval and converts it into something in the $(-\infty, +\infty)$ interval.
-Complementary log-log expression is:
-		\begin{equation}
+		\item The \textit{complementary log-log} (\texttt{clog-log}) takes a response that is restricted to the $(0,1)$ interval and converts it into something in the $(-\infty, +\infty)$ interval (like \texttt{logit} and \texttt{probit} transformations).
+The \texttt{clog-log} expression is:
+		\begin{equation}
+		\nonumber
 		\begin{aligned}
-		\log[-\log[1 - P(y \preceq \mathcal{C}_q | \mathbf{x})]] =&\\
-		= b_q - f(\mathbf{x}), \quad q = 1, ..., Q-1,&
+		\log[-\log[1 - P(y \preceq \mathcal{C}_q | \mathbf{x})]] =b_q - f(\mathbf{x}),
 		\end{aligned}
@@
 		\end{equation}
-		that is:
-		\begin{equation}
+		with $q = 1, ..., Q-1,$ that is:
+		\begin{equation}
+		\nonumber
 		P(y \preceq \mathcal{C}_q | \mathbf{x}) = 1 - e^{-e^{b_q - f(\mathbf{x})}}, \quad q = 1, ..., Q-1.
@@
 
-	\texttt{Logit} and \texttt{probit} links are symmetric:	
-	\begin{equation}
+	\texttt{logit} and \texttt{probit} links are symmetric:	
+	\begin{equation}
+	\nonumber
 	\text{link}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = -\text{link}[1 - P(y \preceq \mathcal{C}_q | \mathbf{x})],
@@
 $P(y \preceq \mathcal{C}_q | \mathbf{x})$ has the same rate when approaching 0 than when approaching 1.
-This symmetric property can be demonstrated as follows:
+This symmetry property can be demonstrated as follows:
 	\begin{enumerate}
@@
 		\begin{equation}
+		\nonumber
 		\begin{aligned}
@@
 		\begin{align}
-		\text{probit}(p) & = \Phi^{-1}(p) = b_q - f(\mathbf{x}),\\
-		-\text{probit}(1-p) &= \Phi^{-1}(1-p) = -b_q + f(\mathbf{x}),
+		\nonumber \text{probit}(p) & = \Phi^{-1}(p) = b_q - f(\mathbf{x}),\\
+		\nonumber -\text{probit}(1-p) &= \Phi^{-1}(1-p) = -b_q + f(\mathbf{x}),
 		\end{align}
@@
 		\begin{equation}
+		\nonumber
 		1 - p = \int_{-\infty}^{-b_q + f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x,
@@
 		\begin{equation}
+		\nonumber
 		p = 1 - \int_{-\infty}^{-b_q + f(\mathbf{x})} \frac{1}{\sqrt{2\pi}} e^{-\frac{1}{2}x^2} \mathrm{d}x.
@@
 
-	Unlike \texttt{logit} and \texttt{probit}, the complementary log-log model is asymmetrical.
+	Unlike \texttt{logit} and \texttt{probit}, the \texttt{clog-log} link is asymmetrical.
 It is frequently used when the probability of an event is very small or very large.
-When the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate.
-However, in this situation, the complementary log-log model might give a satisfying answer.
+When the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate, while \texttt{clog-log} can lead to better results.
+
+	This order is achieved by defining the first threshold and calculating the rest of thresholds from the first in the following form:	
+	\begin{equation}
+	\nonumber
+	b_n = b_1 + \sum_{i=1}^{n-1} \alpha_i^2, \quad n = 2, ..., N,
+	\end{equation}
+	where $b_1$ and $\alpha_i$ are learnable parameters, and $N$ is the number of classes.
+
+	\section{Weighted Kappa as loss function}
+	\label{sect:wk}
+	The Kappa index is a well-known metric that measures the agreement between two different raters.
+The Weighted Kappa (WK)~\cite{ben2008comparison} is based on the Kappa index and adds different weights to the different types of disagreements based on a weight matrix.
+It is useful to evaluate the performance in ordinal problems as it gives a higher weight to the errors that are further from the correct class.
+This metric is defined as follows:
+	\begin{equation}
+	\nonumber
+	\text{QWK} = 1 - \frac{\sum\limits^N_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits^N_{i,j} \omega_{i,j} E_{i,j}},
+	\end{equation}
+	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i\bullet} O_{\bullet j}}{N}$, $O_{i\bullet}$ is the sum of the $i\text{-th}$ row and $O_{\bullet j}$ is the sum of the $j\text{-th}$ column.
+
+	The WK defined above cannot be used as a loss function for the optimization algorithm as it is not continuous. However, it can be redefined in terms of probabilities of the predictions:
+	\begin{equation}
+	\nonumber
+	\text{QWK}_c = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
+	\end{equation}
+	where $\text{QWK}_c \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ (estimated using the CLM structure), and $\omega_{i,j}$ are the elements of the penalization matrix.
+In this case, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, where $\omega_{i,j} \in [0,1]$.
+
+	This loss function can be minimized using a gradient descent based algorithm.
 
@@
 DR is a dataset consisting of extremely high-resolution fundus image data.
-The training set consists of $17563$ pairs of images (where a  pair consists of a left and right eye image corresponding to a patient).
+The training set consists of $17563$ pairs of images (where a  pair includes a left and right eye image corresponding to a patient).
 In this dataset, we try to predict the correct category from five levels of diabetic retinopathy: no DR ($25810$ images), mild DR ($2443$ images), moderate DR ($5292$ images), severe DR ($873$ images), or proliferative DR ($708$ images).
 The test set contains $26788$ pairs of images.
-These images are taken in variable conditions: by different cameras, varying conditions of illumination and different resolutions.
-These images come from the EyePACS dataset that was used in a Diabetic Retinopathy Detection competition hosted on the Kaggle platform.
-Also, this dataset was used in later works~\cite{de2018weighted,nebot2016diabetic}, applying an ordinal QWK cost function in \cite{de2018weighted} to achieve better performance.
+These images are taken in variable conditions: by different cameras,  conditions of illumination and resolutions.
+These images come from the EyePACS dataset that was used in the DR detection competition hosted on the Kaggle platform.
+Also, this dataset has been used in different works~\cite{de2018weighted,nebot2016diabetic}, where an ordinal QWK cost function was considered in \cite{de2018weighted} to achieve better performance.
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
@@
 Data augmentation techniques, described in Section \ref{sect:settings}, are applied to achieve a higher number of samples.
-A few images of this dataset are shown in Figure \ref{fig:DRexamples}.
+A few test images of this dataset are shown in Figure \ref{fig:DRexamples}.
 
@@
 			\end{tabular}						
-			\caption{Examples of the Diabetic Retinopathy test set.}
+			\caption{Examples taken from the Diabetic Retinopathy test set.}
 			\label{fig:DRexamples}
@@
 			\end{tabular}						
-			\caption{Examples of the Adience test set.}
+			\caption{Examples taken from the Adience test set.}
 			\label{fig:AdienceExamples}
@@
 	CNNs have been used for both datasets.
-The different architectures of CNN used in these experiments are presented in tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
+The different architectures of CNN used in these experiments are presented in Tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
 The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
-The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved for obtaining the next pixel.
-Pooling layers have got similar parameters: the pool size is the number of pixels that will be involved in the pooling operation, and the stride represents the same concept that in convolutional layers.
-For convolutional layers, ConvWxH@FsS~=~F filters of size WxH and stride S.
-For pooling layers, PoolWxHsS~=~pool size of WxH and stride S.
-
-	The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used for activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradients problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
+The most important parameters for convolutional layers are the number of filters that are used to make the convolution operation, the size of these filters and the stride, which is the number of pixels that the filter is moved in every operation.
+Pooling layers have similar parameters: pool size (number of pixels that will be involved in the operation) and stride.
+For convolutional layers, ConvWxH@FsS stands for filters of size WxH and stride S.
+For pooling layers, PoolWxHsS corresponds to a pool size of WxH and stride S.
+
+	The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used as the activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradients problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
 Also, ELUs lead to faster training and better generalization performance than ReLU and Leaky ReLU (LReLU)~\cite{maas2013rectifier} functions on networks with more than five layers.
@@
 This method reduces the internal covariate shift by normalizing layer outputs.
-It allows us to use higher learning rates and be less careful about weights initialization.
+It allows us to use higher learning rates and be less careful about weight initialization.
 It also eliminates the need for using regularization techniques like Dropout.
@@
 	At the output of the network, the CLM is used.
-Also, a learnable parameter has been used to rescale the projections used by the Cumulative Link Model to make it more stable and guarantee the convergence in most cases.
+Also, the learnable parameter $\tau$ has been used to rescale the projections used by the CLM to make it more stable and guarantee the convergence in most cases.
+The following expression describes the transformation applied to these projections:
+	\begin{equation}
+		\nonumber
+		f'(x) = \frac{f(x)}{\tau}
+	\end{equation}
+%	where $\tau$ is the learnable parameter that is adjusted by the optimization algorithm.
 
@@
 We study different initial learning rates ($\eta$) in order to find the optimal one for each problem.
-We apply an exponential decay across training epochs to the initial learning rate ($\eta_0$) following the expression below:
-	\begin{equation}
+We apply an exponential decay \cite{chin2015learning} across training epochs to the initial learning rate ($\eta_0$) following the expression below:
+	\begin{equation}
+		\nonumber
 		\eta = \eta_0 \cdot e^{-0.025 \cdot \text{epoch}}.
@@
 
-	Both datasets are artificially equalized using data augmentation techniques~\cite{van2001art}.
+	Both datasets are artificially balanced using data augmentation techniques~\cite{van2001art}.
 However, different transformations are applied to each one.
 DR dataset augmentation is based on image cropping and zooming, horizontal and vertical flipping, brightness adjustment and random rotations.
-Horizontal flipping is the only transformation applied to Adience dataset.
-These transformations are applied every time a new batch is loaded, and the parameters of each one are randomly chosen from a defined range, providing a new set of transformed images for each batch.
+Horizontal flipping is the only transformation applied to the Adience dataset.
+These transformations are applied every time a new batch is loaded, and the parameters of each one are randomly chosen from a defined range ($[0.8, 1.2]$ for zoom, $[0.5, 1.5]$ for brightness and $[0, 90]$ degrees for rotation), providing a new set of transformed images for each batch.
 This technique reduces the overfitting risk and provides an important performance boost as we always work with different but similar images \cite{krizhevsky2012imagenet}.
@@
 
-	The model is evaluated using the Quadratic Weighted Kappa metric (QWK)~\cite{ben2008comparison}.
-This evaluation measure gives a higher weight to the errors that are further from the correct class.
+	The model is evaluated using the Weighted Kappa metric described in Section \ref{sect:wk} with a quadratic penalization matrix (Quadratic Weighted Kappa, QWK).
+%	\textcolor{red}{Es importante distinguir entre función de coste (usada para el ajuste de los pesos en el algoritmo de entrenamiento) y función de evaluación (usada para evaluar los modelos, en test o validación).
+Yo en esta parte describiría la de evaluación no la de coste, que debería estar descrita con el algoritmo, como hicimos en el congreso}
+%	This evaluation measure gives a higher weight to the errors that are further from the correct class.
 A similar approach to the one described in \cite{de2018weighted} is used as the loss function as it gives better performance for ordinal classification problems.
-In this case, we define the QWK loss function ($\text{QWK}_l$) as follows:
-	\begin{equation}
-	\text{QWK}_l = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
-	\end{equation}
-	where $\text{QWK}_l \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
+In this case, we define the QWK loss function ($\text{QWK}_c$) as follows:
+%	\begin{equation}
+%	\nonumber
+%	\text{QWK}_c = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
+%	\end{equation}
+%	where $\text{QWK}_c \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ (estimated using the CLM structure), and $\omega_{i,j}$ are the elements of the penalization matrix.
 In this case, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, where $\omega_{i,j} \in [0,1]$.
 
-	Also, other evaluation metrics are used to ease the comparison with other works: Minimum Sensitivity (MS) \cite{cruz2014metrics}, Mean Absolute Error (MAE) \cite{cruz2014metrics}, Mean Squared Error (MSE) \cite{wang2009mean}, Correct Classification Rate (CCR), Top-2 CCR \cite{beckham2017unimodal}, Top-3 CCR \cite{beckham2017unimodal} and 1-off accuracy \cite{chen2016cascaded,levi2015age,eidinger2014age}.
-
-	Experiments are run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the Cumulative Link Model).
+	Also, other evaluation metrics are used to ease the comparison with other works:
+	\begin{itemize}
+		\item Minimum Sensitivity (MS) \cite{cruz2014metrics} is the lowest percentage of samples correctly predicted to belong to a class with respect to the number of samples of that class.
+		\begin{equation}
+			\nonumber
+			\text{MS} = \min\left\lbrace S_q = \frac{O_{qq}}{O_{q\bullet}}, q = 1, ..., Q \right\rbrace,
+		\end{equation}
+		where $O$ is the confusion matrix and $Q$ is the number of classes.
+
+		\item Mean Absolute Error (MAE) \cite{cruz2014metrics} is the average absolute deviation of the predicted category from the real one.
+		\begin{equation}
+			\nonumber
+			\text{MAE} = \frac{1}{N} \sum^Q_{i,j = 1} |i-j|O_{ij},
+		\end{equation}
+		where $N$ is the number of samples, $Q$ is the number of classes and O is the confusion matrix.
+
+		\item Accuracy-based metrics.
+Correct Classification Rate (CCR) or standard accuracy is the most common metric for classification tasks and shows the percentage of correctly classified samples, Top-2 CCR \cite{beckham2017unimodal} and Top-3 CCR \cite{beckham2017unimodal} are based on CCR but they take a prediction as correct when the real class is between the two (or three) predictions with the highest probability.
+
+		\item 1-off accuracy \cite{eidinger2014age,chen2016cascaded,levi2015age} marks the prediction as correct when the correct class is at one category of distance from the predicted one.
+It can be considered as an ordinal metric as it calculates the distance between the real class and the predicted one based on the ordinal information of the problem.
+	\end{itemize}
+
+	Experiments are run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the CLM).
 The results of these experiments are analysed in Section \ref{sect:NominalComparison}.
@@
 	\subsection{Factors}
-	Three different factors are considered: learning rate, batch size and link function for the final output layer.
-
+	Three different factors are considered: learning rate, batch size and link function for the final output layer:
 	\begin{itemize}
@@
 Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical,senior2013empirical}.
-Within this work, we consider three different values for this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
+In this work, we consider three different values for the parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
 		\item \textit{Batch size} (BS).
@@
 In this paper, we try three separate batch sizes for each dataset.
-For DR dataset, we use $5$, $10$ and $15$ while, for the Adience dataset, $64$, $128$ and $256$ images are used.
+For the DR dataset, we use $5$, $10$ and $15$, while, for Adience, $64$, $128$ and $256$ images are used.
 We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expanded the range on both sides.
@@
 	\label{sect:dr}
-	Detailed test results for the Diabetic Retinopathy dataset are presented in Table \ref{table:DRresults}. The best result for each metric is marked in bold and the second best is in italic font.
+	Detailed test results for the DR dataset are presented in Table \ref{table:DRresults}. The best result for each metric is marked in bold and the second best is in italic font.
 
 	\begin{table*}[!t]
-		\caption{Diabetic Retinopathy results. BS stands for Batch Size, LF for link function and LR for Learning Rate. Mean and standard deviation $\text{Mean}_\text{SD}$.}
+		\caption{DR results. BS stands for Batch Size, LF for link function and LR for Learning Rate. Mean and standard deviation are represented as $\text{Mean}_\text{SD}$.}
 		\label{table:DRresults}
@@
 		\centering
-		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
-			\hline
-			\hline
-			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-			5 & \texttt{clog-log} & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.165_{(0.020)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
-			5 & \texttt{clog-log} & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.123_{(0.004)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
-			5 & \texttt{clog-log} & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.104_{(0.001)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
-			5 & \texttt{logit} & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.162_{(0.018)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
-			5 & \texttt{logit} & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.123_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
-			5 & \texttt{logit} & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.102_{(0.001)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
-			5 & \texttt{probit} & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.182_{(0.053)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
-			5 & \texttt{probit} & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.132_{(0.014)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
-			5 & \texttt{probit} & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.105_{(0.001)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
-			10 & \texttt{clog-log} & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.120_{(0.014)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
-			10 & \texttt{clog-log} & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.115_{(0.002)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
-			10 & \texttt{clog-log} & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.096_{(0.001)}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
-			10 & \texttt{logit} & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.140_{(0.008)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
-			10 & \texttt{logit} & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.113_{(0.004)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
-			10 & \texttt{logit} & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.095_{(0.002)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
-			10 & \texttt{probit} & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.137_{(0.014)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
-			10 & \texttt{probit} & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.120_{(0.002)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
-			10 & \texttt{probit} & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.098_{(0.001)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
-			15 & \texttt{clog-log} & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.134_{(0.005)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
-			15 & \texttt{clog-log}g & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
-			15 & \texttt{clog-log} & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $\mathit{0.093_{(0.001)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
-			15 & \texttt{logit} & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.129_{(0.009)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
-			15 & \texttt{logit} & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.114_{(0.005)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
-			15 & \texttt{logit} & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.090_{(0.001)}}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
-			15 & \texttt{probit} & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.138_{(0.014)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
-			15 & \texttt{probit} & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.116_{(0.005)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
-			15 & \texttt{probit} & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $0.094_{(0.001)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$\\
+		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+			\hline
+			\hline
+			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
+			5 & \texttt{clog-log} & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
+			5 & \texttt{clog-log} & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
+			5 & \texttt{clog-log} & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
+			5 & \texttt{logit} & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
+			5 & \texttt{logit} & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
+			5 & \texttt{logit} & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
+			5 & \texttt{probit} & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
+			5 & \texttt{probit} & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
+			5 & \texttt{probit} & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
+			10 & \texttt{clog-log} & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
+			10 & \texttt{clog-log} & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
+			10 & \texttt{clog-log} & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
+			10 & \texttt{logit} & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
+			10 & \texttt{logit} & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
+			10 & \texttt{logit} & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
+			10 & \texttt{probit} & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
+			10 & \texttt{probit} & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
+			10 & \texttt{probit} & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
+			15 & \texttt{clog-log} & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
+			15 & \texttt{clog-log} & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
+			15 & \texttt{clog-log} & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
+			15 & \texttt{logit} & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
+			15 & \texttt{logit} & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
+			15 & \texttt{logit} & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
+			15 & \texttt{probit} & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
+			15 & \texttt{probit} & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
+			15 & \texttt{probit} & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$\\
 			\hline
@@
 		\centering
-		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
-			\hline
-			\hline
-			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{MSE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-			64 & \texttt{clog-log} & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.129_{(0.007)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
-			64 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $0.101_{(0.003)}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
-			64 & \texttt{clog-log} & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.100_{(0.002)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
-			64 & \texttt{logit} & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.137_{(0.007)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
-			64 & \texttt{logit} & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $0.098_{(0.003)}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
-			64 & \texttt{logit} & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.108_{(0.004)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
-			64 & \texttt{probit} & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.121_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
-			64 & \texttt{probit} & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.105_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
-			64 & \texttt{probit} & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.100_{(0.002)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
-			128 & \texttt{clog-log} & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.117_{(0.002)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
-			128 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.100_{(0.001)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
-			128 & \texttt{clog-log} & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.125_{(0.004)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
-			128 & \texttt{logit} & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.125_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
-			128 & \texttt{logit} & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.099_{(0.003)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
-			128 & \texttt{logit} & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.151_{(0.005)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
-			128 & \texttt{probit} & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.115_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
-			128 & \texttt{probit} & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.100_{(0.003)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
-			128 & \texttt{probit} & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.110_{(0.002)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
-			256 & \texttt{clog-log} & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.110_{(0.001)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
-			256 & \texttt{clog-log} & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.097_{(0.004)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
-			256 & \texttt{clog-log} & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.165_{(0.004)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
-			256 & \texttt{logit} & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.125_{(0.015)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
-			256 & \texttt{logit} & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $\mathbf{0.094_{(0.002)}}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
-			256 & \texttt{logit} & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.191_{(0.002)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
-			256 & \texttt{probit} & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.112_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
-			256 & \texttt{probit} & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $\mathit{0.095_{(0.001)}}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
-			256 & \texttt{probit} & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.150_{(0.005)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$\\
+		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
+			\hline
+			\hline
+			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
+			64 & \texttt{clog-log} & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
+			64 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
+			64 & \texttt{clog-log} & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
+			64 & \texttt{logit} & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
+			64 & \texttt{logit} & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
+			64 & \texttt{logit} & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
+			64 & \texttt{probit} & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
+			64 & \texttt{probit} & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
+			64 & \texttt{probit} & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
+			128 & \texttt{clog-log} & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
+			128 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
+			128 & \texttt{clog-log} & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
+			128 & \texttt{logit} & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
+			128 & \texttt{logit} & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
+			128 & \texttt{logit} & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
+			128 & \texttt{probit} & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
+			128 & \texttt{probit} & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
+			128 & \texttt{probit} & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
+			256 & \texttt{clog-log} & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
+			256 & \texttt{clog-log} & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
+			256 & \texttt{clog-log} & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
+			256 & \texttt{logit} & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
+			256 & \texttt{logit} & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
+			256 & \texttt{logit} & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
+			256 & \texttt{probit} & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
+			256 & \texttt{probit} & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
+			256 & \texttt{probit} & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$\\
 			\hline
@@
 	\label{sect:statisticalanalysis}
-	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the result.
-
+	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the results.
 The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each of them, were obtained using an ANalysis Of the VAriance (ANOVA).
@@
 ANOVA is essentially a method of analysing the variance to which a response is subject into its various components, corresponding to the sources of variation which can be identified.
-
 ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
@@
 	We denote by $\text{QWK}_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level.
-We assume that the three factors do not act independently and therefore there exists an interaction between each pair of them and between the three factors.
+We assume that the three factors do not act independently, and, therefore, there exists an interaction between each pair of them and between the three factors.
 In this case, the observations fit:
 	\begin{equation}
+	\nonumber
 	\begin{aligned}
@@
 The same interaction effect is appreciated on $LB_{i,k}$, $PB_{j,k}$ and $LPB_{i,j,k}$.
-The term $\epsilon_{i,j,k,l}$ is the influence on the result of everything that could not be assigned or of random factors.
+The term $\epsilon_{i,j,k,l}$ is the influence on the results of everything that could not be evaluated or of random factors.
 $QWK_{i,j,k,l}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
 
-	We consider some hypotheses testing where the null hypothesis is proposed that each term of the above equation is independent of the levels involved.
+	We consider the null hypothesis that each term of the above equation is independent of the levels involved.
 The hypotheses for the levels of the L factor are $H_0 \equiv L_1 = L_2 = L_3,$ and $H_1 \equiv \text{ some } L_i \text{ is different}$.
-
 The same hypotheses are made for the other factors.
-In this way, we test in the null hypothesis that all of the population means are equal against an alternative hypothesis that there is at least one mean that is not equal to the others.
+In this way, we test in the null hypothesis that all the population averages are equal against the alternative hypothesis that there is at least one mean that is not equal to the others.
 
@@
 
-	The analysis of variance table represents the initial study in a compact form, containing the sum of squares, degrees of freedom, mean square, test statistics and significance level, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
-These factors and interactions take part of the error component now.
-In this way, the results of the ANOVA III test for the Diabetic Retinopathy dataset are summarised in Table  \ref{table:ANOVARetinopathy}.
+	The analysis of variance table represents the initial study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
+These factors and interactions take part on the error component.
+In this way, the results of the ANOVA III test for the DR dataset are summarised in Table  \ref{table:ANOVARetinopathy}.
 There are significant differences in average QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$ ($\text{p-value} = 0.000$).
@@
 
-	Given that there exist significant differences between the means, we analyse now those differences.
+	Given that there exist significant differences between the means, we analyse now these differences.
 A post-hoc multiple comparison test has been performed on the mean QWK obtained.
@@
 	\begin{table}[!t]
-		\caption{Tukey's test results for the Diabetic Retinopathy dataset.}
+		\caption{Tukey's test results for the DR dataset.}
 		\label{table:TukeyDR}
@@
 	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for Adience.
-Under the null hypothesis that the variance of the error of the dependent variable is the same between groups, an HSD Tukey's test has been applied.
+Under the null hypothesis that the variance of the error of the dependent variable is the same between the groups, an HSD Tukey's test has been applied.
 The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.
@@
 	The best batch size for DR was 10 while the best value for Adience was 128 (intermediate values considered).
-	Finally, there are more interactions between the three factors for the Adience dataset than for the Diabetic Retinopathy one.
+	Finally, there are more interactions between the three factors for the Adience dataset than for the DR one.
 This highlights the importance of making experimental designs associated with each dataset to determine the best value for each factor.
@@
 
-	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function for the optimizer and the softmax function instead of the Cumulative Link Model for the output of the network.
+	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function and the softmax function instead of the CLM for the output of the network.
 The evaluation metrics remains the same in order to be able to compare.
@@
 
-	For the Diabetic Retinopathy dataset, the best mean value of QWK was $0.497$ and was obtained when using a batch size of 10 and a learning rate of $10^{-4}$.
-
+	For the DR dataset, the best mean value of QWK was $0.497$ and was obtained when using a batch size of 10 and a learning rate of $10^{-4}$.
 In the case of Adience dataset, the highest QWK was $0.787$ and was achieved with a batch size of 64 and a learning rate of $10^{-3}$.
 
-	Finally, a comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
+	The comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in Tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
 All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).
 The proposed ordinal model outperforms all the other alternatives in terms of QWK.
-The performance gain of CLM over the softmax reaches $16.8\%$ for Diabetic Retinopathy and $11.9\%$ for Adience dataset.
+The performance gain of CLM over the softmax reaches $16.8\%$ for DR and $11.9\%$ for Adience dataset.
 The improvement of the ordinal method for Retinopathy dataset is higher than for Adience dataset.
@@
 	\begin{table}[!t]
-		\caption{Comparison between the best results of nominal, ordinal and previous works for the Diabetic Retinopathy dataset.}
+		\caption{Comparison between the best results of nominal, ordinal and previous works for the DR dataset.}
 		\label{table:ComparisonDR}
@@
 			Ordinal network                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
-			Nominal network                          &    $0.498_{(0.011)}$    &    $0.692_{(0.012)}$    &        $0.854_{(0.006)}$         \\
+			Nominal network                          &    $0.498_{(0.013)}$    &    $0.692_{(0.014)}$    &        $0.854_{(0.006)}$         \\
 			J. Torre et al. \cite{de2018weighted}    &  $0.537_{(\text{-})}$   &            -            &                -                 \\
@@
 	\label{sect:conclusions}
-	The first conclusion obtained from the results of our experiments is that the optimal values for the different parameters considered are problem-dependant.
-
-	The complementary log-log function offers the best results in Diabetic Retinopathy dataset while the \texttt{logit} link is the best option for the Adience dataset.
-These results provide an opportunity for exploring new generalised link functions that could be dynamically adapted to any problem.
-
-	The best value for the learning rate parameter for both datasets is $\eta = 10^{-3}$. It can be considered a good value for this parameter when training the model with new datasets.
-
-	Both datasets have obtained the best performance with an intermediate batch size: 10 for Diabetic Retinopathy and 128 for Adience.
-
-	Also, the statistical tests reported that there are relevant interactions between the three factors that we have take into account.
-The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
-
 	The proposed CLM has improved the performance of the deep network compared to the model that uses the softmax function and the models proposed in previous works.
@@
 So, the most significant improvements of these link functions are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
+
+	Also, we have concluded that the optimal values for the different parameters considered are problem-dependant.
+The complementary log-log function offers the best results in DR dataset while the \texttt{logit} link is the best option for the Adience dataset.
+These results provide an opportunity for exploring new generalised link functions that could be dynamically adapted to any problem.
+The best value for the learning rate parameter for both datasets is $\eta = 10^{-3}$.
+It can be considered a good value for this parameter when training the model with new datasets.
+Both datasets have obtained the best performance with an intermediate batch size: 10 for DR and 128 for Adience.
+	Also, the statistical tests reported that there are relevant interactions between the three factors that we have take into account.
+The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
 

### 2019-05-21 paper/ieee_old.tex
Correciones paper v2

--- 2019-03-15 paper/ieee.tex
@@
 	\begin{equation}
-	\text{QWK} = 1 - \frac{\sum\limits_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits_{i,j} \omega_{i,j} E_{i,j}},
-	\end{equation}
-	where $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix and $E$ is the normalized outer product between the prediction and the true vector.
+	\text{QWK} = 1 - \frac{\sum\limits^N_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits^N_{i,j} \omega_{i,j} E_{i,j}},
+	\end{equation}
+	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i.} O_{.j}}{N}$, $O_{i.}$ is the sum of the $i\text{-th}$ row and $O_{.j}$ is the sum of the $j\text{-th}$ column.
 
@@
 	These three types of links are explained below and represented in Figure \ref{fig:linkfunctions}.
-They all follow the same form $P(y \preceq \mathcal{C}_q | \mathbf{x}) = \Phi(b_q - f(\mathbf{x}))$ for a continuous cdf~$\Phi$.
+They all follow the same form $\text{link}[P(y \preceq \mathcal{C}_q | \mathbf{x})] = b_q - f(\mathbf{x})$.
 
@@
 			15 & \texttt{clog-log} & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.134_{(0.005)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
-			15 & \texttt{clog-log}g & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
+			15 & \texttt{clog-log} & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.113_{(0.003)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
 			15 & \texttt{clog-log} & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $\mathit{0.093_{(0.001)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\

### 2019-05-21 losses.py

@@ -29,7 +29,7 @@ def qwk_loss(cost_matrix):
 	def _qwk_loss(true_prob, pred_prob):
 		targets = tf.argmax(true_prob, axis=1)
 		costs = tf.gather(cost_matrix, targets)
-		# targets = tf.Print(targets, data=[targets], summarize=100, message='targets')
+
 
 		# costs = tf.Print(costs, data=[costs], summarize=100, message='costs')
 

### 2019-05-22 net_keras.py
Binomial. Plot gamma

@@ -4,6 +4,7 @@ from layers import GeometricLayer
 from resnet import Resnet_2x4
 
 from inception_resnet_v2 import InceptionResNetV2 as Irnv2
+from unimodal_extensions import _add_binom_m
 
 
 class Net:
@@ -306,6 +307,8 @@ class Net:
 			model.add(tf.keras.layers.Dense(1))
 			model.add(tf.keras.layers.BatchNormalization())
 			model.add(NNPOM(self.num_classes, 'expgauss', self.f_a_params, use_tau=self.use_tau))
+		elif self.final_activation == 'binomial':
+			_add_binom_m(model, self.num_classes, 1.0, 'sigm_learnable')
 		else:
 			model.add(tf.keras.layers.Dense(self.num_classes))
 			if self.prob_layer == 'geometric':

### 2019-05-22 plot_gamma.py

@@ -1,0 +1,35 @@
+import matplotlib.pyplot as plt
+import numpy as np
+import random
+from scipy.special import gamma, gammainc
+
+
+def loggamma(x, a, d, p):
+	return gammainc(d/p, (x/a)**p) / gamma(d/p)
+
+plots = [
+	{'as': np.round(np.arange(0.1, 1.5, 0.2), 2), 'ds': [1.0], 'ps': [0.1]},
+	{'as': [0.5], 'ds': np.round(np.arange(0.1, 1.5, 0.2), 2), 'ps': [0.1]},
+]
+
+for plot in plots:
+	aas = plot['as']
+	ds = plot['ds']
+	ps = plot['ps']
+
+	colors = ['r', 'g', 'b', 'y', 'k', 'c', 'm']
+	for i in range(len(colors), len(aas) * len(ds) * len(ps)):
+		colors.append((random.random(), random.random(), random.random()))
+
+	cid = 0
+	for a in sorted(aas):
+		for d in ds:
+			for p in ps:
+				x = np.arange(-5, 5, 0.001)
+				y = loggamma(x, a, d, p)
+				# plt.plot(x,num, linestyle='--', c=colors[cid])
+				plt.plot(x, y, label='a={},d={},p={}'.format(a, d, p), c=colors[cid])
+				# plt.plot(x,logfunc(x, a, r, mu), label='a={},r={},mu={}'.format(a, r, mu), c = colors[cid])
+				cid += 1
+	plt.legend()
+	plt.show()

### 2019-05-22 unimodal_extensions.py

@@ -1,0 +1,152 @@
+# -*- coding: utf-8 -*-
+
+import numpy as np
+import tensorflow as tf
+
+from tensorflow.keras.layers import Layer, Input, Activation, Dense, Conv2D, MaxPool2D, AveragePooling2D, Flatten, Lambda
+from tensorflow.keras.initializers import Ones, constant
+from tensorflow.keras import backend as K
+import numpy as np
+
+class TauLayer(Layer):
+    """Capa que contiene el parámetro tau a ser entrenado. Se divide la entrada por b + g(tau), donde b es
+    sesgo especificado y g es un función de transferencia.
+
+    :param tau: Valor de tau por el que dividr la entrada.
+    :param tau_learn: Booleano para especificar si aprender tau o mantener el valor recibido constante.
+    :param bias: Valor del sesgo.
+    :param nonlinearity: No linealidad para aplicar a tau.
+    """
+    def __init__(self, tau, bias=1.0, nonlinearity='linear', tau_learn='True',  **kwargs):
+        self.tau_ = constant(tau)
+        self.tau_learn_ = tau_learn
+        self.bias_ = constant(bias)
+        self.nonlinearity = nonlinearity
+        super(TauLayer, self).__init__(**kwargs)
+
+    def build(self, input_shape):
+        # Create a trainable weight variable for this layer.
+        self.tau = self.add_weight(name='tau', 
+                                   shape=(1,),
+                                   initializer=self.tau_,
+                                   trainable=self.tau_learn_)
+        # Create a trainable weight variable for this layer.
+        self.bias = self.add_weight(name='bias',
+                                    shape=(1,),
+                                    initializer=self.bias_)
+        super(TauLayer, self).build(input_shape)  # Be sure to call this at the end
+
+    def get_config(self):
+        pass
+
+    def call(self, x):
+        return x / (self.bias + Activation(self.nonlinearity)(self.tau))
+
+    def compute_output_shape(self, input_shape):
+        return input_shape
+
+
+def _add_pois(layer, num_classes, end_nonlinearity, tau, tau_mode, extra_depth=None):
+    """Añade el bloque final de la red que contiene la implementación de la distribución de Poisson.
+    
[…]

### 2019-05-22 experiment.py
Changed patience. (Before keras import change)

@@ -551,7 +551,7 @@ class Experiment:
 							initial_epoch=start_epoch,
 							steps_per_epoch=steps,
 							callbacks=[#tf.keras.callbacks.LearningRateScheduler(learning_rate_scheduler),
-									   tf.keras.callbacks.ReduceLROnPlateau(monitor='val_loss', factor=0.5, patience=15, mode='min', min_lr=1e-4, verbose=1),
+									   tf.keras.callbacks.ReduceLROnPlateau(monitor='val_loss', factor=0.5, patience=25, mode='min', min_lr=1e-4, verbose=1),
 									   tf.keras.callbacks.ModelCheckpoint(
 										   os.path.join(self.checkpoint_dir, self.model_file)),
 									   save_epoch_callback,

### 2019-05-22 plot_gamma.py

@@ -8,8 +8,8 @@ def loggamma(x, a, d, p):
 	return gammainc(d/p, (x/a)**p) / gamma(d/p)
 
 plots = [
-	{'as': np.round(np.arange(0.1, 1.5, 0.2), 2), 'ds': [1.0], 'ps': [0.1]},
-	{'as': [0.5], 'ds': np.round(np.arange(0.1, 1.5, 0.2), 2), 'ps': [0.1]},
+	{'as': np.round(np.arange(0.1, 1, 0.2), 2), 'ds': np.round(np.arange(0.1, 1, 0.2), 2), 'ps': np.round(np.arange(0.1, 1, 0.2), 2)},
+	# {'as': [0.5], 'ds': np.round(np.arange(0.1, 1.5, 0.2), 2), 'ps': [0.1]},
 ]
 
 for plot in plots:
@@ -25,7 +25,7 @@ for plot in plots:
 	for a in sorted(aas):
 		for d in ds:
 			for p in ps:
-				x = np.arange(-5, 5, 0.001)
+				x = np.arange(-2, 2, 0.001)
 				y = loggamma(x, a, d, p)
 				# plt.plot(x,num, linestyle='--', c=colors[cid])
 				plt.plot(x, y, label='a={},d={},p={}'.format(a, d, p), c=colors[cid])

### 2019-05-22 activations.py
Keras refactor

@@ -1,8 +1,9 @@
-import tensorflow as tf
 import math
+import keras
+from tensorflow import distributions, matrix_band_part, igamma, lgamma
+from keras import backend as K
 
-
-class SPP(tf.keras.layers.Activation):
+class SPP(keras.layers.Activation):
 	"""
 	Parametric softplus activation layer.
 	"""
@@ -20,12 +21,12 @@ def parametric_softplus(spp_alpha):
 	"""
 
 	def spp(x):
-		return tf.log(1 + tf.exp(x)) - spp_alpha
+		return K.log(1 + K.exp(x)) - spp_alpha
 
 	return spp
 
 
-class MPELU(tf.keras.layers.Layer):
+class MPELU(keras.layers.Layer):
 	def __init__(self, channel_wise=True, **kwargs):
 		super(MPELU, self).__init__(**kwargs)
 		self.channel_wise = channel_wise
@@ -36,19 +37,19 @@ class MPELU(tf.keras.layers.Layer):
 		if self.channel_wise:
 			shape = [int(input_shape[-1])]  # Number of channels
 
-		self.alpha = self.add_weight(name='alpha', shape=shape, dtype=tf.float32,
-									 initializer=tf.random_uniform_initializer(minval=-1, maxval=1, dtype=tf.float32),
+		self.alpha = self.add_weight(name='alpha', shape=shape, dtype=K.floatx(),
+									 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1, dtype=K.floatx()),
 									 trainable=True)
-		self.beta = self.add_weight(name='beta', shape=shape, dtype=tf.float32,
-									initializer=tf.random_uniform_initializer(minval=-1, maxval=1, dtype=tf.float32),
+		self.beta = self.add_weight(name='beta', shape=shape, dtype=K.floatx(),
+									initializer=keras.initializers.RandomUniform(minval=-1, maxval=1, dtype=K.floatx()),
 									trainable=True)
 
 		# Finish buildidng
 		super(MPELU, self).build(input_shape)
 
 	def call(self, inputs):
-		positive = tf.nn.relu(inputs)
-		negative = self.alpha * (tf.exp(-tf.nn.relu(-inputs) * self.beta) - 1)
+		positive = K.nn.relu(inputs)
+		negative = self.alpha * (K.exp(-K.nn.relu(-inputs) * self.beta) - 1)
 
 		return positive + negative
 
[…]

### 2019-05-22 callbacks.py

@@ -1,10 +1,10 @@
-import tensorflow as tf
+import keras
 import numpy as np
 from sklearn.metrics import confusion_matrix, accuracy_score
 from metrics import quadratic_weighted_kappa_cm, quadratic_weighted_kappa
 from losses import make_cost_matrix
 
-class ComputeMetricsCallback(tf.keras.callbacks.Callback):
+class ComputeMetricsCallback(keras.callbacks.Callback):
 	"""
 	Callback that computes train and/or validation metrics for a batch.
 	Computed metrics are: accuracy, loss and QWK.
@@ -24,7 +24,7 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 			self.classes.append(i)
 
 	def _compute_metrics(self, generator, num_batches, classes):
-		sess = tf.keras.backend.get_session()
+		sess = keras.backend.get_session()
 		conf_mat = None
 		mean_acc = 0
 		mean_loss = 0
@@ -111,7 +111,7 @@ class ComputeMetricsCallback(tf.keras.callbacks.Callback):
 
 
 
-class PrintWeightsCallback(tf.keras.callbacks.Callback):
+class PrintWeightsCallback(keras.callbacks.Callback):
 	def __init__(self):
 		pass
 

### 2019-05-22 dataset.py

@@ -4,7 +4,7 @@ import os
 import math
 import h5py
 from sklearn.model_selection import train_test_split
-import tensorflow as tf
+import keras
 import cv2
 from PIL import Image
 from sklearn.utils.class_weight import compute_class_weight
@@ -166,7 +166,7 @@ class Dataset:
 
 
 	def _load_cifar10(self, split):
-		(x_train, y_train), (x_test, y_test) = tf.keras.datasets.cifar10.load_data()
+		(x_train, y_train), (x_test, y_test) = keras.datasets.cifar10.load_data()
 
 		self._data = {}
 		self._data['x'] = []

### 2019-05-22 experiment.py

@@ -1,4 +1,4 @@
-import tensorflow as tf
+import keras
 import numpy as np
 import resnet
 from net_keras import Net
@@ -17,7 +17,7 @@ from dataset import Dataset
 from sklearn.metrics import confusion_matrix
 import math
 import gc
-
+from keras import backend as K
 
 class Experiment:
 	"""
@@ -404,7 +404,7 @@ class Experiment:
 			return
 
 		# Train data generator
-		train_datagen = tf.keras.preprocessing.image.ImageDataGenerator(
+		train_datagen = keras.preprocessing.image.ImageDataGenerator(
 			rescale=self.rescale_factor,
 			**self.augmentation
 		)
@@ -422,7 +422,7 @@ class Experiment:
 		# fill_mode='nearest',
 
 		# Validation data generator
-		val_datagen = tf.keras.preprocessing.image.ImageDataGenerator(rescale=self.rescale_factor, **eval_augmentation)
+		val_datagen = keras.preprocessing.image.ImageDataGenerator(rescale=self.rescale_factor, **eval_augmentation)
 
 		# Get database paths
 		train_path, val_path, _ = self.get_db_path(self.db)
@@ -502,7 +502,7 @@ class Experiment:
 				f.write('\n' + str(self.best_metric))
 
 
-		save_epoch_callback = tf.keras.callbacks.LambdaCallback(
+		save_epoch_callback = keras.callbacks.LambdaCallback(
 			on_epoch_end=save_epoch
 		)
 
@@ -523,7 +523,7 @@ class Experiment:
 			model.load_weights(os.path.join(self.checkpoint_dir, self.model_file))
 
 		# Create the cost matrix that will be used to compute qwk
-		cost_matrix = tf.constant(make_cost_matrix(num_classes), dtype=tf.float32)
+		cost_matrix = K.constant(make_cost_matrix(num_classes), dtype=K.floatx())
 
 		# Cross-entropy loss by default
 		loss = 'categorical_crossentropy'
@@ -538,7 +538,7 @@ class Experiment:
 
 		# Compile the keras model
 		model.compile(
-			optimizer=tf.keras.optimizers.Adam(lr=self.lr),  # tf.keras.optimizers.SGD(self.lr, 0.9),
+			optimizer=keras.optimizers.Adam(lr=self.lr),  # keras.optimizers.SGD(self.lr, 0.9),
 			loss=loss,
 			metrics=metrics
 		)
[…]

### 2019-05-22 experimentset.py

@@ -1,6 +1,7 @@
 import os
 import json
 import tensorflow as tf
+from keras import backend as K
 import gc
 from experiment import Experiment
 
@@ -116,7 +117,7 @@ class ExperimentSet:
 				if experiment.task != 'train': # 'test' or 'both'
 					experiment.evaluate()
 			# Clear session
-			tf.keras.backend.clear_session()
+			K.clear_session()
 
 			# Free memory
 			del experiment

### 2019-05-22 inception_resnet_v2.py

@@ -182,8 +182,8 @@ def inception_resnet_block(x, scale, block_type, block_idx, activation='relu'):
             x = activation(x)
     return x
 
-from tensorflow.keras import utils as keras_utils
-from tensorflow.keras import backend, layers, models
+from keras import utils as keras_utils
+from keras import backend, layers, models
 
 def InceptionResNetV2(include_top=True,
                       weights='imagenet',

### 2019-05-22 layers.py

@@ -1,6 +1,7 @@
-import tensorflow as tf
+import keras
+from keras import backend as K
 
-class GeometricLayer(tf.keras.layers.Layer):
+class GeometricLayer(keras.layers.Layer):
 	def __init__(self, **kwargs):
 		super(GeometricLayer, self).__init__(**kwargs)
 
@@ -10,4 +11,4 @@ class GeometricLayer(tf.keras.layers.Layer):
 		super(GeometricLayer, self).build(input_shape)
 
 	def call(self, inputs):
-		return tf.pow(1. - inputs, int(self.num_classes)) * inputs
+		return K.pow(1. - inputs, int(self.num_classes)) * inputs

### 2019-05-22 losses.py

@@ -1,6 +1,6 @@
-import tensorflow as tf
+import keras
 import numpy as np
-
+from keras import backend as K
 
 def make_cost_matrix(num_ratings):
 	"""
@@ -27,30 +27,30 @@ def qwk_loss(cost_matrix):
 	:return: QWK loss value.
 	"""
 	def _qwk_loss(true_prob, pred_prob):
-		targets = tf.argmax(true_prob, axis=1)
-		costs = tf.gather(cost_matrix, targets)
+		targets = K.argmax(true_prob, axis=1)
+		costs = K.gather(cost_matrix, targets)
 
 
-		# costs = tf.Print(costs, data=[costs], summarize=100, message='costs')
+		# costs = K.Print(costs, data=[costs], summarize=100, message='costs')
 
-#		pred_cls = tf.argmax(pred_prob, axis=1)
+#		pred_cls = K.argmax(pred_prob, axis=1)
 
-# 		conf_mat = tf.confusion_matrix(targets, pred_cls)
+# 		conf_mat = K.confusion_matrix(targets, pred_cls)
 
 		numerator = costs * pred_prob
-		numerator = tf.reduce_sum(numerator)
+		numerator = K.sum(numerator)
 
-		sum_prob = tf.reduce_sum(pred_prob, axis=0)
-		n = tf.reduce_sum(true_prob, axis=0)
+		sum_prob = K.sum(pred_prob, axis=0)
+		n = K.sum(true_prob, axis=0)
 
-		a = tf.reshape(tf.matmul(cost_matrix, tf.reshape(sum_prob, shape=[-1, 1])), shape=[-1])
-		b = tf.reshape(n / tf.reduce_sum(n), shape=[-1])
+		a = K.reshape(K.dot(cost_matrix, K.reshape(sum_prob, shape=[-1, 1])), shape=[-1])
+		b = K.reshape(n / K.sum(n), shape=[-1])
 
 		epsilon = 10e-9
 
 		denominator = a * b
-		denominator = tf.reduce_sum(denominator) + epsilon
+		denominator = K.sum(denominator) + epsilon
 
-		return numerator / denominator # + tf.cast(tf.reduce_sum(conf_mat) * 0, dtype=tf.float32)
+		return numerator / denominator # + K.cast(K.sum(conf_mat) * 0, dtype=K.floatx())
 
 	return _qwk_loss

### 2019-05-22 main_experiment.py

@@ -2,6 +2,7 @@ import click
 from experiment import Experiment
 from experimentset import ExperimentSet
 import tensorflow as tf
+from keras import backend as K
 
 @click.group()
 def cli():
@@ -25,9 +26,9 @@ def cli():
 # @click.option('--rep', '-r', default=1, help=u'Repetitions for this execution.')
 # @click.option('--dropout', '-o', default=0.0, help=u'Drop rate.')
 # def train(db, net_type, batch_size, epochs, checkpoint_dir, loss, activation, final_activation, prob_layer, spp_alpha, lr, momentum, rep, dropout):
-# 	config = tf.ConfigProto()
+# 	config = K.ConfigProto()
 # 	config.gpu_options.allow_growth = True
-# 	tf.keras.backend.set_session(tf.Session(config=config))
+# 	K.keras.backend.set_session(K.Session(config=config))
 # 	for execution in range(1, rep + 1):
 # 		experiment = Experiment('', db, net_type, batch_size, epochs, checkpoint_dir, loss, activation, final_activation, prob_layer, spp_alpha, lr, momentum, dropout)
 # 		experiment.set_auto_name()
@@ -40,7 +41,7 @@ def cli():
 def experiment(file, gpu):
 	config = tf.ConfigProto(allow_soft_placement=True)
 	config.gpu_options.allow_growth = True
-	tf.keras.backend.set_session(tf.Session(config=config))
+	K.set_session(tf.Session(config=config))
 	experimentSet = ExperimentSet()
 	experimentSet.load_from_file(file)
 	experimentSet.run_all(gpu_number=gpu)

### 2019-05-22 metrics.py

@@ -1,5 +1,7 @@
 import tensorflow as tf
+import keras
 import numpy as np
+from keras import backend as K
 from sklearn.metrics import confusion_matrix
 
 def quadratic_weighted_kappa(num_classes, cost_matrix):
@@ -16,25 +18,25 @@ def quadratic_weighted_kappa(num_classes, cost_matrix):
 		:param y_pred: predicted labels.
 		:return: qwk value.
 		"""
-		y_pred = tf.argmax(y_pred, 1, output_type=tf.int32)
-		y_true = tf.argmax(y_true, 1, output_type=tf.int32)
-		conf_mat = tf.confusion_matrix(y_true, y_pred, num_classes=num_classes, dtype=tf.float32)
+		y_pred = K.argmax(y_pred, 1, output_type=K.int32)
+		y_true = K.argmax(y_true, 1, output_type=K.int32)
+		conf_mat = K.confusion_matrix(y_true, y_pred, num_classes=num_classes, dtype=K.floatx())
 
 		return quadratic_weighted_kappa_cm(conf_mat, num_classes, cost_matrix)
 
-		# hist_y_pred = tf.reshape(
-		# 	tf.bincount(y_pred, minlength=num_classes, maxlength=num_classes, dtype=tf.float32),
+		# hist_y_pred = K.reshape(
+		# 	K.bincount(y_pred, minlength=num_classes, maxlength=num_classes, dtype=K.floatx()),
 		# 	shape=[num_classes, 1])
-		# hist_y_true = tf.reshape(
-		# 	tf.bincount(y_true, minlength=num_classes, maxlength=num_classes, dtype=tf.float32),
+		# hist_y_true = K.reshape(
+		# 	K.bincount(y_true, minlength=num_classes, maxlength=num_classes, dtype=K.floatx()),
 		# 	shape=[1, num_classes])
 		#
-		# num_scored_items = tf.shape(y_pred)[0]
+		# num_scored_items = K.shape(y_pred)[0]
 		#
-		# expected_count = tf.matmul(hist_y_pred, hist_y_true) / tf.cast(num_scored_items, dtype=tf.float32)
+		# expected_count = K.matmul(hist_y_pred, hist_y_true) / K.cast(num_scored_items, dtype=K.floatx())
 		#
-		# numerator = tf.reduce_sum(cost_matrix * conf_mat)
[…]

### 2019-05-22 net_keras.py

@@ -1,5 +1,5 @@
-import tensorflow as tf
-from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, NNPOM, RReLu, PELU, SlopedReLU, PTELU
+import keras
+from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, CLM, RReLu, PELU, SlopedReLU, PTELU
 from layers import GeometricLayer
 from resnet import Resnet_2x4
 
@@ -21,80 +21,80 @@ class Net:
 		self.dropout = dropout
 
 		# Add new activation function
-		tf.keras.utils.get_custom_objects().update({'spp': SPP(parametric_softplus(spp_alpha))})
+		keras.utils.get_custom_objects().update({'spp': SPP(parametric_softplus(spp_alpha))})
 
 	def vgg19(self):
-		model = tf.keras.models.Sequential([
+		model = keras.models.Sequential([
 			# Block 1
-			tf.keras.layers.Conv2D(64, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same',
+			keras.layers.Conv2D(64, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same',
 								   input_shape=(self.size, self.size, self.num_channels), data_format='channels_last'),
 			self.__get_activation(),
-			tf.keras.layers.BatchNormalization(),
-			tf.keras.layers.Conv2D(64, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
+			keras.layers.BatchNormalization(),
+			keras.layers.Conv2D(64, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
 			self.__get_activation(),
-			tf.keras.layers.BatchNormalization(),
-			tf.keras.layers.MaxPooling2D(),
+			keras.layers.BatchNormalization(),
+			keras.layers.MaxPooling2D(),
 
 			# Block 2
-			tf.keras.layers.Conv2D(128, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
+			keras.layers.Conv2D(128, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
 			self.__get_activation(),
-			tf.keras.layers.BatchNormalization(),
[…]

### 2019-05-22 resnet.py

@@ -1,10 +1,10 @@
 # -*- coding: utf-8 -*-
 
-from tensorflow.keras.regularizers import l2
+from keras.regularizers import l2
 
-from tensorflow.keras.models import Model, Sequential
-from tensorflow.keras.initializers import Constant, he_normal
-from tensorflow.keras.layers import Input, Conv2D, MaxPooling2D, AveragePooling2D, \
+from keras.models import Model, Sequential
+from keras.initializers import Constant, he_normal
+from keras.layers import Input, Conv2D, MaxPooling2D, AveragePooling2D, \
 	Dense, Flatten, Activation, ZeroPadding2D, \
 	Add, Activation, BatchNormalization, GlobalAveragePooling2D
 

### 2019-05-22 tools.py

@@ -6,12 +6,13 @@ import pickle
 import os
 import prettytable
 import h5py
-import tensorflow as tf
+import keras
 import cv2
 from PIL import Image
 from sklearn.model_selection import train_test_split
 from sklearn.preprocessing import StandardScaler
 from shutil import copy
+from keras import backend as K
 
 evaluation_file = 'evaluation.pickle'
 
@@ -218,12 +219,12 @@ def create_h5_dataset(path, file):
 	f.create_dataset('y', data = y, compression = 'gzip', compression_opts = 9)
 
 def create_h5_cifar10(file, shape):
-	(x_train, y_train), (x_test, y_test) = tf.keras.datasets.cifar10.load_data()
-	train_rs_op = tf.image.resize_images(x_train, shape, method=tf.image.ResizeMethod.BILINEAR)
-	test_rs_op = tf.image.resize_images(x_test, shape, method=tf.image.ResizeMethod.BILINEAR)
+	(x_train, y_train), (x_test, y_test) = keras.datasets.cifar10.load_data()
+	train_rs_op = K.image.resize_images(x_train, shape, method=K.image.ResizeMethod.BILINEAR)
+	test_rs_op = K.image.resize_images(x_test, shape, method=K.image.ResizeMethod.BILINEAR)
 	val_perc = 0.2
 
-	with tf.Session() as sess:
+	with K.Session() as sess:
 		print('Resizing images to {}'.format(shape))
 		train_rs, test_rs = sess.run([train_rs_op, test_rs_op])
 

### 2019-05-22 unimodal_extensions.py

@@ -1,11 +1,10 @@
 # -*- coding: utf-8 -*-
 
 import numpy as np
-import tensorflow as tf
 
-from tensorflow.keras.layers import Layer, Input, Activation, Dense, Conv2D, MaxPool2D, AveragePooling2D, Flatten, Lambda
-from tensorflow.keras.initializers import Ones, constant
-from tensorflow.keras import backend as K
+from keras.layers import Layer, Input, Activation, Dense, Conv2D, MaxPool2D, AveragePooling2D, Flatten, Lambda
+from keras.initializers import Ones, constant
+from keras import backend as K
 import numpy as np
 
 class TauLayer(Layer):

### 2019-05-23 paper/ieee.tex
Paper, tanh

@@
 These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
-Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that comes in the form of multiple arrays.
+Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays.
 CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
-On image classification tasks, each colour channel is represented by a 2D array.
-In this case, convolutional layers extract the main features from the pixels of the images and, after that, a fully connected layer classify every sample based on its extracted features.
+For images, each colour channel is represented by a 2D array, and convolutional layers extract the main features from the pixels, and, after that, a fully connected layer classify every sample based on its extracted features.
 At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks.
-These outputs are compared against the correct values.
-
-	Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of classes.
-This kind of problem can be treated as a nominal classification problem, but this discards the ordinal information.
+However, the softmax may not be the best option depending on the problem considered.
+
+	Ordinal classification problems are those classification tasks where labels are ordered, and there are different inter-classes importances for each pair of categories.
+This kind of problem can be treated as nominal classification, but this discards the ordinal information.
 A better approach is to use specific methods that take the ordinality into account to improve the performance of the classification model.
@@
 It belongs to a wider family of models called Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
-CLMs are inspired in the concept of a latent variable that is projected in a 1-dimensional space and a set of thresholds that divides that space into the different ordinal levels.
-This kind of models uses a link function which can be of different types, although the most common link function is the \texttt{logit}, which is used in POM.
-We explore different alternatives, as explained in depth in Section \ref{sect:ordinalproblem}.
-
-	Ordinal models can also be applied to deep learning models.
+CLMs are inspired in the concept of a latent variable that is projected into a 1-dimensional space and a set of thresholds that divides the projection into the different ordinal levels.
+A link function needs to be specified, which can be of different types, although the most common option is the \texttt{logit}, which is used in POM.
+In this paper, we explore different existing alternatives, as explained in depth in Section \ref{sect:ordinalproblem}.
+
+	In this paper, we propose the use of CLMs for deriving deep learning ordinal classifiers.
 In the case of CNNs, the model projection used by the threshold model can be obtained from the last layer of the network.
-Given that we work with a 1-dimensional space, the last layer has only one neuron (projection of the pattern), and its value is used to classify the sample into the corresponding class according to the thresholds.
+Given that we work with a 1-dimensional space, the last layer would have only one neuron (projection of the pattern), and its value could be used to classify the sample into the corresponding class according to the thresholds.
 Some previous works have used the \texttt{logit} in shallow neural networks~\cite{gutierrez2016ordinal}, but this strategy has not been considered for deep learning, and alternative link functions have not been evaluated.
@@
 
-	In this paper, we propose the use of CLMs for deriving deep learning ordinal classifiers.
 	An experimental study evaluating the three most common link functions is performed.
@@
 We contrast the results obtained with a statistical analysis to provide more robust conclusions.
-An ANOVA III test \cite{miller1997beyond} followed by a posthoc Tukey's test \cite{tukey1949comparing} is performed over $5$ runs of the experiments, because of the demands of computational time required to run a higher number of executions.
+An ANOVA III test \cite{miller1997beyond}, followed by a posthoc Tukey's test \cite{tukey1949comparing}, is performed over $5$ runs of the experiments, because of the demands of computational time required to run a higher number of executions.
 The experiments are run using two different ordinal datasets: Diabetic Retinopathy~\cite{de2018weighted}, which contains high-resolution fundus images related with diabetes disease, and Adience~\cite{beckham2017unimodal}, which includes human faces images associated with an age range.
 
-	This paper is organized as follows: in Section~\ref{sect:relatedwork}, we take a look at previous works related to this paper.
-Section~\ref{sect:ordinalproblem} present a formal description of an ordinal problem and CLMs.
-In Section~\ref{sect:experiments}, we describe the model, the experiments and the datasets used, while, in Section~\ref{sect:results}, we present the results obtained and the statistical analysis.
+	The paper is organized as follows: in Section~\ref{sect:relatedwork}, we analyse previous related works.
+Section~\ref{sect:modelProposal} presents a formal description of the proposal in this paper, which combines a CLM with an ordinal loss function.
+In Section~\ref{sect:experiments}, we describe the experiments and the datasets used, while, in Section~\ref{sect:results}, we present the results obtained and the statistical analysis.
 Finally, Section~\ref{sect:conclusions} exposes the conclusions of this work.
@@
 	There are many works related to the application and development of CNN models \cite{liu2017deep}, but few works focus on ordinal classification problems.
-The approaches proposed on those works are mainly related to
-	solving the ordinal problem as multiple binary sub-problems, using an ordinal loss function, solving the problem as a multi-class problem with constraints or simply using an ordinal evaluation metric.
-These works are described below:
-
-	\vspace{0.2cm}
-	$\bullet$ \textit{Solving the ordinal problem as multiple binary sub-problems.}
+The existing deep ordinal approaches are mainly based on simply using an ordinal evaluation metric, on solving the ordinal problem as multiple binary sub-problems, on using an ordinal loss functions or on constraining the probability distribution of the output layer.
+These works are described in the following subsections.
+
+	\subsection{Simply using an ordinal evaluation metric.}
+
+	%\textbf{(Métrica ordinal (MAE))}
+	M.
+ALALI et al.
+\cite{alali2018multi} proposed a complex CNN architecture for solving Twitter Sentiment Classification as an ordinal problem.
+They checked that using average pooling preserves significant features that provide more expressiveness to ordinal scale.
+They didn't propose any method to include the ordinal information into the classifier, but they tried to find the best CNN model architecture based on an ordinal metric.
+
+	\subsection{Solving the ordinal problem as multiple binary sub-problems}
 
@@
 Niu et al.
-\cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using convolutional neural networks.
+\cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using CNNs.
 They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively solve these classification sub-problems, taking into account the correlation between them.
@@
 \cite{liu2017deep} proposed a new approach which transforms the ordinal regression problem to binary classification sub-problems and use triplets with instances from different categories to train deep neural networks.
-In this way, high-level features describing the ordinal relationship are extracted automatically.
+In this way, high-level features describing the ordinal relationships are extracted automatically.
 Given that triplets must be generated, this approach is only recommended for small datasets.
@@
 
-	\vspace{0.2cm}
-	$\bullet$ \textit{Using an ordinal loss function.}
+	In general, all these approaches increment the number of parameters to adjust, as several binary classifiers are simultaneously learnt.
+
+	\subsection{Using an ordinal loss function}
 
@@
 	J.
-de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the QWK metric as loss function for the optimization algorithm.
-They compared this cost function against the traditional log-loss function across three different databases, including the Diabetic Retinopathy database as the most complex one.
+de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the quadratic weighted kappa (QWK) metric as loss function for the optimization algorithm.
+They compared this cost function against the traditional log-loss function using three different datasets, including the Diabetic Retinopathy database as the most complex one.
 They proved that their function could improve the results as it reduces overfitting and training time.
 Also, they checked the importance of hyper-parameter tuning.
-
-%		\textbf{(Función de coste ordinal y distribución unimodal.)}
-	C.
-Beckham and C.
-Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
-The parameters of these distributions were learnt by using a deep neural network.
-They evaluated this approach on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.
-They also proposed a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
 
@@
 
-	\vspace{0.2cm}
-	$\bullet$ \textit{Solving the problem as a multi-class problem with constraints.}
-
 %		\textbf{(Multi-clase con restricciones)}
@@
 
-	\vspace{0.2cm}
-	$\bullet$ \textit{Simply using an ordinal evaluation metric.}
-
-%		\textbf{(Métrica ordinal (MAE))}
-	M.
-ALALI et al.
-\cite{alali2018multi} proposed a complex CNN architecture for solving Twitter Sentiment Classification as an ordinal problem.
-They checked that using average pooling preserves significant features that provide more expressiveness to ordinal scale.
-They didn't propose any method to include the ordinal information into the classifier but they tried to find the best CNN model architecture based on an ordinal metric.
-
-	Adience dataset has been used in other works for human age estimation but most of them solved the problem as a multi-class problem instead of using the ordinal relation between classes.
-E.
-Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks.
-J.-C.
-Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep CNNs, while G.
-Levi \cite{levi2015age} presented another convolutional network model for age estimation.
-
-	However, none of the works mentioned have combined a CNN model with an unimodal probability distribution, without dividing the problem in multiple binary sub-problems and using a continuous loss function based on one of the most common metrics for ordinal classification (Weighted Kappa).
-This is the approach that will be proposed in this work for solving two separate ordinal problems.
+	Although the use of these losses introduces the ordinality in model learning, the nature of the models remain nominal.
+
+	\subsection{Unimodal probability distributions}
+
+	%\textbf{(Función de coste ordinal y distribución unimodal.)}
+	C.
+Beckham and C.
+Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
+The parameters of these distributions were learnt by using a deep neural network.
+They evaluated this approach on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results.
+They also included a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.
+
+	This approach is the one most related to the CLMs considered in this paper.
+However, CLMs indirectly model a latent space together with the set of threshold separating the ordered classes, which provides a more flexible and interpretable approach to deep ordinal classification.
 
@@
 
-	\section{Cumulative Link Models (CLM)}
+	\section{Model proposal}
+	\label{sect:modelProposal}
+
+	Based on the previous analysis of the state-of-the-art, our proposal is to combine a flexible threshold model in the output layer (different forms of a CLM) with an ordinal loss function, in order to better introduce ordinal constraints during learning.
+
+	\subsection{Cumulative Link Model (CLM)}
 	\label{sect:ordinalproblem}
 	An ordinal classification problem consists in predicting the label $y$ of an input vector $\mathbf{x}$, where $\mathbf{x} \in \mathcal{X} \subseteq \mathds{R}^K$ and $y \in \mathcal{Y}~=~\{\mathcal{C}_1, \mathcal{C}_2, ..., \mathcal{C}_Q\}$, i.e.
-$\mathbf{x}$ is in a K-dimensional input space, and $y$ is in a label space of $Q$ different labels.
-The objective of the ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ samples, $D = \{(\mathbf{x}_i, y_i), i = 1, ..., N\}$.
+$\mathbf{x}$ is in a $K$-dimensional input space, and $y$ is in a label space of $Q$ different labels.
+The objective in an ordinal problem is to find a function $r : \mathcal{X} \rightarrow \mathcal{Y}$ to predict the labels or categories of new patterns, given a training set of $N$ samples, $D = \{(\mathbf{x}_i, y_i), i = 1, ..., N\}$.
 Labels have a natural ordering in ordinal problems: $\mathcal{C}_1 \prec \mathcal{C}_2 \prec ...
@@
 	The Proportional Odds Model (POM) arises from a statistical background and is one of the first models designed explicitly for ordinal regression~\cite{mccullagh1980regression}.
-It dated back to 1980 and is a member of a wider family of models recognised as Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
+It dated back to 1980 and is a member of a wider family of models lately recognised as Cumulative Link Models (CLMs)~\cite{agresti2010analysis}.
 CLMs predict probabilities of groups of contiguous categories, taking the ordinal scale into account.
@@
 The constraints $b_1 \le b_2 \le ...
-\le b_{Q-1}$ ensures that $P(y \preceq \mathcal{C}_q | \mathbf{x})$ increases with $q$ \cite{mccullagh1980regression}.
+\le b_{Q-1}$ ensure that $P(y \preceq \mathcal{C}_q | \mathbf{x})$ increases with $q$ \cite{mccullagh1980regression}.
 
@@
 
-		\item The \textit{complementary log-log} (\texttt{clog-log}) takes a response that is restricted to the $(0,1)$ interval and converts it into something in the $(-\infty, +\infty)$ interval (like \texttt{logit} and \texttt{probit} transformations).
+		\item The \texttt{clog-log} takes a response that is restricted to the $(0,1)$ interval and converts it into a value in the $(-\infty, +\infty)$ interval (like \texttt{logit} and \texttt{probit} transformations).
 The \texttt{clog-log} expression is:
@@
 		\begin{align}
-		\nonumber \text{probit}(p) & = \Phi^{-1}(p) = b_q - f(\mathbf{x}),\\
-		\nonumber -\text{probit}(1-p) &= \Phi^{-1}(1-p) = -b_q + f(\mathbf{x}),
+		\nonumber \Phi^{-1}(p) & = \Phi^{-1}(p) = b_q - f(\mathbf{x}),\\
+		\nonumber -\Phi^{-1}(1-p) &= \Phi^{-1}(1-p) = -b_q + f(\mathbf{x}),
 		\end{align}
@@
 	Unlike \texttt{logit} and \texttt{probit}, the \texttt{clog-log} link is asymmetrical.
-It is frequently used when the probability of an event is very small or very large.
-When the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate, while \texttt{clog-log} can lead to better results.
-
-	This order is achieved by defining the first threshold and calculating the rest of thresholds from the first in the following form:	
-	\begin{equation}
-	\nonumber
-	b_n = b_1 + \sum_{i=1}^{n-1} \alpha_i^2, \quad n = 2, ..., N,
-	\end{equation}
-	where $b_1$ and $\alpha_i$ are learnable parameters, and $N$ is the number of classes.
-
-	\section{Weighted Kappa as loss function}
+In this way, when the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate, while \texttt{clog-log} can lead to better results.
+
+	In this paper, the probabilistic structure of CLMs is proposed as a link function for deep convolutional neural networks.
+This can be achieved by defining a new type of output layer alternative to the standard softmax layer.
+In this way, the proposed output layer will transform the one-dimensional projection, previously denoted as $f(\mathbf{x})$, into a set of probabilities.
+$f(\mathbf{x})$ is estimated from a nonlinear transformation of the set of features learnt by the previous layers, $l(\mathbf{x})=f(\mathbf{x})$, where $\mathbf{x}$ is the pattern being evaluated and $l(\mathbf{x})$ is a latent representation of the pattern given by the output of a single neuron.
+In order to apply unconstrained optimizers while ensuring $b_1 \le b_2 \le ...
+\le b_{Q-1}$, we can redefine the thresholds.
+All of them can be derived from the first one in the following form:
+	\begin{equation}
+	b_q = b_1 + \sum_{q=1}^{q-1} \alpha_q^2, \quad q = 2, ..., Q,
+	\end{equation}
+	where $b_1$ and $\alpha_q$ are the learnable parameters, and $Q$ is the number of classes.
+
+	\subsection{Continuous Quadratic Weighted Kappa (QWK) loss function}
 	\label{sect:wk}
+
+	In order to increase the performance of the deep ordinal model, the CLM structure in the output layer is combined with the continuous version of the QWK loss \cite{de2018weighted} function.
 The Kappa index is a well-known metric that measures the agreement between two different raters.
 The Weighted Kappa (WK)~\cite{ben2008comparison} is based on the Kappa index and adds different weights to the different types of disagreements based on a weight matrix.
-It is useful to evaluate the performance in ordinal problems as it gives a higher weight to the errors that are further from the correct class.
+It is useful to evaluate the performance in ordinal problems, as it gives a higher weight to the errors that are further from the correct class.
 This metric is defined as follows:
 	\begin{equation}
-	\nonumber
+	\label{eq:qwk}
 	\text{QWK} = 1 - \frac{\sum\limits^N_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits^N_{i,j} \omega_{i,j} E_{i,j}},
 	\end{equation}
-	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i\bullet} O_{\bullet j}}{N}$, $O_{i\bullet}$ is the sum of the $i\text{-th}$ row and $O_{\bullet j}$ is the sum of the $j\text{-th}$ column.
-
-	The WK defined above cannot be used as a loss function for the optimization algorithm as it is not continuous. However, it can be redefined in terms of probabilities of the predictions:
+	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, $\omega_{i,j} \in [0,1]$), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i\bullet} O_{\bullet j}}{N}$, $O_{i\bullet}$ is the sum of the $i\text{-th}$ row and $O_{\bullet j}$ is the sum of the $j\text{-th}$ column.
+
+	The WK defined above cannot be used as a loss function for the optimization algorithm as it is not continuous.
+However, it has been previously redefined \cite{de2018weighted} in terms of probabilities of the predictions:
 	\begin{equation}
@@
 	\end{equation}
-	where $\text{QWK}_c \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ (estimated using the CLM structure), and $\omega_{i,j}$ are the elements of the penalization matrix.
-In this case, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, where $\omega_{i,j} \in [0,1]$.
-
+	where $\text{QWK}_c \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ (estimated using the CLM structure), and $\omega_{i,j}$ are the elements of the penalization matrix ($\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$).
 This loss function can be minimized using a gradient descent based algorithm.
@@
 	In order to evaluate the different models, we make use of two ordinal datasets:
-
-	\begin{itemize}
-		\item \textit{Diabetic Retinopathy (DR)}\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data}.
-DR is a dataset consisting of extremely high-resolution fundus image data.
+    \subsubsection{Diabetic Retinopathy (DR)}
+    DR\footnote{https://www.kaggle.com/c/diabetic-retinopathy-detection/data} is a dataset consisting of extremely high-resolution fundus image data.
 The training set consists of $17563$ pairs of images (where a  pair includes a left and right eye image corresponding to a patient).
@@
 These images are taken in variable conditions: by different cameras,  conditions of illumination and resolutions.
-These images come from the EyePACS dataset that was used in the DR detection competition hosted on the Kaggle platform.
-Also, this dataset has been used in different works~\cite{de2018weighted,nebot2016diabetic}, where an ordinal QWK cost function was considered in \cite{de2018weighted} to achieve better performance.
+They come from the EyePACS dataset that was used in the DR detection competition hosted on the Kaggle platform.
+Also, this dataset has been used in different works~\cite{de2018weighted,nebot2016diabetic}, where the $\text{QWK}_c$ cost function was considered in \cite{de2018weighted} to achieve better performance.
 A validation set is set aside, consisting of $10\%$ of the patients in the training set.
@@
 
-		\item \textit{Adience}\footnote{http://www.openu.ac.il/home/hassner/Adience/data.html}.
-This dataset consists of $26580$ faces belonging to $2284$ subjects.
+	\subsubsection{Adience}
+	Adience\footnote{http://www.openu.ac.il/home/hassner/Adience/data.html} dataset consists of $26580$ faces belonging to $2284$ subjects.
 We use the form of the dataset where faces have been pre-cropped and aligned.
@@
 Some images of this dataset are shown in Figure \ref{fig:AdienceExamples}.
+Adience dataset has been used in other works for human age estimation but most of them solved the problem as a multi-class problem instead of using the ordinal relation between classes.
+E.
+Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks.
+J.-C.
+Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep CNNs.
+G.
+Levi \cite{levi2015age} presented another convolutional network model for age estimation, while Beckham \cite{beckham2017unimodal} proposed a straightforward method to constrain discrete ordinal probability distributions to be unimodal.
 
@@
 		\end{figure}
-	\end{itemize}
 
@@
 	CNNs have been used for both datasets.
-The different architectures of CNN used in these experiments are presented in Tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
+The different architectures of CNNs used in these experiments are presented in Tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
 The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
@@
 
-	The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used as the activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradients problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
+	The Exponential Linear Unit (ELU)~\cite{clevert2015fast} has been used as the activation function for all the convolutional and dense layers, instead of the ReLU~\cite{nair2010rectified} function, as it mitigates the effects of the vanishing gradient problem \cite{bengio1994learning,pascanu2013difficulty} via the identity for positive values.
 Also, ELUs lead to faster training and better generalization performance than ReLU and Leaky ReLU (LReLU)~\cite{maas2013rectifier} functions on networks with more than five layers.
@@
 
-	At the output of the network, the CLM is used.
-Also, the learnable parameter $\tau$ has been used to rescale the projections used by the CLM to make it more stable and guarantee the convergence in most cases.
+	At the output of the network, the CLM is used (see Section \ref{sect:ordinalproblem}).
+Also, a learnable parameter $\tau$ has been used to rescale the projections used by the CLM to make it more stable and guarantee the convergence in most cases.
 The following expression describes the transformation applied to these projections:
@@
 		\nonumber
-		f'(x) = \frac{f(x)}{\tau}
-	\end{equation}
-%	where $\tau$ is the learnable parameter that is adjusted by the optimization algorithm.
+		f(\mathbf{x}) = \frac{l(\mathbf{x})}{\tau}.
+	\end{equation}
+	where $\tau$ is optimized as a free parameter.
 
@@
 	\label{sect:settings}
-	The model is optimized using a batch based first-order optimization algorithm called Adam~\cite{kingma2014adam}.
+	Weights are adjusted using a batch based first-order optimization algorithm called Adam~\cite{kingma2014adam}.
 We study different initial learning rates ($\eta$) in order to find the optimal one for each problem.
@@
 Horizontal flipping is the only transformation applied to the Adience dataset.
-These transformations are applied every time a new batch is loaded, and the parameters of each one are randomly chosen from a defined range ($[0.8, 1.2]$ for zoom, $[0.5, 1.5]$ for brightness and $[0, 90]$ degrees for rotation), providing a new set of transformed images for each batch.
+These transformations are applied every time a new batch is loaded, and the parameters of each one are randomly chosen from a defined range ($[0.8, 1.2]$ for zooming, $[0.5, 1.5]$ for brightness and $[0, 90]$ degrees for rotation), providing a new set of transformed images for each batch.
 This technique reduces the overfitting risk and provides an important performance boost as we always work with different but similar images \cite{krizhevsky2012imagenet}.
@@
 
-	The model is evaluated using the Weighted Kappa metric described in Section \ref{sect:wk} with a quadratic penalization matrix (Quadratic Weighted Kappa, QWK).
 %	\textcolor{red}{Es importante distinguir entre función de coste (usada para el ajuste de los pesos en el algoritmo de entrenamiento) y función de evaluación (usada para evaluar los modelos, en test o validación).
@@
 
-	Also, other evaluation metrics are used to ease the comparison with other works:
+	The models are mainly evaluated using the QWK metric defined in Eq. \eqref{eq:qwk}. Also, other evaluation metrics are used to ease the comparison with alternative works:
 	\begin{itemize}
@@
 		\item Accuracy-based metrics.
-Correct Classification Rate (CCR) or standard accuracy is the most common metric for classification tasks and shows the percentage of correctly classified samples, Top-2 CCR \cite{beckham2017unimodal} and Top-3 CCR \cite{beckham2017unimodal} are based on CCR but they take a prediction as correct when the real class is between the two (or three) predictions with the highest probability.
-
-		\item 1-off accuracy \cite{eidinger2014age,chen2016cascaded,levi2015age} marks the prediction as correct when the correct class is at one category of distance from the predicted one.
-It can be considered as an ordinal metric as it calculates the distance between the real class and the predicted one based on the ordinal information of the problem.
+Correct Classification Rate (CCR) or standard accuracy is the most common metric for classification tasks and shows the percentage of correctly classified samples.
+We also include Top-2 CCR \cite{beckham2017unimodal} and Top-3 CCR \cite{beckham2017unimodal}, which are similar to CCR, but they take a prediction as correct when the real class is between the two or three classes, respectively, with the highest probability.
+
+		\item 1-off accuracy \cite{eidinger2014age,chen2016cascaded,levi2015age} marks the prediction as correct when the correct class is at one category of distance (in the ordinal scale) from the predicted one.
 	\end{itemize}
-
-	Experiments are run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the CLM).
-The results of these experiments are analysed in Section \ref{sect:NominalComparison}.
+	QWK, MAE and 1-off accuracy are ordinal evaluation metrics, while MS, CCR, Top-2 CCR and Top-3 CCR do not take the order of categories into consideration.
 
 	\subsection{Factors}
-	Three different factors are considered: learning rate, batch size and link function for the final output layer:
+	In our study, three different factors are considered:
 	\begin{itemize}
 		\item \textit{Learning rate} (LR, $\eta$).
-Learning rate is one of the most critical hyper-parameters to tune for training deep neural networks.
+LR is one of the most critical hyper-parameters to tune for training deep neural networks.
 Optimal learning rate can vary depending on the dataset and the CNN architecture.
 Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical,senior2013empirical}.
-In this work, we consider three different values for the parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
+In this work, we consider three different values for the initial value of this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
 		\item \textit{Batch size} (BS).
@@
 It can affect the training time and the model performance.
-In this paper, we try three separate batch sizes for each dataset.
+In this paper, we try three different batch sizes for each dataset.
 For the DR dataset, we use $5$, $10$ and $15$, while, for Adience, $64$, $128$ and $256$ images are used.
-We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expanded the range on both sides.
-		\item \textit{Link function} (LF). Different link functions are used for the CLM at the last layer output: \texttt{logit}, \texttt{probit} and complementary log-log.
+We took the batch sizes that were used in \cite{de2018weighted} and \cite{beckham2017unimodal} as a reference, and we expand the range on both sides.
+		\item \textit{Link function} (LF).
+Different link functions are used for the CLM at the last layer output: \texttt{logit}, \texttt{probit} and complementary log-log (see Section \ref{sect:ordinalproblem}).
 	\end{itemize}
@@
 	\label{sect:results}
-	In this section, we present the results of the experiments.
+	In this Section, we present the results of the experiments.
+First, in Sections \ref{sect:dr}, \ref{sect:adience}, and \ref{sect:statisticalanalysis}, we perform the study for adjusting the value of the different parameters.
+Then, Section \ref{sect:NominalComparison} compares the results against the state of the art.
+
 	For each dataset, we show a table with the detailed results of the experiments performed for training the model with each combination of parameters.
@@
 
-	The best mean QWK value was obtained with the complementary log-log link function using a batch size of 10 and a learning rate of $10^{-3}$.
-However, the best CCR value was obtained with a batch size of 15, the \texttt{logit} link and a learning rate of $10^{-4}$.
+	The best mean QWK value was obtained with the \texttt{clog-log} link function using a BS of 10 and a LR of $10^{-3}$.
+However, the best CCR value was obtained with a BS of 15, the \texttt{logit} link and a LR of $10^{-4}$.
 The optimal configuration depends on the metric we are analysing.
@@
 
-	The best mean QWK value was obtained with the \texttt{logit} link function using a batch size of 64 and a learning rate of $10^{-4}$.
+	The best mean QWK value was obtained with the \texttt{logit} link function using a BS of 64 and a LR of $10^{-4}$.
 Also, this configuration obtained the best score for Top-2, Top-3 and 1-off accuracy, and the second best for MS, MAE and CCR.
@@
 	In this subsection, a statistical analysis will be performed in order to obtain conclusions from the results.
-The significance and relative importance of the parameters concerning the results obtained, as well as suitable values for each of them, were obtained using an ANalysis Of the VAriance (ANOVA).
+The significance and relative importance of the parameters concerning the results obtained, as well as the most suitable values, were obtained using an ANalysis Of the VAriance (ANOVA).
 
@@
 ANOVA, in this case, examines the effects of three quantitative variables (termed factors) on one quantitative response.
-Considered factors are the link function, the learning rate for the Adam optimization algorithm, and the batch size.
-
-	Following the setup of the previous study, we performed an ANOVA III analysis and multiple comparison tests.
+Considered factors are the LF, the LR for the Adam optimization algorithm, and the BS.
 We assume that five executions are enough to do the statistical tests because of the computational time limitations.
 
-	We denote by $\text{QWK}_{i,j,k,l}(i=1, ..., 3; j = 1, ..., 3; k = 1, ..., 3)$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level.
+	The test variable will be QWK, given by Eq.
+\eqref{eq:qwk}.
+We denote by $\text{QWK}_{i,j,k,l}(i,j,k\in \{1, 2, 3\})$ the value observed when the first factor is at the $i$-th level, the second at the $j$-th level and the third at the $k$-th level.
 We assume that the three factors do not act independently, and, therefore, there exists an interaction between each pair of them and between the three factors.
@@
 	\end{equation}
-	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the link factor (\texttt{logit}, \texttt{probit}, complementary log-log); $P_j$ is the effect associated with the \textit{j-th} level of the learning rate factor and $B_k$ is the effect associated with the \textit{k-th} level of the batch size factor.
+	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the LF factor (\texttt{logit}, \texttt{probit}, \texttt{clog-log}); $P_j$ is the effect associated with the \textit{j-th} level of the LR factor and $B_k$ is the effect associated with the \textit{k-th} level of the BS factor.
 The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors.
@@
 The term $\epsilon_{i,j,k,l}$ is the influence on the results of everything that could not be evaluated or of random factors.
-$QWK_{i,j,k,l}$ is the quadratic weighted kappa measure, the response variable used to perform the statistical analysis.
 
 	We consider the null hypothesis that each term of the above equation is independent of the levels involved.
-The hypotheses for the levels of the L factor are $H_0 \equiv L_1 = L_2 = L_3,$ and $H_1 \equiv \text{ some } L_i \text{ is different}$.
+The hypotheses for the levels of the L factor are $H_0 \equiv \left( L_1 = L_2 = L_3 \right),$ and $H_1 \equiv \left( \exists i,j | L_i\neq L_j\right)$.
 The same hypotheses are made for the other factors.
-In this way, we test in the null hypothesis that all the population averages are equal against the alternative hypothesis that there is at least one mean that is not equal to the others.
-
-	The hypothesis associated with the interaction between $L$ and $P$ is $H_0 \equiv LP_{i,j} = 0, \forall i,j$, and $H_1 \equiv \exists LP_{i,j} \ne 0$.
+	The hypothesis associated with the interaction between $L$ and $P$ is $H_0 \equiv \left(LP_{i,j} = 0, \forall i,j\right)$, and $H_1 \equiv \left(\exists LP_{i,j} \ne 0\right)$.
 Similar hypotheses can be assumed for the interaction between the other factors.
 
-	The analysis of variance table represents the initial study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
+	The ANOVA table represents the study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
 These factors and interactions take part on the error component.
 In this way, the results of the ANOVA III test for the DR dataset are summarised in Table  \ref{table:ANOVARetinopathy}.
-There are significant differences in average QWK depending on the link function and also depending on the learning rate for $\alpha=0.05$ ($\text{p-value} = 0.000$).
-Moreover, an interaction between the link function and the learning rate can be recognised ($\text{p-value} = 0.001$).
-It means that the learning rate and the link functions have a significant impact on the optimization algorithm results.
+There are significant differences in average QWK depending on the LF and also depending on the LR for $\alpha=0.05$ ($\text{p-value} = 0.000$).
+Moreover, an interaction between the LF and the LR can be recognised ($\text{p-value} = 0.001$).
 
@@
 A post-hoc multiple comparison test has been performed on the mean QWK obtained.
-An HSD Tukey's test \cite{tukey1949comparing} was made under the null hypothesis that the variance of the error of the dependent variable is the same between the groups.
+An HSD Tukey's test \cite{tukey1949comparing} has been selected under the null hypothesis that the variance of the error of the dependent variable is the same between the groups.
 The results of this test over the test set are shown in Table \ref{table:TukeyDR}.
-They show that the best link function is the complementary log-log but the \texttt{probit} link performance is close to it.
-Also, the best value for the learning rate parameter is $10^{-3}$.
-The batch size is not relevant for this dataset with the values considered.
+They show that the best LF is the \texttt{clog-log} but the \texttt{probit} link performance is close to it.
+Also, the best value for the LR parameter is $10^{-3}$.
+The BS is not relevant for this dataset with the values considered.
 
@@
 First, we observe that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$).
-Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$).
-It means that the joint action of two or three factors significantly affects the results obtained by the algorithm.
+Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$, respectively).
 
 	As we did for the DR dataset, a post-hoc multiple comparison test has been performed on the average QWK obtained for Adience.
-Under the null hypothesis that the variance of the error of the dependent variable is the same between the groups, an HSD Tukey's test has been applied.
+Under the null hypothesis that the variance of the error of the dependent variable is the same between the groups, the HSD Tukey's test has been applied.
 The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.
@@
 
-	The results over the test set show that the best link function is the \texttt{logit} one, the best learning rate is $10^{-3}$ and the best batch size is 128.
-However, the interactions between these factors made the configuration that uses a \texttt{logit} link, $\eta=10^{-3}$ and batch size of 64, the best configuration.
+	The results over the test set show that the best LF is the \texttt{logit}, the best LR is $10^{-3}$ and the best BS is 128.
+However, the interactions between these factors made the configuration that uses a \texttt{logit} link, $\eta=10^{-3}$ and BS of 64, the best configuration.
 It obtained a mean QWK value of $0.940$ for validation and $0.881$ for test.
@@
 	To sum up, the results showed that the best parameter configuration depends on the problem that is being solved.
-The optimal value for the batch size and the optimal link function are not the same for Retinopathy and Adience datasets.
+The optimal value for the batch size and the optimal LF are not the same for Retinopathy and Adience datasets.
 These results highlight the importance of adjusting the hyper-parameters for each problem instead of trying to find an optimal configuration for all the datasets.
-However, the best learning rate for both datasets were $10^{-3}$.
+However, the best LR for both datasets were $10^{-3}$.
 It is recommended to use this value for future datasets.
-	The best batch size for DR was 10 while the best value for Adience was 128 (intermediate values considered).
-	Finally, there are more interactions between the three factors for the Adience dataset than for the DR one.
+The best BS for DR was 10, while the best value for Adience was 128 (intermediate values considered).
+Finally, there are more interactions between the three factors for the Adience dataset than for DR.
 This highlights the importance of making experimental designs associated with each dataset to determine the best value for each factor.
@@
 	\label{sect:NominalComparison}
-
-	The same experiments described in Section \ref{sect:experiments} were repeated using the cross-entropy instead of the QWK as loss function and the softmax function instead of the CLM for the output of the network.
+	Once the factor parameters have been studied and selected, experiments are run with the standard cross-entropy loss and the softmax function too in order to prove the performance improvement of considering the ordinality of the problem (QWK loss and the CLM).
 The evaluation metrics remains the same in order to be able to compare.
+When considering the nominal version, for the DR dataset, the best mean value of QWK was $0.497$ and was obtained when using a BS of 10 and a LR of $10^{-4}$.
+In the case of Adience dataset, the highest QWK was $0.787$ and was achieved with a BS of 64 and a LR of $10^{-3}$.
 There are some parameter configurations where the training process gets stagnated and a very low QWK is obtained.
@@
 
-	For the DR dataset, the best mean value of QWK was $0.497$ and was obtained when using a batch size of 10 and a learning rate of $10^{-4}$.
-In the case of Adience dataset, the highest QWK was $0.787$ and was achieved with a batch size of 64 and a learning rate of $10^{-3}$.
-
-	The comparison of the best results for each dataset for ordinal and nominal cases and previous works is shown in Tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}.
+	These results are included in Tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}, together with the comparison against previous works of the state-of-the-art.
 All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).
 The proposed ordinal model outperforms all the other alternatives in terms of QWK.
-The performance gain of CLM over the softmax reaches $16.8\%$ for DR and $11.9\%$ for Adience dataset.
-The improvement of the ordinal method for Retinopathy dataset is higher than for Adience dataset.
+
+	The performance gain of CLM over the nominal version reaches $16.8\%$ for DR and $11.9\%$ for Adience dataset.
+The improvement of the ordinal method for DR is higher than that for Adience.
 It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
+Moreover, when compared against alternative ordinal methods (many of them with a deep structure), CLMs are very competitive, possibly because of the flexibility provided by the threshold model structure (where the threshold of each class is independently adjusted).
 
@@
 		\begin{tabular}{lccc}
-			\hline
-			\hline
+			\hline\hline
 			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
@@
 			Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
+			Beckham et al. \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
 			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
 			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
-			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$		 \\
-			\hline
-			\hline
+			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
 		\end{tabular}
@@
 	\label{sect:conclusions}
-	The proposed CLM has improved the performance of the deep network compared to the model that uses the softmax function and the models proposed in previous works.
-Also, it reduces the chance that the model gets stuck when training with some parameter configurations.
-So, the most significant improvements of these link functions are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention of the over-fitting and the stagnation.
-
-	Also, we have concluded that the optimal values for the different parameters considered are problem-dependant.
-The complementary log-log function offers the best results in DR dataset while the \texttt{logit} link is the best option for the Adience dataset.
-These results provide an opportunity for exploring new generalised link functions that could be dynamically adapted to any problem.
+
+	This paper introduces a new deep ordinal network based on combining CLM models with a continuous QWK loss function.
+The proposed model is able to improve the performance of the deep network compared to the equivalent nominal version and other models proposed in previous works.
+Also, it is able to reduce the chance that the model gets stuck when training with some parameter configurations.
+
+	Moreover, we also conclude that the optimal values for the different parameters considered are problem-dependant.
+The \texttt{clog-log} function offers the best results in DR dataset while the \texttt{logit} link is the best option for the Adience dataset.
 The best value for the learning rate parameter for both datasets is $\eta = 10^{-3}$.
-It can be considered a good value for this parameter when training the model with new datasets.
-Both datasets have obtained the best performance with an intermediate batch size: 10 for DR and 128 for Adience.
-	Also, the statistical tests reported that there are relevant interactions between the three factors that we have take into account.
+It can be considered a good value when training the model with new datasets.
+Both datasets have obtained the best performance with an intermediate BS: 10 for DR and 128 for Adience.
 The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
+
+	In summary, the most significant contributions of the model proposal are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention from over-fitting and stagnation.
+
+	As future research, it seems that the design of new generalised link functions could be promising, which could be dynamically adapted to any problem based on a learnable parameter.
 

### 2019-05-23 activations.py

@@ -321,7 +321,8 @@ class CLM(keras.layers.Layer):
 		elif self.link_function == 'gauss':
 			# a3T = 1.0 / 2.0 + K.sign(z3) * K.igamma(1.0 / self.alpha, K.pow(K.abs(z3) / self.r, self.alpha)) / (2 * K.exp(K.lgamma(1.0 / self.alpha)))
 			# z3 = K.Print(z3, data=[K.reduce_max(K.abs(z3))], message='z3 abs max')
-			a3T = 1.0 / 2.0 + (2 * K.sigmoid(z3 - self.p['mu']) - 1) * igamma(1.0 / self.p['alpha'],
+			# K.sigmoid(z3 - self.p['mu']) - 1)
+			a3T = 1.0 / 2.0 + K.tanh(z3 - self.p['mu']) * igamma(1.0 / self.p['alpha'],
 																	K.pow(K.pow((z3 - self.p['mu']) / self.p['r'], 2),
 																		   self.p['alpha'])) / (
 								  2 * K.exp(lgamma(1.0 / self.p['alpha'])))

### 2019-05-23 plot_gamma.py

@@ -4,11 +4,11 @@ import random
 from scipy.special import gamma, gammainc
 
 
-def loggamma(x, a, d, p):
+def ggamma(x, a, d, p):
 	return gammainc(d/p, (x/a)**p) / gamma(d/p)
 
 plots = [
-	{'as': np.round(np.arange(0.1, 1, 0.2), 2), 'ds': np.round(np.arange(0.1, 1, 0.2), 2), 'ps': np.round(np.arange(0.1, 1, 0.2), 2)},
+	{'as': np.round(np.arange(0.1, 1, 0.3), 2), 'ds': np.round(np.arange(0.1, 1, 0.3), 2), 'ps': np.round(np.arange(0.1, 1, 0.3), 2)},
 	# {'as': [0.5], 'ds': np.round(np.arange(0.1, 1.5, 0.2), 2), 'ps': [0.1]},
 ]
 
@@ -26,7 +26,7 @@ for plot in plots:
 		for d in ds:
 			for p in ps:
 				x = np.arange(-2, 2, 0.001)
-				y = loggamma(x, a, d, p)
+				y = ggamma(x, a, d, p)
 				# plt.plot(x,num, linestyle='--', c=colors[cid])
 				plt.plot(x, y, label='a={},d={},p={}'.format(a, d, p), c=colors[cid])
 				# plt.plot(x,logfunc(x, a, r, mu), label='a={},r={},mu={}'.format(a, r, mu), c = colors[cid])

### 2019-05-24 paper/ieee.tex
Paper + fixed multiprocessing issue

@@
 
-\usepackage{hyperref}
+\usepackage[bookmarks=false]{hyperref}
 
@@
 	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
-These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy protection~\cite{yu2017iprivacy}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
+These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
 Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays.
@@
 	\begin{equation}
+	\nonumber
 	b_q = b_1 + \sum_{q=1}^{q-1} \alpha_q^2, \quad q = 2, ..., Q,
@@
 	CNNs have been used for both datasets.
-The different architectures of CNNs used in these experiments are presented in Tables \ref{table:CNNArchitecture} and \ref{table:ResNetArchitecture}.
+The different architectures of CNNs used in these experiments are presented in Table \ref{table:Architecture}.
 The architecture for DR is the same that was used in \cite{de2018weighted} and the network for Adience is a small Residual Network (ResNet) \cite{he2016deep} that was used in \cite{beckham2017unimodal}.
@@
 
+%	\begin{table}[!t]
+%		\caption{Description of the architecture used in the DR experiments.}
+%		\label{table:CNNArchitecture}
+%		\centering
+%		\begin{tabular}{lc}
+%			\hline
+%			\hline
+%			\textbf{Layer} & \textbf{Output shape}\\
+%			\hline
+%			2 x Conv3x3@32s1 & 252x252x32\\
+%			MaxPool2x2s2 & 126x126x32\\
+%			2 x Conv3x3@64s1 & 122x122x64\\
+%			MaxPool2x2s2 & 61x61x64\\
+%			2 x Conv3x3@128s1 & 57x57x128\\
+%			MaxPool2x2s2 & 28x28x128\\
+%			2 x Conv3x3@128s1 & 24x24x128\\
+%			MaxPool2x2s2 & 12x12x128\\		
+%			Conv4x4@128s1 & 9x9x128\\
+%			\hline
+%			\hline
+%		\end{tabular}	
+%	\end{table}
+%	
+%	\begin{table}[!t]
+%		\caption{Description of the architecture used in the Adience experiments.}
+%		\label{table:ResNetArchitecture}
+%		\centering
+%		\begin{tabular}{lc}
+%			\hline
+%			\hline
+%			\textbf{Layer} & \textbf{Output shape}\\
+%			\hline
+%			Conv7x7@32s2 & 112x112x32\\
+%			MaxPool3x3s2 & 55x55x32\\
+%			2 x ResBlock3x3@64s1 & 55x55x32\\
+%			1 x ResBlock3x3@128s2 & 28x28x64\\
+%			2 x ResBlock3x3@128s1 & 28x28x64\\
+%			1 x ResBlock3x3@256s2 & 14x14x128\\
+%			2 x ResBlock3x3@256s1 & 14x14x128\\
+%			1 x ResBlock3x3@512s2 & 7x7x256\\
+%			2 x ResBlock3x3@512s1 & 7x7x256\\
+%			AveragePool7x7s2 & 1x1x256\\
+%			\hline
+%			\hline
+%		\end{tabular}	
+%	\end{table}
+
 	\begin{table}[!t]
-		\caption{Description of the architecture used in the DR experiments.}
-		\label{table:CNNArchitecture}
+		\caption{Description of the architecture used for each dataset.}
+		\label{table:Architecture}
 		\centering
-		\begin{tabular}{lc}
+		\resizebox{\columnwidth}{!}{
+		\begin{tabular}{lclc}
+			\hline\hline
+			\multicolumn{2}{c}{\textbf{Diabetic Retinopathy}} & \multicolumn{2}{c}{\textbf{Adience}}\\
 			\hline
-			\hline
-			\textbf{Layer} & \textbf{Output shape}\\
-			\hline
-			%Conv3x3@32s1 & 254x254x32\\\hline
-			2 x Conv3x3@32s1 & 252x252x32\\
-			MaxPool2x2s2 & 126x126x32\\
-
-			%Conv3x3@64s1 & 124x124x64\\\hline
-			2 x Conv3x3@64s1 & 122x122x64\\
-			MaxPool2x2s2 & 61x61x64\\
-
-			%Conv3x3@128s1 & 59x59x128\\\hline
-			2 x Conv3x3@128s1 & 57x57x128\\
-			MaxPool2x2s2 & 28x28x128\\
-
-			%Conv3x3@128s1 & 26x26x128\\\hline
-			2 x Conv3x3@128s1 & 24x24x128\\
-			MaxPool2x2s2 & 12x12x128\\
-
-			Conv4x4@128s1 & 9x9x128\\
-			\hline
-			\hline
-		\end{tabular}	
-	\end{table}
-
-	\begin{table}[!t]
-		\caption{Description of the architecture used in the Adience experiments.}
-		\label{table:ResNetArchitecture}
-		\centering
-		\begin{tabular}{lc}
-			\hline
-			\hline
-			\textbf{Layer} & \textbf{Output shape}\\
-			\hline
-			Conv7x7@32s2 & 112x112x32\\
-			MaxPool3x3s2 & 55x55x32\\
-			2 x ResBlock3x3@64s1 & 55x55x32\\
-			1 x ResBlock3x3@128s2 & 28x28x64\\
-			2 x ResBlock3x3@128s1 & 28x28x64\\
-			1 x ResBlock3x3@256s2 & 14x14x128\\
-			2 x ResBlock3x3@256s1 & 14x14x128\\
-			1 x ResBlock3x3@512s2 & 7x7x256\\
-			2 x ResBlock3x3@512s1 & 7x7x256\\
-			AveragePool7x7s2 & 1x1x256\\
-			\hline
-			\hline
-		\end{tabular}	
+			\textbf{Layer}  & \textbf{Output} & \textbf{Layer}      & \textbf{Output} \\ \hline
+			2 Conv3x3@32s1  &   252x252x32    & Conv7x7@32s2        &   112x112x32    \\
+			MaxPool2x2s2    &   126x126x32    & MaxPool3x3s2        &    55x55x32     \\
+			2 Conv3x3@64s1  &   122x122x64    & 2 ResBlock3x3@64s1  &    55x55x32     \\
+			MaxPool2x2s2    &    61x61x64     & ResBlock3x3@128s2   &    28x28x64     \\
+			2 Conv3x3@128s1 &    57x57x128    & 2 ResBlock3x3@128s1 &    28x28x64     \\
+			MaxPool2x2s2    &    28x28x128    & 1 ResBlock3x3@256s2 &    14x14x128    \\
+			2 Conv3x3@128s1 &    24x24x128    & 2 ResBlock3x3@256s1 &    14x14x128    \\
+			MaxPool2x2s2    &   12x12x128\    & 1 ResBlock3x3@512s2 &     7x7x256     \\
+			Conv4x4@128s1   &     9x9x128     & 2 ResBlock3x3@512s1 &     7x7x256     \\
+			                &                 & AveragePool7x7s2    &     1x1x256     \\ \hline\hline
+		\end{tabular}}	
 	\end{table}
@@
 
-	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
-	\begin{figure}[!t]
-		\centering
-		\includegraphics[width=3in]{img/lr.pdf}
-		\caption{Representation of the learning rate decay.}
-		\label{fig:lrdecay}
-	\end{figure}
+%	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
+%	\begin{figure}[!t]
+%		\centering
+%		\includegraphics[width=3in]{img/lr.pdf}
+%		\caption{Representation of the learning rate decay.}
+%		\label{fig:lrdecay}
+%	\end{figure}
 
@@
 
-	The test variable will be QWK, given by Eq.
+%	The test variable will be QWK, given by Eq.
 \eqref{eq:qwk}.
@@
 In this case, the observations fit:
-	\begin{equation}
-	\nonumber
-	\begin{aligned}
-	\footnotesize
-	\text{QWK}_{i,j,k,l} = \mu & + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
-	\label{eq:anova3}
-	\end{aligned}
-	\end{equation}
-	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the LF factor (\texttt{logit}, \texttt{probit}, \texttt{clog-log}); $P_j$ is the effect associated with the \textit{j-th} level of the LR factor and $B_k$ is the effect associated with the \textit{k-th} level of the BS factor.
+%	\begin{equation}
+%	\nonumber
+%	\begin{aligned}
+%	\footnotesize
+%	\text{QWK}_{i,j,k,l} = \mu & + L_i + P_j + B_k + LP_{i,j} + LB_{i,k} \\& + PB_{j,k} + LPB_{i,j,k} + \epsilon_{i,j,k,l},
+%	\label{eq:anova3}
+%	\end{aligned}
+%	\end{equation}
+%	where $\mu$ is the fixed effect that is common to all the populations; $L_i$ is the effect associated with the \textit{i-th} level of the LF factor (\texttt{logit}, \texttt{probit}, \texttt{clog-log}); $P_j$ is the effect associated with the \textit{j-th} level of the LR factor and $B_k$ is the effect associated with the \textit{k-th} level of the BS factor.
 The term $LP_{i,j}$ denotes the joint effect of the presence of level $i$ of the first factor and level $j$ of the second one; this, therefore, is denominated the interaction term between $L$ and $P$ factors.
@@
 
-	We consider the null hypothesis that each term of the above equation is independent of the levels involved.
+	%	We consider the null hypothesis that each term of the above equation is independent of the levels involved.
 The hypotheses for the levels of the L factor are $H_0 \equiv \left( L_1 = L_2 = L_3 \right),$ and $H_1 \equiv \left( \exists i,j | L_i\neq L_j\right)$.
@@
 
-	The ANOVA table represents the study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
+	%	The ANOVA table represents the study in a compact form, containing the sum of squares, degrees of freedom, mean square value, test statistics and significance levels, where non-significative factors and interactions have been removed ($\text{p-value} > 0.05$).
 These factors and interactions take part on the error component.
 In this way, the results of the ANOVA III test for the DR dataset are summarised in Table  \ref{table:ANOVARetinopathy}.
-There are significant differences in average QWK depending on the LF and also depending on the LR for $\alpha=0.05$ ($\text{p-value} = 0.000$).
+	The ANOVA test results show that there are significant differences in average QWK depending on the LF and also depending on the LR for $\alpha=0.05$ ($\text{p-value} = 0.000$).
 Moreover, an interaction between the LF and the LR can be recognised ($\text{p-value} = 0.001$).
 
-	\begin{table}[!t]
-		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
-		\label{table:ANOVARetinopathy}
-		\centering
-		\small
-		\begin{tabular}{lccccc}
-			\hline
-			\hline
-			           \multicolumn{6}{c}{Response variable QWK}             \\ \hline
-			Source       &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
-			Model        & $37.860$ &  $9$  & $4.207$ & $1562.840$ & $0.000$ \\
-			$L$ factor   & $0.057$  &  $2$  & $0.029$ &  $10.646$  & $0.000$ \\
-			$P$ factor   & $0.121$  &  $2$  & $0.060$ &  $22.468$  & $0.000$ \\
-			$LP$ factors & $0.057$  &  $4$  & $0.014$ &  $5.261$   & $0.001$ \\
-			Error        & $0.339$  & $126$ & $0.003$ &            &  \\ \hline
-			Total        & $38.199$ & $135$ &         &            & \\
-			\hline
-			\hline
-		\end{tabular}
-	\end{table}
+%	\begin{table}[!t]
+%		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Retinopathy dataset.}
+%		\label{table:ANOVARetinopathy}
+%		\centering
+%		\small
+%		\begin{tabular}{lccccc}
+%			\hline
+%			\hline
+%			           \multicolumn{6}{c}{Response variable QWK}             \\ \hline
+%			Source       &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
+%			Model        & $37.860$ &  $9$  & $4.207$ & $1562.840$ & $0.000$ \\
+%			$L$ factor   & $0.057$  &  $2$  & $0.029$ &  $10.646$  & $0.000$ \\
+%			$P$ factor   & $0.121$  &  $2$  & $0.060$ &  $22.468$  & $0.000$ \\
+%			$LP$ factors & $0.057$  &  $4$  & $0.014$ &  $5.261$   & $0.001$ \\
+%			Error        & $0.339$  & $126$ & $0.003$ &            &  \\ \hline
+%			Total        & $38.199$ & $135$ &         &            & \\
+%			\hline
+%			\hline
+%		\end{tabular}
+%	\end{table}
 
@@
 An HSD Tukey's test \cite{tukey1949comparing} has been selected under the null hypothesis that the variance of the error of the dependent variable is the same between the groups.
-The results of this test over the test set are shown in Table \ref{table:TukeyDR}.
+The results of this test over the test set are shown in Table \ref{table:Tukey}.
 They show that the best LF is the \texttt{clog-log} but the \texttt{probit} link performance is close to it.
@@
 The BS is not relevant for this dataset with the values considered.
-
-	\begin{table}[!t]
-		\caption{Tukey's test results for the DR dataset.}
-		\label{table:TukeyDR}
-		\centering
-		\begin{tabular}{cccc}
-			\hline\hline
-			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
-			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
-			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
-			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
-			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
-			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
-			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
-			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
-			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
-			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
-			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
-			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
-			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
-			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
-		\end{tabular}
-	\end{table}
-
-	\begin{table}[!t]
-		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
-		\label{table:ANOVAAdience}
-		\centering
-		\small
-		\begin{tabular}{lccccc}
-			\hline\hline
-			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
-			Source        &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
-			Model         & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
-			$L$ factor    & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
-			$P$ factor    & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
-			$B$ factor    & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
-			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
-			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
-			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
-			$LPB$ factors & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
-			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
-			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
-		\end{tabular}
-	\end{table}
-
-	The results of the ANOVA III test for the Adience dataset are shown in Table \ref{table:ANOVAAdience}.
-First, we observe that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$).
+%		
+%	\begin{table}[!t]
+%		\caption{Tukey's test results for the DR dataset.}
+%		\label{table:TukeyDR}
+%		\centering
+%		\begin{tabular}{cccc}
+%			\hline\hline
+%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
+%			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
+%			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
+%			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
+%			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
+%			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
+%			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
+%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
+%			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
+%			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
+%			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
+%			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
+%			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
+%			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
+%		\end{tabular}
+%	\end{table}
+
+%	\begin{table}[!t]
+%		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
+%		\label{table:ANOVAAdience}
+%		\centering
+%		\small
+%		\begin{tabular}{lccccc}
+%			\hline\hline
+%			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
+%			Source        &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
+%			Model         & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
+%			$L$ factor    & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
+%			$P$ factor    & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
+%			$B$ factor    & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
+%			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
+%			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
+%			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
+%			$LPB$ factors & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
+%			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
+%			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
+%		\end{tabular}
+%	\end{table}
+%	
+	The results of the ANOVA III test for the Adience dataset, first, demonstrate that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$).
 Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$, respectively).
@@
 Under the null hypothesis that the variance of the error of the dependent variable is the same between the groups, the HSD Tukey's test has been applied.
-The results of this test over the test set are shown in Table \ref{table:TukeyAdience}.
+The results of this test over the test set are shown in Table \ref{table:Tukey}.
+
+%	\begin{table}[!t]
+%		\caption{Tukey's test results for the Adience dataset.}
+%		\label{table:TukeyAdience}
+%		\centering
+%		\begin{tabular}{cccc}
+%			\hline\hline
+%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
+%			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
+%			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
+%			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
+%			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
+%			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
+%			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
+%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
+%			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
+%			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
+%			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
+%			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
+%			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
+%			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
+%			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
+%			       64         &        128        &  $-0.041$  & $0.026$ \\
+%			                  &        256        &  $-0.027$  & $0.000$ \\
+%			       128        &        64         &  $0.041$   & $0.026$ \\
+%			                  &        256        &  $0.014$   & $0.000$ \\
+%			       256        &        64         &  $0.027$   & $0.000$ \\
+%			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
+%		\end{tabular}
+%	\end{table}
 
 	\begin{table}[!t]
-		\caption{Tukey's test results for the Adience dataset.}
-		\label{table:TukeyAdience}
+		\caption{Tukey's test results for both datasets.}
+		\label{table:Tukey}
 		\centering
-		\begin{tabular}{cccc}
+		\resizebox{\columnwidth}{!}{
+		\begin{tabular}{cccccc}
 			\hline\hline
-			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
-			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
-			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
-			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
-			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
-			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
-			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
-			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
-			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
-			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
-			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
-			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
-			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
-			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
-			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
-			       64         &        128        &  $-0.041$  & $0.026$ \\
-			                  &        256        &  $-0.027$  & $0.000$ \\
-			       128        &        64         &  $0.041$   & $0.026$ \\
-			                  &        256        &  $0.014$   & $0.000$ \\
-			       256        &        64         &  $0.027$   & $0.000$ \\
-			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
-		\end{tabular}
+			                  &                   & \multicolumn{2}{c}{\textbf{DR}} & \multicolumn{2}{c}{\textbf{Adience}} \\ \hline
+			       LF         &        LF         & Mean diff. &        Sig.        & Mean diff. &          Sig.           \\ \hline
+			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   &      $0.000$       &  $-0.002$  &         $0.011$         \\
+			                  & \texttt{clog-log} &  $0.084$   &      $0.000$       &  $0.012$   &         $0.000$         \\
+			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  &      $0.000$       &  $0.002$   &         $0.011$         \\
+			                  & \texttt{clog-log} &  $0.038$   &      $0.000$       &  $0.014$   &         $0.248$         \\
+			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  &      $0.000$       &  $-0.012$  &         $0.000$         \\
+			                  &  \texttt{probit}  &  $-0.038$  &      $0.000$       &  $-0.014$  &         $0.248$         \\ \hline\hline
+			       LR         &        LR         & Mean diff. &        Sig.        & Mean diff. &          Sig.           \\ \hline
+			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  &      $0.000$       &  $-0.073$  &         $0.000$         \\
+			                  &     $10^{-4}$     &  $0.148$   &      $0.000$       &  $-0.044$  &         $0.000$         \\
+			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   &      $0.000$       &  $0.073$   &         $0.000$         \\
+			                  &     $10^{-4}$     &  $0.194$   &      $0.000$       &  $0.029$   &         $0.023$         \\
+			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  &      $0.000$       &  $0.044$   &         $0.000$         \\
+			                  &     $10^{-3}$     &  $-0.194$  &      $0.000$       &  $-0.029$  &         $0.023$         \\ \hline\hline
+			       BS         &        BS         & Mean diff. &        Sig.        & Mean diff. &          Sig.           \\ \hline
+			       64         &        128        &  $-0.041$  &      $0.026$       &     -      &            -            \\
+			                  &        256        &  $-0.027$  &      $0.000$       &     -      &            -            \\
+			       128        &        64         &  $0.041$   &      $0.026$       &     -      &            -            \\
+			                  &        256        &  $0.014$   &      $0.000$       &     -      &            -            \\
+			       256        &        64         &  $0.027$   &      $0.000$       &     -      &            -            \\
+			                  &        128        &  $-0.014$  &      $0.000$       &     -      &            -
+		\end{tabular}}
 	\end{table}
@@
 
-	These results are included in Tables \ref{table:ComparisonDR} and \ref{table:ComparisonAdience}, together with the comparison against previous works of the state-of-the-art.
+	These results are included in Table \ref{table:Comparison}, together with the comparison against previous works of the state-of-the-art.
 All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).
+The results for \cite{beckham2017unimodal} were obtained by reproducing their experiments because they didn't provide exact results for test set that could be used to compare with our results.
 The proposed ordinal model outperforms all the other alternatives in terms of QWK.
@@
 
+%	\begin{table}[!t]
+%		\caption{Comparison between the best results of nominal, ordinal and previous works for the DR dataset.}
+%		\label{table:ComparisonDR}
+%		\scriptsize
+%		\centering
+%		\def\arraystretch{1.3}
+%		\begin{tabular}{lccc}
+%			\hline
+%			\hline
+%			Method                                   & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
+%			Ordinal network                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
+%			Nominal network                          &    $0.498_{(0.013)}$    &    $0.692_{(0.014)}$    &        $0.854_{(0.006)}$         \\
+%			J. Torre et al. \cite{de2018weighted}    &  $0.537_{(\text{-})}$   &            -            &                -                 \\
+%			À. Nebot et al. \cite{nebot2016diabetic} &  $0.555_{(\text{-})}$   &            -            &                -					\\
+%			\hline
+%			\hline
+%		\end{tabular}
+%	\end{table}
+%	
+%	\begin{table}[!t]
+%		\caption{Comparison between the best results of nominal, ordinal and previous works for the Adience dataset.}
+%		\label{table:ComparisonAdience}
+%		\scriptsize
+%		\centering
+%		\def\arraystretch{1.3}
+%		\begin{tabular}{lccc}
+%			\hline\hline
+%			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
+%			Ordinal network                           &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
+%			Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
+%			Beckham et al. \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
+%			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
+%			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
+%			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
+%		\end{tabular}
+%	\end{table}
+
 	\begin{table}[!t]
-		\caption{Comparison between the best results of nominal, ordinal and previous works for the DR dataset.}
-		\label{table:ComparisonDR}
+		\caption{Comparison between the best results of nominal, ordinal and previous works for the both datasets.}
+		\label{table:Comparison}
 		\scriptsize
@@
 		\begin{tabular}{lccc}
-			\hline
+			\hline\hline
+			\multicolumn{4}{c}{\textbf{Diabetic Retinopathy}}\\
 			\hline
@@
 			\hline
+			\multicolumn{4}{c}{\textbf{Adience}}\\
 			\hline
-		\end{tabular}
-	\end{table}
-
-	\begin{table}[!t]
-		\caption{Comparison between the best results of nominal, ordinal and previous works for the Adience dataset.}
-		\label{table:ComparisonAdience}
-		\scriptsize
-		\centering
-		\def\arraystretch{1.3}
-		\begin{tabular}{lccc}
-			\hline\hline
 			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline

### 2019-05-24 experiment.py

@@ -563,7 +563,7 @@ class Experiment:
 									   PrintWeightsCallback()
 									   ],
 							workers=self.workers,
-							use_multiprocessing=True,
+							use_multiprocessing=False,
 							max_queue_size=self.queue_size,
 							class_weight=class_weight,
 							validation_data=val_generator,

### 2019-05-24 paper/ieee.tex
ggamma, inceptionresnetv2 functional api, paper

@@
 	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
-These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}.
+These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly,jin2018deep}.
 Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays.
@@
 
-%		\textbf{(Binarización. Resolución de varios subproblemas.)}
 	Z.
@@
 
-%		\textbf{(Binarización. Resolución de varios subproblemas.)}
 	H.
@@
 
-%		\textbf{(Binarización. Resolución de varios subproblemas.)}
 	Y.
@@
 
-%		\textbf{(Binarización. Resolución de varios subproblemas.)}
 	S.
@@
 
-%		\textbf{(Función de coste ordinal)}
 	J.
@@
 
-%		\textbf{(Funcion de coste ordinal)}
 	A.
@@
 
-%		\textbf{(Funcion de coste ordinal)}
 	H.
@@
 Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.
-%	\textcolor{red}{La parte ordinal no queda muy clara}
-
-%		\textbf{(Funcion de coste ordinal)}
+
 	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.
 
-%		\textbf{(Multi-clase con restricciones)}
 	Y.
@@
 
-	%\textbf{(Función de coste ordinal y distribución unimodal.)}
 	C.
@@
 However, CLMs indirectly model a latent space together with the set of threshold separating the ordered classes, which provides a more flexible and interpretable approach to deep ordinal classification.
-
-%	The QWK metric is defined as follows:
-%	\begin{equation}
-%	\nonumber
-%	\text{QWK} = 1 - \frac{\sum\limits^N_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits^N_{i,j} \omega_{i,j} E_{i,j}},
-%	\end{equation}
-%	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i\bullet} O_{\bullet j}}{N}$, $O_{i\bullet}$ is the sum of the $i\text{-th}$ row and $O_{\bullet j}$ is the sum of the $j\text{-th}$ column.
-%	
-%	Then, they provided a continuous version of the QWK metric ($\text{QWK}_c$) based on the probabilities of the predictions:
-%	\begin{equation}
-%	\nonumber
-%	\text{QWK}_c = 1 - \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q \left( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k)\right)},
-%	\end{equation}
-%	where $\text{QWK}_c \in [-1,1]$, $\mathbf{x}_k$ and $t_k$ are the input vector and the real class of the $k$-th sample, respectively, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix.
-Generally, $\omega_{i,j} = \frac{|i-j|^n}{(C-1)^n}$, where $\omega_{i,j} \in [0,1]$.
-%	
-%	Then, they defined the loss function based on the QWK as follows:
-%	\begin{equation}
-%	\nonumber
-%	\mathscr{L} = \log(1 - \text{QWK}_c),
-%	\end{equation}
-%	where $\mathscr{L} \in [-\infty, \log 2]$. $\mathscr{L}$ should be minimized, while the $\text{QWK}_c$ metric should be maximized.
-
-%	\textcolor{red}{Yo intentaría organizar un poco el análisis que has hecho.
-Por ejemplo, podrías distinguir entre trabajos que modifican la función de error o los que modifican el modelo (ya sea aplicando binarización o utilizando distribuciones unimodales).
-o los que hacen las dos cosas.
-También habría que ir poniendo posibles pegas a cada artículo y destacar las ventajas de lo que proponemos (se impone una distribución unimodal, sin aplicar binarización, junco con una versión continua de una de las funciones d eerror más usadas)}
 
@@
 	where $\tau$ is optimized as a free parameter.
-
-%	\begin{table}[!t]
-%		\caption{Description of the architecture used in the DR experiments.}
-%		\label{table:CNNArchitecture}
-%		\centering
-%		\begin{tabular}{lc}
-%			\hline
-%			\hline
-%			\textbf{Layer} & \textbf{Output shape}\\
-%			\hline
-%			2 x Conv3x3@32s1 & 252x252x32\\
-%			MaxPool2x2s2 & 126x126x32\\
-%			2 x Conv3x3@64s1 & 122x122x64\\
-%			MaxPool2x2s2 & 61x61x64\\
-%			2 x Conv3x3@128s1 & 57x57x128\\
-%			MaxPool2x2s2 & 28x28x128\\
-%			2 x Conv3x3@128s1 & 24x24x128\\
-%			MaxPool2x2s2 & 12x12x128\\		
-%			Conv4x4@128s1 & 9x9x128\\
-%			\hline
-%			\hline
-%		\end{tabular}	
-%	\end{table}
-%	
-%	\begin{table}[!t]
-%		\caption{Description of the architecture used in the Adience experiments.}
-%		\label{table:ResNetArchitecture}
-%		\centering
-%		\begin{tabular}{lc}
-%			\hline
-%			\hline
-%			\textbf{Layer} & \textbf{Output shape}\\
-%			\hline
-%			Conv7x7@32s2 & 112x112x32\\
-%			MaxPool3x3s2 & 55x55x32\\
-%			2 x ResBlock3x3@64s1 & 55x55x32\\
-%			1 x ResBlock3x3@128s2 & 28x28x64\\
-%			2 x ResBlock3x3@128s1 & 28x28x64\\
-%			1 x ResBlock3x3@256s2 & 14x14x128\\
-%			2 x ResBlock3x3@256s1 & 14x14x128\\
-%			1 x ResBlock3x3@512s2 & 7x7x256\\
-%			2 x ResBlock3x3@512s1 & 7x7x256\\
-%			AveragePool7x7s2 & 1x1x256\\
-%			\hline
-%			\hline
-%		\end{tabular}	
-%	\end{table}
 
@@
 
-%	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
-%	\begin{figure}[!t]
-%		\centering
-%		\includegraphics[width=3in]{img/lr.pdf}
-%		\caption{Representation of the learning rate decay.}
-%		\label{fig:lrdecay}
-%	\end{figure}
-
 	Both datasets are artificially balanced using data augmentation techniques~\cite{van2001art}.
@@
 However, we always save the best model, that is evaluated when the training finishes.
-
-%	\textcolor{red}{Es importante distinguir entre función de coste (usada para el ajuste de los pesos en el algoritmo de entrenamiento) y función de evaluación (usada para evaluar los modelos, en test o validación).
-Yo en esta parte describiría la de evaluación no la de coste, que debería estar descrita con el algoritmo, como hicimos en el congreso}
-%	This evaluation measure gives a higher weight to the errors that are further from the correct class.
-A similar approach to the one described in \cite{de2018weighted} is used as the loss function as it gives better performance for ordinal classification problems.
-In this case, we define the QWK loss function ($\text{QWK}_c$) as follows:
-%	\begin{equation}
-%	\nonumber
-%	\text{QWK}_c = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
-%	\end{equation}
-%	where $\text{QWK}_c \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ (estimated using the CLM structure), and $\omega_{i,j}$ are the elements of the penalization matrix.
-In this case, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, where $\omega_{i,j} \in [0,1]$.
 
@@
 The BS is not relevant for this dataset with the values considered.
-%		
-%	\begin{table}[!t]
-%		\caption{Tukey's test results for the DR dataset.}
-%		\label{table:TukeyDR}
-%		\centering
-%		\begin{tabular}{cccc}
-%			\hline\hline
-%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
-%			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
-%			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
-%			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
-%			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
-%			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
-%			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
-%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
-%			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
-%			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
-%			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
-%			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
-%			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
-%			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
-%		\end{tabular}
-%	\end{table}
 
@@
 	%	\end{table}
-%	
+
 	The results of the ANOVA III test for the Adience dataset, first, demonstrate that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$).
@@
 The results of this test over the test set are shown in Table \ref{table:Tukey}.
-
-%	\begin{table}[!t]
-%		\caption{Tukey's test results for the Adience dataset.}
-%		\label{table:TukeyAdience}
-%		\centering
-%		\begin{tabular}{cccc}
-%			\hline\hline
-%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
-%			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
-%			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
-%			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
-%			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
-%			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
-%			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
-%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
-%			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
-%			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
-%			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
-%			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
-%			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
-%			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
-%			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
-%			       64         &        128        &  $-0.041$  & $0.026$ \\
-%			                  &        256        &  $-0.027$  & $0.000$ \\
-%			       128        &        64         &  $0.041$   & $0.026$ \\
-%			                  &        256        &  $0.014$   & $0.000$ \\
-%			       256        &        64         &  $0.027$   & $0.000$ \\
-%			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
-%		\end{tabular}
-%	\end{table}
 
@@
 
-%	\begin{table}[!t]
-%		\caption{Comparison between the best results of nominal, ordinal and previous works for the DR dataset.}
-%		\label{table:ComparisonDR}
-%		\scriptsize
-%		\centering
-%		\def\arraystretch{1.3}
-%		\begin{tabular}{lccc}
-%			\hline
-%			\hline
-%			Method                                   & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-%			Ordinal network                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
-%			Nominal network                          &    $0.498_{(0.013)}$    &    $0.692_{(0.014)}$    &        $0.854_{(0.006)}$         \\
-%			J. Torre et al. \cite{de2018weighted}    &  $0.537_{(\text{-})}$   &            -            &                -                 \\
-%			À. Nebot et al. \cite{nebot2016diabetic} &  $0.555_{(\text{-})}$   &            -            &                -					\\
-%			\hline
-%			\hline
-%		\end{tabular}
-%	\end{table}
-%	
-%	\begin{table}[!t]
-%		\caption{Comparison between the best results of nominal, ordinal and previous works for the Adience dataset.}
-%		\label{table:ComparisonAdience}
-%		\scriptsize
-%		\centering
-%		\def\arraystretch{1.3}
-%		\begin{tabular}{lccc}
-%			\hline\hline
-%			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-%			Ordinal network                           &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
-%			Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
-%			Beckham et al. \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
-%			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
-%			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
-%			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
-%		\end{tabular}
-%	\end{table}
-
 	\begin{table}[!t]

### 2019-05-24 activations.py

@@ -332,6 +332,8 @@ class CLM(keras.layers.Layer):
 			dist1 = distributions.Normal(loc=0., scale=v)
 			dist2 = distributions.Normal(loc=v, scale=K.pow(v, 2))
 			a3T = dist1.cdf(u) - K.exp(-u + K.pow(v, 2) / 2 + K.log(dist2.cdf(u)))
+		elif self.link_function == 'ggamma':
+			a3T = igamma(self.p['d'] / self.p['p'], K.pow((z3 / self.p['a']), self.p['p'])) / K.exp(lgamma(self.p['d'] / self.p['p']))
 		else:
 			a3T = 1.0 / (1.0 + K.exp(-z3))
 
@@ -388,6 +390,10 @@ class CLM(keras.layers.Layer):
 			self.mu = self.add_weight('mu_nnpom', shape=(1,), initializer=keras.initializers.Constant(0.0))
 			self.sigma = self.add_weight('sigma_nnpom', shape=(1,), initializer=keras.initializers.Constant(1.0))
 			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=keras.initializers.Constant(1.0))
+		elif self.link_function == 'ggamma':
+			self._set_default_param('a', self.add_weight('a_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
+			self._set_default_param('d', self.add_weight('d_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
+			self._set_default_param('p', self.add_weight('p_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
 
 
 	def call(self, x):
@@ -396,3 +402,7 @@ class CLM(keras.layers.Layer):
 
 	def compute_output_shape(self, input_shape):
 		return (input_shape[0], 1)
+
+	def _set_default_param(self, param, value):
+		if not param in self.p:
+			self.p[param] = value

### 2019-05-24 inception_resnet_v2.py

@@ -134,6 +134,7 @@ def inception_resnet_block(x, scale, block_type, block_idx, activation='relu'):
         ValueError: if `block_type` is not one of `'block35'`,
             `'block17'` or `'block8'`.
     """
+
     if block_type == 'block35':
         branch_0 = conv2d_bn(x, 32, 1)
         branch_1 = conv2d_bn(x, 32, 1)
@@ -175,7 +176,6 @@ def inception_resnet_block(x, scale, block_type, block_idx, activation='relu'):
                       arguments={'scale': scale},
                       name=block_name)([x, up])
     if activation is not None:
-        x = layers.Activation(activation, name=block_name + '_ac')(x)
         if type(activation) is str:
             x = layers.Activation(activation, name=block_name + '_ac')(x)
         else:
@@ -184,6 +184,7 @@ def inception_resnet_block(x, scale, block_type, block_idx, activation='relu'):
 
 from keras import utils as keras_utils
 from keras import backend, layers, models
+from keras.engine.topology import get_source_inputs
 
 def InceptionResNetV2(include_top=True,
                       weights='imagenet',
@@ -353,7 +354,7 @@ def InceptionResNetV2(include_top=True,
     # Ensure that the model takes into account
     # any potential predecessors of `input_tensor`.
     if input_tensor is not None:
-        inputs = keras_utils.get_source_inputs(input_tensor)
+        inputs = get_source_inputs(input_tensor)
     else:
         inputs = img_input
 

### 2019-05-24 net_keras.py

@@ -185,21 +185,26 @@ class Net:
 		return model
 
 	def inception_resnet_v2_custom(self):
-		model = keras.Sequential()
-		inception = Irnv2(include_top=False, input_shape=(self.size, self.size, self.num_channels),
-						  classes=self.num_classes, pooling='avg', activation=self.__get_activation())
+		input = keras.layers.Input(shape=(self.size, self.size, self.num_channels))
+		x = input
+		# Required size >= 75 x 75
+		size = self.size
+		if size < 75:
+			size = 75
+			x = keras.layers.ZeroPadding2D(padding=(75-self.size) // 2 + 1)(x)
 
-		# for layer in inception.layers:
-		# 	layer.trainable = False
+		x = Irnv2(input_tensor=x, include_top=False, input_shape=(size, size, self.num_channels),
+						  classes=self.num_classes, pooling='avg', activation=self.__get_activation())(x)
 
-		model.add(inception)
-		model.add(keras.layers.Flatten())
-		model.add(keras.layers.Dense(512))
+		x = keras.layers.Dense(512)(x)
 
 		if self.dropout > 0:
-			model.add(keras.layers.Dropout(rate=self.dropout))
+			x = keras.layers.Dropout(rate=self.dropout)(x)
 
-		model = self.__add_activation(model)
+		x = keras.layers.Dense(self.num_classes)(x)
+		x = keras.layers.Activation(self.final_activation)(x)
+
+		model = keras.models.Model(input, x)
 
 		return model
 
@@ -295,10 +300,10 @@ class Net:
 			model.add(keras.layers.Dense(1))
 			model.add(keras.layers.BatchNormalization())
 			model.add(CLM(self.num_classes, 'cauchit', self.f_a_params, use_tau=self.use_tau))
-		elif self.final_activation == 'clmgamma':
+		elif self.final_activation == 'clmggamma':
 			model.add(keras.layers.Dense(1))
 			model.add(keras.layers.BatchNormalization())
-			model.add(CLM(self.num_classes, 'lgamma', self.f_a_params, use_tau=self.use_tau))
+			model.add(CLM(self.num_classes, 'ggamma', self.f_a_params, use_tau=self.use_tau))
 		elif self.final_activation == 'clmgauss':
 			model.add(keras.layers.Dense(1))
 			model.add(keras.layers.BatchNormalization())

### 2019-05-24 activations.py
Functional API

@@ -391,9 +391,9 @@ class CLM(keras.layers.Layer):
 			self.sigma = self.add_weight('sigma_nnpom', shape=(1,), initializer=keras.initializers.Constant(1.0))
 			self.lmbd = self.add_weight('lambda_nnpom', shape=(1,), initializer=keras.initializers.Constant(1.0))
 		elif self.link_function == 'ggamma':
-			self._set_default_param('a', self.add_weight('a_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
-			self._set_default_param('d', self.add_weight('d_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
-			self._set_default_param('p', self.add_weight('p_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
+			self.__set_default_param('a', self.add_weight('a_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
+			self.__set_default_param('d', self.add_weight('d_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
+			self.__set_default_param('p', self.add_weight('p_clm', shape=(1,), initializer=keras.initializers.Constant(0.5)))
 
 
 	def call(self, x):
@@ -403,6 +403,6 @@ class CLM(keras.layers.Layer):
 	def compute_output_shape(self, input_shape):
 		return (input_shape[0], 1)
 
-	def _set_default_param(self, param, value):
+	def __set_default_param(self, param, value):
 		if not param in self.p:
 			self.p[param] = value

### 2019-05-24 net_keras.py

@@ -1,5 +1,6 @@
 import keras
-from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, CLM, RReLu, PELU, SlopedReLU, PTELU
+from activations import SPP, parametric_softplus, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, CLM, RReLu, \
+	PELU, SlopedReLU, PTELU
 from layers import GeometricLayer
 from resnet import Resnet_2x4
 
@@ -8,7 +9,8 @@ from unimodal_extensions import _add_binom_m
 
 
 class Net:
-	def __init__(self, size, activation, final_activation, f_a_params={}, use_tau=True, prob_layer=None, num_channels=3, num_classes=5, spp_alpha=0.2, dropout=0):
+	def __init__(self, size, activation, final_activation, f_a_params={}, use_tau=True, prob_layer=None, num_channels=3,
+				 num_classes=5, spp_alpha=0.2, dropout=0):
 		self.size = size
 		self.activation = activation
 		self.final_activation = final_activation
@@ -27,65 +29,65 @@ class Net:
 		model = keras.models.Sequential([
 			# Block 1
 			keras.layers.Conv2D(64, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same',
-								   input_shape=(self.size, self.size, self.num_channels), data_format='channels_last'),
-			self.__get_activation(),
+								input_shape=(self.size, self.size, self.num_channels), data_format='channels_last'),
+			self.__activation(),
 			keras.layers.BatchNormalization(),
 			keras.layers.Conv2D(64, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
-			self.__get_activation(),
+			self.__activation(),
 			keras.layers.BatchNormalization(),
 			keras.layers.MaxPooling2D(),
 
 			# Block 2
 			keras.layers.Conv2D(128, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
-			self.__get_activation(),
+			self.__activation(),
 			keras.layers.BatchNormalization(),
 			keras.layers.Conv2D(128, 3, strides=(1, 1), kernel_initializer='he_uniform', padding='same', ),
-			self.__get_activation(),
+			self.__activation(),
 			keras.layers.BatchNormalization(),
 			keras.layers.MaxPooling2D(),
 
[…]

### 2019-05-24 resnet.py

@@ -97,9 +97,9 @@ def _resnet_2x4(l_in, nf=(32, 64, 128, 256), N=2, activation='relu'):
 	# layer = AveragePooling2D(pool_size=int(layer.get_shape()[-1]), strides=1, padding='valid')(layer)
 	layer = GlobalAveragePooling2D(data_format='channels_last')(layer)
 
-	layer = Flatten()(layer)
+	# layer = Flatten()(layer)
 
-	model = Sequential([Model(l_in, layer, name='resnet2x4')])
+	model = Model(l_in, layer, name='resnet2x4')
 
 	return model
 

### 2019-05-29 paper/ieee.tex
Paper, wiki

@@
 
-	\author{Víctor-Manuel~Vargas, Pedro-Antonio~Gutiérrez and César~Hervás}
+	\author{Víctor-Manuel~Vargas, Pedro-Antonio~Gutiérrez,~\IEEEmembership{Senior~Member,~IEEE,} and César~Hervás-Mart\'inez,~\IEEEmembership{Senior~Member,~IEEE}}
 
@@
 	% The paper headers
-	\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-	{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+	\markboth{}%
+	{}
 	% The only time the second header will appear is for the odd numbered pages
@@
 Three different link functions are studied in the experimental study, and the results are contrasted with statistical analysis.
-The experiments run over two different ordinal classification problems and the statistical tests confirm that these models improve the results of a nominal model and outperform other proposals considered in the literature.
+The experiments run over two different ordinal classification problems, and the statistical tests confirm that these models improve the results of a nominal model and outperform other proposals considered in the literature.
 	\end{abstract}
@@
 	\begin{IEEEkeywords}
-		Deep learning, ordinal regression, cumulative link models.
+		Deep learning, ordinal regression, cumulative link models, Kappa index.
 	\end{IEEEkeywords}
@@
 	% and "HIS" in caps to complete the first word.
-	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
+	\IEEEPARstart{D}{eep learning}, introduced by Lecun~et al.
+\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
 These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly,jin2018deep}.
@@
 
-	In this paper, we propose the use of CLMs for deriving deep learning ordinal classifiers.
+	In this paper, we propose the use of CLMs for deriving deep learning ordinal classifiers\footnote{The source code is available at \url{https://github.com/ayrna/deep-ordinal-clm}.}.
 In the case of CNNs, the model projection used by the threshold model can be obtained from the last layer of the network.
@@
 	%\textbf{(Métrica ordinal (MAE))}
-	M.
 	ALALI et al.
@@
 
-	Z.
 	Niu et al.
@@
 
-	H.
 	Li et al.
@@
 
-	Y.
 	Liu et al.
@@
 
-	S.
 	Chen et al.
@@
 
-	J.
 	de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the quadratic weighted kappa (QWK) metric as loss function for the optimization algorithm.
@@
 
-	A.
 	Rios et al.
@@
 
-	H.
 	Fu et al.
@@
 
-	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.
-
-	Y.
+	Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.
+
 	Liu et al.
@@
 
-	C.
-Beckham and C.
-Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
+	Beckham and Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions.
 The parameters of these distributions were learnt by using a deep neural network.
@@
 Adience dataset has been used in other works for human age estimation but most of them solved the problem as a multi-class problem instead of using the ordinal relation between classes.
-E.
-Eidinger \cite{eidinger2014age} presented an approach using support vector machines and neural networks.
-J.-C.
-Chen \cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep CNNs.
-G.
-Levi \cite{levi2015age} presented another convolutional network model for age estimation, while Beckham \cite{beckham2017unimodal} proposed a straightforward method to constrain discrete ordinal probability distributions to be unimodal.
+Eidinger et al.
+\cite{eidinger2014age} presented an approach using support vector machines and neural networks.
+Chen et al.
+\cite{chen2016cascaded} proposed a coarse-to-fine strategy for deep CNNs.
+Levi and Hassner \cite{levi2015age} presented another convolutional network model for age estimation.
+As previously discussed, Beckham and Pal \cite{beckham2017unimodal} proposed a straightforward method to constrain discrete probability distributions to be unimodal.
 
@@
 			\hline\hline
-			\multicolumn{2}{c}{\textbf{Diabetic Retinopathy}} & \multicolumn{2}{c}{\textbf{Adience}}\\
-			\hline
+			\multicolumn{2}{c}{\textbf{Diabetic Retinopathy}} & \multicolumn{2}{c}{\textbf{Adience}}  \\ \hline
 			\textbf{Layer}  &         \textbf{Output}         & \textbf{Layer}      & \textbf{Output} \\ \hline
-			2 Conv3x3@32s1  &   252x252x32    & Conv7x7@32s2        &   112x112x32    \\
-			MaxPool2x2s2    &   126x126x32    & MaxPool3x3s2        &    55x55x32     \\
-			2 Conv3x3@64s1  &   122x122x64    & 2 ResBlock3x3@64s1  &    55x55x32     \\
-			MaxPool2x2s2    &    61x61x64     & ResBlock3x3@128s2   &    28x28x64     \\
-			2 Conv3x3@128s1 &    57x57x128    & 2 ResBlock3x3@128s1 &    28x28x64     \\
-			MaxPool2x2s2    &    28x28x128    & 1 ResBlock3x3@256s2 &    14x14x128    \\
-			2 Conv3x3@128s1 &    24x24x128    & 2 ResBlock3x3@256s1 &    14x14x128    \\
-			MaxPool2x2s2    &   12x12x128\    & 1 ResBlock3x3@512s2 &     7x7x256     \\
-			Conv4x4@128s1   &     9x9x128     & 2 ResBlock3x3@512s1 &     7x7x256     \\
+			2 Conv3x3@32s1  &           124x124x32            & Conv7x7@32s2        &   112x112x32    \\
+			MaxPool2x2s2    &            62x62x32             & MaxPool3x3s2        &    55x55x32     \\
+			2 Conv3x3@64s1  &            58x58x64             & 2 ResBlock3x3@64s1  &    55x55x32     \\
+			MaxPool2x2s2    &            29x29x64             & ResBlock3x3@128s2   &    28x28x64     \\
+			2 Conv3x3@128s1 &            25x25x128            & 2 ResBlock3x3@128s1 &    28x28x64     \\
+			MaxPool2x2s2    &            12x12x128            & 1 ResBlock3x3@256s2 &    14x14x128    \\
+			2 Conv3x3@128s1 &             8x8x128             & 2 ResBlock3x3@256s1 &    14x14x128    \\
+			MaxPool2x2s2    &             4x4x128             & 1 ResBlock3x3@512s2 &     7x7x256     \\
+			Conv4x4@128s1   &             1x1x128             & 2 ResBlock3x3@512s1 &     7x7x256     \\
 			                &                                 & AveragePool7x7s2    &     1x1x256     \\ \hline\hline
@@
 Correct Classification Rate (CCR) or standard accuracy is the most common metric for classification tasks and shows the percentage of correctly classified samples.
-We also include Top-2 CCR \cite{beckham2017unimodal} and Top-3 CCR \cite{beckham2017unimodal}, which are similar to CCR, but they take a prediction as correct when the real class is between the two or three classes, respectively, with the highest probability.
+We also include Top-2 CCR and Top-3 CCR \cite{beckham2017unimodal}, which are similar to CCR, but they take a prediction as correct when the real class is between the two or three classes, respectively, with the highest probability.
 
@@
 
+	In order to ease reproducibility, the source code is available in a public repository\footnote{\url{https://github.com/ayrna/deep-ordinal-clm}}.
 	\subsection{Factors}
@@
 			       256        &        64         &  $0.027$   &      $0.000$       &     -      &            -            \\
-			                  &        128        &  $-0.014$  &      $0.000$       &     -      &            -
+			                  &        128        &  $-0.014$  &      $0.000$       &     -      &            -\\\hline\hline
 		\end{tabular}}
@@
 	To sum up, the results showed that the best parameter configuration depends on the problem that is being solved.
-The optimal value for the batch size and the optimal LF are not the same for Retinopathy and Adience datasets.
-These results highlight the importance of adjusting the hyper-parameters for each problem instead of trying to find an optimal configuration for all the datasets.
+The \texttt{clog-log} function offers the best results in DR dataset while the \texttt{logit} link is the best option for the Adience dataset.
 However, the best LR for both datasets were $10^{-3}$.
@@
 Finally, there are more interactions between the three factors for the Adience dataset than for DR.
-This highlights the importance of making experimental designs associated with each dataset to determine the best value for each factor.
+These results highlight the importance of adjusting the hyper-parameters for each problem instead of trying to find an optimal configuration for all the datasets.
 
@@
 All the results are given for the test set, except those from \cite{de2018weighted} (DR dataset), because the authors only provided validation results for $128\times 128$ images (however, validation results are usually better than test results).
-The results for \cite{beckham2017unimodal} were obtained by reproducing their experiments because they didn't provide exact results for test set that could be used to compare with our results.
-The proposed ordinal model outperforms all the other alternatives in terms of QWK.
+The results for \cite{beckham2017unimodal} were obtained by reproducing their experiments because they did not provide the results for test set.
+As can be checked, the proposed ordinal model outperforms all the other alternatives in terms of QWK.
 
@@
 	\begin{table}[!t]
-		\caption{Comparison between the best results of nominal, ordinal and previous works for the both datasets.}
+		\caption{Comparison between the best results of the CLM network, a nominal network (using softmax and cross-entropy) and previous works for both datasets.}
 		\label{table:Comparison}
@@
 			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-			Ordinal network                           &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
+			CLM network (proposal)                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
 			Nominal network                           &    $0.498_{(0.013)}$    &    $0.692_{(0.014)}$    &        $0.854_{(0.006)}$         \\
-			J. Torre et al. \cite{de2018weighted}     &  $0.537_{(\text{-})}$   &            -            &                -                 \\
-			À. Nebot et al. \cite{nebot2016diabetic}  &  $0.555_{(\text{-})}$   &            -            &                -                 \\
+			de la Torre et al. \cite{de2018weighted}     &  $0.537_{(\text{-})}$   &            -            &                -                 \\
+			Nebot et al. \cite{nebot2016diabetic}  &  $0.555_{(\text{-})}$   &            -            &                -                 \\
 			\hline
@@
 			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-			Ordinal network                           &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
+			CLM network (proposal)                          &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
 			Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
-			Beckham et al. \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
-			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
-			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
-			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
+			Beckham and Pal \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
+			Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
+			Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
+			Levi and Hassner \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
 		\end{tabular}
@@
 	\label{sect:conclusions} 
-
 	This paper introduces a new deep ordinal network based on combining CLM models with a continuous QWK loss function.
@@
 Also, it is able to reduce the chance that the model gets stuck when training with some parameter configurations.
-
-	Moreover, we also conclude that the optimal values for the different parameters considered are problem-dependant.
-The \texttt{clog-log} function offers the best results in DR dataset while the \texttt{logit} link is the best option for the Adience dataset.
-The best value for the learning rate parameter for both datasets is $\eta = 10^{-3}$.
-It can be considered a good value when training the model with new datasets.
-Both datasets have obtained the best performance with an intermediate BS: 10 for DR and 128 for Adience.
+We conclude that the optimal values for the different parameters considered are problem-dependant.
 The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
-
 In summary, the most significant contributions of the model proposal are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention from over-fitting and stagnation.
@@
 	%
+
+% use section* for acknowledgement
+\section*{Acknowledgment}
+This work has been partially subsidised by the TIN2017-85887-C2-1-P and TIN2017-90567-REDT projects of the Spanish Ministry of Economy and Competitiveness (MINECO), and FEDER funds of the European Union.
 
@@
 	% that's all folks
+
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{img/bio/VVargas.png}}]{Víctor Manuel Vargas} was born in Córdoba, Spain.
+He received the degree of Computer Engineering from the University of Córdoba, Spain, in 2018.
+He is currently studying a master's degree at the International University of Menéndez Pelayo, Spain.
+He is a member of the AYRNA group of the Department of Computer Science and Numerical Analysis of the University of Córdoba.
+His current research interests include deep neural networks and their applications to image classification on ordinal problems.
+
+	\end{IEEEbiography}
+
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{img/bio/PAGutierrez.png}}]{Pedro Antonio Gutiérrez}  (M'07-SM'15) received the B.S.
+degree in computer science from the University of Sevilla (Spain) in 2006, and the Ph.D.
+degree in computer science and artificial intelligence from the University of Granada (Spain) in 2009.
+He is currently an Assistant Professor with the Department of Computer Science and Numerical Analysis, University of Córdoba (Spain).
+		His research interests are in the areas of supervised learning, evolutionary artificial neural networks, ordinal classification and the application of these techniques to different real world problems, including precision agriculture, renewable energy, climatology and biomedicine, among others.
+He serves on the Editorial board for the journals \textit{IEEE Transaction on Neural Networks and Learning Systems} and \textit{Progress in Artificial Intelligence} and on the organization/program committees of several computational intelligence conferences.
+	\end{IEEEbiography}
+
+	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{img/bio/CHervas.png}}]{César Hervás-Martínez}  (M'07-SM'14) was born in Cuenca, Spain.
+He received the B.S.
+degree in statistics and operations research from the Universidad Complutense de Madrid, Madrid, Spain, in 1978, and the Ph.D.
+degree in mathematics from the University of Seville, Seville, Spain, in 1986.
+	He is currently a Professor of Computer Science and Artificial Intelligence with the Department of Computer Science and Numerical Analysis, University of Córdoba, Córdoba, Spain, and an Associate Professor with the Department of Mathematics and Engineering, Loyola University Andalucía, Spain.
+His current research interests include neural networks, evolutionary computation, and the modelling of natural systems.
+	\end{IEEEbiography}
+%	
+%	
+%	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{CHervas.png}}]{C\'{e}sar Herv\'{a}s-Mart\'{i}nez} was born in Cuenca, Spain.
+He received his B.S.
+degree in Statistics and Operation Research from the Universidad Complutense, Madrid, Spain, in 1978, and his Ph.D.
+degree in Mathematics from the University of Seville, Seville, Spain, in 1986.
+He is a Professor at the University of C\'{o}rdoba in the Department of Computer Science and Numerical Analysis, in the area of Computer Science and Artificial Intelligence, and an Associate Professor in the Department of Quantitative Methods in the School of Economics.
+His current research interests include neural networks, evolutionary computation, and the modelling of natural systems.
+%	\end{IEEEbiography}
+
 \end{document}

### 2019-05-29 experiment.py

@@ -751,22 +751,11 @@ class Experiment:
 		if db.lower() == 'retinopathy':
 			return "../retinopathy/128/train", "../retinopathy/128/val", "../retinopathy/128/test"
 			# return "../retinopathy/h5/retinopathy_128_train.h5", "../retinopathy/h5/retinopathy_128_val.h5", "../retinopathy/h5/retinopathy_128_test.h5"
-		elif db.lower() == 'retinopathy1':
-			return "../retinopathy/128/split1/train", "../retinopathy/128/split1/val", "../retinopathy/128/test"
-		elif db.lower() == 'retinopathy2':
-			return "../retinopathy/128/split2/train", "../retinopathy/128/split2/val", "../retinopathy/128/test"
-		elif db.lower() == 'retinopathy3':
-			return "../retinopathy/128/split3/train", "../retinopathy/128/split3/val", "../retinopathy/128/test"
-		elif db.lower() == 'retinopathy4':
-			return "../retinopathy/128/split4/train", "../retinopathy/128/split4/val", "../retinopathy/128/test"
-		elif db.lower() == 'retinopathy5':
-			return "../retinopathy/128/split5/train", "../retinopathy/128/split5/val", "../retinopathy/128/test"
 		elif db.lower() == 'retinopathytoy':
 			return "../retinopathy/h5/retinopathytoy_128_train.h5", "../retinopathy/h5/retinopathytoy_128_val.h5", "../retinopathy/h5/retinopathytoy_128_test.h5"
 		elif db.lower() == 'retinopathy256':
 			return "../retinopathy/256/train", "../retinopathy/256/val", "../retinopathy/256/test"
 		elif db.lower() == 'adience':
-			# return "../adience/256/train", "../adience/256/val", "../adience/256/test"
 			return "../adience/adience_train_256.h5", "../adience/adience_val_256.h5", "../adience/adience_test_256.h5"
 		elif db.lower() == 'cifar10_128':
 			return "../cifar10/cifar10_128_train.h5", "../cifar10/cifar10_128_val.h5", "../cifar10/cifar10_128_test.h5"
@@ -774,6 +763,8 @@ class Experiment:
 			return "../cifar10/cifar10_75_train.h5", "../cifar10/cifar10_75_val.h5", "../cifar10/cifar10_75_test.h5"
 		elif db.lower() == 'cifar10' or db.lower() == 'cifar100':
[…]

### 2019-10-04 paper/elsarticle-template.tex
Paper neurocomputing

--- 2019-05-29 paper/ieee.tex
@@
-% !TeX spellcheck = en_GB
-
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***
-% The testflow support page is at:                                        ***
-% http://www.michaelshell.org/tex/testflow/                               ***
-
-\documentclass[journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-% declare the path(s) where your graphic files are
-% \graphicspath{{../pdf/}{../jpeg/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
-% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-% will default to the driver specified in the system graphics.cfg if no
-% driver is specified.
-% \usepackage[dvips]{graphicx}
-% declare the path(s) where your graphic files are
-% \graphicspath{{../eps/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
-% \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
+\documentclass[preprint]{elsarticle}
+
+\usepackage{lineno,hyperref}
+%\usepackage[pdftex]{graphicx}
 \usepackage{amsmath}
 \usepackage{mathrsfs}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
 \usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
 \usepackage[utf8]{inputenc}
-
-%\usepackage[backend=bibtex, style=ieee]{biblatex}
-
 \usepackage{lmodern}
-
 \usepackage{dsfont}
 \usepackage{amssymb}
-
 \usepackage{color}
-
-%\usepackage{ulem}
-
 \usepackage{array,booktabs}
-
-\usepackage[bookmarks=false]{hyperref}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor mi-ni-mi-zes des-cri-bed di-ffe-rent sig-ni-fi-can-ce}
-
-%\addbibresource{main.bib}
-
-%\renewcommand{\bibfont}{\footnotesize}
+%\usepackage[bookmarks=false]{hyperref}
+
+\modulolinenumbers[5]
+
+\journal{Neurocomputing}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{document}
-	%
-	% paper title
-	% Titles are generally capitalized except for words such as a, an, and, as,
-	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-	% not capitalized unless they are the first or last word of the title.
-	% Linebreaks \\ can be used within to get better formatting as desired.
-	% Do not put math or special symbols in the title.
+
+\begin{frontmatter}
+
 \title{Deep ordinal classification based on cumulative link models}
-	%
-	%
-	% author names and IEEE memberships
-	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-	% a structure at a ~ so this keeps an author's name from being broken across
-	% two lines.
-	% use \thanks{} to gain access to the first footnote area
-	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-	% was not built to handle multiple paragraphs
-	%
-
-	\author{Víctor-Manuel~Vargas, Pedro-Antonio~Gutiérrez,~\IEEEmembership{Senior~Member,~IEEE,} and César~Hervás-Mart\'inez,~\IEEEmembership{Senior~Member,~IEEE}}
-
-	% note the % following the last \IEEEmembership and also \thanks - 
-	% these prevent an unwanted space from occurring between the last author name
-	% and the end of the author line. i.e., if you had this:
-	% 
-	% \author{....lastname \thanks{...} \thanks{...} }
-	%                     ^------------^------------^----Do not want these spaces!
-	%
-	% a space would be appended to the last name and could cause every name on that
-	% line to be shifted left slightly. This is one of those "LaTeX things". For
-	% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-	% "AB" then you have to do: "\textbf{A}\textbf{B}"
-	% \thanks is no different in this regard, so shield the last } of each \thanks
-	% that ends a line with a % and do not let a space in before the next \thanks.
-	% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-	% you are supposed to have spaces between the names. For what it is worth,
-	% this is a minor point as most people would not even notice if the said evil
-	% space somehow managed to creep in.
-
-	% The paper headers
-	\markboth{}%
-	{}
-	% The only time the second header will appear is for the odd numbered pages
-	% after the title page when using the twoside option.
-	% 
-	% *** Note that you probably will NOT want to include the author's ***
-	% *** name in the headers of peer review papers.                   ***
-	% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-	% you desire.
-
-	% If you want to put a publisher's ID mark on the page you can do it like
-	% this:
-	%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-	% Remember, if you use this you must call \IEEEpubidadjcol in the second
-	% column for its text to clear the IEEEpubid mark.
-
-	% use for special paper notices
-	%\IEEEspecialpapernotice{(Invited Paper)}
-
-	% make the title area
-	\maketitle
-
-	% As a general rule, do not put math, special symbols or citations
-	% in the abstract or keywords.
+
+\author{V\'ictor Manuel Vargas}
+\author{Pedro Antonio Guti\'errez}
+\author{C\'esar Herv\'as Mart\'inez}
+\address{Department of Computer Science and Numerical Analysis, University of C\'ordoba, C\'ordoba, Spain}
+
 \begin{abstract}
@@
 
-	% Note that keywords are not normally used for peerreview papers.
-	\begin{IEEEkeywords}
-		Deep learning, ordinal regression, cumulative link models, Kappa index.
-	\end{IEEEkeywords}
-
-	% For peer review papers, you can put extra information on the cover
-	% page as needed:
-	% \ifCLASSOPTIONpeerreview
-	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-	% \fi
-	%
-	% For peerreview papers, this IEEEtran command inserts a page break and
-	% creates the second title. It will be ignored for other modes.
-	\IEEEpeerreviewmaketitle
+\begin{keyword}
+Deep learning\sep ordinal regression\sep cumulative link models\sep Kappa index.
+\end{keyword}
+
+\end{frontmatter}
+
+%\linenumbers
 
@@
 \label{sect:introduction}
-	% The very first letter is a 2 line initial drop letter followed
-	% by the rest of the first word in caps.
-	% 
-	% form to use if the first word consists of a single letter:
-	% \IEEEPARstart{A}{demo} file is ....
-	% 
-	% form to use if you need the single drop letter followed by
-	% normal text (unknown if ever used by the IEEE):
-	% \IEEEPARstart{A}{}demo file is ....
-	% 
-	% Some journals put the first two words in caps:
-	% \IEEEPARstart{T}{his demo} file is ....
-	% 
-	% Here we have the typical use of a "T" for an initial drop letter
-	% and "HIS" in caps to complete the first word.
-	\IEEEPARstart{D}{eep learning}, introduced by Lecun~et al.
+Deep learning, introduced by Lecun~et al.
 \cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
@@
 
-	Li et al.
-\cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease as multiple binary sub-problems.
+Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease as multiple binary sub-problems.
 
@@
 
-	de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the quadratic weighted kappa (QWK) metric as loss function for the optimization algorithm.
+De la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the quadratic weighted kappa (QWK) metric as loss function for the optimization algorithm.
 They compared this cost function against the traditional log-loss function using three different datasets, including the Diabetic Retinopathy database as the most complex one.
@@
 Also, they checked the importance of hyper-parameter tuning.
+Later, in 2019, they published another work \cite{de2019deep} related to the Diabetic Retinopathy dataset where they combined the QWK loss function with the use of images of a higher resolution and new dataset partitions with many more samples on the training split.
+They achieved a proper classification score.
+Still, they tested the classifier against a tiny testing set compared to the original one from the Kaggle competition (around $12\%$ of the samples for testing against $60\%$ on the initial dataset splits).
+Further comparisons with this work are not possible as they didn't provide the dataset splits along with the paper.
 
@@
 Unlike \texttt{logit} and \texttt{probit}, the \texttt{clog-log} link is asymmetrical.
-In this way, when the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate, while \texttt{clog-log} can lead to better results.
+In this way, when the distribution of the given data is not symmetric in the $[0,1]$ interval and increase slowly at small to moderate value but increases sharply near 1, the \texttt{logit} and \texttt{probit} models are inappropriate, while \texttt{clog-log} can lead to better results.
 
@@
 \end{equation}
-	where $b_1$ and $\alpha_q$ are the learnable parameters, and $Q$ is the number of classes.
+where $b_1$ is a learning parameter corresponding to the first threshold, $\alpha_q$ is a learnable vector of parameters used to obtain the rest of the thresholds, and $Q$ is the number of classes.
 
@@
 	\begin{tabular}{cccc}
-			\includegraphics[width=1.6cm]{img/retinopathy/1.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/2.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/3.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/4.jpg}\\
-			\includegraphics[width=1.6cm]{img/retinopathy/5.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/6.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/7.jpg} & \includegraphics[width=1.6cm]{img/retinopathy/8.jpg}
+		\includegraphics[width=2.4cm]{img/retinopathy/1.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/2.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/3.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/4.jpg}\\
+		\includegraphics[width=2.4cm]{img/retinopathy/5.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/6.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/7.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/8.jpg}
 	\end{tabular}						
@@
 	\begin{tabular}{cccc}
-				\includegraphics[width=1.6cm]{img/adience/1.jpg} & \includegraphics[width=1.6cm]{img/adience/2.jpg} & \includegraphics[width=1.6cm]{img/adience/3.jpg} & \includegraphics[width=1.6cm]{img/adience/4.jpg}\\
-				\includegraphics[width=1.6cm]{img/adience/5.jpg} & \includegraphics[width=1.6cm]{img/adience/6.jpg} & \includegraphics[width=1.6cm]{img/adience/7.jpg} & \includegraphics[width=1.6cm]{img/adience/8.jpg}
+		\includegraphics[width=2.4cm]{img/adience/1.jpg} & \includegraphics[width=2.4cm]{img/adience/2.jpg} & \includegraphics[width=2.4cm]{img/adience/3.jpg} & \includegraphics[width=2.4cm]{img/adience/4.jpg}\\
+		\includegraphics[width=2.4cm]{img/adience/5.jpg} & \includegraphics[width=2.4cm]{img/adience/6.jpg} & \includegraphics[width=2.4cm]{img/adience/7.jpg} & \includegraphics[width=2.4cm]{img/adience/8.jpg}
 	\end{tabular}						
@@
 	\centering
-		\resizebox{\columnwidth}{!}{
+	\footnotesize
 	\begin{tabular}{lclc}
@@
 		                &                                 & AveragePool7x7s2    &     1x1x256     \\ \hline\hline
-		\end{tabular}}	
+	\end{tabular}	
 \end{table}
@@
 	\centering
-		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
-			\hline
-			\hline
-			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-			5 & \texttt{clog-log} & $10^{-2}$ & $0.414_{(0.057)}$ & $0.075_{(0.042)}$ & $0.177_{(0.023)}$ & $0.556_{(0.057)}$ & $0.833_{(0.042)}$ & $0.968_{(0.011)}$ & $0.816_{(0.021)}$\\
-			5 & \texttt{clog-log} & $10^{-3}$ & $0.534_{(0.027)}$ & $0.102_{(0.011)}$ & $0.137_{(0.006)}$ & $0.658_{(0.015)}$ & $0.871_{(0.011)}$ & $0.966_{(0.003)}$ & $0.852_{(0.002)}$\\
-			5 & \texttt{clog-log} & $10^{-4}$ & $0.520_{(0.006)}$ & $0.067_{(0.008)}$ & $0.123_{(0.003)}$ & $0.697_{(0.006)}$ & $0.842_{(0.008)}$ & $0.961_{(0.003)}$ & $0.851_{(0.002)}$\\
-			5 & \texttt{logit} & $10^{-2}$ & $0.416_{(0.041)}$ & $0.095_{(0.029)}$ & $0.175_{(0.021)}$ & $0.563_{(0.054)}$ & $0.762_{(0.040)}$ & $0.908_{(0.026)}$ & $0.807_{(0.029)}$\\
-			5 & \texttt{logit} & $10^{-3}$ & $0.554_{(0.013)}$ & $0.093_{(0.009)}$ & $0.137_{(0.003)}$ & $0.660_{(0.008)}$ & $0.802_{(0.005)}$ & $0.936_{(0.004)}$ & $0.853_{(0.005)}$\\
-			5 & \texttt{logit} & $10^{-4}$ & $0.520_{(0.003)}$ & $0.063_{(0.004)}$ & $0.122_{(0.002)}$ & $0.706_{(0.005)}$ & $0.823_{(0.004)}$ & $0.949_{(0.003)}$ & $0.862_{(0.003)}$\\
-			5 & \texttt{probit} & $10^{-2}$ & $0.460_{(0.048)}$ & $0.079_{(0.046)}$ & $0.197_{(0.064)}$ & $0.504_{(0.167)}$ & $0.808_{(0.034)}$ & $0.927_{(0.073)}$ & $0.689_{(0.240)}$\\
-			5 & \texttt{probit} & $10^{-3}$ & $0.564_{(0.018)}$ & $0.099_{(0.013)}$ & $0.147_{(0.018)}$ & $0.636_{(0.045)}$ & $0.822_{(0.040)}$ & $0.939_{(0.020)}$ & $0.840_{(0.015)}$\\
-			5 & \texttt{probit} & $10^{-4}$ & $0.523_{(0.005)}$ & $0.067_{(0.012)}$ & $0.122_{(0.002)}$ & $0.701_{(0.006)}$ & $0.823_{(0.002)}$ & $0.953_{(0.002)}$ & $0.860_{(0.003)}$\\
-			10 & \texttt{clog-log} & $10^{-2}$ & $0.423_{(0.239)}$ & $0.062_{(0.051)}$ & $0.127_{(0.017)}$ & $0.684_{(0.046)}$ & $\mathbf{0.894_{(0.062)}}$ & $\mathbf{0.986_{(0.012)}}$ & $0.832_{(0.020)}$\\
-			10 & \texttt{clog-log} & $10^{-3}$ & $\mathbf{0.582_{(0.016)}}$ & $0.102_{(0.006)}$ & $0.128_{(0.003)}$ & $0.680_{(0.007)}$ & $\mathit{0.880_{(0.004)}}$ & $0.972_{(0.003)}$ & $0.861_{(0.004)}$\\
-			10 & \texttt{clog-log} & $10^{-4}$ & $0.537_{(0.010)}$ & $0.064_{(0.004)}$ & $\mathit{0.116_{(0.001)}}$ & $0.717_{(0.003)}$ & $0.837_{(0.002)}$ & $0.971_{(0.001)}$ & $0.860_{(0.002)}$\\
-			10 & \texttt{logit} & $10^{-2}$ & $0.531_{(0.031)}$ & $0.107_{(0.008)}$ & $0.151_{(0.010)}$ & $0.623_{(0.025)}$ & $0.802_{(0.022)}$ & $0.934_{(0.013)}$ & $0.838_{(0.014)}$\\
-			10 & \texttt{logit} & $10^{-3}$ & $0.579_{(0.009)}$ & $0.096_{(0.012)}$ & $0.127_{(0.005)}$ & $0.686_{(0.013)}$ & $0.817_{(0.006)}$ & $0.954_{(0.005)}$ & $0.861_{(0.002)}$\\
-			10 & \texttt{logit} & $10^{-4}$ & $0.539_{(0.007)}$ & $0.074_{(0.013)}$ & $0.126_{(0.005)}$ & $0.707_{(0.010)}$ & $0.823_{(0.007)}$ & $0.957_{(0.005)}$ & $0.858_{(0.004)}$\\
-			10 & \texttt{probit} & $10^{-2}$ & $0.508_{(0.037)}$ & $0.088_{(0.044)}$ & $0.145_{(0.018)}$ & $0.639_{(0.045)}$ & $0.835_{(0.015)}$ & $0.960_{(0.008)}$ & $0.829_{(0.020)}$\\
-			10 & \texttt{probit} & $10^{-3}$ & $0.558_{(0.034)}$ & $\mathbf{0.111_{(0.005)}}$ & $0.134_{(0.003)}$ & $0.666_{(0.008)}$ & $0.831_{(0.007)}$ & $0.955_{(0.001)}$ & $0.863_{(0.003)}$\\
-			10 & \texttt{probit} & $10^{-4}$ & $0.541_{(0.010)}$ & $0.076_{(0.006)}$ & $0.119_{(0.002)}$ & $0.712_{(0.005)}$ & $0.828_{(0.003)}$ & $0.961_{(0.002)}$ & $0.862_{(0.001)}$\\
-			15 & \texttt{clog-log} & $10^{-2}$ & $0.564_{(0.016)}$ & $0.108_{(0.014)}$ & $0.143_{(0.006)}$ & $0.640_{(0.015)}$ & $0.879_{(0.011)}$ & $0.972_{(0.005)}$ & $0.851_{(0.006)}$\\
-			15 & \texttt{clog-log} & $10^{-3}$ & $0.559_{(0.026)}$ & $\mathit{0.111_{(0.008)}}$ & $0.127_{(0.004)}$ & $0.682_{(0.010)}$ & $0.871_{(0.008)}$ & $\mathit{0.974_{(0.002)}}$ & $\mathbf{0.868_{(0.002)}}$\\
-			15 & \texttt{clog-log} & $10^{-4}$ & $0.538_{(0.009)}$ & $0.054_{(0.003)}$ & $\mathbf{0.115_{(0.002)}}$ & $0.720_{(0.006)}$ & $0.835_{(0.007)}$ & $0.970_{(0.003)}$ & $0.860_{(0.006)}$\\
-			15 & \texttt{logit} & $10^{-2}$ & $0.551_{(0.020)}$ & $0.104_{(0.008)}$ & $0.139_{(0.011)}$ & $0.654_{(0.027)}$ & $0.815_{(0.017)}$ & $0.948_{(0.016)}$ & $0.856_{(0.015)}$\\
-			15 & \texttt{logit} & $10^{-3}$ & $0.551_{(0.010)}$ & $0.106_{(0.016)}$ & $0.129_{(0.008)}$ & $0.680_{(0.019)}$ & $0.818_{(0.008)}$ & $0.952_{(0.007)}$ & $\mathit{0.866_{(0.001)}}$\\
-			15 & \texttt{logit} & $10^{-4}$ & $0.543_{(0.008)}$ & $0.056_{(0.003)}$ & $0.121_{(0.004)}$ & $\mathbf{0.723_{(0.004)}}$ & $0.833_{(0.004)}$ & $0.964_{(0.003)}$ & $0.862_{(0.004)}$\\
-			15 & \texttt{probit} & $10^{-2}$ & $0.534_{(0.032)}$ & $0.104_{(0.013)}$ & $0.148_{(0.015)}$ & $0.631_{(0.038)}$ & $0.845_{(0.030)}$ & $0.964_{(0.010)}$ & $0.852_{(0.010)}$\\
-			15 & \texttt{probit} & $10^{-3}$ & $\mathit{0.580_{(0.021)}}$ & $0.104_{(0.016)}$ & $0.129_{(0.008)}$ & $0.680_{(0.018)}$ & $0.832_{(0.010)}$ & $0.959_{(0.007)}$ & $0.866_{(0.003)}$\\
-			15 & \texttt{probit} & $10^{-4}$ & $0.533_{(0.004)}$ & $0.065_{(0.005)}$ & $0.117_{(0.002)}$ & $\mathit{0.721_{(0.004)}}$ & $0.832_{(0.002)}$ & $0.964_{(0.001)}$ & $0.863_{(0.001)}$\\
-			\hline
-			\hline
-		\end{tabular}
+	\resizebox{\linewidth}{!}{
+	\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c}
+		\hline
+		\hline
+		BS & LF & LR & $\overline{\text{QWK}}_{{SD}}$ & $\overline{\text{MS}}_{{SD}}$ & $\overline{\text{MAE}}_{{SD}}$ & $\overline{\text{CCR}}_{{SD}}$ & $\overline{\text{Top-2}}_{{SD}}$ & $\overline{\text{Top-3}}_{{SD}}$ & $\overline{\text{1-off}}_{{SD}}$\\\hline
+		5 & \texttt{clog-log} & $10^{-2}$ & $0.414_{0.057}$ & $0.075_{0.042}$ & $0.177_{0.023}$ & $0.556_{0.057}$ & $0.833_{0.042}$ & $0.968_{0.011}$ & $0.816_{0.021}$\\
+		5 & \texttt{clog-log} & $10^{-3}$ & $0.534_{0.027}$ & $0.102_{0.011}$ & $0.137_{0.006}$ & $0.658_{0.015}$ & $0.871_{0.011}$ & $0.966_{0.003}$ & $0.852_{0.002}$\\
+		5 & \texttt{clog-log} & $10^{-4}$ & $0.520_{0.006}$ & $0.067_{0.008}$ & $0.123_{0.003}$ & $0.697_{0.006}$ & $0.842_{0.008}$ & $0.961_{0.003}$ & $0.851_{0.002}$\\
+		5 & \texttt{logit} & $10^{-2}$ & $0.416_{0.041}$ & $0.095_{0.029}$ & $0.175_{0.021}$ & $0.563_{0.054}$ & $0.762_{0.040}$ & $0.908_{0.026}$ & $0.807_{0.029}$\\
+		5 & \texttt{logit} & $10^{-3}$ & $0.554_{0.013}$ & $0.093_{0.009}$ & $0.137_{0.003}$ & $0.660_{0.008}$ & $0.802_{0.005}$ & $0.936_{0.004}$ & $0.853_{0.005}$\\
+		5 & \texttt{logit} & $10^{-4}$ & $0.520_{0.003}$ & $0.063_{0.004}$ & $0.122_{0.002}$ & $0.706_{0.005}$ & $0.823_{0.004}$ & $0.949_{0.003}$ & $0.862_{0.003}$\\
+		5 & \texttt{probit} & $10^{-2}$ & $0.460_{0.048}$ & $0.079_{0.046}$ & $0.197_{0.064}$ & $0.504_{0.167}$ & $0.808_{0.034}$ & $0.927_{0.073}$ & $0.689_{0.240}$\\
+		5 & \texttt{probit} & $10^{-3}$ & $0.564_{0.018}$ & $0.099_{0.013}$ & $0.147_{0.018}$ & $0.636_{0.045}$ & $0.822_{0.040}$ & $0.939_{0.020}$ & $0.840_{0.015}$\\
+		5 & \texttt{probit} & $10^{-4}$ & $0.523_{0.005}$ & $0.067_{0.012}$ & $0.122_{0.002}$ & $0.701_{0.006}$ & $0.823_{0.002}$ & $0.953_{0.002}$ & $0.860_{0.003}$\\
+		10 & \texttt{clog-log} & $10^{-2}$ & $0.423_{0.239}$ & $0.062_{0.051}$ & $0.127_{0.017}$ & $0.684_{0.046}$ & $\mathbf{0.894_{0.062}}$ & $\mathbf{0.986_{0.012}}$ & $0.832_{0.020}$\\
+		10 & \texttt{clog-log} & $10^{-3}$ & $\mathbf{0.582_{0.016}}$ & $0.102_{0.006}$ & $0.128_{0.003}$ & $0.680_{0.007}$ & $\mathit{0.880_{0.004}}$ & $0.972_{0.003}$ & $0.861_{0.004}$\\
+		10 & \texttt{clog-log} & $10^{-4}$ & $0.537_{0.010}$ & $0.064_{0.004}$ & $\mathit{0.116_{0.001}}$ & $0.717_{0.003}$ & $0.837_{0.002}$ & $0.971_{0.001}$ & $0.860_{0.002}$\\
+		10 & \texttt{logit} & $10^{-2}$ & $0.531_{0.031}$ & $0.107_{0.008}$ & $0.151_{0.010}$ & $0.623_{0.025}$ & $0.802_{0.022}$ & $0.934_{0.013}$ & $0.838_{0.014}$\\
+		10 & \texttt{logit} & $10^{-3}$ & $0.579_{0.009}$ & $0.096_{0.012}$ & $0.127_{0.005}$ & $0.686_{0.013}$ & $0.817_{0.006}$ & $0.954_{0.005}$ & $0.861_{0.002}$\\
+		10 & \texttt{logit} & $10^{-4}$ & $0.539_{0.007}$ & $0.074_{0.013}$ & $0.126_{0.005}$ & $0.707_{0.010}$ & $0.823_{0.007}$ & $0.957_{0.005}$ & $0.858_{0.004}$\\
+		10 & \texttt{probit} & $10^{-2}$ & $0.508_{0.037}$ & $0.088_{0.044}$ & $0.145_{0.018}$ & $0.639_{0.045}$ & $0.835_{0.015}$ & $0.960_{0.008}$ & $0.829_{0.020}$\\
+		10 & \texttt{probit} & $10^{-3}$ & $0.558_{0.034}$ & $\mathbf{0.111_{0.005}}$ & $0.134_{0.003}$ & $0.666_{0.008}$ & $0.831_{0.007}$ & $0.955_{0.001}$ & $0.863_{0.003}$\\
+		10 & \texttt{probit} & $10^{-4}$ & $0.541_{0.010}$ & $0.076_{0.006}$ & $0.119_{0.002}$ & $0.712_{0.005}$ & $0.828_{0.003}$ & $0.961_{0.002}$ & $0.862_{0.001}$\\
+		15 & \texttt{clog-log} & $10^{-2}$ & $0.564_{0.016}$ & $0.108_{0.014}$ & $0.143_{0.006}$ & $0.640_{0.015}$ & $0.879_{0.011}$ & $0.972_{0.005}$ & $0.851_{0.006}$\\
+		15 & \texttt{clog-log} & $10^{-3}$ & $0.559_{0.026}$ & $\mathit{0.111_{0.008}}$ & $0.127_{0.004}$ & $0.682_{0.010}$ & $0.871_{0.008}$ & $\mathit{0.974_{0.002}}$ & $\mathbf{0.868_{0.002}}$\\
+		15 & \texttt{clog-log} & $10^{-4}$ & $0.538_{0.009}$ & $0.054_{0.003}$ & $\mathbf{0.115_{0.002}}$ & $0.720_{0.006}$ & $0.835_{0.007}$ & $0.970_{0.003}$ & $0.860_{0.006}$\\
+		15 & \texttt{logit} & $10^{-2}$ & $0.551_{0.020}$ & $0.104_{0.008}$ & $0.139_{0.011}$ & $0.654_{0.027}$ & $0.815_{0.017}$ & $0.948_{0.016}$ & $0.856_{0.015}$\\
+		15 & \texttt{logit} & $10^{-3}$ & $0.551_{0.010}$ & $0.106_{0.016}$ & $0.129_{0.008}$ & $0.680_{0.019}$ & $0.818_{0.008}$ & $0.952_{0.007}$ & $\mathit{0.866_{0.001}}$\\
+		15 & \texttt{logit} & $10^{-4}$ & $0.543_{0.008}$ & $0.056_{0.003}$ & $0.121_{0.004}$ & $\mathbf{0.723_{0.004}}$ & $0.833_{0.004}$ & $0.964_{0.003}$ & $0.862_{0.004}$\\
+		15 & \texttt{probit} & $10^{-2}$ & $0.534_{0.032}$ & $0.104_{0.013}$ & $0.148_{0.015}$ & $0.631_{0.038}$ & $0.845_{0.030}$ & $0.964_{0.010}$ & $0.852_{0.010}$\\
+		15 & \texttt{probit} & $10^{-3}$ & $\mathit{0.580_{0.021}}$ & $0.104_{0.016}$ & $0.129_{0.008}$ & $0.680_{0.018}$ & $0.832_{0.010}$ & $0.959_{0.007}$ & $0.866_{0.003}$\\
+		15 & \texttt{probit} & $10^{-4}$ & $0.533_{0.004}$ & $0.065_{0.005}$ & $0.117_{0.002}$ & $\mathit{0.721_{0.004}}$ & $0.832_{0.002}$ & $0.964_{0.001}$ & $0.863_{0.001}$\\
+		\hline
+		\hline
+	\end{tabular}}
 \end{table*}
@@
 	\centering
-		\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.30cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c@{\hskip 0.20cm}c}
-			\hline
-			\hline
-			BS & LF & LR & $\overline{\text{QWK}}_{{(SD)}}$ & $\overline{\text{MS}}_{{(SD)}}$ & $\overline{\text{MAE}}_{{(SD)}}$ & $\overline{\text{CCR}}_{{(SD)}}$ & $\overline{\text{Top-2}}_{{(SD)}}$ & $\overline{\text{Top-3}}_{{(SD)}}$ & $\overline{\text{1-off}}_{{(SD)}}$\\\hline
-			64 & \texttt{clog-log} & $10^{-2}$ & $0.808_{(0.025)}$ & $0.086_{(0.041)}$ & $0.147_{(0.008)}$ & $0.415_{(0.031)}$ & $0.677_{(0.024)}$ & $0.798_{(0.036)}$ & $0.804_{(0.015)}$\\
-			64 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $0.144_{(0.057)}$ & $\mathbf{0.124_{(0.003)}}$ & $\mathbf{0.519_{(0.014)}}$ & $\mathit{0.764_{(0.010)}}$ & $0.861_{(0.019)}$ & $0.886_{(0.006)}$\\
-			64 & \texttt{clog-log} & $10^{-4}$ & $0.799_{(0.010)}$ & $0.000_{(0.000)}$ & $0.174_{(0.001)}$ & $0.324_{(0.015)}$ & $0.616_{(0.020)}$ & $0.795_{(0.012)}$ & $0.771_{(0.014)}$\\
-			64 & \texttt{logit} & $10^{-2}$ & $0.778_{(0.019)}$ & $0.074_{(0.041)}$ & $0.159_{(0.006)}$ & $0.366_{(0.025)}$ & $0.636_{(0.015)}$ & $0.785_{(0.010)}$ & $0.775_{(0.015)}$\\
-			64 & \texttt{logit} & $10^{-3}$ & $\mathbf{0.881_{(0.005)}}$ & $\mathit{0.178_{(0.023)}}$ & $\mathit{0.126_{(0.001)}}$ & $\mathit{0.518_{(0.008)}}$ & $\mathbf{0.765_{(0.015)}}$ & $\mathbf{0.902_{(0.005)}}$ & $\mathbf{0.894_{(0.005)}}$\\
-			64 & \texttt{logit} & $10^{-4}$ & $0.784_{(0.011)}$ & $0.000_{(0.000)}$ & $0.180_{(0.001)}$ & $0.318_{(0.026)}$ & $0.621_{(0.034)}$ & $0.772_{(0.024)}$ & $0.731_{(0.030)}$\\
-			64 & \texttt{probit} & $10^{-2}$ & $0.836_{(0.005)}$ & $0.135_{(0.021)}$ & $0.134_{(0.002)}$ & $0.468_{(0.011)}$ & $0.720_{(0.009)}$ & $0.861_{(0.009)}$ & $0.829_{(0.005)}$\\
-			64 & \texttt{probit} & $10^{-3}$ & $\mathit{0.874_{(0.004)}}$ & $0.134_{(0.012)}$ & $0.126_{(0.003)}$ & $0.511_{(0.014)}$ & $0.756_{(0.009)}$ & $\mathit{0.895_{(0.003)}}$ & $\mathit{0.889_{(0.003)}}$\\
-			64 & \texttt{probit} & $10^{-4}$ & $0.805_{(0.004)}$ & $0.000_{(0.000)}$ & $0.170_{(0.001)}$ & $0.360_{(0.011)}$ & $0.653_{(0.011)}$ & $0.809_{(0.009)}$ & $0.790_{(0.009)}$\\
-			128 & \texttt{clog-log} & $10^{-2}$ & $0.832_{(0.013)}$ & $0.123_{(0.031)}$ & $0.135_{(0.004)}$ & $0.463_{(0.013)}$ & $0.705_{(0.019)}$ & $0.813_{(0.025)}$ & $0.832_{(0.006)}$\\
-			128 & \texttt{clog-log} & $10^{-3}$ & $0.873_{(0.006)}$ & $\mathbf{0.185_{(0.029)}}$ & $0.128_{(0.002)}$ & $0.513_{(0.007)}$ & $0.758_{(0.008)}$ & $0.870_{(0.011)}$ & $0.880_{(0.009)}$\\
-			128 & \texttt{clog-log} & $10^{-4}$ & $0.659_{(0.025)}$ & $0.000_{(0.000)}$ & $0.190_{(0.002)}$ & $0.235_{(0.026)}$ & $0.466_{(0.031)}$ & $0.640_{(0.030)}$ & $0.536_{(0.041)}$\\
-			128 & \texttt{logit} & $10^{-2}$ & $0.781_{(0.041)}$ & $0.096_{(0.059)}$ & $0.153_{(0.007)}$ & $0.398_{(0.031)}$ & $0.638_{(0.033)}$ & $0.790_{(0.025)}$ & $0.779_{(0.020)}$\\
-			128 & \texttt{logit} & $10^{-3}$ & $0.865_{(0.005)}$ & $0.127_{(0.026)}$ & $0.134_{(0.001)}$ & $0.497_{(0.009)}$ & $0.754_{(0.008)}$ & $0.882_{(0.009)}$ & $0.874_{(0.008)}$\\
-			128 & \texttt{logit} & $10^{-4}$ & $0.586_{(0.008)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.192_{(0.001)}$ & $0.364_{(0.060)}$ & $0.581_{(0.034)}$ & $0.396_{(0.002)}$\\
-			128 & \texttt{probit} & $10^{-2}$ & $0.849_{(0.005)}$ & $0.132_{(0.010)}$ & $0.131_{(0.001)}$ & $0.479_{(0.004)}$ & $0.728_{(0.007)}$ & $0.854_{(0.009)}$ & $0.847_{(0.007)}$\\
-			128 & \texttt{probit} & $10^{-3}$ & $0.866_{(0.002)}$ & $0.124_{(0.043)}$ & $0.130_{(0.002)}$ & $0.505_{(0.006)}$ & $0.750_{(0.010)}$ & $0.882_{(0.004)}$ & $0.873_{(0.006)}$\\
-			128 & \texttt{probit} & $10^{-4}$ & $0.718_{(0.015)}$ & $0.000_{(0.000)}$ & $0.185_{(0.001)}$ & $0.300_{(0.031)}$ & $0.575_{(0.015)}$ & $0.733_{(0.010)}$ & $0.640_{(0.033)}$\\
-			256 & \texttt{clog-log} & $10^{-2}$ & $0.853_{(0.004)}$ & $0.157_{(0.024)}$ & $0.130_{(0.002)}$ & $0.485_{(0.009)}$ & $0.744_{(0.006)}$ & $0.842_{(0.016)}$ & $0.858_{(0.004)}$\\
-			256 & \texttt{clog-log} & $10^{-3}$ & $0.840_{(0.017)}$ & $0.095_{(0.017)}$ & $0.144_{(0.005)}$ & $0.456_{(0.021)}$ & $0.720_{(0.022)}$ & $0.840_{(0.018)}$ & $0.842_{(0.018)}$\\
-			256 & \texttt{clog-log} & $10^{-4}$ & $0.552_{(0.010)}$ & $0.000_{(0.000)}$ & $0.199_{(0.001)}$ & $0.187_{(0.001)}$ & $0.368_{(0.022)}$ & $0.475_{(0.025)}$ & $0.387_{(0.001)}$\\
-			256 & \texttt{logit} & $10^{-2}$ & $0.764_{(0.102)}$ & $0.077_{(0.067)}$ & $0.155_{(0.020)}$ & $0.387_{(0.083)}$ & $0.632_{(0.103)}$ & $0.790_{(0.077)}$ & $0.783_{(0.065)}$\\
-			256 & \texttt{logit} & $10^{-3}$ & $0.851_{(0.008)}$ & $0.100_{(0.030)}$ & $0.147_{(0.003)}$ & $0.449_{(0.015)}$ & $0.726_{(0.015)}$ & $0.861_{(0.006)}$ & $0.850_{(0.008)}$\\
-			256 & \texttt{logit} & $10^{-4}$ & $0.558_{(0.008)}$ & $0.000_{(0.000)}$ & $0.202_{(0.001)}$ & $0.187_{(0.002)}$ & $0.206_{(0.007)}$ & $0.395_{(0.046)}$ & $0.389_{(0.003)}$\\
-			256 & \texttt{probit} & $10^{-2}$ & $0.858_{(0.005)}$ & $0.164_{(0.033)}$ & $0.130_{(0.002)}$ & $0.486_{(0.007)}$ & $0.741_{(0.008)}$ & $0.867_{(0.008)}$ & $0.862_{(0.005)}$\\
-			256 & \texttt{probit} & $10^{-3}$ & $0.850_{(0.008)}$ & $0.111_{(0.040)}$ & $0.144_{(0.002)}$ & $0.460_{(0.011)}$ & $0.732_{(0.006)}$ & $0.865_{(0.006)}$ & $0.853_{(0.007)}$\\
-			256 & \texttt{probit} & $10^{-4}$ & $0.565_{(0.010)}$ & $0.000_{(0.000)}$ & $0.196_{(0.001)}$ & $0.189_{(0.001)}$ & $0.409_{(0.014)}$ & $0.602_{(0.022)}$ & $0.392_{(0.002)}$\\
-			\hline
-			\hline
-		\end{tabular}
+	\resizebox{\linewidth}{!}{
+	\begin{tabular}{c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c@{\hskip 0.15cm}c}
+		\hline
+		\hline
+		BS & LF & LR & $\overline{\text{QWK}}_{{SD}}$ & $\overline{\text{MS}}_{{SD}}$ & $\overline{\text{MAE}}_{{SD}}$ & $\overline{\text{CCR}}_{{SD}}$ & $\overline{\text{Top-2}}_{{SD}}$ & $\overline{\text{Top-3}}_{{SD}}$ & $\overline{\text{1-off}}_{{SD}}$\\\hline
+		64 & \texttt{clog-log} & $10^{-2}$ & $0.808_{0.025}$ & $0.086_{0.041}$ & $0.147_{0.008}$ & $0.415_{0.031}$ & $0.677_{0.024}$ & $0.798_{0.036}$ & $0.804_{0.015}$\\
+		64 & \texttt{clog-log} & $10^{-3}$ & $0.873_{0.006}$ & $0.144_{0.057}$ & $\mathbf{0.124_{0.003}}$ & $\mathbf{0.519_{0.014}}$ & $\mathit{0.764_{0.010}}$ & $0.861_{0.019}$ & $0.886_{0.006}$\\
+		64 & \texttt{clog-log} & $10^{-4}$ & $0.799_{0.010}$ & $0.000_{0.000}$ & $0.174_{0.001}$ & $0.324_{0.015}$ & $0.616_{0.020}$ & $0.795_{0.012}$ & $0.771_{0.014}$\\
+		64 & \texttt{logit} & $10^{-2}$ & $0.778_{0.019}$ & $0.074_{0.041}$ & $0.159_{0.006}$ & $0.366_{0.025}$ & $0.636_{0.015}$ & $0.785_{0.010}$ & $0.775_{0.015}$\\
+		64 & \texttt{logit} & $10^{-3}$ & $\mathbf{0.881_{0.005}}$ & $\mathit{0.178_{0.023}}$ & $\mathit{0.126_{0.001}}$ & $\mathit{0.518_{0.008}}$ & $\mathbf{0.765_{0.015}}$ & $\mathbf{0.902_{0.005}}$ & $\mathbf{0.894_{0.005}}$\\
+		64 & \texttt{logit} & $10^{-4}$ & $0.784_{0.011}$ & $0.000_{0.000}$ & $0.180_{0.001}$ & $0.318_{0.026}$ & $0.621_{0.034}$ & $0.772_{0.024}$ & $0.731_{0.030}$\\
+		64 & \texttt{probit} & $10^{-2}$ & $0.836_{0.005}$ & $0.135_{0.021}$ & $0.134_{0.002}$ & $0.468_{0.011}$ & $0.720_{0.009}$ & $0.861_{0.009}$ & $0.829_{0.005}$\\
+		64 & \texttt{probit} & $10^{-3}$ & $\mathit{0.874_{0.004}}$ & $0.134_{0.012}$ & $0.126_{0.003}$ & $0.511_{0.014}$ & $0.756_{0.009}$ & $\mathit{0.895_{0.003}}$ & $\mathit{0.889_{0.003}}$\\
+		64 & \texttt{probit} & $10^{-4}$ & $0.805_{0.004}$ & $0.000_{0.000}$ & $0.170_{0.001}$ & $0.360_{0.011}$ & $0.653_{0.011}$ & $0.809_{0.009}$ & $0.790_{0.009}$\\
+		128 & \texttt{clog-log} & $10^{-2}$ & $0.832_{0.013}$ & $0.123_{0.031}$ & $0.135_{0.004}$ & $0.463_{0.013}$ & $0.705_{0.019}$ & $0.813_{0.025}$ & $0.832_{0.006}$\\
+		128 & \texttt{clog-log} & $10^{-3}$ & $0.873_{0.006}$ & $\mathbf{0.185_{0.029}}$ & $0.128_{0.002}$ & $0.513_{0.007}$ & $0.758_{0.008}$ & $0.870_{0.011}$ & $0.880_{0.009}$\\
+		128 & \texttt{clog-log} & $10^{-4}$ & $0.659_{0.025}$ & $0.000_{0.000}$ & $0.190_{0.002}$ & $0.235_{0.026}$ & $0.466_{0.031}$ & $0.640_{0.030}$ & $0.536_{0.041}$\\
+		128 & \texttt{logit} & $10^{-2}$ & $0.781_{0.041}$ & $0.096_{0.059}$ & $0.153_{0.007}$ & $0.398_{0.031}$ & $0.638_{0.033}$ & $0.790_{0.025}$ & $0.779_{0.020}$\\
+		128 & \texttt{logit} & $10^{-3}$ & $0.865_{0.005}$ & $0.127_{0.026}$ & $0.134_{0.001}$ & $0.497_{0.009}$ & $0.754_{0.008}$ & $0.882_{0.009}$ & $0.874_{0.008}$\\
+		128 & \texttt{logit} & $10^{-4}$ & $0.586_{0.008}$ & $0.000_{0.000}$ & $0.196_{0.001}$ & $0.192_{0.001}$ & $0.364_{0.060}$ & $0.581_{0.034}$ & $0.396_{0.002}$\\
+		128 & \texttt{probit} & $10^{-2}$ & $0.849_{0.005}$ & $0.132_{0.010}$ & $0.131_{0.001}$ & $0.479_{0.004}$ & $0.728_{0.007}$ & $0.854_{0.009}$ & $0.847_{0.007}$\\
+		128 & \texttt{probit} & $10^{-3}$ & $0.866_{0.002}$ & $0.124_{0.043}$ & $0.130_{0.002}$ & $0.505_{0.006}$ & $0.750_{0.010}$ & $0.882_{0.004}$ & $0.873_{0.006}$\\
+		128 & \texttt{probit} & $10^{-4}$ & $0.718_{0.015}$ & $0.000_{0.000}$ & $0.185_{0.001}$ & $0.300_{0.031}$ & $0.575_{0.015}$ & $0.733_{0.010}$ & $0.640_{0.033}$\\
+		256 & \texttt{clog-log} & $10^{-2}$ & $0.853_{0.004}$ & $0.157_{0.024}$ & $0.130_{0.002}$ & $0.485_{0.009}$ & $0.744_{0.006}$ & $0.842_{0.016}$ & $0.858_{0.004}$\\
+		256 & \texttt{clog-log} & $10^{-3}$ & $0.840_{0.017}$ & $0.095_{0.017}$ & $0.144_{0.005}$ & $0.456_{0.021}$ & $0.720_{0.022}$ & $0.840_{0.018}$ & $0.842_{0.018}$\\
+		256 & \texttt{clog-log} & $10^{-4}$ & $0.552_{0.010}$ & $0.000_{0.000}$ & $0.199_{0.001}$ & $0.187_{0.001}$ & $0.368_{0.022}$ & $0.475_{0.025}$ & $0.387_{0.001}$\\
+		256 & \texttt{logit} & $10^{-2}$ & $0.764_{0.102}$ & $0.077_{0.067}$ & $0.155_{0.020}$ & $0.387_{0.083}$ & $0.632_{0.103}$ & $0.790_{0.077}$ & $0.783_{0.065}$\\
+		256 & \texttt{logit} & $10^{-3}$ & $0.851_{0.008}$ & $0.100_{0.030}$ & $0.147_{0.003}$ & $0.449_{0.015}$ & $0.726_{0.015}$ & $0.861_{0.006}$ & $0.850_{0.008}$\\
+		256 & \texttt{logit} & $10^{-4}$ & $0.558_{0.008}$ & $0.000_{0.000}$ & $0.202_{0.001}$ & $0.187_{0.002}$ & $0.206_{0.007}$ & $0.395_{0.046}$ & $0.389_{0.003}$\\
+		256 & \texttt{probit} & $10^{-2}$ & $0.858_{0.005}$ & $0.164_{0.033}$ & $0.130_{0.002}$ & $0.486_{0.007}$ & $0.741_{0.008}$ & $0.867_{0.008}$ & $0.862_{0.005}$\\
+		256 & \texttt{probit} & $10^{-3}$ & $0.850_{0.008}$ & $0.111_{0.040}$ & $0.144_{0.002}$ & $0.460_{0.011}$ & $0.732_{0.006}$ & $0.865_{0.006}$ & $0.853_{0.007}$\\
+		256 & \texttt{probit} & $10^{-4}$ & $0.565_{0.010}$ & $0.000_{0.000}$ & $0.196_{0.001}$ & $0.189_{0.001}$ & $0.409_{0.014}$ & $0.602_{0.022}$ & $0.392_{0.002}$\\
+		\hline
+		\hline
+	\end{tabular}}
 \end{table*}
@@
 	\centering
-		\resizebox{\columnwidth}{!}{
+	\footnotesize
 		\begin{tabular}{cccccc}
@@
 			&        128        &  $-0.014$  &      $0.000$       &     -      &            -\\\hline\hline
-		\end{tabular}}
+	\end{tabular}
 \end{table}
@@
 The results for \cite{beckham2017unimodal} were obtained by reproducing their experiments because they did not provide the results for test set.
-As can be checked, the proposed ordinal model outperforms all the other alternatives in terms of QWK.
+As can be checked, the proposed ordinal model with the best configuration found in the previous step outperforms all the other alternatives in terms of QWK.
 
@@
 
-	% if have a single appendix:
-	%\appendix[Proof of the Zonklar Equations]
-	% or
-	%\appendix  % for no appendix heading
-	% do not use \section anymore after \appendix, only \section*
-	% is possibly needed
-
-	% use appendices with more than one appendix
-	% then use \section to start each appendix
-	% you must declare a \section before using any
-	% \subsection or using \label (\appendices by itself
-	% starts a section numbered zero.)
-	%
-
-% use section* for acknowledgement
 \section*{Acknowledgment}
@@
 
-	% Can use something like this to put references on a page
-	% by themselves when using endfloat and the captionsoff option.
-	\ifCLASSOPTIONcaptionsoff
-	\newpage
-	\fi
-
-	% trigger a \newpage just before the given reference
-	% number - used to balance the columns on the last page
-	% adjust value as needed - may need to be readjusted if
-	% the document is modified later
-	%\IEEEtriggeratref{8}
-	% The "triggered" command can be changed if desired:
-	%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-	% references section
-
-	% can use a bibliography generated by BibTeX as a .bbl file
-	% BibTeX documentation can be easily obtained at:
-	% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-	% The IEEEtran BibTeX style support page is at:
-	% http://www.michaelshell.org/tex/ieeetran/bibtex/
-	\bibliographystyle{IEEEtran}
-	% argument is your BibTeX string definitions and bibliography database(s)
+\section*{References}
+
 \bibliography{main.bib}
-	%
-	% <OR> manually copy in the resultant .bbl file
-	% set second argument of \begin to the number of references
-	% (used to reserve space for the reference number labels box)
-
-	%\printbibliography
-
-	% You can push biographies down or up by placing
-	% a \vfill before or after them. The appropriate
-	% use of \vfill depends on what kind of text is
-	% on the last page and whether or not the columns
-	% are being equalized.
-
-	%\vfill
-
-	% Can be used to pull up biographies so that the bottom of the last one
-	% is flush with the other column.
-	%\enlargethispage{-5in}
-
-	% that's all folks
-
-	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{img/bio/VVargas.png}}]{Víctor Manuel Vargas} was born in Córdoba, Spain.
-He received the degree of Computer Engineering from the University of Córdoba, Spain, in 2018.
-He is currently studying a master's degree at the International University of Menéndez Pelayo, Spain.
-He is a member of the AYRNA group of the Department of Computer Science and Numerical Analysis of the University of Córdoba.
-His current research interests include deep neural networks and their applications to image classification on ordinal problems.
-
-	\end{IEEEbiography}
-
-	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{img/bio/PAGutierrez.png}}]{Pedro Antonio Gutiérrez}  (M'07-SM'15) received the B.S.
-degree in computer science from the University of Sevilla (Spain) in 2006, and the Ph.D.
-degree in computer science and artificial intelligence from the University of Granada (Spain) in 2009.
-He is currently an Assistant Professor with the Department of Computer Science and Numerical Analysis, University of Córdoba (Spain).
-		His research interests are in the areas of supervised learning, evolutionary artificial neural networks, ordinal classification and the application of these techniques to different real world problems, including precision agriculture, renewable energy, climatology and biomedicine, among others.
-He serves on the Editorial board for the journals \textit{IEEE Transaction on Neural Networks and Learning Systems} and \textit{Progress in Artificial Intelligence} and on the organization/program committees of several computational intelligence conferences.
-	\end{IEEEbiography}
-
-	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{img/bio/CHervas.png}}]{César Hervás-Martínez}  (M'07-SM'14) was born in Cuenca, Spain.
-He received the B.S.
-degree in statistics and operations research from the Universidad Complutense de Madrid, Madrid, Spain, in 1978, and the Ph.D.
-degree in mathematics from the University of Seville, Seville, Spain, in 1986.
-	He is currently a Professor of Computer Science and Artificial Intelligence with the Department of Computer Science and Numerical Analysis, University of Córdoba, Córdoba, Spain, and an Associate Professor with the Department of Mathematics and Engineering, Loyola University Andalucía, Spain.
-His current research interests include neural networks, evolutionary computation, and the modelling of natural systems.
-	\end{IEEEbiography}
-%	
-%	
-%	\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{CHervas.png}}]{C\'{e}sar Herv\'{a}s-Mart\'{i}nez} was born in Cuenca, Spain.
-He received his B.S.
-degree in Statistics and Operation Research from the Universidad Complutense, Madrid, Spain, in 1978, and his Ph.D.
-degree in Mathematics from the University of Seville, Seville, Spain, in 1986.
-He is a Professor at the University of C\'{o}rdoba in the Department of Computer Science and Numerical Analysis, in the area of Computer Science and Artificial Intelligence, and an Associate Professor in the Department of Quantitative Methods in the School of Economics.
-His current research interests include neural networks, evolutionary computation, and the modelling of natural systems.
-%	\end{IEEEbiography}
 

### 2019-10-08 paper/elsarticle-template.tex
Paper neuro

@@
 \cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction.
-These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly,jin2018deep}.
+These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{yu2017convolutional,fang2019image,zhu2019image}, speech recognition~\cite{song2018music,liu2018speech}, control problems~\cite{mnih2015human}, object detection~\cite{sun2018face,chu2018deep,olmos2018automatic}, privacy and security protection~\cite{tan2018deep,yuan2019adversarial}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{li2019deep} and image retrieval~\cite{tzelepi2018deep,qayyum2017medical,bai2018optimization}.
 Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays.
-CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}.
+CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,ronneberger2015u}.
 For images, each colour channel is represented by a 2D array, and convolutional layers extract the main features from the pixels, and, after that, a fully connected layer classify every sample based on its extracted features.
@@
 	\centering
+	\resizebox{\columnwidth}{!}{
 	\begin{tabular}{cccc}
@@
 		\includegraphics[width=2.4cm]{img/retinopathy/5.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/6.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/7.jpg} & \includegraphics[width=2.4cm]{img/retinopathy/8.jpg}
-	\end{tabular}						
+	\end{tabular}}					
 	\caption{Examples taken from the Diabetic Retinopathy test set.}
@@
 As previously discussed, Beckham and Pal \cite{beckham2017unimodal} proposed a straightforward method to constrain discrete probability distributions to be unimodal.
+M.
+Duan et al.
+\cite{duan2018hybrid} proposed a hybrid approach that combines CNN with Extreme Learning Machine (ELM).
 
@@
 		\includegraphics[width=2.4cm]{img/adience/5.jpg} & \includegraphics[width=2.4cm]{img/adience/6.jpg} & \includegraphics[width=2.4cm]{img/adience/7.jpg} & \includegraphics[width=2.4cm]{img/adience/8.jpg}
-	\end{tabular}						
+	\end{tabular}}				
 	\caption{Examples taken from the Adience test set.}
@@
 	\footnotesize
+	\resizebox{\columnwidth}{!}{
 	\begin{tabular}{lclc}
@@
 		                &                                 & AveragePool7x7s2    &     1x1x256     \\ \hline\hline
-	\end{tabular}	
+	\end{tabular}}
 \end{table}
@@
 The performance gain of CLM over the nominal version reaches $16.8\%$ for DR and $11.9\%$ for Adience dataset.
-The improvement of the ordinal method for DR is higher than that for Adience.
+The DR dataset obtains a higher performance gain from the ordinal method than the Adience dataset.
 It seems that the method proposed in this work offers a more significant improvement as the given problem complexity increases.
 Moreover, when compared against alternative ordinal methods (many of them with a deep structure), CLMs are very competitive, possibly because of the flexibility provided by the threshold model structure (where the threshold of each class is independently adjusted).
+Our proposed model shows a high score and a very low standard deviation, which proves very high stability compared to other alternatives.
 
@@
 		Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
-		Levi and Hassner \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
+		Levi and Hassner \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ 
+		M. Duan et al. \cite{duan2018hybrid}         &            -            &    $0.523_{(0.057)}$    &        -         \\ \hline\hline
 	\end{tabular}

### 2019-10-08 activations.py
Activations fixes

@@ -48,18 +48,18 @@ class MPELU(keras.layers.Layer):
 			shape = [int(input_shape[-1])]  # Number of channels
 
 		self.alpha = self.add_weight(name='alpha', shape=shape, dtype=K.floatx(),
-									 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1, dtype=K.floatx()),
+									 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1),
 									 trainable=True)
 		self.beta = self.add_weight(name='beta', shape=shape, dtype=K.floatx(),
-									initializer=keras.initializers.RandomUniform(minval=-1, maxval=1, dtype=K.floatx()),
+									initializer=keras.initializers.RandomUniform(minval=0.0001, maxval=1),
 									trainable=True)
 
 		# Finish buildidng
 		super(MPELU, self).build(input_shape)
 
 	def call(self, inputs):
-		positive = K.nn.relu(inputs)
-		negative = self.alpha * (K.exp(-K.nn.relu(-inputs) * self.beta) - 1)
+		positive = keras.activations.relu(inputs)
+		negative = self.alpha * (K.exp(-keras.activations.relu(-inputs) * K.pow(self.beta, 2)) - 1)
 
 		return positive + negative
 
@@ -75,14 +75,14 @@ class RTReLU(keras.layers.Layer):
 		shape = [int(input_shape[-1])]  # Number of channels
 
 		self.a = self.add_weight(name='a', shape=shape, dtype=K.floatx(),
-								 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1, dtype=K.floatx()),
+								 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1),
 								 trainable=False)
 
 		# Finish building
 		super(RTReLU, self).build(input_shape)
 
 	def call(self, inputs):
-		return K.nn.relu(inputs + self.a)
+		return keras.activations.relu(inputs + self.a)
 
 	def compute_output_shape(self, input_shape):
 		return input_shape
@@ -96,15 +96,15 @@ class RTPReLU(keras.layers.PReLU):
 		shape = [int(input_shape[-1])]  # Number of channels
 
 		self.a = self.add_weight(name='a', shape=shape, dtype=K.floatx(),
-								 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1, dtype=K.floatx()),
[…]

### 2019-10-08 net_keras.py
Vgg16

@@ -2,8 +2,7 @@ import keras
 from keras.models import Sequential
 from keras.layers import Conv2D, MaxPooling2D, BatchNormalization, Activation, Dropout, Flatten, Dense
 from keras import regularizers
-from activations import SPP, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, CLM, RReLu, \
-	PELU, SlopedReLU, PTELU, Antirectifier, CReLU
+from activations import SPP, MPELU, RTReLU, RTPReLU, PairedReLU, EReLU, SQRTActivation, CLM, RReLu, PELU, SlopedReLU, PTELU, Antirectifier, CReLU, EPReLU
 from layers import GeometricLayer
 from resnet import Resnet_2x4
 
@@ -104,7 +103,7 @@ class Net:
 
 		return model
 
-	def vgg19_v2(self):
+	def vgg16(self):
 		# Build the network of vgg for 10 classes with massive dropout and weight decay as described in the paper.
 		model = Sequential()
 		weight_decay = 0.0005

### 2019-10-08 callbacks.py
Dynamic class weights

@@ -1,7 +1,7 @@
 import keras
 import numpy as np
 from sklearn.metrics import confusion_matrix, accuracy_score
-from metrics import quadratic_weighted_kappa_cm, quadratic_weighted_kappa
+from metrics import quadratic_weighted_kappa_cm, quadratic_weighted_kappa, _compute_sensitivities
 from losses import make_cost_matrix
 
 class ComputeMetricsCallback(keras.callbacks.Callback):
@@ -112,8 +112,67 @@ class ComputeMetricsCallback(keras.callbacks.Callback):
 
 
 class PrintWeightsCallback(keras.callbacks.Callback):
-	def __init__(self):
-		pass
+	def __init__(self, class_weights):
+		self.class_weights = class_weights
 
-	def on_epoch_end(self, epoch, logs={}):
-		print(self.model.layers[-1].get_weights())
+#	def on_epoch_end(self, epoch, logs={}):
+#		print(self.model.layers[-1].get_weights())
+
+	def on_epoch_begin(self, epoch, logs):
+		print(self.class_weights)
+
+'''
+ Compute class weights based on class sensitivity on the validation dataset.
+'''
+class ReweightClassesCallback(keras.callbacks.Callback):
+	'''
+	:param validation_data: validation data tuple (x, y)
+	:param class_weights: weights list that is going to be adjusted according to sensitvity.
+	'''
+	def __init__(self, val_generator, val_steps, class_weights):
+		self.class_weights = class_weights
+		self.val_generator = val_generator
+		self.val_steps = val_steps
+
+		super(ReweightClassesCallback, self).__init__()
+
+	def on_epoch_begin(self, epoch, logs):
+		print(self.class_weights)
+
+		steps = 0
+
+		y_pred = None
+		y_true = None
+
+		for x, y in self.val_generator:
+			if steps >= self.val_steps:
+				break
+			steps += 1
+
+			y_pred_batch = self.model.predict_on_batch(x)
+
+			if y_pred is None:
+				y_pred = y_pred_batch
+			else:
+				y_pred = np.vstack((y_pred, y_pred_batch))
+
+			if y_true is None:
+				y_true = y
+			else:
+				y_true = np.vstack((y_true, y))
+
+		sensis = _compute_sensitivities(y_true, y_pred)
+
+		del y_true
+		del y_pred
+
+		# weights = np.exp(1/(sensis+1e-9))
+
[…]

### 2019-10-08 experiment.py

@@ -9,7 +9,7 @@ import click
 import pickle
 import h5py
 from scipy import io as spio
-from callbacks import ComputeMetricsCallback, PrintWeightsCallback
+from callbacks import ComputeMetricsCallback, PrintWeightsCallback, ReweightClassesCallback
 from losses import qwk_loss, make_cost_matrix, ms_n_qwk_loss
 from metrics import np_quadratic_weighted_kappa, quadratic_weighted_kappa_cm, top_2_accuracy, top_3_accuracy, \
 	minimum_sensitivity, accuracy_off1
@@ -446,6 +446,7 @@ class Experiment:
 
 		# Get class weights based on frequency
 		class_weight = ds_train.get_class_weights()
+		# class_weight = np.array([0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 100000.0])
 
 		# Free dataset object
 		del ds_train
@@ -536,7 +537,8 @@ class Experiment:
 									   keras.callbacks.TensorBoard(log_dir=self.checkpoint_dir),
 									   keras.callbacks.TerminateOnNaN(),
 									   keras.callbacks.EarlyStopping(min_delta=0.0005, patience=40, verbose=1),
-									   # PrintWeightsCallback()
+									   # PrintWeightsCallback(class_weight),
+									   # ReweightClassesCallback(val_generator=val_generator, val_steps=steps_val, class_weights=class_weight)
 									   ],
 							workers=self.workers,
 							use_multiprocessing=False,
@@ -689,8 +691,8 @@ class Experiment:
 	def get_model(self, net_object, name):
 		if name == 'vgg19':
 			model = net_object.vgg19()
-		elif name == 'vgg19_v2':
-			model = net_object.vgg19_v2()
+		elif name == 'vgg16':
+			model = net_object.vgg16()
 		elif name == 'conv128':
 			model = net_object.conv128()
 		elif name == 'testing':

### 2019-10-08 activations.py
Activations constraints

@@ -3,6 +3,10 @@ import keras
 from tensorflow import distributions, matrix_band_part, igamma, lgamma
 from keras import backend as K
 
+def cons_greater_zero(value):
+	epsilon = 1e-9
+	return epsilon + K.pow(value, 2)
+
 class SPP(keras.layers.Layer):
 	"""
 	Parametric softplus activation layer.
@@ -51,7 +55,7 @@ class MPELU(keras.layers.Layer):
 									 initializer=keras.initializers.RandomUniform(minval=-1, maxval=1),
 									 trainable=True)
 		self.beta = self.add_weight(name='beta', shape=shape, dtype=K.floatx(),
-									initializer=keras.initializers.RandomUniform(minval=0.0001, maxval=1),
+									initializer=keras.initializers.RandomUniform(minval=0.0, maxval=1),
 									trainable=True)
 
 		# Finish buildidng
@@ -59,7 +63,7 @@ class MPELU(keras.layers.Layer):
 
 	def call(self, inputs):
 		positive = keras.activations.relu(inputs)
-		negative = self.alpha * (K.exp(-keras.activations.relu(-inputs) * K.pow(self.beta, 2)) - 1)
+		negative = self.alpha * (K.exp(-keras.activations.relu(-inputs) * cons_greater_zero(self.beta)) - 1)
 
 		return positive + negative
 
@@ -217,18 +221,18 @@ class PELU(keras.layers.Layer):
 
 	def build(self, input_shape):
 		self.alpha = self.add_weight(name='alpha', shape=(1,), dtype=K.floatx(),
-									 initializer=keras.initializers.RandomUniform(minval=0.01, maxval=1))
-		self.alpha = K.clip(self.alpha, 0.0001, 10)
+									 initializer=keras.initializers.RandomUniform(minval=0.0, maxval=1))
+		# self.alpha = K.clip(self.alpha, 0.0001, 10)
 
 		self.beta = self.add_weight(name='beta', shape=(1,), dtype=K.floatx(),
-									initializer=keras.initializers.RandomUniform(minval=0.01, maxval=1))
-		self.beta = K.clip(self.beta, 0.0001, 10)
+									initializer=keras.initializers.RandomUniform(minval=0.0, maxval=1))
+		# self.beta = K.clip(self.beta, 0.0001, 10)
 
 		super(PELU, self).build(input_shape)
 
 	def call(self, inputs):
[…]

### 2019-10-09 paper/elsarticle-template.tex
Paper
Correcciones paper

@@
 %% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
+%\bibliographystyle{elsarticle-num}
+\bibliographystyle{IEEEtran}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\title{Deep ordinal classification based on cumulative link models}
+\title{Cumulative link models for deep ordinal classification}
 
@@
 Three different link functions are studied in the experimental study, and the results are contrasted with statistical analysis.
-The experiments run over two different ordinal classification problems, and the statistical tests confirm that these models improve the results of a nominal model and outperform other proposals considered in the literature.
+The experiments run over two different ordinal classification problems, and the statistical tests confirm that these models improve the results of a nominal model and outperform other robust proposals considered in the literature.
 \end{abstract}
@@
 At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks.
-However, the softmax may not be the best option depending on the problem considered.
+However, the softmax may not be the best option depending on the classification problem considered.
 
@@
 
+The highlights of this work are to introduce the CLM for CNNs combined with the QWK loss function to achieve high classification performance and better stability than previous works in terms of standard deviation and stagnation problems.
+
 The paper is organized as follows: in Section~\ref{sect:relatedwork}, we analyse previous related works.
@@
 %\textbf{(Métrica ordinal (MAE))}
-ALALI et al.
+Alali et al.
 \cite{alali2018multi} proposed a complex CNN architecture for solving Twitter Sentiment Classification as an ordinal problem.
@@
 Also, they checked the importance of hyper-parameter tuning.
-Later, in 2019, they published another work \cite{de2019deep} related to the Diabetic Retinopathy dataset where they combined the QWK loss function with the use of images of a higher resolution and new dataset partitions with many more samples on the training split.
-They achieved a proper classification score.
-Still, they tested the classifier against a tiny testing set compared to the original one from the Kaggle competition (around $12\%$ of the samples for testing against $60\%$ on the initial dataset splits).
+Later, in 2019, another work related to the Diabetic Retinopathy dataset was published \cite{de2019deep} where they combined the QWK loss function with the use of images of a higher resolution and new dataset partitions with many more samples on the training split.
+They achieved a proper classification score but tested the classifier against a tiny testing set compared to the original one from the Kaggle competition (around $12\%$ of the samples for testing against $60\%$ on the initial dataset splits).
 Further comparisons with this work are not possible as they didn't provide the dataset splits along with the paper.
@@
 \cite{rios2017ordinal} presented a CNN model designed to handle ordinal regression tasks on psychiatric notes.
-They combined an ordinal loss function, a CNN model and conventional feature engineering.
-Also, they applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.
+They combined an ordinal loss function, a CNN model and conventional feature extraction.
+Also, the authors applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.
 
@@
 	\centering
-	\includegraphics[width=3in]{img/linkfunctions.pdf}
+	\includegraphics[width=\columnwidth]{img/linkfunctions.pdf}
 	\caption{Different link functions commonly used for CLMs.}
@@
 This method reduces the internal covariate shift by normalizing layer outputs.
-It allows us to use higher learning rates and be less careful about weight initialization.
-It also eliminates the need for using regularization techniques like Dropout.
+As the authors stated \cite{ioffe2015batch}, it allows us to use higher learning rates and be less careful about weight initialization.
+In some cases, it also eliminates the need for using regularization techniques like Dropout.
 
 At the output of the network, the CLM is used (see Section \ref{sect:ordinalproblem}).
-Also, a learnable parameter $\tau$ has been used to rescale the projections used by the CLM to make it more stable and guarantee the convergence in most cases.
+Also, a learnable parameter $\tau$ rescales the projections used by the CLM to make it more stable and guarantee the convergence in most cases.
 The following expression describes the transformation applied to these projections:
@@
 \end{equation}
-where $\tau$ is optimized as a free parameter.
+where $\tau$ is optimized as a free parameter along with the parameters of the model.
 
@@
 Previous works have presented some techniques that adjust this parameter in order to achieve better performance~\cite{smith2017cyclical,senior2013empirical}.
-In this work, we consider three different values for the initial value of this parameter: $10^{-2}$, $10^{-3}$ and $10^{-4}$.
+In this work, we consider three different values for the initial value of this parameter: $10^{-4}$, $10^{-3}$ and $10^{-2}$.
 	\item \textit{Batch size} (BS).
@@
 		&                   & \multicolumn{2}{c}{\textbf{DR}} & \multicolumn{2}{c}{\textbf{Adience}} \\ \hline
-		LF         &        LF         & Mean diff. &        Sig.        & Mean diff. &          Sig.           \\ \hline
+		LF         &        LF         & Mean diff. &        P-val        & Mean diff. &          P-val           \\ \hline
 		\texttt{logit}   &  \texttt{probit}  &  $0.046$   &      $0.000$       &  $-0.002$  &         $0.011$         \\
@@
 		&  \texttt{probit}  &  $-0.038$  &      $0.000$       &  $-0.014$  &         $0.248$         \\ \hline\hline
-		LR         &        LR         & Mean diff. &        Sig.        & Mean diff. &          Sig.           \\ \hline
+		LR         &        LR         & Mean diff. &        P-val        & Mean diff. &          P-val           \\ \hline
 		$10^{-2}$     &     $10^{-3}$     &  $-0.046$  &      $0.000$       &  $-0.073$  &         $0.000$         \\
@@
 		&     $10^{-3}$     &  $-0.194$  &      $0.000$       &  $-0.029$  &         $0.023$         \\ \hline\hline
-		BS         &        BS         & Mean diff. &        Sig.        & Mean diff. &          Sig.           \\ \hline
+		BS         &        BS         & Mean diff. &        P-val        & Mean diff. &          P-val           \\ \hline
 		64         &        128        &  $-0.041$  &      $0.026$       &     -      &            -            \\
@@
 The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
-In summary, the most significant contributions of the model proposal are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention from over-fitting and stagnation.
+In summary, the most significant contributions of the model proposal are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention from over-fitting and stagnation, which gives our method high stability compared to other alternatives.
 
@@
 \section*{Acknowledgment}
-This work has been partially subsidised by the TIN2017-85887-C2-1-P and TIN2017-90567-REDT projects of the Spanish Ministry of Economy and Competitiveness (MINECO), and FEDER funds of the European Union.
+This work has been partially subsidised by the TIN2017-85887-C2-1-P project of the Spanish Ministry of Economy and Competitiveness (MINECO), and FEDER funds of the European Union.
+Víctor Manuel Vargas's research has been subsidized by the FPU Predoctoral Program of the Spanish Ministry of Education, Culture and Sport (MECD), grant reference FPU18/00358.
 

### 2019-10-10 paper/elsarticle-template.tex
paper, bios

@@
 %% `Elsevier LaTeX' style
-%\bibliographystyle{elsarticle-num}
-\bibliographystyle{IEEEtran}
+\bibliographystyle{elsarticle-num}
 %%%%%%%%%%%%%%%%%%%%%%%
@@
 \author{Pedro Antonio Guti\'errez}
-\author{C\'esar Herv\'as Mart\'inez}
+\author{C\'esar Herv\'as-Mart\'inez}
 \address{Department of Computer Science and Numerical Analysis, University of C\'ordoba, C\'ordoba, Spain}
+\cortext[a]{V\'ictor Manuel Vargas is the corresponding author.}
 
@@
 Three different link functions are studied in the experimental study, and the results are contrasted with statistical analysis.
-The experiments run over two different ordinal classification problems, and the statistical tests confirm that these models improve the results of a nominal model and outperform other robust proposals considered in the literature.
+The experiments run over two different ordinal classification problems and the statistical tests confirm that these models improve the results of a nominal model and outperform other robust proposals considered in the literature.
 \end{abstract}
@@
 
-The highlights of this work are to introduce the CLM for CNNs combined with the QWK loss function to achieve high classification performance and better stability than previous works in terms of standard deviation and stagnation problems.
+The main contribution of this work is to introduce CLM for CNNs combined with the QWK loss function to achieve high classification performance and better stability than previous works in terms of standard deviation and stagnation problems.
 
@@
 Also, they checked the importance of hyper-parameter tuning.
-Later, in 2019, another work related to the Diabetic Retinopathy dataset was published \cite{de2019deep} where they combined the QWK loss function with the use of images of a higher resolution and new dataset partitions with many more samples on the training split.
-They achieved a proper classification score but tested the classifier against a tiny testing set compared to the original one from the Kaggle competition (around $12\%$ of the samples for testing against $60\%$ on the initial dataset splits).
-Further comparisons with this work are not possible as they didn't provide the dataset splits along with the paper.
+Later, in 2019, another work related to the Diabetic Retinopathy dataset was published \cite{de2019deep} where the authors combined the QWK loss function with the use of images of a higher resolution and new dataset partitions with many more samples on the training split.
+Although they achieved a proper classification score, the test set only contained a small portion of the test patterns used in the Kaggle competition (around $12\%$ of the samples for testing against $60\%$ on the initial dataset splits).
 
@@
 	\footnotesize
+	\resizebox{\columnwidth}{!}{
 	\begin{tabular}{cccccc}
@@
 		&        128        &  $-0.014$  &      $0.000$       &     -      &            -\\\hline\hline
-	\end{tabular}
+	\end{tabular}}
 \end{table}
@@
 Moreover, when compared against alternative ordinal methods (many of them with a deep structure), CLMs are very competitive, possibly because of the flexibility provided by the threshold model structure (where the threshold of each class is independently adjusted).
-Our proposed model shows a high score and a very low standard deviation, which proves very high stability compared to other alternatives.
+Our proposed model shows a high score and a very low standard deviation, which proves very high robustness compared to other alternatives.
 
@@
 	\def\arraystretch{1.3}
+	\resizebox{\columnwidth}{!}{
 	\begin{tabular}{lccc}
@@
 		\hline
-		Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-		CLM network (proposal)                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
-		Nominal network                           &    $0.498_{(0.013)}$    &    $0.692_{(0.014)}$    &        $0.854_{(0.006)}$         \\
-		de la Torre et al. \cite{de2018weighted}     &  $0.537_{(\text{-})}$   &            -            &                -                 \\
-		Nebot et al. \cite{nebot2016diabetic}  &  $0.555_{(\text{-})}$   &            -            &                -                 \\
+		Method                                    & $\overline{QWK}_{SD}$ & $\overline{CCR}_{SD}$ & $\overline{\text{1-off}}_{SD}$ \\ \hline
+		CLM network (proposal)                          &    $0.582_{0.016}$    &    $0.723_{0.004}$    &        $0.868_{0.002}$         \\
+		Nominal network                           &    $0.498_{0.013}$    &    $0.692_{0.014}$    &        $0.854_{0.006}$         \\
+		de la Torre et al. \cite{de2018weighted}     &  $0.537_{\text{-}}$   &            -            &                -                 \\
+		Nebot et al. \cite{nebot2016diabetic}  &  $0.555_{\text{-}}$   &            -            &                -                 \\
 		\hline
@@
 		\hline
-		Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
-		CLM network (proposal)                          &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
-		Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
-		Beckham and Pal \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
-		Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
-		Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
-		Levi and Hassner \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ 
-		M. Duan et al. \cite{duan2018hybrid}         &            -            &    $0.523_{(0.057)}$    &        -         \\ \hline\hline
-	\end{tabular}
+		Method                                    & $\overline{QWK}_{SD}$ & $\overline{CCR}_{SD}$ & $\overline{\text{1-off}}_{SD}$ \\ \hline
+		CLM network (proposal)                          &    $0.881_{0.005}$    &    $0.519_{0.013}$    &        $0.894_{0.005}$         \\
+		Nominal network                           &    $0.787_{0.004}$    &    $0.458_{0.008}$    &        $0.800_{0.007}$         \\
+		Beckham and Pal \cite{beckham2017unimodal} &    $0.855_{0.012}$    &    $0.467_{0.019}$    &        $0.867_{0.011}$         \\
+		Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{0.026}$    &        $0.807_{0.011}$         \\
+		Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{0.060}$    &        $0.885_{0.022}$         \\
+		Levi and Hassner \cite{levi2015age}         &            -            &    $0.507_{0.051}$    &        $0.847_{0.022}$         \\ 
+		M. Duan et al. \cite{duan2018hybrid}         &            -            &    $0.523_{0.057}$    &        -         \\ \hline\hline
+	\end{tabular}}
 \end{table}
@@
 The results highlight the importance of making an experimental design where all of these parameters are adjusted for each problem.
-In summary, the most significant contributions of the model proposal are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention from over-fitting and stagnation, which gives our method high stability compared to other alternatives.
+In summary, the most significant contributions of the model proposal are the performance increase, the reduction of the number of parameters configurations that should be tried to find the best one and the prevention from over-fitting and stagnation, which grants our method high stability compared to other alternatives.
 
@@
 \section*{Acknowledgment}
-This work has been partially subsidised by the TIN2017-85887-C2-1-P project of the Spanish Ministry of Economy and Competitiveness (MINECO), and FEDER funds of the European Union.
-Víctor Manuel Vargas's research has been subsidized by the FPU Predoctoral Program of the Spanish Ministry of Education, Culture and Sport (MECD), grant reference FPU18/00358.
+This work has been partially subsidised by the TIN2017-85887-C2-1-P and TIN2017-90567-REDT projects of the Spanish Ministry of Economy and Competitiveness (MINECO), and FEDER funds of the European Union.
+Víctor Manuel Vargas's research has been subsidized by the FPU Predoctoral Program of the Spanish Ministry of Science, Innovation and Universities (MCIU), grant reference FPU18/00358.
 

### 2019-10-11 layers.py
Neuro submit

@@ -12,3 +12,8 @@ class GeometricLayer(keras.layers.Layer):
 
 	def call(self, inputs):
 		return K.pow(1. - inputs, int(self.num_classes)) * inputs
+
+
+class DenseMultiplicative(keras.layers.Dense):
+	def call(self, inputs):
+		pass
